### 2023-11-21 texts/paper_closing.tex
add paper_closing.tex to git repo

% Created 2023-11-19 zo 22:29
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}

\usepackage[hyphens]{url}                
\usepackage{hyperref}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{pdflscape}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{datetime}
\usepackage{amsfonts}
\usepackage[section]{placeins}
\usepackage{dirtree}
\usepackage{siunitx}
\usepackage{afterpage}
\usepackage{pdflscape}
\usepackage{svg}
\usepackage[export]{adjustbox}

\usepackage{booktabs}
\usepackage{dcolumn}
\makeatletter
\newcolumntype{D}[3]{>{\textfont0=\the\font\DC@{#1}{#2}{#3}}c<{\DC@end}}
\makeatother

\newcolumntype{L}{>{$}l<{$}}

\usepackage{bibentry}

\sisetup{detect-all}

\sloppy
\usepackage{scalerel,stackengine}

\stackMath
\newcommand\reallywidehat[1]{%
\savestack{\tmpbox}{\stretchto{%
  \scaleto{%
    \scalerel*[\widthof{\ensuremath{#1}}]{\kern-.6pt\bigwedge\kern-.6pt}%
    {\rule[-\textheight/2]{1ex}{\textheight}}%WIDTH-LIMITED BIG WEDGE
  }{\textheight}% 
}{0.5ex}}%
\stackon[1pt]{#1}{\tmpbox}%
}

\usepackage{caption}
\usepackage[draft]{todonotes}

\captionsetup{skip=0pt}
\usepackage[utf8]{inputenc}
\usepackage[style=apa, backend=biber]{biblatex} 
\usepackage[english, american]{babel}
\DeclareLanguageMapping{american}{american-apa}
\DeclareFieldFormat{apacase}{#1}

\usepackage[T1]{fontenc}
\usepackage{csquotes}

\addbibresource{/home/johannes/Dropbox/references.bib}
\addbibresource{/home/johannes/Dropbox/references2.bib}

\usepackage{floatrow}

\usepackage{listings}
\usepackage{xcolor}
\usepackage{colortbl}

\lstset{
  language=R,                    
  basicstyle=\footnotesize,      
  numbers=left,                  
  numberstyle=\tiny\color{gray}, 
  stepnumber=1,                  
  numbersep=5pt,                 
  backgroundcolor=\color{white}, 
  showspaces=false,              
  showstringspaces=false,        
  showtabs=false,                
  frame=single,                  
  rulecolor=\color{black},       
  tabsize=2,                     
  captionpos=b,                  
  breaklines=true,               
  breakatwhitespace=false,       
  title=\lstname,                
  keywordstyle=\color{red},     
  commentstyle=\color{blue},  
  stringstyle=\color{violet},     
  escapeinside={\%*}{*)},        
  morekeywords={*,...}           
}

\usepackage{crimson}
\usepackage{microtype}

\usepackage{fancyhdr}
\usepackage{setspace}
\singlespace
\usepackage{longtable}
\usepackage{subfig}
\usepackage[a4paper, total={18cm, 24cm}]{geometry}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\maketitle}{}

\usepackage{enumitem}
\setlist[itemize]{topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt}

\usepackage{multicol}
\setlength\multicolsep{0pt}

\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[normalem]{ulem}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{hyperref}

\newlist{propertyList}{itemize}{1}
\setlist[propertyList]{
  label=\textbullet,
  noitemsep,
  leftmargin=10pt,
  before=\begin{multicols}{3},
  after=\end{multicols}
  }

\cfoot {Johannes Aengenheyster}
\rfoot {\thepage}

\listfiles

\setlength{\parindent}{1.2cm}
\author{Johannes }
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes },
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.1 (Org mode 9.6.7)}, 
 pdflang={English}}
\begin{document}

\section*{Private museum closures}

\subsection*{Abstract: TODO}

\subsection*{Introduction}

In recent years, private, collector-run museums have seen an unprecedented proliferation.
These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums run/financed by the state or foundations and associations.
Despite their occasionally spectacular/sensationalist press coverage (TODO:ref), these institutions and the motivations of their founders have remained remarkably intransparent.
Financed in large parts by their founders' private wealth, few reporting requirements exists; and while some founders highlight their charitable and distintersted intentions in media coverage, such statements intended for a public audience might not necessarily accurately reflect underlying founder motivations.

This study (attempts to) elucidate the hard-to-observe collector motivations by studying the one of the most decisive actions that their founder can take: the decision to close the museum.
Besides investigating the longevity of members of this new organizational form, this study gives insights into the motivations and decision making of founders.
In other words, what can the factors leading to the closure of private museums tell us about the internal processes and dependence relationships of these institutions, as well as about the motivations of their founders?

\bigbreak
\noindent
Private museums:
\begin{itemize}
\item founded by collector -> needs to have amassed substantial art collection
\item building of its own, limited public/corporate funding, has to be visitable -> requires substantial resources
\end{itemize}

\subsection*{Theory}

TODO: the theory section (including the hypotheses) is mostly copied from an earlier literature review on organizational closure, and while there are some references to how it could relate to private museums, it isn't integrated with the current focus on collector decision making and private museum sustainability.

\subsubsection*{Size}

Larger NPOs are generally found to have lower mortality rates \parencite{Hager_1999_demise,Duckles_Hager_Galaskiewicz_2005_close}, with size being measured through indicators such as assets \parencite{Lu_Shon_Zhang_2019_dissolution}, number of employees \parencite{Bielefeld_1994_survival} and volunteers \parencite{Fernandez_2007_dissolution}, or revenues \parencite{Searing_2020_zombies}.
Smaller organiations are argued to face greater difficulty in collecting resources and recruiting staff as well as relatively higher costs for administration and regulation \parencite{Helmig_Ingerfurth_Pinz_2013_nonprofit}, while being less able to diversify or benefit from economies of scale \parencite{Hager_1999_demise}. 
Larger organizations are also argued to be able to waste some resources during normal times which can be utilized effectively during situations of crisis without having to scale back services (which generate revenue) \parencite{Hager_2001_vulnerability} and hence avoid downsizing, which can lead to dissolution \parencite{Duckles_Hager_Galaskiewicz_2005_close,Bielefeld_1994_survival}.

\bigbreak
\noindent
\textbf{H\textsubscript{size}}: Larger private museums are less likely to close than smaller ones.

\subsubsection*{Resource diversification}

A substantial amount of literature focuses on resources as resource depletion is a leading cause of (nonprofit) organizational demise. 
Diversification and (i.e. a multitude of funding sources) is found to reduce mortality \parencite{Fernandez_2007_dissolution,Bielefeld_1994_survival,Hager_2001_vulnerability,Lu_Shon_Zhang_2019_dissolution}; similarly volatility (rapid changes in revenues) is found to increase mortality \parencite{Mayer_2022_slimmer}. 
While private museums are likely already generally leaning toward higher concentration than NPOs generally due to high reliance on the financial contributions of the founder-collector, there might still be variation in the degree of revenue concentration as museums might vary in the proportion of revenues received from ticket prices, restaurants, cafes, museum shops or other activities.

\bigbreak
\noindent
\textbf{H\textsubscript{diversification}}: Private museums with more diversified revenue channels are less likely to close than more diversified ones.

\subsubsection*{Age}

The age of an organization is considered in different ways to be related to closing.
What started with liability of newness \parencite{Stinchcombe_1965_structure}, which posited that organizational mortality decreases over time due to acquisition of capabilities and connections, has lead to a number of extensions \parencite{Carroll_Khessina_2019_demography,Hannan_1998_mortality}:
Liability of adolescence argues that shortly after foundings organizations can still draw on endowments, the expiration of which leads to a peak of mortality some time after opening.
While according this view mortality still decreases after the peak as the organization becomes more established, other perspectives argue also for a positive relationship between age and mortality:
According to "liability of obsolescence" the environment changes faster than organizations which are seen as relatively constrained by inertia, which therefore leads to declining fitness and survival chances.
Similar, according to "liability of senescence" capabilities/routines/coalitions can constrain the actions of organizations.
Given such conflicting predictions, \textcite{Carroll_Khessina_2019_demography} propose to model age dependence with piece-wise constant hazard models (rather than parametric models) to estimate age-specific effects which can, but do not have to, indicate a relationship between age and mortality.

\subsubsection*{Organizational transformation}

\textcite{Carroll_Khessina_2019_demography} argue that transformation of core features of organizations such as changes in technology or authority can have divergent consequences. 
On the one hand, it can disrupt internal routines as well as external customer relations by decreasing (perceived) reliability and accountability as the change upsets established perceptions, which can lead to higher mortality. 
On the other hand, organizational transformation can be necessary to adapt to a changing environment, and hence be beneficial for survival.

The death of the founder can potentially constitute a substantial transformation as authority has to be reconfigured.
Abandonment by insiders (such as divorce of directors) has been argued to contribute to NPO closure \parencite{Duckles_Hager_Galaskiewicz_2005_close}.\footnote{Conflict is similarly argued to contribute to closure but is not testable with the current data.}
Even if plans have been made for a handover, the new leaders might not share quite the same commitment to art as the original founder, potentially decreasing museum sustainability. 
In the case of private museums, founder death has been speculated to pose a challenge to their sustainability as "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museum indefinitely" \parencite[p.234]{Walker_2019_collector}.
However, existing research has not found a straightforward effect of founder death on museum closure \parencite{Velthuis_Gera_forthcoming_fragility,Velthuis_etal_2023_boom}.
Nevertheless as previous research has relied primarily on descriptive statistics, investigating founder death in a multivariate survival model allows to investigate the effect of founder death with more precision.
\bigbreak
\noindent
\textbf{H\textsubscript{death}}: A private museum is more likely to close after the death of the founder.

\subsubsection*{legitimacy/understandability}

Legitimacy is necessary for being understood/tolerated/supported by other the organizations in the environemnt; to the extent that this influences resource acquisition it could influence survival prospects.
While \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close, other studies find limited impact of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
In the context of private museums, decline of legitimacy/status could lead to lower visitor numbers, less discounts from art dealers, less government grants (?) or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.

Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
Understandability/sense-making \parencite{Glynn_Abzug_2002_names} might thus be limited if an organization is atypical \parencite{Rosch_1975_family}, i.e. displays an unusual combination of features.
In the case of private museums, such cases might be combinations of features from house museums (e.g. accessibility only by appointment) with full-service museums (e.g. extensive activities). 
Next to "hard" organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate. 
However, the category of museums could be relatively flexible (for example, it is generally not subject to state regulation), which might result in a relatively high tolerance of diversity as "anything goes" and hence limited "devaluation" of non-conforming/atypical members.

\bigbreak
\noindent
\textbf{H\textsubscript{typicality}}: Atypical private museums have higher mortality rates.

Legitimacy might also be measured by inclusion in industry registers, such as the Museum of the World (MOW) database \parencite{deGruyter_2021_MOW}.

\bigbreak
\noindent
\textbf{H\textsubscript{mow}}: Private museums included in the MOW database have higher survival chances.

\subsubsection*{reputation}

Reputation has been argued to enhance organizational survival \parencite{Rao_1994_reputation}.
However, reputation effects could also be a spurious effect of organizational capabilities as more competent organizations are more able to both aquire reputation through certification contests and survive in long run \parencite{Goldfarb_Zavyalova_Pillai_2018_Rao}.
Recognition might be measured by inclusion in the Artnews top 200 collector ranking.

\bigbreak
\noindent
\textbf{H\textsubscript{artnews}}: Private museums of collectors included in the Artnews top 200 collector ranking are less likely to close.

\subsection*{Data and Methods}

\subsubsection*{Dependent Variable}

A newly constructed database (see \textcite{Velthuis_etal_2023_boom} for details) is used to measure museum survival.
The unit of analysis is the country year.
The main dependenent variable is an indicator of museum closure, which takes for the museums which close in the year of their closure, and zero otherwise.
Typically for survival data, museums that do not close during the observation period are right-censored, i.e. for such museums the dependent variable is zero for all years.

\subsubsection*{Predictors}

TODO: the current do not yet measure all the concepts discussed in the theory, and some are not justified yet on theoretical grouns (founder name in museum name, gender, density).

\bigbreak
\noindent
On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
Founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder.

On the museum level, selfidentification measures whether a museum's name includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent).
Further analyzing the name, a binary indicator also measures whether the name of the founder is included.
Finally, a binary predictor measures whether the museum is included in the "Museums of the World" database \parencite{deGruyter_2021_MOW}, a database containig 55k museums.

On the level of the environment, the density (number) of private museum per country is included both in linear and squared form.
Organizational theory \parencite{hannan89_organ} predicts a U-shaped relationship between density and mortality: While at low levels, increases in the number of organizations are argued to primarily increase legitimacy/familiarity and lower exit rates, increases at higher numbers increase the competition over resources and thereby raise mortality rates.

\bigbreak
\noindent
TODO: 
\begin{itemize}
\item add museum size/diversification indicators: most museum-level variables that we collected have many missing values (figure \ref{fig:p_vrblcvrg_ratio}), so it's challenging to get good estimates out of them. I'm thinking of using some dimensionality reduction like PCA.
\item add inclusion in Artnews collector ranking
\item add Tax incentives (country-level)
\item expand densities: 
\begin{itemize}
\item per capita
\item include MOW museums, for now density is based only on private museums
\item within proximate environment (circle of X kilometer around museum), rather than country-level
\end{itemize}
\item account for clustering within countries/regions
\end{itemize}

\subsubsection*{Analytical framework}

First, we investigate the relationship between age and closing descriptively using hazard rates and the Kaplan-Meier survival function.
This non-parametric method estimates the hazard rate as the conditional probability of exiting at time t\textsubscript{i} given being alive as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at time \(t_i\) and \(d_i\) as the number of exits at time \(t_i\)), and the survival function as the product of these conditional probabilities as \(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\).

In a second step, I use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), with \(\psi = \exp(\sum_{j=1}^p x_j \beta_j)\), with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient of the \(j\) -th variable.
Estimation via partial maximum likelihood allows estimation of \(\beta\) without estimating the baseline hazard rate, which is therefore not constrained to a parametric form. 
Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.

This model assume proportional hazards, i.e. that the coefficient of a variable stays constant over time, which indicates that for a variable at every time point the hazard ratio is the same.
So far, tests show a violation of the proportionality assumption only for the variable indicating whether the museum name includes the name of the founder  which furthermore is marginal as it slightly varies by the type of time transformation (table \ref{tbl:t_coxzph}, figure \ref{fig:p_coxphdiag_more}).

\subsection*{Results}

\subsubsection*{Summary statistics}

In total, 479 private museums are included in the database, 53 of them have closed
7282 museum-years are observed.

\noindent
TODO: summary statistics for all the variables

\subsubsection*{Hazard rate and Age Dependence}

\begin{figure}[htbp]
\centering
\includegraphics[width=16cm]{../figures/p_hazard.pdf}
\caption{\label{fig:p_hazard}Private Museum hazard function}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=14cm]{../figures/p_surv.pdf}
\caption{\label{fig:p_surv}Private Museum Survival probability}
\end{figure}

Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
The hazard rate doubles over the first 10 years from approximately 0.45\% to 0.9\%, at which value it approximately stays constant for the next 20 years, after which it appears to decline.
However, the decline after thirty years is presumably less certain as very few private museums have already reached this age (figure \ref{fig:p_agedens}).

The increase in the first years is likely due to endowments: As the establishment of a museum requires considerable resources, their founders appear to allocate enough resources to keep the risk of closure small in the first years after opening.
Given that founders are likely aware that their endeavor is unlikely to generate a profit, they are not vulnerable to the liability of newness \parencite{Stinchcombe_1965_structure}.
The relative stability of the hazard rate after ten years has no correspondence in classical theories on age dependence:
While an increase in mortality as observed here is predicted by the idea of "liability of adolescence" \parencite{Carroll_Khessina_2019_demography}, this framework also predicts a decline in mortality after a peak due to becoming established.
Furthermore, while "liability of obsolescence" and "liability of senescence" (ibid.) predict higher mortality for older organizations due to mismatch with the environment and inertia (inflexible internal routines), it seems questionable whether museums would have reached obsolescence or senescence already after ten years.
Furthermore, the applicability of obsolescence and senescence might be limited for non-profit organizations.

Overall the entire life span, the average hazard rate is 0.79\%, which allows comparison to other studies of NPO closure.
While after very cursory search of the literature I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations (see table \ref{tbl:litreview}).

\begin{table}[htbp]
\caption{\label{tbl:litreview}Hazard rates in studies of museums and other non-profits}
\centering
\begin{tabular}{llll}
\hline
study & population & avg. hazard rate & data source\\
\hline
\cite{Hager_2001_vulnerability} & Art Museums & 2.4\% & IRS\\
\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\% & IRS\\
\hline
\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\% & IRS\\
\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\% & IRS\\
\cite{Gordon_etal_2013_insolvency} & all NPOs & 1.58\% & IRS\\
\cite{Hager_Galaskiewicz_Larson_2007_liability} & NPOs & 1.25\% & own data\\
\cite{Clifford_2018_reinforcing} & Charities & 2\%-5\% & Reg. of Charities (UK)\\
\cite{Mayer_2022_slimmer} & NPOs & 0.17\% & IRS\\
\hline
\end{tabular}
\end{table}

\textcite{Hager_2001_vulnerability} and \textcite{Gordon_etal_2013_insolvency} both study NPOs more generally, but report survival estimates by organizational form.
At the moment it is not clear which factors account for their hazard rates to differ substantially, but it might be due to selection criteria.
Both these studies also report substantial variation in hazard rates between organizational forms.
While preliminary results indicate that private museums have dissolution rates lower or similar to museums and non-profit organizations generally, more research is needed to establish the comparability of these hazard rates.

\noindent
TODO:
\begin{itemize}
\item get confidence interval for hazard rate
\item see how age can be integrated into survival models (linear term doesn't work)
\item expand comparison to other studies
\end{itemize}

\subsubsection*{Regression Results}

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Sun Nov 19 21:58:11 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .31 \; (0.36) \\ 
   & Gender - Couple & -.07 \; (0.36) \\ 
   & Founder died & .11 \; (0.51) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .76 \; (0.46) \\ 
   & Self-Identification - Collection & .52 \; (0.54) \\ 
   & Self-Identification - Other & 1.12 \; (0.36)^{**} \\ 
   & Founder name in Museum name & -.27 \; (0.31) \\ 
   & MOW inclusion & -.97 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density & -.03 \; (0.03) \\ 
   & PM density$^{2}$ & .00 \; (0.00) \\ 
   \hline
 & Museum-years & 7282 \\ 
   & Closures & 53 \\ 
   & log. Likelihood & -271.10 \\ 
   & AIC & 562.20 \\ 
   & BIC & 581.91 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

Table \ref{tbl:t_reg_coxph} shows the results of Cox proportional hazard regression model.
Founder-level variables are not substantial, as neither gender nor the death of the founder is associated with a significant difference in private museum closure.
While there is no particular reason to expect a gender effect, the not substantially higher likelihood for museums to close after their founder has died indicates that private museums might be less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.

Museums which include the term "museum" in their name are the least likely to close, while those with the term "foundation" or "collection" have higher closure rates (but not significantly higher).
Museums which include neither of these are the most likely to close, and have mortality rates more than three times as high (\(e\)\textsuperscript{1.12} = 3.06 , p<0.01) than institutions including the term "museum".
The usage of unconventional names might reflect adherence to museum standards which makes museums more understandable and familiar to third parties (e.g. audiences, other museums, companies or the government) and thereby facilitates interactions which are beneficial for long-term survival (e.g. attracting visitors, cooperations, sponsorships or subsidies).
However, as founders can choose their museum’s name arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.

Inclusion of founder name is not significantly associated with mortality rates.
While generally organizations whose name include the name of their founder might be more centered around the founder, and hence display higher inertia, making them less able to adapt to changing environments (TODO: add reference, very speculative!!), these results indicate that it does not seem to be case for private museums.

Museums included in the Museum of the World Database are \(e\)\textsuperscript{-0.97} = 0.38 times as likely to close than museums which are not, yet this result might be produced by different mechanisms.
On the one hand, it might reflect that larger and richer institutions are both more likely to be noticed by the MOW and more likely to survive (MOW inclusion would then be a proxy for resources).
On the other hand, similar to unconventional naming patterns, lack of inclusion in the MOW could be an indicator of deviance from museum standards, which could increase the unfamiliarity of the museum vis-a-vis third parties, reducing the chance of survival-enhancing interactions.
Thirdly, the MOW effect might be endogenous: As no longitudinal MOW data is available, museums might be absent in the MOW because they have closed (TODO: Because of this I wonder if it even makes even sense to include MOW).

Environmental variables show no association with mortality (TODO: this might be due to no per capita numbers).
While the density-dependence paradigm predicts a negative effect of numbers of organizations on closing rate at low numbers (due to legitimacy, i.e. growing familiarity with a new organizational form), and a positive effect at high numbers (due to competition over resources), neither relationship is significant in the case of private museums.

\begin{sloppypar}
\printbibliography
\end{sloppypar}

\section*{Appendix}

\begin{figure}[htbp]
\centering
\includegraphics[width=19cm]{../figures/p_yeardens.pdf}
\caption{\label{fig:p_yeardens}Private Museum-year Distribution}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=17cm]{../figures/p_agedens.pdf}
\caption{\label{fig:p_agedens}Age distribution of private museums}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=19cm]{../figures/p_coxphdiag_more.pdf}
\caption{\label{fig:p_coxphdiag_more}Model Diagnostics}
\end{figure}

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Sun Nov 19 21:58:05 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{.}{.}{5}D{.}{.}{5}D{.}{.}{5}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Kaplan-Meier} & \multicolumn{1}{l}{Identity} & \multicolumn{1}{l}{Rank}\\ 
 \hline
  \multicolumn{2}{l}{\textbf{Founder}} \\ 
 & Founder Gender & .63 & .53 & .62 \\ 
   & Founder died & .68 & .64 & .87 \\ 
   \multicolumn{2}{l}{\textbf{Museum}} \\ 
 & Founder name in Museum name & .06 & .05 & .05^{*} \\ 
   & MOW inclusion & .39 & .43 & .59 \\ 
   & Self- Identification & .96 & .94 & .74 \\ 
   \multicolumn{2}{l}{\textbf{Environment}} \\ 
 & PM density & .78 & .80 & .81 \\ 
   & PM density$^{2}$ & .93 & .89 & .87 \\ 
   \multicolumn{2}{l}{\textbf{Miscellaneous}} \\ 
 & Global & .41 & .32 & .41 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Z-test of proportional hazards} 
\label{tbl:t_coxzph}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_vrblcvrg_ratio.pdf}
\caption{\label{fig:p_vrblcvrg_ratio}PMDB variable coverage (abs/rel prop) by museum status and variable group}
\end{figure}
\end{document}

### 2023-11-21 scripts/closing_main.R
more gc_vvs documentation

@@ -61,6 +61,8 @@ gc_vvs <- function() {
     #' dt_termlbls: EXPERIMENTAL combination of dt_vrblinfo and dt_ctgterm_lbls:
     #' should save merging the two dts in each function that needs both vrblinfo and lbls;
     #' for categorical variables contains both the information on vrbls and term (e.g. term=gender and term=genderF)
+    #' so far it works that by right-joining on dt_termlbls (dt_termlbls[dt_coef]) substantive coef tables can pick 
+    #' the things they need, and ignore those that they don't include
     #' vrbl, term, term_lbl, vrblgrp, vrblgrp_lbl
 
     #' ADDME: atm it's not super flexible with multiple variable groupings (e.g. different themes),

### 2023-11-21 texts/paper_closing.tex
update t_coxzph in tex

@@
-% Created 2023-11-19 zo 22:29
+% Created 2023-11-21 di 10:37
 % Intended LaTeX compiler: pdflatex
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Sun Nov 19 21:58:11 2023
+% Tue Nov 21 10:36:10 2023
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Sun Nov 19 21:58:05 2023
+% Tue Nov 21 10:36:04 2023
 \begin{table}[ht]
@@
   \multicolumn{2}{l}{\textbf{Founder}} \\ 
- & Founder Gender & .63 & .53 & .62 \\ 
  & Founder died & .68 & .64 & .87 \\ 
+   & Gender - Couple & .35 & .26 & .35 \\ 
+   & Gender - Female & .67 & .73 & .60 \\ 
    \multicolumn{2}{l}{\textbf{Museum}} \\ 
@@
    & MOW inclusion & .39 & .43 & .59 \\ 
-   & Self- Identification & .96 & .94 & .74 \\ 
+   & Self-Identification - Collection & .72 & .64 & .44 \\ 
+   & Self-Identification - Foundation & .78 & .90 & .73 \\ 
+   & Self-Identification - Other & .76 & .79 & .63 \\ 
    \multicolumn{2}{l}{\textbf{Environment}} \\ 

### 2023-11-22 texts/paper_closing.tex
add summary statistics table, also update tasks

@@
-% Created 2023-11-21 di 10:37
+% Created 2023-11-22 wo 17:48
 % Intended LaTeX compiler: pdflatex
@@
 
+% latex table generated in R 4.3.2 by xtable 1.8-4 package
+% Wed Nov 22 17:48:02 2023
+\begin{table}[ht]
+\centering
+\begin{tabular}{llrrrrrr}
+  \hline
+ & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
+\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\
+ \hline
+  \multicolumn{8}{l}{\textbf{Founder}} \\ 
+ & Gender - Male & 275 & 0.574 &  0.589 &  0.49 & 0 &  1 \\ 
+   & Gender - Female & 76 & 0.159 &  0.162 &  0.37 & 0 &  1 \\ 
+   & Gender - Couple & 128 & 0.267 &  0.249 &  0.43 & 0 &  1 \\ 
+   & Founder died & 58 & 0.121 &  0.097 &  0.30 & 0 &  1 \\ 
+   \multicolumn{8}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Museum & 179 & 0.374 &  0.417 &  0.49 & 0 &  1 \\ 
+   & Self-Identification - Foundation & 101 & 0.211 &  0.188 &  0.39 & 0 &  1 \\ 
+   & Self-Identification - Collection & 74 & 0.154 &  0.135 &  0.34 & 0 &  1 \\ 
+   & Self-Identification - Other & 125 & 0.261 &  0.259 &  0.44 & 0 &  1 \\ 
+   & Founder name in Museum name & 229 & 0.478 &  0.491 &  0.50 & 0 &  1 \\ 
+   & MOW inclusion & 91 & 0.190 &  0.317 &  0.47 & 0 &  1 \\ 
+   \multicolumn{8}{l}{\textbf{Environment}} \\ 
+ & PM density &  &  & 19.615 & 18.32 & 1 & 62 \\ 
+   & Europe and North America & 313 & 0.653 &  0.651 &  0.48 & 0 &  1 \\ 
+   & Region - Africa & 7 & 0.015 &  0.013 &  0.11 & 0 &  1 \\ 
+   & Region - Asia & 127 & 0.265 &  0.278 &  0.45 & 0 &  1 \\ 
+   & Region - Europe & 242 & 0.505 &  0.500 &  0.50 & 0 &  1 \\ 
+   & Region - Latin America & 22 & 0.046 &  0.040 &  0.20 & 0 &  1 \\ 
+   & Region - North America & 71 & 0.148 &  0.150 &  0.36 & 0 &  1 \\ 
+   & Region - Oceania & 10 & 0.021 &  0.018 &  0.13 & 0 &  1 \\ 
+   \hline
+\end{tabular}
+\caption{Summary Statistics} 
+\label{tbl:t_sumstats}
+\end{table}
+
 \subsubsection*{Hazard rate and Age Dependence}
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Tue Nov 21 10:36:10 2023
+% Wed Nov 22 17:42:15 2023
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Tue Nov 21 10:36:04 2023
+% Wed Nov 22 17:42:09 2023
 \begin{table}[ht]

### 2023-11-22 scripts/closing_main.R

@@ -499,7 +499,11 @@ gc_tbls <- function(c_tblargs) {
         t_reg_coxph = list(
             l_mdls = quote(l_mdls),
             l_mdlnames = quote(l_mdlnames_coxph), # FIXME: gw_fargs should be able to handle vectors
-            caption = "Cox Proportional Hazards Regression Results")
+            caption = "Cox Proportional Hazards Regression Results"),
+        t_sumstats = list(
+            dt_pmyear = quote(dt_pmyear),
+            dt_pmcpct = quote(dt_pmcpct),
+            caption = "Summary Statistics")
     )
 
     
@@ -601,6 +605,100 @@ gt_reg_coxph <- function(l_mdls, l_mdlnames) {
     
 }
 
+
+gt_sumstats <- function(dt_pmyear, dt_pmcpct) {
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
+    1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
+    gw_fargs(match.call())
+
+    c_vvs <- gc_vvs()
+
+    ## expand categorical variables to dummies
+    ## requires calling model.matrix for each variable
+
+    dt_dummies <- map(chuck(c_vvs, "dt_vrblinfo")[vrbltype == "cat", vrbl],
+        ~model.matrix(as.formula(sprintf("~ %s -1", .x)), dt_pmyear)) %>%
+        Reduce(cbind, .) %>% adt %>%
+        melt(measure.vars = names(.), variable.name = "term")
+
+    ## get numeric and dummy variables, only get those that are in the table (no squares/interactions)
+    vrbls_num <- intersect(names(dt_pmyear), chuck(c_vvs, "dt_vrblinfo")[vrbltype %in% c("num", "bin"), vrbl])
+    dt_numvrbls <- dt_pmyear[, vrbls_num, with = F] %>% melt(measure.vars = names(.), variable.name = "term")
+
+    ## summary functions to apply
+    funcs_sumry <- .c(mean, sd, min, max)
+
+    ## apply summary functions, merge with term labels to get variables names and groupings
+    dt_cbn <- rbind(dt_dummies, dt_numvrbls) %>%
+        .[, map(funcs_sumry, ~get(.x)(value)), term] %>%
+        setnames(old = paste0("V", 1:len(funcs_sumry)), new = funcs_sumry) %>%
+        c_vvs$dt_termlbls[., on = "term"]
+        
[…]

### 2023-11-22 scripts/closing_main.R
factorize dt_vrblinfo$vrbl, move dt_vrblinfo_generation together
having vrbl as a factor allows setting order

@@ -96,15 +96,46 @@ gc_vvs <- function() {
         museum = "Museum",
         envir = "Environment",
         misc = "Miscellaneous")
+
     
-    
-    dt_vrbl_lbls = data.table(vrbl = names(l_vrbl_lbls), vrbl_lbl = unlist(l_vrbl_lbls))
+    dt_vrbl_lbls = data.table(vrbl = names(l_vrbl_lbls), vrbl_lbl = unlist(l_vrbl_lbls)) %>%
+        .[, vrbl := factor(vrbl, levels = vrbl)]
 
     dt_vrblgrp_lbls <- data.table(vrblgrp = names(l_vrblgrp_lbls), vrblgrp_lbl = unlist(l_vrblgrp_lbls)) %>%
         .[, vrblgrp := factor(vrblgrp, levels = names(l_vrblgrps))]
 
     dt_vrblgrps <- imap(l_vrblgrps, ~data.table(vrbl = .x, vrblgrp = .y)) %>% rbindlist %>%
         .[, vrblgrp := factor(vrblgrp, levels = names(l_vrblgrps))]
+
+    ## ## list of variable configs
+    ## l_cvrbl <- list(
+    ##     list(vrbl = "gender", vrbl_label = "Founder Gender", vrblgrp = "founder", vrblgrp_lbl = "Founder",
+    ##          tv = F, vrbltype = "cat"),
+    ## check that the variables that are grouped/labelled are the same
+    if (!setequal(dt_vrbl_lbls$vrbl, dt_vrblgrps$vrbl)) {
+        stop("something wrong with vrbl labels and groups")}
+
+    ## specify whether variable is time-varying or not
+    vrbls_tiv <- .c(gender, slfidfcn, muem_fndr_name, mow, west, reg6)
+    vrbls_tv <- .c(pm_dens, "I(pm_dens^2)",  founder_dead)
+
+    ## specify variable type: binary, numeric, categorical
+    l_vrbltypes <- list(        
+        bin = .c(founder_dead, muem_fndr_name, mow, west),
+        num = .c(pm_dens, "I(pm_dens^2)"),
+        cat = .c(gender, slfidfcn, reg6))
+
+    dt_vrbltypes <- imap(l_vrbltypes, ~data.table(vrbl = .x, vrbltype = .y)) %>% rbindlist
+
+    ## combine variable labels, variable groups, time-varying indicators, and variable types
+
[…]

### 2023-11-22 scripts/regression.R

@@ -153,7 +153,8 @@ gd_pmtiv <- function(dt_pmx) {
 
     
     ## construct tiv vrbl vector: first get all time-invariant variables
-    vrbls_tiv_temp_prep <- c("ID", "iso3c", "name", gc_vvs() %>% chuck("dt_vrblinfo") %>% .[vrbl_tv==0, vrbl])
+    vrbls_tiv_temp_prep <- c("ID", "iso3c", "name",
+                             gc_vvs() %>% chuck("dt_vrblinfo") %>% .[vrbl_tv==0, as.character(vrbl)])
     ## then yeet those that aren't there yet, .e.g MOW (gets added later)
     vrbls_tiv_temp <- intersect(vrbls_tiv_temp_prep, names(dt_pmx2))
     

### 2024-01-06 texts/paper_closing.tex
export paper after changing some numbers (e.g. Artnews addition)

--- 2023-11-21 texts/paper_closing.tex
@@
-% Created 2023-11-19 zo 22:29
+% Created 2024-01-06 za 14:02
 % Intended LaTeX compiler: pdflatex
@@
 
+% latex table generated in R 4.3.2 by xtable 1.8-4 package
+% Fri Dec  8 22:31:01 2023
+\begin{table}[ht]
+\centering
+\begin{tabular}{llrrrrrr}
+  \hline
+ & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
+\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\
+ \hline
+  \multicolumn{8}{l}{\textbf{Founder}} \\ 
+ & Gender - Male & 276 & 0.575 &  0.592 &  0.49 & 0 &  1 \\ 
+   & Gender - Female & 76 & 0.158 &  0.168 &  0.37 & 0 &  1 \\ 
+   & Gender - Couple & 128 & 0.267 &  0.240 &  0.43 & 0 &  1 \\ 
+   & Founder died & 58 & 0.121 &  0.093 &  0.29 & 0 &  1 \\ 
+   \multicolumn{8}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Museum & 179 & 0.373 &  0.408 &  0.49 & 0 &  1 \\ 
+   & Self-Identification - Foundation & 101 & 0.210 &  0.191 &  0.39 & 0 &  1 \\ 
+   & Self-Identification - Collection & 74 & 0.154 &  0.141 &  0.35 & 0 &  1 \\ 
+   & Self-Identification - Other & 126 & 0.263 &  0.261 &  0.44 & 0 &  1 \\ 
+   & Founder name in Museum name & 229 & 0.477 &  0.487 &  0.50 & 0 &  1 \\ 
+   & MOW inclusion & 91 & 0.190 &  0.296 &  0.46 & 0 &  1 \\ 
+   & AN Ranking - Not Included &  &  &  0.794 &  0.40 & 0 &  1 \\ 
+   & AN Ranking - Included &  &  &  0.149 &  0.36 & 0 &  1 \\ 
+   & AN Ranking - Dropped &  &  &  0.057 &  0.23 & 0 &  1 \\ 
+   \multicolumn{8}{l}{\textbf{Environment}} \\ 
+ & PM density &  &  & 20.541 & 18.37 & 1 & 62 \\ 
+   & Europe and North America & 313 & 0.652 &  0.645 &  0.48 & 0 &  1 \\ 
+   & Region - Africa & 7 & 0.015 &  0.012 &  0.11 & 0 &  1 \\ 
+   & Region - Asia & 128 & 0.267 &  0.281 &  0.45 & 0 &  1 \\ 
+   & Region - Europe & 242 & 0.504 &  0.502 &  0.50 & 0 &  1 \\ 
+   & Region - Latin America & 22 & 0.046 &  0.042 &  0.20 & 0 &  1 \\ 
+   & Region - North America & 71 & 0.148 &  0.144 &  0.35 & 0 &  1 \\ 
+   & Region - Oceania & 10 & 0.021 &  0.019 &  0.14 & 0 &  1 \\ 
+   \hline
+\end{tabular}
+\caption{Summary Statistics} 
+\label{tbl:t_sumstats}
+\end{table}
+
+Table \ref{tbl:t_sumstats} shows summary statistics for all variables.
+
 \subsubsection*{Hazard rate and Age Dependence}
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Sun Nov 19 21:58:11 2023
+% Fri Dec  8 22:38:34 2023
 \begin{table}[ht]
@@
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .31 \; (0.36) \\ 
-   & Gender - Couple & -.07 \; (0.36) \\ 
-   & Founder died & .11 \; (0.51) \\ 
+ & Gender - Female & .30 \; (0.36) \\ 
+   & Gender - Couple & -.03 \; (0.36) \\ 
+   & Founder died & .04 \; (0.54) \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .76 \; (0.46) \\ 
-   & Self-Identification - Collection & .52 \; (0.54) \\ 
-   & Self-Identification - Other & 1.12 \; (0.36)^{**} \\ 
-   & Founder name in Museum name & -.27 \; (0.31) \\ 
-   & MOW inclusion & -.97 \; (0.40)^{*} \\ 
+ & Self-Identification - Foundation & .79 \; (0.47) \\ 
+   & Self-Identification - Collection & .50 \; (0.55) \\ 
+   & Self-Identification - Other & 1.18 \; (0.37)^{**} \\ 
+   & AN Ranking - Included & .34 \; (0.41) \\ 
+   & AN Ranking - Dropped & 1.16 \; (0.45)^{*} \\ 
+   & Founder name in Museum name & -.35 \; (0.32) \\ 
+   & MOW inclusion & -.88 \; (0.39)^{*} \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density & -.03 \; (0.03) \\ 
+ & PM density & -.04 \; (0.03) \\ 
    & PM density$^{2}$ & .00 \; (0.00) \\ 
    \hline
- & Museum-years & 7282 \\ 
+ & Museum-years & 6903 \\ 
    & Closures & 53 \\ 
-   & log. Likelihood & -271.10 \\ 
-   & AIC & 562.20 \\ 
-   & BIC & 581.91 \\ 
+   & log. Likelihood & -266.76 \\ 
+   & AIC & 557.52 \\ 
+   & BIC & 581.16 \\ 
    \hline 
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Sun Nov 19 21:58:05 2023
+% Fri Dec  8 22:31:01 2023
 \begin{table}[ht]
@@
   \multicolumn{2}{l}{\textbf{Founder}} \\ 
- & Founder Gender & .63 & .53 & .62 \\ 
-   & Founder died & .68 & .64 & .87 \\ 
+ & Founder died & .59 & .55 & .72 \\ 
+   & Gender - Couple & .31 & .23 & .32 \\ 
+   & Gender - Female & .61 & .68 & .56 \\ 
    \multicolumn{2}{l}{\textbf{Museum}} \\ 
- & Founder name in Museum name & .06 & .05 & .05^{*} \\ 
-   & MOW inclusion & .39 & .43 & .59 \\ 
-   & Self- Identification & .96 & .94 & .74 \\ 
+ & AN Ranking - Dropped & .88 & .98 & .71 \\ 
+   & AN Ranking - Included & .59 & .46 & .41 \\ 
+   & Founder name in Museum name & .09 & .09 & .08 \\ 
+   & MOW inclusion & .28 & .28 & .51 \\ 
+   & Self-Identification - Collection & .60 & .53 & .36 \\ 
+   & Self-Identification - Foundation & .93 & .93 & .84 \\ 
+   & Self-Identification - Other & .90 & .83 & .85 \\ 
    \multicolumn{2}{l}{\textbf{Environment}} \\ 
- & PM density & .78 & .80 & .81 \\ 
-   & PM density$^{2}$ & .93 & .89 & .87 \\ 
+ & PM density & .95 & 1.00 & .90 \\ 
+   & PM density$^{2}$ & .77 & .70 & .78 \\ 
    \multicolumn{2}{l}{\textbf{Miscellaneous}} \\ 
- & Global & .41 & .32 & .41 \\ 
+ & Global & .52 & .39 & .51 \\ 
    \hline 

### 2024-01-06 scripts/closing_main.R
update tasks/code

@@ -33,16 +33,17 @@ library(Hmisc, include.only = "latexTranslate") # latexTranslate
 
 ## *** config functions
 
-gc_dirs <- function(dir_proj) {
-    list(
-        proj = dir_proj,
-        figs = paste0(dir_proj, "figures/"),
-        tbls = paste0(dir_proj, "tables/"),
-        data = paste0(dir_proj, "data/"),
-        code = paste0(dir_proj, "scripts/"),
-        misc = paste0(dir_proj, "misc/")
-    )
-}
+## moved to jtls
+## gc_dirs <- function(dir_proj) {
+##     list(
+##         proj = dir_proj,
+##         figs = paste0(dir_proj, "figures/"),
+##         tbls = paste0(dir_proj, "tables/"),
+##         data = paste0(dir_proj, "data/"),
+##         code = paste0(dir_proj, "scripts/"),
+##         misc = paste0(dir_proj, "misc/")
+##     )
+## }
 
 gc_vvs <- function() {
     if (as.character(match.call()[[1]]) %in% fstd){browser()}
@@ -862,6 +863,13 @@ check_if_file_is_open(paste0(c_dirs$tbls, "t_testtable.pdf"))
 
 
 screenreg(l_mdls$r_more)
+## ejj <- test_package("pmdata")
+
+## test_all("~/Dropbox/phd/pmdata")
+
+## build_install_test("~/Dropbox/phd/pmdata/", at_home = F)
+
+## build_install_test("~/home/johannes/R/x86_64-pc-linux-gnu-library/4.3/pmdata/")
 
 
 

### 2024-01-06 texts/paper_closing.tex
fix some typos

@@
-% Created 2024-01-06 za 14:02
+% Created 2024-01-06 za 15:19
 % Intended LaTeX compiler: pdflatex
@@
 
-This study (attempts to) elucidate the hard-to-observe collector motivations by studying the one of the most decisive actions that their founder can take: the decision to close the museum.
+This study (attempts to) elucidate the hard-to-observe collector motivations by studying one of the most decisive actions that their founder can take: the decision to close the museum.
 Besides investigating the longevity of members of this new organizational form, this study gives insights into the motivations and decision making of founders.
@@
 A substantial amount of literature focuses on resources as resource depletion is a leading cause of (nonprofit) organizational demise. 
-Diversification and (i.e.
+Diversification (i.e.
 a multitude of funding sources) is found to reduce mortality \parencite{Fernandez_2007_dissolution,Bielefeld_1994_survival,Hager_2001_vulnerability,Lu_Shon_Zhang_2019_dissolution}; similarly volatility (rapid changes in revenues) is found to increase mortality \parencite{Mayer_2022_slimmer}.
@@
 Liability of adolescence argues that shortly after foundings organizations can still draw on endowments, the expiration of which leads to a peak of mortality some time after opening.
-While according this view mortality still decreases after the peak as the organization becomes more established, other perspectives argue also for a positive relationship between age and mortality:
-According to "liability of obsolescence" the environment changes faster than organizations which are seen as relatively constrained by inertia, which therefore leads to declining fitness and survival chances.
+While according to this view mortality still decreases after the peak as the organization becomes more established, other perspectives argue also for a positive relationship between age and mortality:
+According to the liability of obsolescence paradigm the environment changes faster than organizations which are seen as relatively constrained by inertia, which therefore leads to declining fitness and survival chances.
 Similar, according to "liability of senescence" capabilities/routines/coalitions can constrain the actions of organizations.
@@
 
-The death of the founder can potentially constitute a substantial transformation as authority has to be reconfigured.
+In the case of private museums, the death of the founder might constitute a substantial transformation as authority has to be reconfigured.
 Abandonment by insiders (such as divorce of directors) has been argued to contribute to NPO closure \parencite{Duckles_Hager_Galaskiewicz_2005_close}.\footnote{Conflict is similarly argued to contribute to closure but is not testable with the current data.}
-Even if plans have been made for a handover, the new leaders might not share quite the same commitment to art as the original founder, potentially decreasing museum sustainability. 
+Even if plans have been made for a handover, the new leaders might not share the same commitment to art as the original founder, potentially decreasing museum sustainability. 
 In the case of private museums, founder death has been speculated to pose a challenge to their sustainability as "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museum indefinitely" \parencite[p.234]{Walker_2019_collector}.
 However, existing research has not found a straightforward effect of founder death on museum closure \parencite{Velthuis_Gera_forthcoming_fragility,Velthuis_etal_2023_boom}.
-Nevertheless as previous research has relied primarily on descriptive statistics, investigating founder death in a multivariate survival model allows to investigate the effect of founder death with more precision.
+Nevertheless as previous research has relied primarily on descriptive statistics, investigating founder death in a multivariate survival model allows to investigate the effect of founder death with higher precision.
 \bigbreak
@@
 A newly constructed database (see \textcite{Velthuis_etal_2023_boom} for details) is used to measure museum survival.
-The unit of analysis is the country year.
+The unit of analysis is country year.
 The main dependenent variable is an indicator of museum closure, which takes for the museums which close in the year of their closure, and zero otherwise.
@@
 
-On the museum level, selfidentification measures whether a museum's name includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent).
+On the museum level, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent).
 Further analyzing the name, a binary indicator also measures whether the name of the founder is included.
 Finally, a binary predictor measures whether the museum is included in the "Museums of the World" database \parencite{deGruyter_2021_MOW}, a database containig 55k museums.
-
 On the level of the environment, the density (number) of private museum per country is included both in linear and squared form.
@@
 
-In total, 479 private museums are included in the database, 53 of them have closed
+In total, 479 private museums are included in the database, 53 of them have closed.
 7282 museum-years are observed.
@@
 \noindent
-TODO: summary statistics for all the variables
 

### 2024-01-06 texts/paper_closing.tex
re-organizing for EGOS

@@
-% Created 2024-01-06 za 15:19
+% Created 2024-01-06 za 18:00
 % Intended LaTeX compiler: pdflatex
@@
 
-\section*{Private museum closures}
-
-\subsection*{Abstract: TODO}
+\section*{The closure of private museums: Legitimacy, identity and reputation}
 
@@
 
-In recent years, private, collector-run museums have seen an unprecedented proliferation.
-These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums run/financed by the state or foundations and associations.
-Despite their occasionally spectacular/sensationalist press coverage (TODO:ref), these institutions and the motivations of their founders have remained remarkably intransparent.
+In recent years, private collector-run museums have seen an unprecedented proliferation.
+These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums operated and financed by the state or foundations and associations.
+While the emergence of this organizational form has attracted attention (cf.
+\cite{Kolbe_etal_2022_privatemuseum} for a literature review), the process of closure has received considerably less attention.
+In this paper, I investigate
+
+argue that studying closures does not only provide insights into private museums, but into more general processes of organizational identity, legitimation and reputation.
+
+In particular concerning identity, I find that museums which are recognized by an international museum database are less likely to close than those which are not.
+With regards to legitimation, results indicate that that museums with more ambiguous names are more likely to close.
+Finally, a reputation effect is indicated by the fact that museums whose founders are dropped from a collector ranking are more likely to close than museums whose founders are included.
+
+\subsection*{Contributions}
+
+\begin{itemize}
+\item Intransparent founder motivations
+\end{itemize}
+
+Despite their occasionally spectacular/sensationalist press coverage, these institutions and the motivations of their founders have remained remarkably intransparent.
 Financed in large parts by their founders' private wealth, few reporting requirements exists; and while some founders highlight their charitable and distintersted intentions in media coverage, such statements intended for a public audience might not necessarily accurately reflect underlying founder motivations.
@@
 In other words, what can the factors leading to the closure of private museums tell us about the internal processes and dependence relationships of these institutions, as well as about the motivations of their founders?
+
+\begin{itemize}
+\item comparison to other forms (more descriptively)
+\end{itemize}
 
@@
 
-\subsection*{Theory}
+\subsection*{Theoretical framework}
 
-TODO: the theory section (including the hypotheses) is mostly copied from an earlier literature review on organizational closure, and while there are some references to how it could relate to private museums, it isn't integrated with the current focus on collector decision making and private museum sustainability.
+\subsubsection*{Legitimacy and the survival prospects of non-profit organizations}
 
-\subsubsection*{Size}
+Legitimacy is necessary for being understood, tolerated and/or supported by other the organizations in the environemnt; to the extent that this influences resource acquisition it could influence survival prospects.
+While \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close, other studies find limited impact of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
+In the context of private museums, decline of legitimacy/status could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
 
-Larger NPOs are generally found to have lower mortality rates \parencite{Hager_1999_demise,Duckles_Hager_Galaskiewicz_2005_close}, with size being measured through indicators such as assets \parencite{Lu_Shon_Zhang_2019_dissolution}, number of employees \parencite{Bielefeld_1994_survival} and volunteers \parencite{Fernandez_2007_dissolution}, or revenues \parencite{Searing_2020_zombies}.
-Smaller organiations are argued to face greater difficulty in collecting resources and recruiting staff as well as relatively higher costs for administration and regulation \parencite{Helmig_Ingerfurth_Pinz_2013_nonprofit}, while being less able to diversify or benefit from economies of scale \parencite{Hager_1999_demise}.
-Larger organizations are also argued to be able to waste some resources during normal times which can be utilized effectively during situations of crisis without having to scale back services (which generate revenue) \parencite{Hager_2001_vulnerability} and hence avoid downsizing, which can lead to dissolution \parencite{Duckles_Hager_Galaskiewicz_2005_close,Bielefeld_1994_survival}.
+Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
+Understandability \parencite{Glynn_Abzug_2002_names} might thus be limited if an organization is atypical \parencite{Rosch_1975_family}, i.e. displays an unusual combination of features.
+In the case of private museums, such cases might be combinations of features from house museums (e.g. accessibility only by appointment) with full-service museums (e.g. extensive activities). 
+Next to "hard" organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate.
+However, the category of museums could be relatively flexible (for example, it is generally not subject to state regulation), which might result in a relatively high tolerance of diversity as "anything goes" and hence limited "devaluation" of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.
 
@@
 \noindent
-\textbf{H\textsubscript{size}}: Larger private museums are less likely to close than smaller ones.
+\textbf{Hypothesis 1}: Private museums which are considered more legitimate are less likely to close.
 
-\subsubsection*{Resource diversification}
+\subsubsection*{Reputation}
 
-A substantial amount of literature focuses on resources as resource depletion is a leading cause of (nonprofit) organizational demise. 
-Diversification (i.e.
-a multitude of funding sources) is found to reduce mortality \parencite{Fernandez_2007_dissolution,Bielefeld_1994_survival,Hager_2001_vulnerability,Lu_Shon_Zhang_2019_dissolution}; similarly volatility (rapid changes in revenues) is found to increase mortality \parencite{Mayer_2022_slimmer}.
-While private museums are likely already generally leaning toward higher concentration than NPOs generally due to high reliance on the financial contributions of the founder-collector, there might still be variation in the degree of revenue concentration as museums might vary in the proportion of revenues received from ticket prices, restaurants, cafes, museum shops or other activities.
-
+Reputation has been argued to enhance organizational survival \parencite{Rao_1994_reputation}.
+However, reputation effects could also be a spurious effect of organizational capabilities as more competent organizations are more able to both aquire reputation through certification contests and survive in long run \parencite{Goldfarb_Zavyalova_Pillai_2018_Rao}.
 \bigbreak
 \noindent
-\textbf{H\textsubscript{diversification}}: Private museums with more diversified revenue channels are less likely to close than more diversified ones.
+\textbf{H\textsubscript{artnews}}: Private museums of collectors included in the Artnews top 200 collector ranking are less likely to close.
 
@@
 
-\subsubsection*{legitimacy/understandability}
-
-Legitimacy is necessary for being understood/tolerated/supported by other the organizations in the environemnt; to the extent that this influences resource acquisition it could influence survival prospects.
-While \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close, other studies find limited impact of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
-In the context of private museums, decline of legitimacy/status could lead to lower visitor numbers, less discounts from art dealers, less government grants (?) or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
-
-Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
-Understandability/sense-making \parencite{Glynn_Abzug_2002_names} might thus be limited if an organization is atypical \parencite{Rosch_1975_family}, i.e. displays an unusual combination of features.
-In the case of private museums, such cases might be combinations of features from house museums (e.g. accessibility only by appointment) with full-service museums (e.g. extensive activities). 
-Next to "hard" organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate.
-However, the category of museums could be relatively flexible (for example, it is generally not subject to state regulation), which might result in a relatively high tolerance of diversity as "anything goes" and hence limited "devaluation" of non-conforming/atypical members.
-
-\bigbreak
-\noindent
-\textbf{H\textsubscript{typicality}}: Atypical private museums have higher mortality rates.
-
-Legitimacy might also be measured by inclusion in industry registers, such as the Museum of the World (MOW) database \parencite{deGruyter_2021_MOW}.
-
-\bigbreak
-\noindent
-\textbf{H\textsubscript{mow}}: Private museums included in the MOW database have higher survival chances.
-
-\subsubsection*{reputation}
-
-Reputation has been argued to enhance organizational survival \parencite{Rao_1994_reputation}.
-However, reputation effects could also be a spurious effect of organizational capabilities as more competent organizations are more able to both aquire reputation through certification contests and survive in long run \parencite{Goldfarb_Zavyalova_Pillai_2018_Rao}.
-Recognition might be measured by inclusion in the Artnews top 200 collector ranking.
-
-\bigbreak
-\noindent
-\textbf{H\textsubscript{artnews}}: Private museums of collectors included in the Artnews top 200 collector ranking are less likely to close.
-
 \subsection*{Data and Methods}
@@
 
-\subsubsection*{Predictors}
+\subsubsection*{Legitimacy}
 
-TODO: the current do not yet measure all the concepts discussed in the theory, and some are not justified yet on theoretical grouns (founder name in museum name, gender, density).
+Two measures are constructed that aim to capture an effect of legitimacy on closing.
+First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent).
+Secondly, binary predictor measures whether the museum is included in the "Museums of the World" database \parencite{deGruyter_2021_MOW}, a database containig 55k museums.
+
+\subsubsection*{Reputation}
+
+Recognition is measured via inclusion of the founder in the Artnews top 200 collector ranking \parencite{Artnews_ranking}.
+This ranking, established in 1990, lists the 200 collectors the editors of the magazine consider most relevant.
+For each year, a museums can have one of three values: "Not included"; in which case the founder is not included in the year in question and has not been so in the past, "Included"; when the founder is included, or "Dropped", for cases where the founder was included at some point in the past but is no longer included in the current year.
+Cases where multiple individuals are involved in the founding of a private museum are resolved by aggregating the Artnews ranking inclusion history to the founder founder level (i.e., if one of two founders is dropped from the Artnews ranking but the other remains included, the founder couple as a whole is considered included).
+
+\subsubsection*{Control variables}
 
@@
 \noindent
+A number of control variables are used: 
 On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
 Founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder. 
-
-On the museum level, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent).
-Further analyzing the name, a binary indicator also measures whether the name of the founder is included.
-Finally, a binary predictor measures whether the museum is included in the "Museums of the World" database \parencite{deGruyter_2021_MOW}, a database containig 55k museums.
-On the level of the environment, the density (number) of private museum per country is included both in linear and squared form.
-Organizational theory \parencite{hannan89_organ} predicts a U-shaped relationship between density and mortality: While at low levels, increases in the number of organizations are argued to primarily increase legitimacy/familiarity and lower exit rates, increases at higher numbers increase the competition over resources and thereby raise mortality rates.
-
-\bigbreak
-\noindent
-TODO: 
-\begin{itemize}
-\item add museum size/diversification indicators: most museum-level variables that we collected have many missing values (figure \ref{fig:p_vrblcvrg_ratio}), so it's challenging to get good estimates out of them.
-I'm thinking of using some dimensionality reduction like PCA.
-\item add inclusion in Artnews collector ranking
-\item add Tax incentives (country-level)
-\item expand densities: 
-\begin{itemize}
-\item per capita
-\item include MOW museums, for now density is based only on private museums
-\item within proximate environment (circle of X kilometer around museum), rather than country-level
-\end{itemize}
-\item account for clustering within countries/regions
-\end{itemize}
+Further analyzing the name, a binary indicator also measures whether the name of the founder is included in the name of the museum as a measure of centrality of the founder's vision.
+Organizational theory \parencite{hannan89_organ} predicts a U-shaped relationship between density and mortality:
+While at low levels, increases in the number of organizations are argued to primarily increase legitimacy and lower exit rates, increases at higher numbers increase the competition over resources and thereby raise mortality rates.
+On the level of the environment, therefore the density (number) of private museum per country is included both in linear and squared form.
 
@@
 
-In a second step, I use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
+In a second step, we use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
 The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), with \(\psi = \exp(\sum_{j=1}^p x_j \beta_j)\), with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient of the \(j\) -th variable.
@@
 Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.
-
-This model assume proportional hazards, i.e. that the coefficient of a variable stays constant over time, which indicates that for a variable at every time point the hazard ratio is the same.
-So far, tests show a violation of the proportionality assumption only for the variable indicating whether the museum name includes the name of the founder  which furthermore is marginal as it slightly varies by the type of time transformation (table \ref{tbl:t_coxzph}, figure \ref{fig:p_coxphdiag_more}).
 
@@
 The hazard rate doubles over the first 10 years from approximately 0.45\% to 0.9\%, at which value it approximately stays constant for the next 20 years, after which it appears to decline.
-However, the decline after thirty years is presumably less certain as very few private museums have already reached this age (figure \ref{fig:p_agedens}).
+However, the decline after thirty years is presumably less certain as very few private museums have already reached this age.
 
@@
 \end{sloppypar}
-
-\section*{Appendix}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=19cm]{../figures/p_yeardens.pdf}
-\caption{\label{fig:p_yeardens}Private Museum-year Distribution}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=17cm]{../figures/p_agedens.pdf}
-\caption{\label{fig:p_agedens}Age distribution of private museums}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=19cm]{../figures/p_coxphdiag_more.pdf}
-\caption{\label{fig:p_coxphdiag_more}Model Diagnostics}
-\end{figure}
-
-% latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Fri Dec  8 22:31:01 2023
-\begin{table}[ht]
-\centering
-\begin{tabular}{p{0mm}lD{.}{.}{5}D{.}{.}{5}D{.}{.}{5}}
-  \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Kaplan-Meier} & \multicolumn{1}{l}{Identity} & \multicolumn{1}{l}{Rank}\\ 
- \hline
-  \multicolumn{2}{l}{\textbf{Founder}} \\ 
- & Founder died & .59 & .55 & .72 \\ 
-   & Gender - Couple & .31 & .23 & .32 \\ 
-   & Gender - Female & .61 & .68 & .56 \\ 
-   \multicolumn{2}{l}{\textbf{Museum}} \\ 
- & AN Ranking - Dropped & .88 & .98 & .71 \\ 
-   & AN Ranking - Included & .59 & .46 & .41 \\ 
-   & Founder name in Museum name & .09 & .09 & .08 \\ 
-   & MOW inclusion & .28 & .28 & .51 \\ 
-   & Self-Identification - Collection & .60 & .53 & .36 \\ 
-   & Self-Identification - Foundation & .93 & .93 & .84 \\ 
-   & Self-Identification - Other & .90 & .83 & .85 \\ 
-   \multicolumn{2}{l}{\textbf{Environment}} \\ 
- & PM density & .95 & 1.00 & .90 \\ 
-   & PM density$^{2}$ & .77 & .70 & .78 \\ 
-   \multicolumn{2}{l}{\textbf{Miscellaneous}} \\ 
- & Global & .52 & .39 & .51 \\ 
-   \hline 
- \multicolumn{3}{l}{\footnotesize{\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
-\end{tabular}
-\caption{Z-test of proportional hazards} 
-\label{tbl:t_coxzph}
-\end{table}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=18cm]{../figures/p_vrblcvrg_ratio.pdf}
-\caption{\label{fig:p_vrblcvrg_ratio}PMDB variable coverage (abs/rel prop) by museum status and variable group}
-\end{figure}
 \end{document}

### 2024-01-09 texts/paper_closing.tex
more rewwriting for EGOS

@@
-% Created 2024-01-06 za 18:00
+% Created 2024-01-08 ma 18:59
 % Intended LaTeX compiler: pdflatex
@@
 
-\section*{The closure of private museums: Legitimacy, identity and reputation}
+\section*{Identity and the closure of private art museums}
 
@@
 
-In recent years, private collector-run museums have seen an unprecedented proliferation.
-These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums operated and financed by the state or foundations and associations.
+In recent years, private collector-run museums have seen an unprecedented proliferation, with hundreds of organizations founded since the beginning of the millenium \parencite{Velthuis_etal_2023_boom,LarrysList_2015_report}.
+These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums operated and financed by the state, foundations or associations.
 While the emergence of this organizational form has attracted attention (cf.
 \cite{Kolbe_etal_2022_privatemuseum} for a literature review), the process of closure has received considerably less attention.
-In this paper, I investigate
+In this paper, I address this gap by investigating the closure event of members of this new organizational form.
+Doing so does not only provide insights into private museums, but more generally into processes of organizational identity, in particular regarding legitimation and reputation.
 
-argue that studying closures does not only provide insights into private museums, but into more general processes of organizational identity, legitimation and reputation.
-
-In particular concerning identity, I find that museums which are recognized by an international museum database are less likely to close than those which are not.
-With regards to legitimation, results indicate that that museums with more ambiguous names are more likely to close.
-Finally, a reputation effect is indicated by the fact that museums whose founders are dropped from a collector ranking are more likely to close than museums whose founders are included.
-
-\subsection*{Contributions}
-
-\begin{itemize}
-\item Intransparent founder motivations
-\end{itemize}
-
-Despite their occasionally spectacular/sensationalist press coverage, these institutions and the motivations of their founders have remained remarkably intransparent.
-Financed in large parts by their founders' private wealth, few reporting requirements exists; and while some founders highlight their charitable and distintersted intentions in media coverage, such statements intended for a public audience might not necessarily accurately reflect underlying founder motivations.
-
-This study (attempts to) elucidate the hard-to-observe collector motivations by studying one of the most decisive actions that their founder can take: the decision to close the museum.
-Besides investigating the longevity of members of this new organizational form, this study gives insights into the motivations and decision making of founders.
-In other words, what can the factors leading to the closure of private museums tell us about the internal processes and dependence relationships of these institutions, as well as about the motivations of their founders?
-
-\begin{itemize}
-\item comparison to other forms (more descriptively)
-\end{itemize}
-
-\bigbreak
-\noindent
-Private museums:
-\begin{itemize}
-\item founded by collector -> needs to have amassed substantial art collection
-\item building of its own, limited public/corporate funding, has to be visitable -> requires substantial resources
-\end{itemize}
+A number of findings highlight the role of identity in the process of private museum closure. 
+First, I find that museums which are recognized by an international museum database are less likely to close than those which are not.
+Secondly, the results furthermore indicate that museums with more ambiguous names are more likely to close.
+Both these findings possibly indicate that adherence to museum standards enhances legitimacy, which in turn improves survival prospects.
+Finally, founder reputation, in particular its loss, is found to be substantial as museums whose founders are dropped from a collector ranking are more likely to close than museums the founders of which both are and are not included.
 
@@
 
-\subsubsection*{Legitimacy and the survival prospects of non-profit organizations}
+\subsubsection*{Identity and the survival prospects of non-profit organizations}
 
-Legitimacy is necessary for being understood, tolerated and/or supported by other the organizations in the environemnt; to the extent that this influences resource acquisition it could influence survival prospects.
-While \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close, other studies find limited impact of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
-In the context of private museums, decline of legitimacy/status could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
+Having an identity that is legitimate (understandable) and favorable (positive) has been shown to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
+As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
+Even for non-profit organizations such as museums, which do not produce tangible goods (a domain where identity-related effects are present, e.g.
+\cite{Hsu_2015_granted}), a clear and positive identity might be helpful in a number of ways:
+In particular in the context of private museums, decline of legitimacy or reputation could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
+
+The empirical record of the link between identity and survival for non-profit organizations is mixed: 
+For example \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close.
+However, other studies find limited impact of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
+Thus, even while this study cannot conclusively answer the overall link between idenity and survival, it nevertheless contributes insights into which dimensions of organizational identity do, and which do not contribute to survival in a particular organizational population; namely that of private art museums.
 
@@
 
+Furthermore, identity of a private museum may be influenced by the identity of persons most closely affiliated with it, in particular the identity of its founders.
+Given that founders are the very reason behind the existence of these organizations, and sometimes plan these as their personal legacies \parencite{Walker_2019_collector}, founder status gains or losses may very well reflect on the wider organization.
+
 \bigbreak
 \noindent
-\textbf{Hypothesis 1}: Private museums which are considered more legitimate are less likely to close.
-
-\subsubsection*{Reputation}
-
-Reputation has been argued to enhance organizational survival \parencite{Rao_1994_reputation}.
-However, reputation effects could also be a spurious effect of organizational capabilities as more competent organizations are more able to both aquire reputation through certification contests and survive in long run \parencite{Goldfarb_Zavyalova_Pillai_2018_Rao}.
-\bigbreak
-\noindent
-\textbf{H\textsubscript{artnews}}: Private museums of collectors included in the Artnews top 200 collector ranking are less likely to close.
-
-\subsubsection*{Age}
-
-The age of an organization is considered in different ways to be related to closing.
-What started with liability of newness \parencite{Stinchcombe_1965_structure}, which posited that organizational mortality decreases over time due to acquisition of capabilities and connections, has lead to a number of extensions \parencite{Carroll_Khessina_2019_demography,Hannan_1998_mortality}:
-Liability of adolescence argues that shortly after foundings organizations can still draw on endowments, the expiration of which leads to a peak of mortality some time after opening.
-While according to this view mortality still decreases after the peak as the organization becomes more established, other perspectives argue also for a positive relationship between age and mortality:
-According to the liability of obsolescence paradigm the environment changes faster than organizations which are seen as relatively constrained by inertia, which therefore leads to declining fitness and survival chances.
-Similar, according to "liability of senescence" capabilities/routines/coalitions can constrain the actions of organizations.
-Given such conflicting predictions, \textcite{Carroll_Khessina_2019_demography} propose to model age dependence with piece-wise constant hazard models (rather than parametric models) to estimate age-specific effects which can, but do not have to, indicate a relationship between age and mortality.
-
-\subsubsection*{Organizational transformation}
-
-\textcite{Carroll_Khessina_2019_demography} argue that transformation of core features of organizations such as changes in technology or authority can have divergent consequences. 
-On the one hand, it can disrupt internal routines as well as external customer relations by decreasing (perceived) reliability and accountability as the change upsets established perceptions, which can lead to higher mortality.
-On the other hand, organizational transformation can be necessary to adapt to a changing environment, and hence be beneficial for survival.
-
-In the case of private museums, the death of the founder might constitute a substantial transformation as authority has to be reconfigured.
-Abandonment by insiders (such as divorce of directors) has been argued to contribute to NPO closure \parencite{Duckles_Hager_Galaskiewicz_2005_close}.\footnote{Conflict is similarly argued to contribute to closure but is not testable with the current data.}
-Even if plans have been made for a handover, the new leaders might not share the same commitment to art as the original founder, potentially decreasing museum sustainability. 
-In the case of private museums, founder death has been speculated to pose a challenge to their sustainability as "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museum indefinitely" \parencite[p.234]{Walker_2019_collector}.
-However, existing research has not found a straightforward effect of founder death on museum closure \parencite{Velthuis_Gera_forthcoming_fragility,Velthuis_etal_2023_boom}.
-Nevertheless as previous research has relied primarily on descriptive statistics, investigating founder death in a multivariate survival model allows to investigate the effect of founder death with higher precision.
-\bigbreak
-\noindent
-\textbf{H\textsubscript{death}}: A private museum is more likely to close after the death of the founder.
+\textbf{Hypothesis 1}: Private museums with identities more understandable, legitimate and favorable are less likely to close.
 
@@
 A newly constructed database (see \textcite{Velthuis_etal_2023_boom} for details) is used to measure museum survival.
-The unit of analysis is country year.
-The main dependenent variable is an indicator of museum closure, which takes for the museums which close in the year of their closure, and zero otherwise.
+The unit of analysis is museum-year: The main dependenent variable is an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
 Typically for survival data, museums that do not close during the observation period are right-censored, i.e. for such museums the dependent variable is zero for all years.
 
-\subsubsection*{Legitimacy}
+\subsubsection*{Main Predictors: Identity Measures}
+
+The organizational identity of a museum is measured primarily in terms of its legitimacy, i.e. its adherence to museum standards, and reputation of its founders.
+
+\paragraph*{Legitimacy}
 
@@
 First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent).
-Secondly, binary predictor measures whether the museum is included in the "Museums of the World" database \parencite{deGruyter_2021_MOW}, a database containig 55k museums.
+Secondly, a binary predictor measures whether the museum is included in the "Museums of the World" database \parencite{deGruyter_2021_MOW}, a database containig over 55.000 museums.
 
-\subsubsection*{Reputation}
+\paragraph*{Reputation}
 
-Recognition is measured via inclusion of the founder in the Artnews top 200 collector ranking \parencite{Artnews_ranking}.
+Reputation is measured via inclusion of the founder in the Artnews top 200 collector ranking \parencite{Artnews_ranking}.
 This ranking, established in 1990, lists the 200 collectors the editors of the magazine consider most relevant.
@@
 On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
-Founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder. 
-Further analyzing the name, a binary indicator also measures whether the name of the founder is included in the name of the museum as a measure of centrality of the founder's vision.
-Organizational theory \parencite{hannan89_organ} predicts a U-shaped relationship between density and mortality:
+Organizational transformation, such as change of authority has been to increase chances of closure both generally \parencite{Carroll_Khessina_2019_demography} and in the case of private museums specifically (\cite[p.234]{Walker_2019_collector}: "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museum indefinitely").
+Therefore, a measure of founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder. 
+Centrality of the founder's vision is measured via the proxy of whether the name of the founder is included in the name of the museum.
+
+Furthermore, organizational theory \parencite{hannan89_organ} predicts a U-shaped relationship between density and mortality:
 While at low levels, increases in the number of organizations are argued to primarily increase legitimacy and lower exit rates, increases at higher numbers increase the competition over resources and thereby raise mortality rates.
@@
 
-First, we investigate the relationship between age and closing descriptively using hazard rates and the Kaplan-Meier survival function.
-This non-parametric method estimates the hazard rate as the conditional probability of exiting at time t\textsubscript{i} given being alive as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at time \(t_i\) and \(d_i\) as the number of exits at time \(t_i\)), and the survival function as the product of these conditional probabilities as \(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\).
-
-In a second step, we use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
-The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), with \(\psi = \exp(\sum_{j=1}^p x_j \beta_j)\), with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient of the \(j\) -th variable.
+We use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
+The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j=1}^p x_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient of the \(j\) -th variable.
 Estimation via partial maximum likelihood allows estimation of \(\beta\) without estimating the baseline hazard rate, which is therefore not constrained to a parametric form. 
@@
 In total, 479 private museums are included in the database, 53 of them have closed.
-7282 museum-years are observed.
+6903 museum-years are observed.
 
@@
 
-\subsubsection*{Hazard rate and Age Dependence}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=16cm]{../figures/p_hazard.pdf}
-\caption{\label{fig:p_hazard}Private Museum hazard function}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=14cm]{../figures/p_surv.pdf}
-\caption{\label{fig:p_surv}Private Museum Survival probability}
-\end{figure}
-
-Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
-The hazard rate doubles over the first 10 years from approximately 0.45\% to 0.9\%, at which value it approximately stays constant for the next 20 years, after which it appears to decline.
-However, the decline after thirty years is presumably less certain as very few private museums have already reached this age.
-
-The increase in the first years is likely due to endowments: As the establishment of a museum requires considerable resources, their founders appear to allocate enough resources to keep the risk of closure small in the first years after opening.
-Given that founders are likely aware that their endeavor is unlikely to generate a profit, they are not vulnerable to the liability of newness \parencite{Stinchcombe_1965_structure}.
-The relative stability of the hazard rate after ten years has no correspondence in classical theories on age dependence:
-While an increase in mortality as observed here is predicted by the idea of "liability of adolescence" \parencite{Carroll_Khessina_2019_demography}, this framework also predicts a decline in mortality after a peak due to becoming established.
-Furthermore, while "liability of obsolescence" and "liability of senescence" (ibid.) predict higher mortality for older organizations due to mismatch with the environment and inertia (inflexible internal routines), it seems questionable whether museums would have reached obsolescence or senescence already after ten years.
-Furthermore, the applicability of obsolescence and senescence might be limited for non-profit organizations.
-
-Overall the entire life span, the average hazard rate is 0.79\%, which allows comparison to other studies of NPO closure.
-While after very cursory search of the literature I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations (see table \ref{tbl:litreview}).
-
-\begin{table}[htbp]
-\caption{\label{tbl:litreview}Hazard rates in studies of museums and other non-profits}
-\centering
-\begin{tabular}{llll}
-\hline
-study & population & avg. hazard rate & data source\\
-\hline
-\cite{Hager_2001_vulnerability} & Art Museums & 2.4\% & IRS\\
-\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\% & IRS\\
-\hline
-\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\% & IRS\\
-\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\% & IRS\\
-\cite{Gordon_etal_2013_insolvency} & all NPOs & 1.58\% & IRS\\
-\cite{Hager_Galaskiewicz_Larson_2007_liability} & NPOs & 1.25\% & own data\\
-\cite{Clifford_2018_reinforcing} & Charities & 2\%-5\% & Reg. of Charities (UK)\\
-\cite{Mayer_2022_slimmer} & NPOs & 0.17\% & IRS\\
-\hline
-\end{tabular}
-\end{table}
-
-\textcite{Hager_2001_vulnerability} and \textcite{Gordon_etal_2013_insolvency} both study NPOs more generally, but report survival estimates by organizational form.
-At the moment it is not clear which factors account for their hazard rates to differ substantially, but it might be due to selection criteria.
-Both these studies also report substantial variation in hazard rates between organizational forms.
-While preliminary results indicate that private museums have dissolution rates lower or similar to museums and non-profit organizations generally, more research is needed to establish the comparability of these hazard rates.
-
-\noindent
-TODO:
-\begin{itemize}
-\item get confidence interval for hazard rate
-\item see how age can be integrated into survival models (linear term doesn't work)
-\item expand comparison to other studies
-\end{itemize}
-
 \subsubsection*{Regression Results}
@@
 Table \ref{tbl:t_reg_coxph} shows the results of Cox proportional hazard regression model.
+
+\paragraph*{Control Variables}
+
 Founder-level variables are not substantial, as neither gender nor the death of the founder is associated with a significant difference in private museum closure.
@@
 
+Inclusion of founder name is not significantly associated with mortality rates.
+While generally organizations whose name include the name of their founder might be more centered around the founder, and hence display higher inertia, making them less able to adapt to changing environments, these results indicate that it does not seem to be case for private museums.
+
+Environmental variables show no association with mortality
+While the density-dependence paradigm predicts a negative effect of numbers of organizations on closing rate at low numbers (due to legitimacy, i.e.
+growing familiarity with a new organizational form), and a positive effect at high numbers (due to competition over resources), neither relationship is significant in the case of private museums.
+
+\paragraph*{Identity Variables}
+
 Museums which include the term "museum" in their name are the least likely to close, while those with the term "foundation" or "collection" have higher closure rates (but not significantly higher).
-Museums which include neither of these are the most likely to close, and have mortality rates more than three times as high (\(e\)\textsuperscript{1.12} = 3.06 , p<0.01) than institutions including the term "museum".
+Museums which include neither of these are the most likely to close, and have mortality rates more than three times as high (\(e\)\textsuperscript{1.18} = 3.25, p<0.01) than institutions including the term "museum".
 The usage of unconventional names might reflect adherence to museum standards which makes museums more understandable and familiar to third parties (e.g.
@@
 
-Inclusion of founder name is not significantly associated with mortality rates.
-While generally organizations whose name include the name of their founder might be more centered around the founder, and hence display higher inertia, making them less able to adapt to changing environments (TODO: add reference, very speculative!!), these results indicate that it does not seem to be case for private museums.
-
-Museums included in the Museum of the World Database are \(e\)\textsuperscript{-0.97} = 0.38 times as likely to close than museums which are not, yet this result might be produced by different mechanisms.
+Museums included in the Museum of the World Database are \(e\)\textsuperscript{-0.88} = 0.41 (p < 0.05) times as likely to close than museums which are not, yet this result might be produced by different mechanisms.
 On the one hand, it might reflect that larger and richer institutions are both more likely to be noticed by the MOW and more likely to survive (MOW inclusion would then be a proxy for resources).
 On the other hand, similar to unconventional naming patterns, lack of inclusion in the MOW could be an indicator of deviance from museum standards, which could increase the unfamiliarity of the museum vis-a-vis third parties, reducing the chance of survival-enhancing interactions.
-Thirdly, the MOW effect might be endogenous: As no longitudinal MOW data is available, museums might be absent in the MOW because they have closed (TODO: Because of this I wonder if it even makes even sense to include MOW).
 
-Environmental variables show no association with mortality (TODO: this might be due to no per capita numbers).
-While the density-dependence paradigm predicts a negative effect of numbers of organizations on closing rate at low numbers (due to legitimacy, i.e.
-growing familiarity with a new organizational form), and a positive effect at high numbers (due to competition over resources), neither relationship is significant in the case of private museums.
+The reputation of the founder is related to closure to some extent. 
+Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (not statistically different) and by founders who were included at some point but are no longer included (statistically significant).
+While the order of the categories does not fully correspond to the expected order, according to which museums whose collectors are not included would be more likely to close than collectors who are, it nevertheless provides some evidence that status matters; as in particular the loss of status appears to be substantially associated with museum closure.
+
+\subsection*{Conclusion}
 

### 2024-01-10 texts/paper_closing.tex
finalize for EGOS submission

@@
-% Created 2024-01-08 ma 18:59
+% Created 2024-01-09 di 19:22
 % Intended LaTeX compiler: pdflatex
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 
@@
 \usepackage{amsmath}
-\usepackage{datetime}
 \usepackage{amsfonts}
@@
 \usepackage{svg}
-\usepackage[export]{adjustbox}
 
@@
 \usepackage{dcolumn}
-\makeatletter
-\newcolumntype{D}[3]{>{\textfont0=\the\font\DC@{#1}{#2}{#3}}c<{\DC@end}}
-\makeatother
-
-\newcolumntype{L}{>{$}l<{$}}
 
@@
 
-\usepackage{crimson}
-\usepackage{microtype}
+% \usepackage{crimson}
+% \usepackage{microtype}
+
+% \usepackage{helvet}
+% \renewcommand{\familydefault}{\sfdefault}
+
+\usepackage{tgtermes} % times font
 
@@
 \usepackage{setspace}
-\singlespace
+\onehalfspacing
 \usepackage{longtable}
 \usepackage{subfig}
-\usepackage[a4paper, total={18cm, 24cm}]{geometry}
+% \usepackage[a4paper, total={18cm, 24cm}]{geometry}
+\usepackage[a4paper, margin=2.5cm]{geometry}
 
@@
 
-\usepackage{array}
-\usepackage{caption}
-\usepackage{graphicx}
-\usepackage{siunitx}
-\usepackage[normalem]{ulem}
-\usepackage{colortbl}
-\usepackage{multirow}
-\usepackage{hhline}
-\usepackage{calc}
-\usepackage{tabularx}
-\usepackage{threeparttable}
-\usepackage{wrapfig}
-\usepackage{adjustbox}
-\usepackage{hyperref}
-
 \newlist{propertyList}{itemize}{1}
@@
 
-\cfoot {Johannes Aengenheyster}
+% \cfoot {Johannes Aengenheyster}
 \rfoot {\thepage}
@@
 
+Johannes Aengenheyster
+
+\noindent
+Phd student at University of Amsterdam
+
+\noindent
+j.aengenheyster@uva.nl
+
 \subsection*{Introduction}
@@
 In this paper, I address this gap by investigating the closure event of members of this new organizational form.
-Doing so does not only provide insights into private museums, but more generally into processes of organizational identity, in particular regarding legitimation and reputation.
+This exercise does not only provide insights into private museums in particular, but also more generally into processes of organizational identity, especially regarding legitimation and reputation.
 
@@
 Both these findings possibly indicate that adherence to museum standards enhances legitimacy, which in turn improves survival prospects.
-Finally, founder reputation, in particular its loss, is found to be substantial as museums whose founders are dropped from a collector ranking are more likely to close than museums the founders of which both are and are not included.
+Finally, founder reputation, in particular its loss, is found to be substantial as museums whose founders are dropped from a collector ranking are more likely to close than museums whose founders both are and are not included.
 
@@
 
-Having an identity that is legitimate (understandable) and favorable (positive) has been shown to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
+An identity that is legitimate (understandable) and favorable (positive) has been shown to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
 As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
 Even for non-profit organizations such as museums, which do not produce tangible goods (a domain where identity-related effects are present, e.g.
-\cite{Hsu_2015_granted}), a clear and positive identity might be helpful in a number of ways:
+\cite{Hsu_2015_granted,Bogaert_etal_2014_ecological}), a clear and positive identity might be helpful in a number of ways:
 In particular in the context of private museums, decline of legitimacy or reputation could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
@@
 Furthermore, identity of a private museum may be influenced by the identity of persons most closely affiliated with it, in particular the identity of its founders.
-Given that founders are the very reason behind the existence of these organizations, and sometimes plan these as their personal legacies \parencite{Walker_2019_collector}, founder status gains or losses may very well reflect on the wider organization.
+Given that founders are the very reason behind the existence of these organizations, and sometimes plan these as their personal legacies \parencite{Walker_2019_collector}, founder status gains or losses may very well reflect on the wider organization and affect its survival propspects.
 
@@
 
-A newly constructed database (see \textcite{Velthuis_etal_2023_boom} for details) is used to measure museum survival.
-The unit of analysis is museum-year: The main dependenent variable is an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
+A newly constructed database, assembled from different sources,  is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
+First, existing databases of private art museums are harmonized.
+Secondly, the online presences of 14 English art publications were exhaustively searched for any mention of private museums.
+After identifying unique institutions, data on these organizations was collected such as opening year, closing year (of those which closed) and founder information.
+Currently, the database includes 547 museums (of which 446 are currently open, the remainder having closed or transformed into other organizational forms).
+Using this database allows to reconstruct the lifecourse of the each institution with the the unit of analysis as museum-year:
+The main dependenent variable is thus an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
 Typically for survival data, museums that do not close during the observation period are right-censored, i.e. for such museums the dependent variable is zero for all years.
@@
 First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent).
-Secondly, a binary predictor measures whether the museum is included in the "Museums of the World" database \parencite{deGruyter_2021_MOW}, a database containig over 55.000 museums.
+Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might very well shape expectations and influence forms of engagement.
+In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums.
+
+Secondly, a binary predictor measures whether the museum is included in the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55.000 museums.
+While the exact criteria of the research process leading to the MOW database are not known, it is plausible that museums who correspond to an ideal-typical museum are more likely to be included.
+Assuming that museums are seen similarly by the creators of the MOW database and other audiences, inclusion in the MOW database constitutes a proxy for adherence to museum standards.
 
@@
 Reputation is measured via inclusion of the founder in the Artnews top 200 collector ranking \parencite{Artnews_ranking}.
-This ranking, established in 1990, lists the 200 collectors the editors of the magazine consider most relevant.
+This ranking, established in 1990, lists each year the 200 collectors the editors of the magazine consider most relevant.
 For each year, a museums can have one of three values: "Not included"; in which case the founder is not included in the year in question and has not been so in the past, "Included"; when the founder is included, or "Dropped", for cases where the founder was included at some point in the past but is no longer included in the current year.
@@
 We use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
-The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j=1}^p x_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient of the \(j\) -th variable.
-Estimation via partial maximum likelihood allows estimation of \(\beta\) without estimating the baseline hazard rate, which is therefore not constrained to a parametric form. 
+The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
+Partial maximum likelihood allows estimation of \(\beta\) without defining the baseline hazard rate, which is therefore not constrained to a parametric form. 
 Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.
@@
 \subsubsection*{Summary statistics}
-
-In total, 479 private museums are included in the database, 53 of them have closed.
-6903 museum-years are observed.
-
-\noindent
 
@@
 
-Table \ref{tbl:t_sumstats} shows summary statistics for all variables.
+In total, 479 private museums are included in the database, 53 of them have closed.
+6903 museum-years are observed; table \ref{tbl:t_sumstats} shows summary statistics for all variables.
 
@@
 
-Founder-level variables are not substantial, as neither gender nor the death of the founder is associated with a significant difference in private museum closure.
-While there is no particular reason to expect a gender effect, the not substantially higher likelihood for museums to close after their founder has died indicates that private museums might be less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
+Neither gender nor the death of the founder is associated with a significant difference in private museum closure.
+While there is no particular reason to expect a gender effect, the not substantially higher likelihood for a museums to close after its founder has died indicates that private museums might be less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
 
@@
 
-Environmental variables show no association with mortality
+Environmental variables show no association with mortality.
 While the density-dependence paradigm predicts a negative effect of numbers of organizations on closing rate at low numbers (due to legitimacy, i.e.
@@
 attracting visitors, cooperations, sponsorships or subsidies).
-However, as founders can choose their museum’s name arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.
+However, as founders can choose the name of their museum arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.
 
@@
 The reputation of the founder is related to closure to some extent. 
-Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (not statistically different) and by founders who were included at some point but are no longer included (statistically significant).
+Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (not statistically significant) and by founders who were included at some point but are no longer included (statistically significant).
 While the order of the categories does not fully correspond to the expected order, according to which museums whose collectors are not included would be more likely to close than collectors who are, it nevertheless provides some evidence that status matters; as in particular the loss of status appears to be substantially associated with museum closure.
@@
 \subsection*{Conclusion}
+
+The conducted analysis shows a substantial association between private museum identity and closures.
+While alternative explanations cannot be completely ruled out, a clearly understandable identity and a favorable founder reputation emerge as important predictors of the chance of a private museum to close.
+Future research can expand on these findings by in more detail investigating the resource perspective of private museums, the intransparency of which has so far aggravated insights about budgetary aspects, in particular how these financial and material characteristics are moderated or mediated by processes of organizational identity.
 

### 2024-01-11 texts/paper_closing.tex
edit paper for EURAM submission
un-uncomment theory/results on age dependence, transformation theory,
closing rate comparison based on literature to get 10 pages, yeet personal information

@@
-% Created 2024-01-09 di 19:22
+% Created 2024-01-11 do 13:48
 % Intended LaTeX compiler: pdflatex
@@
 
-Johannes Aengenheyster
-
-\noindent
-Phd student at University of Amsterdam
-
-\noindent
-j.aengenheyster@uva.nl
-
 \subsection*{Introduction}
@@
 \textbf{Hypothesis 1}: Private museums with identities more understandable, legitimate and favorable are less likely to close.
+
+\subsubsection*{Other predictors of organizational survival}
+
+\paragraph*{Age}
+
+The age of an organization is considered in different ways to be related to closing.
+What started with liability of newness \parencite{Stinchcombe_1965_structure}, which posited that organizational mortality decreases over time due to acquisition of capabilities and connections, has lead to a number of extensions \parencite{Carroll_Khessina_2019_demography,Hannan_1998_mortality}:
+Liability of adolescence argues that shortly after foundings organizations can still draw on endowments, the expiration of which leads to a peak of mortality some time after opening.
+While according to this view mortality still decreases after the peak as the organization becomes more established, other perspectives argue also for a positive relationship between age and mortality:
+According to the liability of obsolescence paradigm the environment changes faster than organizations which are seen as relatively constrained by inertia, which therefore leads to declining fitness and survival chances.
+Similar, according to "liability of senescence" capabilities/routines/coalitions can constrain the actions of organizations.
+Given such conflicting predictions, \textcite{Carroll_Khessina_2019_demography} propose to model age dependence with piece-wise constant hazard models (rather than parametric models) to estimate age-specific effects which can, but do not have to, indicate a relationship between age and mortality.
+
+\paragraph*{Organizational transformation}
+
+\textcite{Carroll_Khessina_2019_demography} argue that transformation of core features of organizations such as changes in technology or authority can have divergent consequences. 
+On the one hand, it can disrupt internal routines as well as external customer relations by decreasing (perceived) reliability and accountability as the change upsets established perceptions, which can lead to higher mortality.
+On the other hand, organizational transformation can be necessary to adapt to a changing environment, and hence be beneficial for survival.
+
+In the case of private museums, the death of the founder might constitute a substantial transformation as authority has to be reconfigured.
+Abandonment by insiders (such as divorce of directors) has been argued to contribute to NPO closure \parencite{Duckles_Hager_Galaskiewicz_2005_close}.\footnote{Conflict is similarly argued to contribute to closure but is not testable with the current data.}
+Even if plans have been made for a handover, the new leaders might not share the same commitment to art as the original founder, potentially decreasing museum sustainability. 
+In the case of private museums, founder death has been speculated to pose a challenge to their sustainability as "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museum indefinitely" \parencite[p.234]{Walker_2019_collector}.
+However, existing research has not found a straightforward effect of founder death on museum closure \parencite{Velthuis_Gera_forthcoming_fragility,Velthuis_etal_2023_boom}.
+Nevertheless as previous research has relied primarily on descriptive statistics, investigating founder death in a multivariate survival model allows to investigate the effect of founder death with higher precision.
+\bigbreak
+\noindent
 
@@
 
-We use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
+First, we investigate the relationship between age and closing descriptively using hazard rates and the Kaplan-Meier survival function.
+This non-parametric method estimates the hazard rate as the conditional probability of exiting at time t\textsubscript{i} given being alive as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at time \(t_i\) and \(d_i\) as the number of exits at time \(t_i\)), and the survival function as the product of these conditional probabilities as \(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\).
+
+Secondly, we use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
 The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
@@
 6903 museum-years are observed; table \ref{tbl:t_sumstats} shows summary statistics for all variables.
+
+\subsubsection*{Hazard rate and Age Dependence}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=16cm]{../figures/p_hazard.pdf}
+\caption{\label{fig:p_hazard}Private Museum hazard function}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=14cm]{../figures/p_surv.pdf}
+\caption{\label{fig:p_surv}Private Museum Survival probability}
+\end{figure}
+
+Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
+The hazard rate doubles over the first 10 years from approximately 0.45\% to 0.9\%, at which value it approximately stays constant for the next 20 years, after which it appears to decline.
+However, the decline after thirty years is presumably less certain as very few private museums have already reached this age.
+
+The increase in the first years is likely due to endowments: As the establishment of a museum requires considerable resources, their founders appear to allocate enough resources to keep the risk of closure small in the first years after opening.
+Given that founders are likely aware that their endeavor is unlikely to generate a profit, they are not vulnerable to the liability of newness \parencite{Stinchcombe_1965_structure}.
+The relative stability of the hazard rate after ten years has no correspondence in classical theories on age dependence:
+While an increase in mortality as observed here is predicted by the idea of "liability of adolescence" \parencite{Carroll_Khessina_2019_demography}, this framework also predicts a decline in mortality after a peak due to becoming established.
+Furthermore, while "liability of obsolescence" and "liability of senescence" (ibid.) predict higher mortality for older organizations due to mismatch with the environment and inertia (inflexible internal routines), it seems questionable whether museums would have reached obsolescence or senescence already after ten years.
+Furthermore, the applicability of obsolescence and senescence might be limited for non-profit organizations.
+
+Overall the entire life span, the average hazard rate is 0.79\%, which allows comparison to other studies of NPO closure.
+While after very cursory search of the literature I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations (see table \ref{tbl:litreview}).
+
+\begin{table}[htbp]
+\caption{\label{tbl:litreview}Hazard rates in studies of museums and other non-profits}
+\centering
+\begin{tabular}{llll}
+\hline
+study & population & avg. hazard rate & data source\\
+\hline
+\cite{Hager_2001_vulnerability} & Art Museums & 2.4\% & IRS\\
+\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\% & IRS\\
+\hline
+\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\% & IRS\\
+\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\% & IRS\\
+\cite{Gordon_etal_2013_insolvency} & all NPOs & 1.58\% & IRS\\
+\cite{Hager_Galaskiewicz_Larson_2007_liability} & NPOs & 1.25\% & own data\\
+\cite{Clifford_2018_reinforcing} & Charities & 2\%-5\% & Reg. of Charities (UK)\\
+\cite{Mayer_2022_slimmer} & NPOs & 0.17\% & IRS\\
+\hline
+\end{tabular}
+\end{table}
+
+\textcite{Hager_2001_vulnerability} and \textcite{Gordon_etal_2013_insolvency} both study NPOs more generally, but report survival estimates by organizational form.
+At the moment it is not clear which factors account for their hazard rates to differ substantially, but it might be due to selection criteria.
+Both these studies also report substantial variation in hazard rates between organizational forms.
+While preliminary results indicate that private museums have dissolution rates lower or similar to museums and non-profit organizations generally, more research is needed to establish the comparability of these hazard rates.
 

### 2024-02-28 scripts/closing_main.R
improve documentation

@@ -7,24 +7,24 @@
 args <- commandArgs(trailingOnly = T)
 options(width = 115)
 
-library(jtls)
-library(pmdata)
-library(memoise)
-library(collapse)
-library(purrr)
-library(docstring) # for annotating 
-library(ggbeeswarm) # move points up/down on vrblcvrg plots.. hopefully avoid
-library(survival) 
-library(ggsurvfit) # easy visualizations of survival objects, hopefully avoid
-library(countrycode) 
-library(muhaz) # for smooth hazard curves
-library(patchwork) # for stichting plots together, hopefully avoid
-library(texreg, include.only = c("screenreg", "texreg")) ## inspection of results
-library(tinytest) # for looking at pmdata tests
+library(jtls)        # custom functions package
+library(pmdata)      # private museum data package
+library(memoise)     # caching time intensive functions
+library(collapse)    # some fast but incomprehensible data transformation framework
+library(purrr)       # parallel processing
+library(docstring)   # for annotating 
+library(ggbeeswarm)  # move points up/down on vrblcvrg plots.. hopefully avoid
+library(survival)    # survival/event history models
+library(ggsurvfit)   # easy visualizations of survival objects, hopefully avoid
+library(countrycode) # will always be necessary when working with countries
+library(muhaz)       # for smooth hazard curves
+library(patchwork)   # for stichting plots together, hopefully avoid
+library(tinytest)    # for looking at pmdata tests
 ## library(parallel) # parallel processing
-library(furrr) # parallel processing
-library(splines) # for gp_schoenfeld, maybe neeeded later too for regressions
-library(Hmisc, include.only = "latexTranslate") # latexTranslate
+library(furrr)       # parallel processing
+library(splines)     # for gp_schoenfeld, maybe neeeded later too for regressions
+library(texreg, include.only = c("screenreg", "texreg")) ## inspection of results
+library(Hmisc, include.only = "latexTranslate")  # latexTranslate
 
 ## LOCS <- list(PROJDIR = "/home/johannes/Dropbox/phd/papers/closing/")
 ## LOCS$FIGDIR <- paste0(FIG

### 2024-02-28 texts/paper_closing.tex
integrate popcircles (for now million in 10km circle),
as part of that, include in gc_vvs, adjust gt_sumstats (decimal digits generation account for non-Int min/max), improve gd_pmyear (now gw_pmyear) to just merge, yeeting rows now moved to (new) gd_pmyear function, cleanup old code

@@
-% Created 2024-01-11 do 13:48
+% Created 2024-02-28 wo 13:52
 % Intended LaTeX compiler: pdflatex
@@
  pdfsubject={},
- pdfcreator={Emacs 29.1 (Org mode 9.6.7)}, 
+ pdfcreator={Emacs 29.2 (Org mode 9.6.15)}, 
  pdflang={English}}
@@
 Finally, founder reputation, in particular its loss, is found to be substantial as museums whose founders are dropped from a collector ranking are more likely to close than museums whose founders both are and are not included.
+
+\bigbreak
+\noindent
+\textbf{keywords}: museum, closure, identity
 
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Fri Dec  8 22:31:01 2023
+% Wed Feb 28 13:49:39 2024
 \begin{table}[ht]
@@
  & PM density &  &  & 20.541 & 18.37 & 1 & 62 \\ 
+   & Population (10km Circle) &  &  &  1.401 &  1.76 & 0.000091 & 10.95 \\ 
    & Europe and North America & 313 & 0.652 &  0.645 &  0.48 & 0 & 1 \\ 
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Fri Dec  8 22:38:34 2023
+% Wed Feb 28 13:49:45 2024
 \begin{table}[ht]
@@
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .30 \; (0.36) \\ 
-   & Gender - Couple & -.03 \; (0.36) \\ 
-   & Founder died & .04 \; (0.54) \\ 
+ & Gender - Female & .24 \; (0.36) \\ 
+   & Gender - Couple & .02 \; (0.36) \\ 
+   & Founder died & .05 \; (0.53) \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .79 \; (0.47) \\ 
-   & Self-Identification - Collection & .50 \; (0.55) \\ 
-   & Self-Identification - Other & 1.18 \; (0.37)^{**} \\ 
-   & AN Ranking - Included & .34 \; (0.41) \\ 
-   & AN Ranking - Dropped & 1.16 \; (0.45)^{*} \\ 
-   & Founder name in Museum name & -.35 \; (0.32) \\ 
-   & MOW inclusion & -.88 \; (0.39)^{*} \\ 
+ & Self-Identification - Foundation & .90 \; (0.47) \\ 
+   & Self-Identification - Collection & .64 \; (0.56) \\ 
+   & Self-Identification - Other & 1.28 \; (0.37)^{***} \\ 
+   & AN Ranking - Included & .28 \; (0.41) \\ 
+   & AN Ranking - Dropped & 1.15 \; (0.45)^{*} \\ 
+   & Founder name in Museum name & -.36 \; (0.32) \\ 
+   & MOW inclusion & -.86 \; (0.40)^{*} \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
@@
    & PM density$^{2}$ & .00 \; (0.00) \\ 
+   & Population (10km Circle) & .14 \; (0.07) \\ 
    \hline
@@
    & Closures & 53 \\ 
-   & log. Likelihood & -266.76 \\ 
-   & AIC & 557.52 \\ 
-   & BIC & 581.16 \\ 
+   & log. Likelihood & -265.13 \\ 
+   & AIC & 556.26 \\ 
+   & BIC & 581.87 \\ 
    \hline 

### 2024-02-28 scripts/closing_main.R

@@ -81,6 +81,7 @@ gc_vvs <- function() {
         mow             = "MOW inclusion",
         pm_dens         = "PM density",
         "I(pm_dens^2)"  = "PM density^2",
+        pop             = "Population (10km Circle)",
         west            = "Europe and North America",
         reg6            = "Region",
         an_inclusion    = "ArtNews Ranking inclusion",
@@ -89,7 +90,7 @@ gc_vvs <- function() {
      l_vrblgrps <- list(# variable groups
          founder  = .c(gender, founder_dead),
          museum   = .c(slfidfcn, muem_fndr_name, mow, an_inclusion),
-         envir    = .c(pm_dens, "I(pm_dens^2)", west, reg6),
+         envir    = .c(pm_dens, "I(pm_dens^2)", pop, west, reg6),
          misc     = .c(GLOBAL)
      )
 
@@ -119,12 +120,12 @@ gc_vvs <- function() {
 
     ## specify whether variable is time-varying or not
     vrbls_tiv <- .c(gender, slfidfcn, muem_fndr_name, mow, west, reg6)
-    vrbls_tv <- .c(pm_dens, "I(pm_dens^2)",  founder_dead, an_inclusion)
+    vrbls_tv <- .c(pm_dens, "I(pm_dens^2)", pop, founder_dead, an_inclusion)
 
     ## specify variable type: binary, numeric, categorical
     l_vrbltypes <- list(        
         bin = .c(founder_dead, muem_fndr_name, mow, west),
-        num = .c(pm_dens, "I(pm_dens^2)"),
+        num = .c(pm_dens, "I(pm_dens^2)", pop),
         cat = .c(gender, slfidfcn, reg6, an_inclusion))
 
     dt_vrbltypes <- imap(l_vrbltypes, ~data.table(vrbl = .x, vrbltype = .y)) %>% rbindlist
@@ -289,7 +290,7 @@ gc_pmdb_vrblgrps <- function(dt_pmdb) {
                        .c(cafe_restrnt, avbl_floorsize, avbl_exhibsize, museumshop, buildgtype, website,
                           reducedtickets, staff_size, rentalpossblt, webshop, nbr_visitrs, ticket_price,
                           opng_time, temp_exhibs, avbl_exhibhist, architect)),
-        existence = .c(city, iso3c, multiplelocs, year_opened, year_closed), #
[…]

### 2024-02-28 scripts/regression.R

@@ -14,7 +14,7 @@ gd_popcircle <- function(dt_pmx) {
     GHSL_YEARS <- seq(1975,2020, by = 5)
     dt_ghsl_years <- data.table(ghsl_year = GHSL_YEARS)
 
-    dt_pmx %>% copy() %>% .[, N := .N, .(lat, long)] %>% .[N > 1] %>% print(n=300)
+    ## dt_pmx %>% copy() %>% .[, N := .N, .(lat, long)] %>% .[N > 1] %>% print(n=300)
 
     ## construct base for GSHL queries: get unique time points per museum
     ## keep this dt to merge GHSL results back to full years later on
@@ -27,13 +27,14 @@ gd_popcircle <- function(dt_pmx) {
     ## construct DT of positions to query
     dt_pmdb_year5 <- funique(dt_pmyear_popprep[, .(ID, year5, lat, lon = long)])
 
+    ## ## some testing code
+    ## imp_ghsl(dt_pmdb_year5[year5  == 2010, .SD[1:10]], # [, ID2 := as.character(ID)],
+    ##          id_vrbl = "ID", year = 2010, radius = 10000) %>% .[, pop]
+
     ## split into year lists for more comfy parallel processing
     ## could squeeze out some more optimization by yeeting duplicate locations, but they shouldn't exist..
     l_dt_pmdb_ghsl <- split(dt_pmdb_year5, dt_pmdb_year5$year5)
 
-
-    ## imp_ghsl(dt_pmdb_ghsl[year_5  == 2010, .SD[1:10]], # [, ID2 := as.character(ID)],
-    ##          id_vrbl = "ID", year = 2010, radius = 10000)    
     
     ## actual multithreaded processing
     plan(multicore, workers = 6)
@@ -42,7 +43,8 @@ gd_popcircle <- function(dt_pmx) {
 
     ## process results
     ## year5 needs to be re-assigned as int probably since future_imap's .y converts it to string
-    dt_popres2 <- rbindlist(l_popres)[, `:=`(year5 = as.integer(year), year = NULL)]
+    dt_popres2 <- rbindlist(l_popres)[, `:=`(year5 = as.integer(year), year = NULL)] %>%
+        .[, pop := pop/1e6]
 
     ## merge to yearly data
     dt_popcircle <- join(dt_pmyear_popprep, dt_popres2, on = c("ID", "year5"))
@@ -135,31 +137,28 @@ gd_pmx <- function(dt_pmdb) {
 
     
 
[…]

### 2024-03-27 texts/paper_closing.tex
new tables (desc stats, reg) with dimred and geo-density

--- 2024-01-11 texts/paper_closing.tex
@@
-% Created 2024-01-11 do 13:48
+% Created 2024-03-20 wo 16:51
 % Intended LaTeX compiler: pdflatex
@@
  pdfsubject={},
- pdfcreator={Emacs 29.1 (Org mode 9.6.7)}, 
+ pdfcreator={Emacs 29.2 (Org mode 9.6.21)}, 
  pdflang={English}}
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Fri Dec  8 22:31:01 2023
+% Wed Mar  6 21:27:16 2024
 \begin{table}[ht]
@@
    & AN Ranking - Dropped &  &  &  0.057 &  0.23 & 0 & 1 \\ 
+   & PC1 (Size) &  &  &  0.344 &  4.26 & -6.2 & 13.90 \\ 
+   & PC2 (Support) &  &  & -0.046 &  1.99 & -5.6 & 6.70 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
  & PM density &  &  & 20.541 & 18.37 & 1 & 62 \\ 
+   & Pop. (millions) within 10km &  &  &  1.382 &  1.74 & 0.000087 & 10.81 \\ 
+   & Nbr PM within 10km &  &  &  2.681 &  2.97 & 1 & 16 \\ 
    & Europe and North America & 313 & 0.652 &  0.645 &  0.48 & 0 & 1 \\ 
@@
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Fri Dec  8 22:38:34 2023
+% Wed Mar  6 21:27:26 2024
 \begin{table}[ht]
@@
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .30 \; (0.36) \\ 
-   & Gender - Couple & -.03 \; (0.36) \\ 
-   & Founder died & .04 \; (0.54) \\ 
+ & Gender - Female & .42 \; (0.37) \\ 
+   & Gender - Couple & .66 \; (0.38) \\ 
+   & Founder died & 1.33 \; (0.55)^{*} \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .79 \; (0.47) \\ 
-   & Self-Identification - Collection & .50 \; (0.55) \\ 
-   & Self-Identification - Other & 1.18 \; (0.37)^{**} \\ 
-   & AN Ranking - Included & .34 \; (0.41) \\ 
-   & AN Ranking - Dropped & 1.16 \; (0.45)^{*} \\ 
-   & Founder name in Museum name & -.35 \; (0.32) \\ 
-   & MOW inclusion & -.88 \; (0.39)^{*} \\ 
+ & Self-Identification - Foundation & .94 \; (0.50) \\ 
+   & Self-Identification - Collection & .07 \; (0.60) \\ 
+   & Self-Identification - Other & 1.16 \; (0.39)^{**} \\ 
+   & AN Ranking - Included & .33 \; (0.43) \\ 
+   & AN Ranking - Dropped & 1.26 \; (0.49)^{*} \\ 
+   & Founder name in Museum name & -.57 \; (0.33) \\ 
+   & MOW inclusion & -.28 \; (0.41) \\ 
+   & PC1 (Size) & -.34 \; (0.06)^{***} \\ 
+   & PC2 (Support) & -.11 \; (0.11) \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density & -.04 \; (0.03) \\ 
+ & PM density & -.05 \; (0.03) \\ 
    & PM density$^{2}$ & .00 \; (0.00) \\ 
+   & Pop. (millions) within 10km & .00 \; (0.11) \\ 
+   & Nbr PM within 10km & .13 \; (0.06)^{*} \\ 
    \hline
@@
    & Closures & 53 \\ 
-   & log. Likelihood & -266.76 \\ 
-   & AIC & 557.52 \\ 
-   & BIC & 581.16 \\ 
+   & log. Likelihood & -236.48 \\ 
+   & AIC & 504.96 \\ 
+   & BIC & 536.48 \\ 
    \hline 

### 2024-04-03 texts/paper_closing.tex
add artfacts size (quantiles), yeet PCA remainders

@@
-% Created 2024-03-20 wo 16:51
+% Created 2024-04-03 wo 13:56
 % Intended LaTeX compiler: pdflatex
@@
 The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
-Partial maximum likelihood allows estimation of \(\beta\) without defining the baseline hazard rate, which is therefore not constrained to a parametric form. 
+Partial maximum likelihood estimation allows calculating \(\beta\) without defining the baseline hazard rate, which therefore is not constrained to a parametric form. 
 Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.
@@
 
-% latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Wed Mar  6 21:27:16 2024
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Wed Apr  3 13:38:27 2024
 \begin{table}[ht]
@@
    & AN Ranking - Dropped &  &  &  0.057 &  0.23 & 0 & 1 \\ 
-   & PC1 (Size) &  &  &  0.344 &  4.26 & -6.2 & 13.90 \\ 
-   & PC2 (Support) &  &  & -0.046 &  1.99 & -5.6 & 6.70 \\ 
+   & Exhibition Quantile &  &  &  0.428 &  0.24 & 0.083 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
@@
 
-% latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Wed Mar  6 21:27:26 2024
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Wed Apr  3 13:14:43 2024
 \begin{table}[ht]
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
   \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more} & \multicolumn{1}{l}{r\_waf}\\ 
  \hline
-  \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .42 \; (0.37) \\ 
-   & Gender - Couple & .66 \; (0.38) \\ 
-   & Founder died & 1.33 \; (0.55)^{*} \\ 
-   \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .94 \; (0.50) \\ 
-   & Self-Identification - Collection & .07 \; (0.60) \\ 
-   & Self-Identification - Other & 1.16 \; (0.39)^{**} \\ 
-   & AN Ranking - Included & .33 \; (0.43) \\ 
-   & AN Ranking - Dropped & 1.26 \; (0.49)^{*} \\ 
-   & Founder name in Museum name & -.57 \; (0.33) \\ 
-   & MOW inclusion & -.28 \; (0.41) \\ 
-   & PC1 (Size) & -.34 \; (0.06)^{***} \\ 
-   & PC2 (Support) & -.11 \; (0.11) \\ 
-   \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density & -.05 \; (0.03) \\ 
-   & PM density$^{2}$ & .00 \; (0.00) \\ 
-   & Pop. (millions) within 10km & .00 \; (0.11) \\ 
-   & Nbr PM within 10km & .13 \; (0.06)^{*} \\ 
+  \multicolumn{4}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & .19 \; (0.36) & .52 \; (0.47) \\ 
+   & Gender - Couple & .08 \; (0.36) & .24 \; (0.44) \\ 
+   & Founder died & .11 \; (0.53) & -.09 \; (0.69) \\ 
+   \multicolumn{4}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .81 \; (0.48) & 1.01 \; (0.67) \\ 
+   & Self-Identification - Collection & .45 \; (0.58) & .85 \; (0.73) \\ 
+   & Self-Identification - Other & 1.29 \; (0.38)^{***} & 1.40 \; (0.56)^{*} \\ 
+   & AN Ranking - Included & .38 \; (0.41) & .38 \; (0.51) \\ 
+   & AN Ranking - Dropped & 1.15 \; (0.45)^{*} & 1.31 \; (0.62)^{*} \\ 
+   & Founder name in Museum name & -.31 \; (0.33) & -.35 \; (0.41) \\ 
+   & MOW inclusion & -.81 \; (0.40)^{*} & -.66 \; (0.51) \\ 
+   & Exhibition Quantile &  & -.70 \; (0.82) \\ 
+   \multicolumn{4}{l}{\textbf{Environment}} \\ 
+ & PM density & -.05 \; (0.03) & -.02 \; (0.04) \\ 
+   & PM density$^{2}$ & .00 \; (0.00) & .00 \; (0.00) \\ 
+   & Pop. (millions) within 10km & .02 \; (0.11) & .10 \; (0.12) \\ 
+   & Nbr PM within 10km & .11 \; (0.06)^{*} & .07 \; (0.09) \\ 
    \hline
- & Museum-years & 6903 \\ 
-   & Closures & 53 \\ 
-   & log. Likelihood & -236.48 \\ 
-   & AIC & 504.96 \\ 
-   & BIC & 536.48 \\ 
+ & Museum-years & 6903 & 3292 \\ 
+   & Closures & 53 & 33 \\ 
+   & log. Likelihood & -263.16 & -137.85 \\ 
+   & AIC & 554.31 & 305.71 \\ 
+   & BIC & 581.90 & 328.16 \\ 
    \hline 
- \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
 \end{tabular}

### 2024-04-03 scripts/cfg.R

@@ -182,13 +182,14 @@ gc_vvs <- function() {
         west            = "Europe and North America",
         reg6            = "Region",
         an_inclusion    = "ArtNews Ranking inclusion",
+        exhbqntl        = "Exhibition Quantile", 
         ## V1              = "PC1 (Size)",
         ## V2              = "PC2 (Support)",
         GLOBAL          = "Global") # from cox.zph
     
      l_vrblgrps <- list(# variable groups
          founder  = .c(gender, founder_dead),
-         museum   = .c(slfidfcn, muem_fndr_name, mow, an_inclusion), # V1, V2
+         museum   = .c(slfidfcn, muem_fndr_name, mow, an_inclusion, exhbqntl), # V1, V2
          envir    = .c(pm_dens, "I(pm_dens^2)", pop, proxcnt10, west, reg6),
          misc     = .c(GLOBAL)
      )
@@ -224,7 +225,7 @@ gc_vvs <- function() {
     ## specify variable type: binary, numeric, categorical
     l_vrbltypes <- list(        
         bin = .c(founder_dead, muem_fndr_name, mow, west),
-        num = .c(pm_dens, "I(pm_dens^2)", pop, proxcnt10), # V1, V2
+        num = .c(pm_dens, "I(pm_dens^2)", pop, proxcnt10, exhbqntl), # V1, V2
         cat = .c(gender, slfidfcn, reg6, an_inclusion))
 
     dt_vrbltypes <- imap(l_vrbltypes, ~data.table(vrbl = .x, vrbltype = .y)) %>% rbindlist

### 2024-04-03 scripts/closing_main.R

@@ -192,7 +192,7 @@ gt_sumstats <- function(dt_pmyear, dt_pmcpct) {
 
     ## apply summary functions, merge with term labels to get variables names and groupings
     dt_cbn <- rbind(dt_dummies, dt_numvrbls) %>%
-        .[, map(funcs_sumry, ~get(.x)(value)), term] %>%
+        .[, map(funcs_sumry, ~get(.x)(value, na.rm = T)), term] %>%
         setnames(old = paste0("V", 1:len(funcs_sumry)), new = funcs_sumry) %>%
         c_vvs$dt_termlbls[., on = "term"]
         
@@ -380,9 +380,9 @@ dt_pmyear <- gd_pmyear(dt_pmyear_prep) # trim down dt to no NAs
 dt_pmcpct <- gd_pmcpct(dt_pmyear) # time-invariant variables (UoA PM, not pm-year)
 
 l_mdls <- gl_mdls(dt_pmyear, dt_pmcpct) # generate models
-l_mdlnames_coxph <- c("r_more") # set model names for t_reg_coxph
+l_mdlnames_coxph <- c("r_more", "r_waf") # set model names for t_reg_coxph
 
-screenreg2(list(l_mdls$r_more)) # just smoe display
+screenreg2(list(l_mdls$r_waf)) # just smoe display
 
 ## screenreg2(list(l_mdls$r_west_cpct, l_mdls$r_west_year, l_mdls$r_west_year2), digits = 4)
 
@@ -434,3 +434,9 @@ dtblF("t_reg_coxph_wcpF")
 
 gdtbl("t_reg_coxph")
 ## gd_reg_coxph(l_mdls$r_more, "r_more")
+
+
+print("everything is DONE")
+
+
+

### 2024-04-03 scripts/regression.R

@@ -6,6 +6,77 @@
 
 ## ** data functions
 
+gd_af_size <- function(dt_pmx) {
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
+    1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
+
+    ## get AF dts 
+    dt_matches_pmdb_af <- gd_af_pmdb_matches()
+    dt_af_exhbs <- gd_af_exhbs()[, iso3c := countrycode(CountryName, "country.name", "iso3c")] %>%
+        .[, CountryName := NULL]
+    
+    ## doesn't seem a lot of issues
+    ## dt_af_exhbs[CountryName == "Kosovo"]
+    ## dt_af_exhbs[is.na(iso3c), .N, CountryName]
+
+    ## expand to pm_year UoA
+    dt_pmyear_size <- copy(dt_pmx)[, last_year := fifelse(museum_status == "closed", year_closed, END_YEAR)] %>%
+        .[, .(year = year_opened:last_year), .(ID, iso3c, year_opened, year_closed)]
+                                               
+
+    ## add info for merging AF data to PDMB
+    dt_pmdb_af <- join(dt_pmx[, .(ID, name, iso3c, museum_status)], dt_matches_pmdb_af,
+                       on = c("ID" = "PMDB_ID"), how = "left", verbose = F) %>%
+        .[, InstitutionID := as.integer(AF_IID)]
+
+    ## merge AF exhibitions data to PMDB
+    dt_af_exhbs_pmdb <- join(dt_af_exhbs[, .(ID, InstitutionID, begin_year = year(BeginDate), iso3c)],
+                         dt_pmdb_af[, .(InstitutionID, PMDB_ID = ID, name)],
+                         on = "InstitutionID", how = 'left', verbose = 0)
+
+    ## first construct grid (expand institution-exhibition link to institution year (fill gaps)):
+    ## all possible combinations with full join?
+    dt_af_grid <- join(dt_af_exhbs_pmdb[!is.na(begin_year), .(begin_year = min(begin_year):max(begin_year)),
+                          .(InstitutionID, PMDB_ID, iso3c)], # AF data
+                       dt_pmyear_size[, .(ID, year, iso3c)],
[…]

### 2024-04-05 texts/paper_closing.tex
update tables after lagging and yeeting size models
one PM is gone (man, slfID museum, in europe),
compare dt_pmx to dt_pmcpct -> ID == 381
is due to closing in 1990 (when AF starts), but now AN is lagged, so
1990 value becomes NA -> museum dropped -> all good

--- 2024-03-27 texts/paper_closing.tex
@@
-% Created 2024-03-20 wo 16:51
+% Created 2024-04-04 do 20:38
 % Intended LaTeX compiler: pdflatex
@@
 
-% latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Wed Mar  6 21:27:16 2024
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Thu Apr  4 20:37:25 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 276 & 0.575 &  0.592 &  0.49 & 0 & 1 \\ 
-   & Gender - Female & 76 & 0.158 &  0.168 &  0.37 & 0 & 1 \\ 
-   & Gender - Couple & 128 & 0.267 &  0.240 &  0.43 & 0 & 1 \\ 
-   & Founder died & 58 & 0.121 &  0.093 &  0.29 & 0 & 1 \\ 
+ & Gender - Male & 275 & 0.574 &  0.593 &  0.49 & 0 & 1 \\ 
+   & Gender - Female & 76 & 0.159 &  0.169 &  0.37 & 0 & 1 \\ 
+   & Gender - Couple & 128 & 0.267 &  0.238 &  0.43 & 0 & 1 \\ 
+   & Founder died & 58 & 0.121 &  0.098 &  0.30 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 179 & 0.373 &  0.408 &  0.49 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 101 & 0.210 &  0.191 &  0.39 & 0 & 1 \\ 
-   & Self-Identification - Collection & 74 & 0.154 &  0.141 &  0.35 & 0 & 1 \\ 
+ & Self-Identification - Museum & 178 & 0.372 &  0.410 &  0.49 & 0 & 1 \\ 
+   & Self-Identification - Foundation & 101 & 0.211 &  0.189 &  0.39 & 0 & 1 \\ 
+   & Self-Identification - Collection & 74 & 0.154 &  0.140 &  0.35 & 0 & 1 \\ 
    & Self-Identification - Other & 126 & 0.263 &  0.261 &  0.44 & 0 & 1 \\ 
-   & Founder name in Museum name & 229 & 0.477 &  0.487 &  0.50 & 0 & 1 \\ 
-   & MOW inclusion & 91 & 0.190 &  0.296 &  0.46 & 0 & 1 \\ 
-   & AN Ranking - Not Included &  &  &  0.794 &  0.40 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  &  0.149 &  0.36 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  &  0.057 &  0.23 & 0 & 1 \\ 
-   & PC1 (Size) &  &  &  0.344 &  4.26 & -6.2 & 13.90 \\ 
-   & PC2 (Support) &  &  & -0.046 &  1.99 & -5.6 & 6.70 \\ 
+   & Founder name in Museum name & 229 & 0.478 &  0.488 &  0.50 & 0 & 1 \\ 
+   & MOW inclusion & 91 & 0.190 &  0.304 &  0.46 & 0 & 1 \\ 
+   & AN Ranking - Not Included &  &  &  0.797 &  0.40 & 0 & 1 \\ 
+   & AN Ranking - Included &  &  &  0.150 &  0.36 & 0 & 1 \\ 
+   & AN Ranking - Dropped &  &  &  0.054 &  0.23 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density &  &  & 20.541 & 18.37 & 1 & 62 \\ 
-   & Pop. (millions) within 10km &  &  &  1.382 &  1.74 & 0.000087 & 10.81 \\ 
-   & Nbr PM within 10km &  &  &  2.681 &  2.97 & 1 & 16 \\ 
-   & Europe and North America & 313 & 0.652 &  0.645 &  0.48 & 0 & 1 \\ 
+ & PM density &  &  & 20.889 & 18.49 & 1 & 62 \\ 
+   & Pop. (millions) within 10km &  &  &  1.378 &  1.74 & 0.000087 & 10.81 \\ 
+   & Nbr PM within 10km &  &  &  2.707 &  2.99 & 1 & 16 \\ 
+   & Europe and North America & 312 & 0.651 &  0.645 &  0.48 & 0 & 1 \\ 
    & Region - Africa & 7 & 0.015 &  0.012 &  0.11 & 0 & 1 \\ 
-   & Region - Asia & 128 & 0.267 &  0.281 &  0.45 & 0 & 1 \\ 
-   & Region - Europe & 242 & 0.504 &  0.502 &  0.50 & 0 & 1 \\ 
+   & Region - Asia & 128 & 0.267 &  0.282 &  0.45 & 0 & 1 \\ 
+   & Region - Europe & 241 & 0.503 &  0.501 &  0.50 & 0 & 1 \\ 
    & Region - Latin America & 22 & 0.046 &  0.042 &  0.20 & 0 & 1 \\ 
-   & Region - North America & 71 & 0.148 &  0.144 &  0.35 & 0 & 1 \\ 
+   & Region - North America & 71 & 0.148 &  0.143 &  0.35 & 0 & 1 \\ 
    & Region - Oceania & 10 & 0.021 &  0.019 &  0.14 & 0 & 1 \\ 
@@
 
-Overall the entire life span, the average hazard rate is 0.79\%, which allows comparison to other studies of NPO closure.
+Overall the entire life span, the average hazard rate is 0.78\%, which allows comparison to other studies of NPO closure.
 While after very cursory search of the literature I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations (see table \ref{tbl:litreview}).
@@
 
-% latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Wed Mar  6 21:27:26 2024
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Thu Apr  4 20:37:33 2024
 \begin{table}[ht]
@@
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .42 \; (0.37) \\ 
-   & Gender - Couple & .66 \; (0.38) \\ 
-   & Founder died & 1.33 \; (0.55)^{*} \\ 
+ & Gender - Female & .20 \; (0.36) \\ 
+   & Gender - Couple & .12 \; (0.37) \\ 
+   & Founder died & .21 \; (0.54) \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .94 \; (0.50) \\ 
-   & Self-Identification - Collection & .07 \; (0.60) \\ 
-   & Self-Identification - Other & 1.16 \; (0.39)^{**} \\ 
-   & AN Ranking - Included & .33 \; (0.43) \\ 
-   & AN Ranking - Dropped & 1.26 \; (0.49)^{*} \\ 
-   & Founder name in Museum name & -.57 \; (0.33) \\ 
-   & MOW inclusion & -.28 \; (0.41) \\ 
-   & PC1 (Size) & -.34 \; (0.06)^{***} \\ 
-   & PC2 (Support) & -.11 \; (0.11) \\ 
+ & Self-Identification - Foundation & .84 \; (0.48) \\ 
+   & Self-Identification - Collection & .46 \; (0.58) \\ 
+   & Self-Identification - Other & 1.34 \; (0.38)^{***} \\ 
+   & AN Ranking - Included & .64 \; (0.38) \\ 
+   & AN Ranking - Dropped & .87 \; (0.53) \\ 
+   & Founder name in Museum name & -.27 \; (0.33) \\ 
+   & MOW inclusion & -.84 \; (0.40)^{*} \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
@@
    & PM density$^{2}$ & .00 \; (0.00) \\ 
-   & Pop. (millions) within 10km & .00 \; (0.11) \\ 
-   & Nbr PM within 10km & .13 \; (0.06)^{*} \\ 
+   & Pop. (millions) within 10km & .02 \; (0.11) \\ 
+   & Nbr PM within 10km & .12 \; (0.06)^{*} \\ 
    \hline
- & Museum-years & 6903 \\ 
-   & Closures & 53 \\ 
-   & log. Likelihood & -236.48 \\ 
-   & AIC & 504.96 \\ 
-   & BIC & 536.48 \\ 
+ & Museum-years & 6423 \\ 
+   & Closures & 52 \\ 
+   & log. Likelihood & -257.05 \\ 
+   & AIC & 542.09 \\ 
+   & BIC & 569.41 \\ 
    \hline 

### 2024-04-07 texts/paper_closing.tex
decide on regional density specification (count + count-popm interaction)
aslo add predicted avg hazard for different proxcnt10/popm_circle10 situations

@@
-% Created 2024-04-04 do 20:38
+% Created 2024-04-07 zo 14:03
 % Intended LaTeX compiler: pdflatex
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Apr  4 20:37:25 2024
+% Sun Apr  7 12:05:30 2024
 \begin{table}[ht]
@@
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density &  &  & 20.889 & 18.49 & 1 & 62 \\ 
-   & Pop. (millions) within 10km &  &  &  1.378 &  1.74 & 0.000087 & 10.81 \\ 
-   & Nbr PM within 10km &  &  &  2.707 &  2.99 & 1 & 16 \\ 
+ & PM density (country) &  &  &   0.411 &   1.23 & 0.00077 & 27.26 \\ 
+   & Pop. (millions) within 10km &  &  &   1.322 &   1.69 & 0.000087 & 10.81 \\ 
+   & Pop. (millions) country &  &  & 156.197 & 287.82 & 0.037 & 1412.36 \\ 
+   & Nbr PM within 10km &  &  &   1.601 &   2.97 & 0 & 15 \\ 
+   & PM density (10km) &  &  &   1.423 &   4.01 & 0 & 41.85 \\ 
    & Europe and North America & 312 & 0.651 &   0.645 &   0.48 & 0 & 1 \\ 
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Apr  4 20:37:33 2024
+% Sun Apr  7 12:05:38 2024
 \begin{table}[ht]
@@
   \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
  \hline
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .20 \; (0.36) \\ 
-   & Gender - Couple & .12 \; (0.37) \\ 
-   & Founder died & .21 \; (0.54) \\ 
+ & Gender - Female & .22 \; (0.37) \\ 
+   & Gender - Couple & .14 \; (0.36) \\ 
+   & Founder died & .28 \; (0.53) \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .84 \; (0.48) \\ 
-   & Self-Identification - Collection & .46 \; (0.58) \\ 
-   & Self-Identification - Other & 1.34 \; (0.38)^{***} \\ 
-   & AN Ranking - Included & .64 \; (0.38) \\ 
-   & AN Ranking - Dropped & .87 \; (0.53) \\ 
-   & Founder name in Museum name & -.27 \; (0.33) \\ 
-   & MOW inclusion & -.84 \; (0.40)^{*} \\ 
+ & Self-Identification - Foundation & .71 \; (0.48) \\ 
+   & Self-Identification - Collection & .14 \; (0.59) \\ 
+   & Self-Identification - Other & 1.32 \; (0.38)^{***} \\ 
+   & AN Ranking - Included & .50 \; (0.38) \\ 
+   & AN Ranking - Dropped & .82 \; (0.52) \\ 
+   & Founder name in Museum name & -.35 \; (0.33) \\ 
+   & MOW inclusion & -.90 \; (0.40)^{*} \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density & -.05 \; (0.03) \\ 
-   & PM density$^{2}$ & .00 \; (0.00) \\ 
-   & Pop. (millions) within 10km & .02 \; (0.11) \\ 
-   & Nbr PM within 10km & .12 \; (0.06)^{*} \\ 
+ & PM density (country) & .56 \; (0.42) \\ 
+   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .29 \; (0.11)^{**} \\ 
+   & Nbr PM within 10km & .30 \; (0.09)^{***} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
    \hline
@@
    & Closures & 52 \\ 
-   & log. Likelihood & -257.05 \\ 
-   & AIC & 542.09 \\ 
-   & BIC & 569.41 \\ 
+   & log. Likelihood & -253.41 \\ 
+   & AIC & 536.82 \\ 
+   & BIC & 566.09 \\ 
    \hline 

### 2024-04-07 scripts/cfg.R

@@ -19,7 +19,7 @@ gc_tbls <- function(c_tblargs) {
             input_data = quote(mtcars),
             caption = "this is a great test table"),
         t_coxzph = list(
-            rx = quote(l_mdls$r_more),
+            rx = quote(l_mdls$r_pop4),
             caption = "Z-test of proportional hazards"),
         t_reg_coxph = list(
             l_mdls = quote(l_mdls),
@@ -121,11 +121,14 @@ gc_plts <- function() {
             width = 19,
             height = 12),
         p_coxphdiag_more = list(
-            rx = quote(l_mdls$r_more),
+            rx = quote(l_mdls$r_pop4),
             caption = "Model Diagnostics",
             width = 19,
-            height = 25
-            )        
+            height = 25),
+        p_pred_popprxcnt = list(
+            caption = "Predicted Avg. Hazard Rate on Regional PM Density and Population",
+            width = 18,
+            height = 8)
     )
 
     ## check that there are no duplicate 
@@ -170,18 +173,23 @@ gc_vvs <- function() {
     ## group variables thematically, add also labels
 
     l_vrbl_lbls <- list( # variable labels
-        gender               = "Founder Gender",
-        founder_dead         = "Founder died",
-        slfidfcn             = "Self- Identification",
-        muem_fndr_name       = "Founder name in Museum name",
-        mow                  = "MOW inclusion",
-        pm_dens              = "PM density",
-        "I(pm_dens^2)"       = "PM density^2",
-        pop                  = "Pop. (millions) within 10km",
-        proxcnt10            = "Nbr PM within 10km",
-        west                 = "Europe and North America",
-        reg6                 = "Region",
-        an_inclusion         = "ArtNews Ranking inclusion",
+        gender                    = "Founder Gender",
+        founder_dead              = "Founder died",
+        slfidfcn                  = "Self- Identification",
+        muem_fndr_name            = "Founder name in Museum name",
+        mow                       = "MOW inclusion",
[…]

### 2024-04-07 scripts/closing_main.R

@@ -25,6 +25,10 @@ library(furrr)       # parallel processing
 library(splines)     # for gp_schoenfeld, maybe neeeded later too for regressions
 library(texreg, include.only = c("screenreg", "texreg")) ## inspection of results
 library(Hmisc, include.only = "latexTranslate")  # latexTranslate
+library(wpp2022)     # population data for Taiwan
+data(pop1dt) # population data for taiwan
+library(khroma)      # plotting
+
 
 ## LOCS <- list(PROJDIR = "/home/johannes/Dropbox/phd/papers/closing/")
 ## LOCS$FIGDIR <- paste0(FIG
@@ -101,7 +105,7 @@ gt_coxzph <- function(rx) {
     coxzph_trfms <- list(km = "Kaplan-Meier", identity = "Identity", rank = "Rank")
 
     ## generate the actual data
-    dt_coxzph_prep <- map(names(coxzph_trfms), ~cox.zph(l_mdls$r_more, terms = F, transform = .x) %>%
+    dt_coxzph_prep <- map(names(coxzph_trfms), ~cox.zph(rx, terms = F, transform = .x) %>%
                                                    chuck("table") %>% adt(keep.rownames = "term") %>%
                                                    .[, src := .x]) %>% list_rbind %>%
                       .[, .(term, src, p)]
@@ -367,15 +371,12 @@ if ("memoised" %!in% class(gd_mow_info)) {
 
 END_YEAR <- 2021
 
-
-
 ## actual pm data
 ## l_pca_dimred <- gl_pca_dimred(dt_pmdb)
 ## l_pca_dimred_woclosed <- gl_pca_dimred(dt_pmdb[museum_status != "closed"])
 
 dt_pmx <- gd_pmx(dt_pmdb) # extract of main variables
 dt_pmtiv <- gd_pmtiv(dt_pmx) # time invariant variables
-
 
 
 dt_pmyear_prep <- gd_pmyear_prep(dt_pmx, dt_pmtiv) # combine all data sources, as complete as possible
@@ -386,14 +387,14 @@ dt_pmcpct <- gd_pmcpct(dt_pmyear) # time-invariant variables (UoA PM, not pm-yea
 
[…]

### 2024-04-07 scripts/regression.R

@@ -152,7 +152,7 @@ gd_pmdb_popcircle <- function(dt_pmx, radius_km) {
     ## process results
     ## year5 needs to be re-assigned as int probably since future_imap's .y converts it to string
     dt_popres2 <- rbindlist(l_popres)[, `:=`(year5 = as.integer(year), year = NULL)] %>%
-        .[, pop := pop/1e6]
+        .[, popm_circle10 := pop/1e6] %>% .[, pop := NULL]
 
     ## merge to yearly data
     dt_popcircle <- join(dt_pmyear_popprep, dt_popres2, on = c("ID", "year5"))
@@ -276,6 +276,20 @@ gd_pmx <- function(dt_pmdb) {
 }
 
     
+gd_pop <- function() {
+    #' generate population data from WB and UN
+    dt_pop_wb <- gd_WB(c("SP.POP.TOTL"), DIR_WBproc = c_dirs$data) %>%
+        .[, popm_country := SP.POP.TOTL/1e6] %>% .[, SP.POP.TOTL := NULL]
+
+    ## for Taiwan use wpp2022 (https://github.com/PPgp/wpp2022)
+    dt_pop_un <- pop1dt[country_code == 158] %>%
+        .[, .(iso3c = "TWN", country = "Taiwan", year, popm_country = pop/1e3)]
+    
+    dt_pop <- rbind(dt_pop_wb, dt_pop_un)
+    return(dt_pop)
+}
+
+
 
 gd_pmyear_prep <- function(dt_pmx, dt_pmtiv) {
     gw_fargs(match.call())
@@ -292,14 +306,24 @@ gd_pmyear_prep <- function(dt_pmx, dt_pmtiv) {
         .[, age := year - year_opened] %>% # set age
         ## founder death: 1 if year > deathyear, else 0 (before death or not dead at all)
         .[, founder_dead := fifelse(!is.na(deathyear),fifelse(year > deathyear, 1, 0), 0)] %>% 
-        .[, `:=`(tstart = age, tstop = age+1)] %>% # set survival time interval variables
-        .[, pm_dens := .N, .(iso3c, year)] # calculate PM density 
+        .[, `:=`(tstart = age, tstop = age+1)] # set survival time interval variables
+        
 
+    ## get country population data
+    dt_pop_country <- gd_pop()
+
+    ## calculate PM country density
+    dt_pmyear_wpop_country <- join(dt_pmyear, dt_pop_country, on = c("iso3c", "year"),
[…]

### 2024-04-10 texts/paper_closing.tex
update text sent to olav/alex some days ago

--- 2024-04-05 texts/paper_closing.tex
@@
-% Created 2024-04-04 do 20:38
+% Created 2024-04-07 zo 17:21
 % Intended LaTeX compiler: pdflatex
@@
 \setlength{\parindent}{1.2cm}
-\author{Johannes }
+\author{Johannes Aengenheyster}
 \date{\today}
@@
 \hypersetup{
- pdfauthor={Johannes },
+ pdfauthor={Johannes Aengenheyster},
  pdftitle={},
@@
 \section*{Identity and the closure of private art museums}
+\label{sec:org16a7685}
 
 \subsection*{Introduction}
+\label{sec:orgef6a080}
 
@@
 
-A number of findings highlight the role of identity in the process of private museum closure. 
-First, I find that museums which are recognized by an international museum database are less likely to close than those which are not.
-Secondly, the results furthermore indicate that museums with more ambiguous names are more likely to close.
-Both these findings possibly indicate that adherence to museum standards enhances legitimacy, which in turn improves survival prospects.
-Finally, founder reputation, in particular its loss, is found to be substantial as museums whose founders are dropped from a collector ranking are more likely to close than museums whose founders both are and are not included.
+\subsection*{Theoretical framework}
+\label{sec:org90170ed}
 
-\bigbreak
-\noindent
-\textbf{keywords}: museum, closure, identity
-
-\subsection*{Theoretical framework}
+As a substantial literature on organizational survival exists,
 
 \subsubsection*{Identity and the survival prospects of non-profit organizations}
-
+\label{sec:org8725d02}
 An identity that is legitimate (understandable) and favorable (positive) has been shown to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
@@
 However, other studies find limited impact of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
-Thus, even while this study cannot conclusively answer the overall link between idenity and survival, it nevertheless contributes insights into which dimensions of organizational identity do, and which do not contribute to survival in a particular organizational population; namely that of private art museums.
-
 Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
@@
 
-\subsubsection*{Other predictors of organizational survival}
-
-\paragraph*{Age}
-
-The age of an organization is considered in different ways to be related to closing.
-What started with liability of newness \parencite{Stinchcombe_1965_structure}, which posited that organizational mortality decreases over time due to acquisition of capabilities and connections, has lead to a number of extensions \parencite{Carroll_Khessina_2019_demography,Hannan_1998_mortality}:
-Liability of adolescence argues that shortly after foundings organizations can still draw on endowments, the expiration of which leads to a peak of mortality some time after opening.
-While according to this view mortality still decreases after the peak as the organization becomes more established, other perspectives argue also for a positive relationship between age and mortality:
-According to the liability of obsolescence paradigm the environment changes faster than organizations which are seen as relatively constrained by inertia, which therefore leads to declining fitness and survival chances.
-Similar, according to "liability of senescence" capabilities/routines/coalitions can constrain the actions of organizations.
-Given such conflicting predictions, \textcite{Carroll_Khessina_2019_demography} propose to model age dependence with piece-wise constant hazard models (rather than parametric models) to estimate age-specific effects which can, but do not have to, indicate a relationship between age and mortality.
-
-\paragraph*{Organizational transformation}
-
+\subsubsection*{Organizational transformation}
+\label{sec:org19d4baf}
 \textcite{Carroll_Khessina_2019_demography} argue that transformation of core features of organizations such as changes in technology or authority can have divergent consequences. 
@@
 \noindent
+\textbf{Hypothesis 2}: A private museum is more likely to close after the death of the founder.
+
+\subsubsection*{Competition}
+\label{sec:org9840956}
+
+needs to write out: 
+\begin{itemize}
+\item \cite{Hager_1999_demise}:
+\begin{itemize}
+\item p.173: Ten organizations cited an inability to compete as a proximate cause for closure, making it the most popular proximate cause of organizational closure.
+\item p.173: Both [art organizations] noted that the majority of the community’s arts dollars, both individual donations/subscriptions and community and corporate grants, tended to go to the singular, most reputable arts organizations of their types (e.g.
+museums, orchestras, dance troupes) in the metro area.
+Other arts organizations faced strong competitive pressures from these flagship organizations, a factor which caused the demise of Organizations 276 and 293
+\end{itemize}
+\item \cite{Lecy_2010_nonprofit}:
+\begin{itemize}
+\item p.27: The analysis shows that a period of rapid sector expansion – a period where many additional resources are being poured into the sector – creates a more competitive environment as evidenced by higher rates of organizational mortality.
+\end{itemize}
+\item \cite{Park_Shon_Lu_2021_mortality}
+\begin{itemize}
+\item p.844: Furthermore, nonprofits that run their business in a county with greater organizational density and population size are more likely to dissolve, which implies that competition, as well as demand for service, prevents nonprofits from surviving
+\end{itemize}
+\item \cite{HernandezOrtiz_2022_discontinuity}
+\begin{itemize}
+\item p.116:  A crowded niche increased the competition and limited their access to resources and clients.
+As reported by informant of organization \#C07: "Well, there was less money to go around and more organizations seeking the money.
+Here we have the same, the same group of people that were supporting the organization, you know, donating to it and that only goes so far.
+So, we had a full-time grant writer, we were always applying for grants.
+But there are so many organizations applying for the same grants".
+(P31, Pos.
+49-51)
+\end{itemize}
+\item \cite{Lu_Shon_Zhang_2019_dissolution}
+\begin{itemize}
+\item p.43: For example, nonprofits operating in a more competitive environment with a higher degree of organizational density would experience a higher chance of dissolution.
+\end{itemize}
+\item \cite{Haugh_etal_2021_nascent}:
+\begin{itemize}
+\item p.1227: SEs are likely to compete with non-profit organizations for grants,donations, and programme-related investments.
+Second,both SEs and non-profit organizations serve the disadvantaged and socially excluded and thus may also compete for service users.
+Although collaboration between SEs and charities could increase the supply of services to those in need (Smiddy 2010), they compete with each other for resources and beneficiaries.
+The more similar the resource needs and markets served, the greater the competition between the organizational forms (Baum and Haveman 1997).
+Hence, the population density ofregistered non-profit organizations will thus have a detrimental effect on SE survival.
+\end{itemize}
+\end{itemize}
+
+\textbf{Hypothesis 3}: A private museum is more likely to close in a more competitive environment.
+
+\subsubsection*{Other predictors of organizational survival}
+\label{sec:org9672c62}
+\paragraph*{Age}
+\label{sec:orgae2e32a}
+
+The age of an organization is considered in different ways to be related to closing.
+What started with liability of newness \parencite{Stinchcombe_1965_structure}, which posited that organizational mortality decreases over time due to acquisition of capabilities and connections, has lead to a number of extensions \parencite{Carroll_Khessina_2019_demography,Hannan_1998_mortality}:
+Liability of adolescence argues that shortly after foundings organizations can still draw on endowments, the expiration of which leads to a peak of mortality some time after opening.
+While according to this view mortality still decreases after the peak as the organization becomes more established, other perspectives argue also for a positive relationship between age and mortality:
+According to the liability of obsolescence paradigm the environment changes faster than organizations which are seen as relatively constrained by inertia, which therefore leads to declining fitness and survival chances.
+Similar, according to "liability of senescence" capabilities/routines/coalitions can constrain the actions of organizations.
+Given such conflicting predictions, \textcite{Carroll_Khessina_2019_demography} propose to model age dependence with piece-wise constant hazard models (rather than parametric models) to estimate age-specific effects which can, but do not have to, indicate a relationship between age and mortality.
 
 \subsection*{Data and Methods}
+\label{sec:org6923afe}
 
 \subsubsection*{Dependent Variable}
-
+\label{sec:org7efae3c}
 A newly constructed database, assembled from different sources,  is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
@@
 
-\subsubsection*{Main Predictors: Identity Measures}
-
-The organizational identity of a museum is measured primarily in terms of its legitimacy, i.e. its adherence to museum standards, and reputation of its founders.
+\subsubsection*{Main Predictors}
+\label{sec:orge0e80eb}
 
 \paragraph*{Legitimacy}
+\label{sec:org9952eec}
 
@@
 \paragraph*{Reputation}
+\label{sec:org051c5db}
 
@@
 For each year, a museums can have one of three values: "Not included"; in which case the founder is not included in the year in question and has not been so in the past, "Included"; when the founder is included, or "Dropped", for cases where the founder was included at some point in the past but is no longer included in the current year.
-Cases where multiple individuals are involved in the founding of a private museum are resolved by aggregating the Artnews ranking inclusion history to the founder founder level (i.e., if one of two founders is dropped from the Artnews ranking but the other remains included, the founder couple as a whole is considered included).
+Cases where multiple individuals are involved in the founding of a private museum are resolved by aggregating the Artnews ranking inclusion history to the founder level (i.e., if only one of two founders is dropped from the Artnews ranking but the other remains included, the founder couple as a whole is considered included).
+The variable is lagged by one year to avoid reverse causality, i.e.
+to exclude the possibility that an association is observed which is present due to founders being dropped from the ranking as a consequence of the closure of their museum.
+
+\paragraph*{Organizational transformation}
+\label{sec:org671fa45}
+A measure of founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder.
+
+\paragraph*{Competition}
+\label{sec:orgc059910}
+On a national level, density of private museum is calculated as the number of private museums per million.
+On a local level, I use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
+To be able to estimate both competition and demand/audience/population separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two.
 
 \subsubsection*{Control variables}
+\label{sec:org4412539}
 
@@
 On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
-Organizational transformation, such as change of authority has been to increase chances of closure both generally \parencite{Carroll_Khessina_2019_demography} and in the case of private museums specifically (\cite[p.234]{Walker_2019_collector}: "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museum indefinitely").
-Therefore, a measure of founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder. 
 Centrality of the founder's vision is measured via the proxy of whether the name of the founder is included in the name of the museum.
 
-Furthermore, organizational theory \parencite{hannan89_organ} predicts a U-shaped relationship between density and mortality:
-While at low levels, increases in the number of organizations are argued to primarily increase legitimacy and lower exit rates, increases at higher numbers increase the competition over resources and thereby raise mortality rates.
-On the level of the environment, therefore the density (number) of private museum per country is included both in linear and squared form.
+\subsubsection*{Analytical framework}
+\label{sec:orge4889f4}
 
-\subsubsection*{Analytical framework}
-
-First, we investigate the relationship between age and closing descriptively using hazard rates and the Kaplan-Meier survival function.
+First, I investigate the relationship between age and closing descriptively using hazard rates and the Kaplan-Meier survival function.
 This non-parametric method estimates the hazard rate as the conditional probability of exiting at time t\textsubscript{i} given being alive as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at time \(t_i\) and \(d_i\) as the number of exits at time \(t_i\)), and the survival function as the product of these conditional probabilities as \(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\).
@@
 \subsection*{Results}
+\label{sec:org9e38ff3}
 
 \subsubsection*{Summary statistics}
+\label{sec:org12efa6c}
 
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Apr  4 20:37:25 2024
+% Sun Apr  7 12:05:30 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 275 & 0.574 &  0.593 &  0.49 & 0 & 1 \\ 
-   & Gender - Female & 76 & 0.159 &  0.169 &  0.37 & 0 & 1 \\ 
-   & Gender - Couple & 128 & 0.267 &  0.238 &  0.43 & 0 & 1 \\ 
-   & Founder died & 58 & 0.121 &  0.098 &  0.30 & 0 & 1 \\ 
+ & Gender - Male & $275$ & $0.574$ & $  0.593$ & $  0.49$ & $0$ & $1$ \\ 
+   & Gender - Female & $76$ & $0.159$ & $  0.169$ & $  0.37$ & $0$ & $1$ \\ 
+   & Gender - Couple & $128$ & $0.267$ & $  0.238$ & $  0.43$ & $0$ & $1$ \\ 
+   & Founder died & $58$ & $0.121$ & $  0.098$ & $  0.30$ & $0$ & $1$ \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 178 & 0.372 &  0.410 &  0.49 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 101 & 0.211 &  0.189 &  0.39 & 0 & 1 \\ 
-   & Self-Identification - Collection & 74 & 0.154 &  0.140 &  0.35 & 0 & 1 \\ 
-   & Self-Identification - Other & 126 & 0.263 &  0.261 &  0.44 & 0 & 1 \\ 
-   & Founder name in Museum name & 229 & 0.478 &  0.488 &  0.50 & 0 & 1 \\ 
-   & MOW inclusion & 91 & 0.190 &  0.304 &  0.46 & 0 & 1 \\ 
-   & AN Ranking - Not Included &  &  &  0.797 &  0.40 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  &  0.150 &  0.36 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  &  0.054 &  0.23 & 0 & 1 \\ 
+ & Self-Identification - Museum & $178$ & $0.372$ & $  0.410$ & $  0.49$ & $0$ & $1$ \\ 
+   & Self-Identification - Foundation & $101$ & $0.211$ & $  0.189$ & $  0.39$ & $0$ & $1$ \\ 
+   & Self-Identification - Collection & $74$ & $0.154$ & $  0.140$ & $  0.35$ & $0$ & $1$ \\ 
+   & Self-Identification - Other & $126$ & $0.263$ & $  0.261$ & $  0.44$ & $0$ & $1$ \\ 
+   & Founder name in Museum name & $229$ & $0.478$ & $  0.488$ & $  0.50$ & $0$ & $1$ \\ 
+   & MOW inclusion & $91$ & $0.190$ & $  0.304$ & $  0.46$ & $0$ & $1$ \\ 
+   & AN Ranking - Not Included & $NA$ & $NA$ & $  0.797$ & $  0.40$ & $0$ & $1$ \\ 
+   & AN Ranking - Included & $NA$ & $NA$ & $  0.150$ & $  0.36$ & $0$ & $1$ \\ 
+   & AN Ranking - Dropped & $NA$ & $NA$ & $  0.054$ & $  0.23$ & $0$ & $1$ \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density &  &  & 20.889 & 18.49 & 1 & 62 \\ 
-   & Pop. (millions) within 10km &  &  &  1.378 &  1.74 & 0.000087 & 10.81 \\ 
-   & Nbr PM within 10km &  &  &  2.707 &  2.99 & 1 & 16 \\ 
-   & Europe and North America & 312 & 0.651 &  0.645 &  0.48 & 0 & 1 \\ 
-   & Region - Africa & 7 & 0.015 &  0.012 &  0.11 & 0 & 1 \\ 
-   & Region - Asia & 128 & 0.267 &  0.282 &  0.45 & 0 & 1 \\ 
-   & Region - Europe & 241 & 0.503 &  0.501 &  0.50 & 0 & 1 \\ 
-   & Region - Latin America & 22 & 0.046 &  0.042 &  0.20 & 0 & 1 \\ 
-   & Region - North America & 71 & 0.148 &  0.143 &  0.35 & 0 & 1 \\ 
-   & Region - Oceania & 10 & 0.021 &  0.019 &  0.14 & 0 & 1 \\ 
+ & PM density (country) & $NA$ & $NA$ & $  0.411$ & $  1.23$ & $0.00077$ & $27.26$ \\ 
+   & Pop. (millions) within 10km & $NA$ & $NA$ & $  1.322$ & $  1.69$ & $0.000087$ & $10.81$ \\ 
+   & Pop. (millions) country & $NA$ & $NA$ & $156.197$ & $287.82$ & $0.037$ & $1412.36$ \\ 
+   & Nbr PM within 10km & $NA$ & $NA$ & $  1.601$ & $  2.97$ & $0$ & $15$ \\ 
+   & PM density (10km) & $NA$ & $NA$ & $  1.423$ & $  4.01$ & $0$ & $41.85$ \\ 
+   & Europe and North America & $312$ & $0.651$ & $  0.645$ & $  0.48$ & $0$ & $1$ \\ 
+   & Region - Africa & $7$ & $0.015$ & $  0.012$ & $  0.11$ & $0$ & $1$ \\ 
+   & Region - Asia & $128$ & $0.267$ & $  0.282$ & $  0.45$ & $0$ & $1$ \\ 
+   & Region - Europe & $241$ & $0.503$ & $  0.501$ & $  0.50$ & $0$ & $1$ \\ 
+   & Region - Latin America & $22$ & $0.046$ & $  0.042$ & $  0.20$ & $0$ & $1$ \\ 
+   & Region - North America & $71$ & $0.148$ & $  0.143$ & $  0.35$ & $0$ & $1$ \\ 
+   & Region - Oceania & $10$ & $0.021$ & $  0.019$ & $  0.14$ & $0$ & $1$ \\ 
    \hline
@@
 \subsubsection*{Hazard rate and Age Dependence}
+\label{sec:org01e6edd}
 
@@
 \centering
-\includegraphics[width=16cm]{../figures/p_hazard.pdf}
+\includegraphics[width=16cm]{../figures/p_hazard.png}
 \caption{\label{fig:p_hazard}Private Museum hazard function}
@@
 \centering
-\includegraphics[width=14cm]{../figures/p_surv.pdf}
+\includegraphics[width=14cm]{../figures/p_surv.png}
 \caption{\label{fig:p_surv}Private Museum Survival probability}
@@
 Overall the entire life span, the average hazard rate is 0.78\%, which allows comparison to other studies of NPO closure.
-While after very cursory search of the literature I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations (see table \ref{tbl:litreview}).
+While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})
 
 \begin{table}[htbp]
-\caption{\label{tbl:litreview}Hazard rates in studies of museums and other non-profits}
+\caption{\label{tbl:litreview}Hazard rates in studies of museums art Art NPOs}
+\centering
+\begin{tabular}{llll}
+\hline
+study & population & avg. hazard rate & org years\\
+\hline
+\cite{Hager_2001_vulnerability} & Art Museums & 2.4\% & \\
+\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\% & \\
+\hline
+\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\% & \\
+\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\% & \\
+\hline
+\end{tabular}
+\end{table}
+
+\textcite{Hager_2001_vulnerability} and \textcite{Gordon_etal_2013_insolvency} both study NPOs more generally, but report survival estimates by organizational form.
+Both these studies also report substantial variation in hazard rates between organizational forms.
+While these comparisons indicate that private museums have dissolution rates lower or similar to museums and non-profit organizations generally, more research is needed to establish the comparability of these hazard rates.
+
+Comparison to other forms of nonprofit organizations reported by \parencite{Gordon_etal_2013_insolvency}
+places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
+While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.78\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
+It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
+In fact, lower dissolution rates are only reported for historical societies (0.5\%) and libraries (0.2\%).
+
+\begin{table}[htbp]
+\caption{\label{tbl:litreview2}Hazard rates in studies of NPOs}
 \centering
@@
 \hline
-\cite{Hager_2001_vulnerability} & Art Museums & 2.4\% & IRS\\
-\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\% & IRS\\
-\hline
-\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\% & IRS\\
-\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\% & IRS\\
-\cite{Gordon_etal_2013_insolvency} & all NPOs & 1.58\% & IRS\\
+\cite{Gordon_etal_2013_insolvency} & NPOs & 1.58\% & IRS\\
 \cite{Hager_Galaskiewicz_Larson_2007_liability} & NPOs & 1.25\% & own data\\
 \cite{Clifford_2018_reinforcing} & Charities & 2\%-5\% & Reg. of Charities (UK)\\
-\cite{Mayer_2022_slimmer} & NPOs & 0.17\% & IRS\\
+\cite{Mayer_2022_slimmer} & public charities & 0.17\% & IRS\\
 \hline
@@
 
-\textcite{Hager_2001_vulnerability} and \textcite{Gordon_etal_2013_insolvency} both study NPOs more generally, but report survival estimates by organizational form.
-At the moment it is not clear which factors account for their hazard rates to differ substantially, but it might be due to selection criteria.
-Both these studies also report substantial variation in hazard rates between organizational forms.
-While preliminary results indicate that private museums have dissolution rates lower or similar to museums and non-profit organizations generally, more research is needed to establish the comparability of these hazard rates.
-
 \subsubsection*{Regression Results}
+\label{sec:org4878b83}
 
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Apr  4 20:37:33 2024
+% Sun Apr  7 15:01:01 2024
 \begin{table}[ht]
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
+\begin{tabular}{p{0mm}ll}
   \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
  \hline
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .20 \; (0.36) \\ 
-   & Gender - Couple & .12 \; (0.37) \\ 
-   & Founder died & .21 \; (0.54) \\ 
+ & Gender - Female & $.22 \; (0.37)$ \\ 
+   & Gender - Couple & $.14 \; (0.36)$ \\ 
+   & Founder died & $.28 \; (0.53)$ \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .84 \; (0.48) \\ 
-   & Self-Identification - Collection & .46 \; (0.58) \\ 
-   & Self-Identification - Other & 1.34 \; (0.38)^{***} \\ 
-   & AN Ranking - Included & .64 \; (0.38) \\ 
-   & AN Ranking - Dropped & .87 \; (0.53) \\ 
-   & Founder name in Museum name & -.27 \; (0.33) \\ 
-   & MOW inclusion & -.84 \; (0.40)^{*} \\ 
+ & Self-Identification - Foundation & $.71 \; (0.48)$ \\ 
+   & Self-Identification - Collection & $.14 \; (0.59)$ \\ 
+   & Self-Identification - Other & $1.32 \; (0.38)^{***}$ \\ 
+   & AN Ranking - Included & $.50 \; (0.38)$ \\ 
+   & AN Ranking - Dropped & $.82 \; (0.52)$ \\ 
+   & Founder name in Museum name & $-.35 \; (0.33)$ \\ 
+   & MOW inclusion & $-.90 \; (0.40)^{*}$ \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density & -.05 \; (0.03) \\ 
-   & PM density$^{2}$ & .00 \; (0.00) \\ 
-   & Pop. (millions) within 10km & .02 \; (0.11) \\ 
-   & Nbr PM within 10km & .12 \; (0.06)^{*} \\ 
+ & PM density (country) & $.56 \; (0.42)$ \\ 
+   & PM density$^{2}$ (country) & $-.02 \; (0.02)$ \\ 
+   & Pop. (millions) within 10km & $.29 \; (0.11)^{**}$ \\ 
+   & Nbr PM within 10km & $.30 \; (0.09)^{***}$ \\ 
+   & Nbr PM (10km) * Pop (10km) & $-.10 \; (0.04)^{**}$ \\ 
    \hline
- & Museum-years & 6423 \\ 
-   & Closures & 52 \\ 
-   & log. Likelihood & -257.05 \\ 
-   & AIC & 542.09 \\ 
-   & BIC & 569.41 \\ 
+ & Museum-years & $6423$ \\ 
+   & Closures & $52$ \\ 
+   & log. Likelihood & $-253.41$ \\ 
+   & AIC & $536.82$ \\ 
+   & BIC & $566.09$ \\ 
    \hline 
@@
 \paragraph*{Control Variables}
+\label{sec:org75141bd}
 
-Neither gender nor the death of the founder is associated with a significant difference in private museum closure.
-While there is no particular reason to expect a gender effect, the not substantially higher likelihood for a museums to close after its founder has died indicates that private museums might be less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
-
-Inclusion of founder name is not significantly associated with mortality rates.
+Neither gender nor inclusion of founder name is significantly associated with mortality rates.
 While generally organizations whose name include the name of their founder might be more centered around the founder, and hence display higher inertia, making them less able to adapt to changing environments, these results indicate that it does not seem to be case for private museums.
 
-Environmental variables show no association with mortality.
-While the density-dependence paradigm predicts a negative effect of numbers of organizations on closing rate at low numbers (due to legitimacy, i.e.
-growing familiarity with a new organizational form), and a positive effect at high numbers (due to competition over resources), neither relationship is significant in the case of private museums.
-
 \paragraph*{Identity Variables}
+\label{sec:orge692d76}
 
@@
 
-The reputation of the founder is related to closure to some extent. 
-Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (not statistically significant) and by founders who were included at some point but are no longer included (statistically significant).
-While the order of the categories does not fully correspond to the expected order, according to which museums whose collectors are not included would be more likely to close than collectors who are, it nevertheless provides some evidence that status matters; as in particular the loss of status appears to be substantially associated with museum closure.
+The reputation of the founder is not statistically related to closure. 
+Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (not statistically significant) and by founders who were included at some point but are no longer included (not statistically significant).
+
+\paragraph*{Organizational transformation}
+\label{sec:orge8aaa4f}
+
+The death of the founder is not associated with a significant difference in private museum closure, i.e. museums are not significantly more likely to close after their founder has died.
+This possibly indicates that private museums might be less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
+
+\paragraph*{Competition}
+\label{sec:orgd4359d4}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=18cm]{../figures/p_pred_popprxcnt.png}
+\caption{\label{fig:p_pred_popprxcnt}Predicted Avg. Hazard Rate on Regional PM Density and Population}
+\end{figure}
+
+Country-level Environmental variables show no association with mortality.
+However, at the local level the number of private museum and population density predicts survival chances as the main effects of population number of private museums as well as its interaction is significant.
+Figure \ref{fig:p_pred_popprxcnt} shows predicted average hazard rates for different conditions of regional PM density and population numbers.
+Museums located in sparsely populated areas have (at low PM densities) lower hazard rates than museums in more densely populated areas. 
+Furthermore, these "rural" museums see an increase in the risk of closing for each additional private museum present within 10 kilometers, whereas the risk of closing decreases with  each additional private museum in the local environment for museums in more urban areas.
 
 \subsection*{Conclusion}
-
-The conducted analysis shows a substantial association between private museum identity and closures.
-While alternative explanations cannot be completely ruled out, a clearly understandable identity and a favorable founder reputation emerge as important predictors of the chance of a private museum to close.
-Future research can expand on these findings by in more detail investigating the resource perspective of private museums, the intransparency of which has so far aggravated insights about budgetary aspects, in particular how these financial and material characteristics are moderated or mediated by processes of organizational identity.
+\label{sec:org77289d2}
+TBD
 

### 2024-04-10 scripts/cfg.R
re-integrate size PCs/dimred into pipeline: loadings based on open PMs
some other minor adjustment: yeet gc_pmdb_vrblgrps from
gl_pca_dimred (just use the actual relation column names), make
gc_pmdb_vrblgrps more verbose in case of errors

@@ -197,15 +197,15 @@ gc_vvs <- function() {
         ## exhbprop_top10_utf   = "Exh. top 10%",
         ## exhbqntl_roll        = "Exhibition Quantile (year, rolled)",
         ## "I(exhbqntl_roll^2)" = "Exhibition Quantile^2 (year, rolled)",
-        ## V1                = "PC1 (Size)",
-        ## V2                = "PC2 (Support)",
+        PC1                       = "PC1 (Size)",
+        PC2                       = "PC2 (Support)",
         GLOBAL          = "Global") # from cox.zph
     
     l_vrblgrps <- list(# variable groups
         founder  = .c(gender, founder_dead),
-        museum   = .c(slfidfcn, muem_fndr_name, mow, an_inclusion), # exhbqntl_cy),
+        museum   = .c(slfidfcn, muem_fndr_name, mow, an_inclusion, PC1, PC2), # exhbqntl_cy),
         ## exhbqntl_year, "I(exhbqntl_year^2)",
-        ## exhbprop_top10_log, exhbprop_top10_utf, exhbqntl_roll, "I(exhbqntl_roll^2)"), # V1, V2
+        ## exhbprop_top10_log, exhbprop_top10_utf, exhbqntl_roll, "I(exhbqntl_roll^2)"), 
         envir    = .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
                       west, reg6,
                       pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10"),
@@ -213,7 +213,7 @@ gc_vvs <- function() {
     )
 
     ## specify whether variable is time-varying or not
-    vrbls_tiv <- .c(gender, slfidfcn, muem_fndr_name, mow, west, reg6)
+    vrbls_tiv <- .c(gender, slfidfcn, muem_fndr_name, mow, west, reg6, PC1, PC2)
     vrbls_tv <- .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
                    founder_dead,
                    an_inclusion, pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10")
@@ -224,9 +224,9 @@ gc_vvs <- function() {
     l_vrbltypes <- list(        
[…]

### 2024-04-10 scripts/closing_main.R

@@ -353,7 +353,7 @@ c_tblargs <- list() # arguments to pass to gc_tbls
 system(sprintf("rm %s", paste0(c_dirs$misc, "farg_calls.csv")))
 
 source(paste0(c_dirs$code, "cfg.R"))
-## source(paste0(c_dirs$code, "pm_dimred.R")) 
+source(paste0(c_dirs$code, "pm_dimred.R")) 
 source(paste0(c_dirs$code, "regression.R"))
 source(paste0(c_dirs$code, "vrblcvrg.R"))
 
@@ -376,7 +376,11 @@ END_YEAR <- 2021
 ## l_pca_dimred_woclosed <- gl_pca_dimred(dt_pmdb[museum_status != "closed"])
 
 dt_pmx <- gd_pmx(dt_pmdb) # extract of main variables
-dt_pmtiv <- gd_pmtiv(dt_pmx) # time invariant variables
+
+## generate PC cores, only use open PMs for loading calculation
+l_pca_dimred_woclosed <- gl_pca_dimred_closed_imputed(dt_pmdb, dt_pmx)
+
+dt_pmtiv <- gd_pmtiv(dt_pmx, l_pca_dimred_woclosed) # time invariant variables
 
 
 dt_pmyear_prep <- gd_pmyear_prep(dt_pmx, dt_pmtiv) # combine all data sources, as complete as possible

### 2024-04-10 scripts/pm_dimred.R

@@ -254,9 +254,9 @@ gl_pca_dimred <- function(dt_pmdb) {
     
     ## set variables
     vrbls_dimred <- c(keep(names(dt_pmdb), ~grepl("^act_", .x)),
-                       keep(names(dt_pmdb), ~grepl("^avbl_", .x)),
-                       gc_pmdb_vrblgrps(dt_pmdb)[grp == "relations", vrbl],
-                       .c(temp_exhibs, cafe_restrnt, reducedtickets, museumshop,
+                      keep(names(dt_pmdb), ~grepl("^avbl_", .x)),
+                      .c(gvtsupport, donorprogram, endowment, sponsorship,  cooperation),
+                      .c(temp_exhibs, cafe_restrnt, reducedtickets, museumshop,
                           rentalpossblt, webshop))
 
     ## debug: visualize coverage 
@@ -279,7 +279,68 @@ gl_pca_dimred <- function(dt_pmdb) {
     return(l_pca_dimred)
 }
 
+gd_pca_score <- function(dt_toscore, prcomp_obj, rotatedLoadings) {
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
+    
+    #' calculates scores for PCs
+    #' comfy way of scoring cases when not using all cases for estimation
+    #' is necessary because prcomp scores don't take rotation into account
+    #' assumes prcomp is run with scale = T and center = T
+    #' @param dt_toscore data.table to calculate PC scores
+    #' @prcomp_obj ojbejc
 
+    ## check that PCA uses centering and scaling (rest of scoring depends on it)
+    ## if prcomp(center/scale =F, prcomp_obj$center/scale will be boolean, else vector -> can check with is.logical
+    if (is.logical(prcomp_obj$center) | is.logical(prcomp_obj$scale)) {
+        stop(sprintf("prcomp center = %s, scale = %s", prcomp_obj$center, prcomp_obj$scale))
+    }
+
+    if (!all(rownames(rotatedLoadings) %in% names(dt_toscore))) {
+        stop("not all variables needed for score calculation are present in dt_toscore")}
+
+    dt_pca_scored <- replace_NA(
+        dt_toscore[, .SD, # prep data: replace NAs with 0s
+                .SDcols = rownames(rotatedLoadings)]) %>% as.matrix %>%
+        subtract(matrix(prcomp_obj$center, # undo centering
[…]

### 2024-04-10 scripts/regression.R

@@ -449,7 +449,7 @@ gd_pmcpct <- function(dt_pmyear) {
     return(dt_pmcpct)
 }
 
-gd_pmtiv <- function(dt_pmx) {
+gd_pmtiv <- function(dt_pmx, l_pca_dimred_woclosed) {
     if (as.character(match.call()[[1]]) %in% fstd){browser()}
     1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
     gw_fargs(match.call())
@@ -486,11 +486,11 @@ gd_pmtiv <- function(dt_pmx) {
         .[, mow := fifelse(is.na(mow), 0, mow)]
     ## dt_mow_info[dt_pmx, on = .(PMDB_ID =  ID)]
 
-    ## join PCA
-    ## dt_pmtiv_wpca <- join(dt_pmtiv, l_pca_dimred2$dt_scores[, .(ID, V1, V2)], on = "ID")
+    ## add PCA scores
+    dt_pmtiv_wpca <- join(dt_pmtiv, l_pca_dimred_woclosed$dt_scores[, .(ID, PC1, PC2)], on = "ID")
 
-    attr(dt_pmtiv, "gnrtdby") <- as.character(match.call()[[1]])
-    return(dt_pmtiv)
+    attr(dt_pmtiv_wpca, "gnrtdby") <- as.character(match.call()[[1]])
+    return(dt_pmtiv_wpca)
 
 
 }

### 2024-04-10 scripts/vrblcvrg.R

@@ -104,7 +104,8 @@ gc_pmdb_vrblgrps <- function(dt_pmdb) {
 
     dt_vrblgrps <- imap(l_vrblgrps, ~data.table(grp = .y, vrbl = .x)) %>% rbindlist
     if (len(setdiff( names(dt_pmdb), dt_vrblgrps$vrbl)) >0) {
-        stop("vrbls has typos, or not all variables are grouped")
+        stop(sprintf("vrbls has typos, or not all variables are grouped: %s",
+                     paste0(setdiff(names(dt_pmdb), dt_vrblgrps$vrbl), collapse = ",")))
     }
     ## print(setdiff(names(dt_pmdb), dt_vrblgrps$vrbl))
 

### 2024-04-10 scripts/closing_main.R
yeet testtable

@@ -76,25 +76,6 @@ library(khroma)      # plotting
 
 
 
-
-
-gt_testtable <- function(input_data) {
-    if (as.character(match.call()[[1]]) %in% fstd){browser()}
-    1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
-    
-    ##
-
-    list(
-        dt_fmtd = adt(input_data, keep.rownames = "model")[1:12, 1:4],
-        align_cfg = rep("l",5),
-        hline_after = c(0,1,4, 6,9),
-        add_to_row = NULL,
-        number_cols = c(F, rep(T, 3)),
-        landscape = F)
-    
-    
-}
-
 gt_coxzph <- function(rx) {
     gw_fargs(match.call())
     if (as.character(match.call()[[1]]) %in% fstd){browser()}

### 2024-04-10 scripts/cfg.R
yeet testtable cfg

@@ -15,9 +15,6 @@ gc_clgrphattrs <- function() {
 
 gc_tbls <- function(c_tblargs) {
     list(
-        t_testtable = list(
-            input_data = quote(mtcars),
-            caption = "this is a great test table"),
         t_coxzph = list(
             rx = quote(l_mdls$r_pop4),
             caption = "Z-test of proportional hazards"),

### 2024-04-16 scripts/closing_main.R
add number of no longer private museum to nbres

@@ -241,6 +241,11 @@ gd_nbrs <- function() {
     if (as.character(match.call()[[1]]) %in% fstd){browser()}
     1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
     
+    dt_descs <-
+        list(nbr_name = "pmdb_n_nlpm",
+             nbr_fmt = dt_pmdb[museum_status == "no longer a private museum", .N],
+             grp = "descs") %>% adt
+
     ## calculate average hazard rate numbers, depending on maximum age
     dt_pehaz <- gd_pehaz(dt_pmcpct, cutwidth = 2)
     dt_meanhaz <- map(c(20, 30, 40, 100), ~list(upper_bound = .x, mean_haz = dt_pehaz[cuts <= .x, mean(haz)])) %>%
@@ -248,6 +253,8 @@ gd_nbrs <- function() {
         .[, .(nbr_name = sprintf("meanhaz_upto_%s", upper_bound),
               nbr_fmt = sprintf("%s%%", format(mean_haz*100, digits = 2, nsmall = 2)),
               grp = "meanhaz")]
+
+    
         
     ## plots: yanking (insertion) and in-text referencing
     dt_ynkplt <- gc_ynkplt()
@@ -256,7 +263,7 @@ gd_nbrs <- function() {
     ## dt_ynktbl <- gc_ynktbl()
     dt_reftbl <- gc_reftbl()
 
-    dt_nbrs_cbnd <- Reduce(rbind, list(dt_meanhaz, dt_ynkplt, dt_refplt, dt_reftbl))
+    dt_nbrs_cbnd <- Reduce(rbind, list(dt_descs, dt_meanhaz, dt_ynkplt, dt_refplt, dt_reftbl))
 
     
     return(dt_nbrs_cbnd)

### 2024-04-16 texts/paper_closing.tex
add limitation: no focus on NLPM

@@
 \end{sloppypar}
+
+\subsubsection*{Limitations}
+
+For this study, I only investigated the occurence of closure events.
+However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms.
+One way in which this can happen is when other parties, such as local governments other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
+Sometimes this involves changes in the composition of the board of directors, with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum, often to an extent that it no longer fits the working definition.
+Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was often not feasible to determine the date of such transitions\footnote{As a consequence of this, they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing.
+However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
+Primarily this was due to the intransparency of these organizations, as well as the gradual process.
+As the presence of non-founder members does not categorically exclude a museum from being categorized as private museum as long as third-party influence is limited, this influence can grow until the museum bears little resemblance to its former self.
+The possibility of other outcomes than surival and closures has been investigated for NPOs more generally
+\parencite{Searing_2020_zombies,HernandezOrtiz_2022_discontinuity,Helmig_Ingerfurth_Pinz_2013_nonprofit}, and for private museums specifically: 
+\textcite{Walker_2019_collector} argues that in the case of Germany, private museum founders turn to the state to ensure the survival of their projects in the form of public-private partnerships.
+Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research. 
 \end{document}

### 2024-04-17 scripts/cfg.R
think about framing:composition might be angle -> explore composition

@@ -165,6 +165,8 @@ gc_vvs <- function() {
         ## "I(exhbqntl_roll^2)" = "Exhibition Quantile^2 (year, rolled)",
         PC1                       = "PC1 (Size)",
         PC2                       = "PC2 (Support)",
+        year                      = "year",
+        "I(year^2)"               = "year^2",
         GLOBAL          = "Global") # from cox.zph
     
     l_vrblgrps <- list(# variable groups
@@ -174,15 +176,17 @@ gc_vvs <- function() {
         ## exhbprop_top10_log, exhbprop_top10_utf, exhbqntl_roll, "I(exhbqntl_roll^2)"), 
         envir    = .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
                       west, reg6,
-                      pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10"),
+                      pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10",
+                      year, "I(year^2)"),
         misc     = .c(GLOBAL)
     )
 
     ## specify whether variable is time-varying or not
     vrbls_tiv <- .c(gender, slfidfcn, muem_fndr_name, mow, west, reg6, PC1, PC2)
     vrbls_tv <- .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
-                   founder_dead,
-                   an_inclusion, pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10")
+                   founder_dead, 
+                   an_inclusion, pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10",
+                   year, "I(year^2)")
     ## exhbqntl_cy, exhbqntl_year, "I(exhbqntl_year^2)", exhbprop_top10_log, exhbprop_top10_utf,
     ## exhbqntl_roll, "I(exhbqntl_roll^2)")
 
@@ -190,7 +194,8 @@ gc_vvs <- function() {
     l_vrbltypes <- list(        
         bin = .c(founder_dead, muem_fndr_name, mow, west),
         num = .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
[…]

### 2024-04-17 scripts/closing_main.R

@@ -359,7 +359,7 @@ dt_pmcpct <- gd_pmcpct(dt_pmyear) # time-invariant variables (UoA PM, not pm-yea
 
 l_mdls <- gl_mdls(dt_pmyear, dt_pmcpct) # generate models
                                         # set model names for t_reg_coxph
-l_mdlnames_coxph <- c("r_pop4")
+l_mdlnames_coxph <- c("r_pop4", "r_pop4_wyr")
 ## l_mdlnames_coxph <- c("r_pop4", paste0("r_wsize", 3:1))
 ## c("r_more", paste0("r_pop", c(1, 3:6)))
 ## "r_woaf", "r_waf_year", "r_waf_roll", "r_waf_roll2")
@@ -423,6 +423,57 @@ gdtbl("t_reg_coxph")
 
 
 print("everything is DONE")
+
+## longitudinal development of variables
+
+gp_lngtdvelp <- function(dt_pmyear) {
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
+    
+    ## categorical and binary variables: proportion
+    dt_vrblinfo <- gc_vvs() %>% chuck("dt_vrblinfo")
+    
+    dt_cat <- dt_pmyear[, .SD, .SDcols = c("ID", "year", dt_vrblinfo[vrbltype %in% c("cat","bin"),
+                                                                     achr(funique(vrbl))])] %>%
+        melt(id.vars = c("ID", "year"), variable.name = "vrbl") %>%
+        .[, .N, .(year, vrbl, value)] %>%
+        .[, value_y := N/sum(N), .(year, vrbl)] %>%
+        .[, N := NULL]
+
+    ## numeric variables: mean
+    dt_num <- dt_pmyear[, .SD, .SDcols = c("ID", "year", "closing",
+                                           dt_vrblinfo[vrbltype == "num" & !grepl("I\\(|:", vrbl),
+                                                       achr(funique(vrbl))])] %>%
+        .[, cnt := .N, year] %>% # set up count (gets meaned)
+        .[, will_close := fifelse(any(closing == 1), 1, 0), ID] %>% # whether a museum will close
+        melt(id.vars = c("ID", "year"), variable.name = "vrbl") %>%
+        .[, .(value_y = mean(value)), .(year, vrbl)] %>%
+        .[, `:=`(value = vrbl)] %>%
+        .[vrbl != "year"] # don't need avg year, is just year
+
+    dt_viz <- rbind(dt_cat, dt_num)
+        
[…]

### 2024-04-17 scripts/regression.R

@@ -806,6 +806,11 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
                             slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
                             proxcnt10*popm_circle10,
                        dt_pmyear),
+
+        r_pop4_wyr = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + mow +
+                            slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
+                            proxcnt10*popm_circle10 + year + I(year^2),
+                       copy(dt_pmyear)[, year := year - 2010]),
         
         r_wsize1 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + mow +
                             slfidfcn + founder_dead + muem_fndr_name + an_inclusion +

### 2024-04-17 texts/paper_closing.tex
paper update: new org version? wcpF, add limitation note

@@
-% Created 2024-04-07 zo 17:21
+% Created 2024-04-16 di 12:30
 % Intended LaTeX compiler: pdflatex
@@
 \setlength{\parindent}{1.2cm}
-\author{Johannes Aengenheyster}
+\author{Johannes }
 \date{\today}
@@
 \hypersetup{
- pdfauthor={Johannes Aengenheyster},
+ pdfauthor={Johannes },
  pdftitle={},
@@
  pdfsubject={},
- pdfcreator={Emacs 29.2 (Org mode 9.6.21)}, 
+ pdfcreator={Emacs 29.2 (Org mode 9.6.26)}, 
  pdflang={English}}
@@
 \section*{Identity and the closure of private art museums}
-\label{sec:org16a7685}
 
 \subsection*{Introduction}
-\label{sec:orgef6a080}
 
@@
 
+\subsection*{Private museums}
+
 \subsection*{Theoretical framework}
-\label{sec:org90170ed}
 
@@
 \subsubsection*{Identity and the survival prospects of non-profit organizations}
-\label{sec:org8725d02}
+
 An identity that is legitimate (understandable) and favorable (positive) has been shown to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
@@
 \subsubsection*{Organizational transformation}
-\label{sec:org19d4baf}
+
 \textcite{Carroll_Khessina_2019_demography} argue that transformation of core features of organizations such as changes in technology or authority can have divergent consequences. 
@@
 \subsubsection*{Competition}
-\label{sec:org9840956}
 
@@
 \subsubsection*{Other predictors of organizational survival}
-\label{sec:org9672c62}
+
 \paragraph*{Age}
-\label{sec:orgae2e32a}
 
@@
 \subsection*{Data and Methods}
-\label{sec:org6923afe}
 
 \subsubsection*{Dependent Variable}
-\label{sec:org7efae3c}
+
 A newly constructed database, assembled from different sources,  is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
@@
 \subsubsection*{Main Predictors}
-\label{sec:orge0e80eb}
 
 \paragraph*{Legitimacy}
-\label{sec:org9952eec}
 
@@
 \paragraph*{Reputation}
-\label{sec:org051c5db}
 
@@
 \paragraph*{Organizational transformation}
-\label{sec:org671fa45}
+
 A measure of founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder.
@@
 \paragraph*{Competition}
-\label{sec:orgc059910}
+
 On a national level, density of private museum is calculated as the number of private museums per million.
@@
 \subsubsection*{Control variables}
-\label{sec:org4412539}
 
@@
 \subsubsection*{Analytical framework}
-\label{sec:orge4889f4}
 
@@
 \subsection*{Results}
-\label{sec:org9e38ff3}
 
 \subsubsection*{Summary statistics}
-\label{sec:org12efa6c}
 
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Sun Apr  7 12:05:30 2024
+% Mon Apr 15 11:30:07 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & $275$ & $0.574$ & $  0.593$ & $  0.49$ & $0$ & $1$ \\ 
-   & Gender - Female & $76$ & $0.159$ & $  0.169$ & $  0.37$ & $0$ & $1$ \\ 
-   & Gender - Couple & $128$ & $0.267$ & $  0.238$ & $  0.43$ & $0$ & $1$ \\ 
-   & Founder died & $58$ & $0.121$ & $  0.098$ & $  0.30$ & $0$ & $1$ \\ 
+ & Gender - Male & 275 & 0.574 &   0.593 &   0.49 & 0 & 1 \\ 
+   & Gender - Female & 76 & 0.159 &   0.169 &   0.37 & 0 & 1 \\ 
+   & Gender - Couple & 128 & 0.267 &   0.238 &   0.43 & 0 & 1 \\ 
+   & Founder died & 58 & 0.121 &   0.098 &   0.30 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & $178$ & $0.372$ & $  0.410$ & $  0.49$ & $0$ & $1$ \\ 
-   & Self-Identification - Foundation & $101$ & $0.211$ & $  0.189$ & $  0.39$ & $0$ & $1$ \\ 
-   & Self-Identification - Collection & $74$ & $0.154$ & $  0.140$ & $  0.35$ & $0$ & $1$ \\ 
-   & Self-Identification - Other & $126$ & $0.263$ & $  0.261$ & $  0.44$ & $0$ & $1$ \\ 
-   & Founder name in Museum name & $229$ & $0.478$ & $  0.488$ & $  0.50$ & $0$ & $1$ \\ 
-   & MOW inclusion & $91$ & $0.190$ & $  0.304$ & $  0.46$ & $0$ & $1$ \\ 
-   & AN Ranking - Not Included & $NA$ & $NA$ & $  0.797$ & $  0.40$ & $0$ & $1$ \\ 
-   & AN Ranking - Included & $NA$ & $NA$ & $  0.150$ & $  0.36$ & $0$ & $1$ \\ 
-   & AN Ranking - Dropped & $NA$ & $NA$ & $  0.054$ & $  0.23$ & $0$ & $1$ \\ 
+ & Self-Identification - Museum & 178 & 0.372 &   0.410 &   0.49 & 0 & 1 \\ 
+   & Self-Identification - Foundation & 101 & 0.211 &   0.189 &   0.39 & 0 & 1 \\ 
+   & Self-Identification - Collection & 74 & 0.154 &   0.140 &   0.35 & 0 & 1 \\ 
+   & Self-Identification - Other & 126 & 0.263 &   0.261 &   0.44 & 0 & 1 \\ 
+   & Founder name in Museum name & 229 & 0.478 &   0.488 &   0.50 & 0 & 1 \\ 
+   & MOW inclusion & 91 & 0.190 &   0.304 &   0.46 & 0 & 1 \\ 
+   & AN Ranking - Not Included &  &  &   0.797 &   0.40 & 0 & 1 \\ 
+   & AN Ranking - Included &  &  &   0.150 &   0.36 & 0 & 1 \\ 
+   & AN Ranking - Dropped &  &  &   0.054 &   0.23 & 0 & 1 \\ 
+   & PC1 (Size) & 76.0366391388584 & 0.159 &   0.138 &   1.88 & -6.4 & 2.62 \\ 
+   & PC2 (Support) & 58.6628793020593 & 0.122 &   0.179 &   1.49 & -5 & 2.74 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density (country) & $NA$ & $NA$ & $  0.411$ & $  1.23$ & $0.00077$ & $27.26$ \\ 
-   & Pop. (millions) within 10km & $NA$ & $NA$ & $  1.322$ & $  1.69$ & $0.000087$ & $10.81$ \\ 
-   & Pop. (millions) country & $NA$ & $NA$ & $156.197$ & $287.82$ & $0.037$ & $1412.36$ \\ 
-   & Nbr PM within 10km & $NA$ & $NA$ & $  1.601$ & $  2.97$ & $0$ & $15$ \\ 
-   & PM density (10km) & $NA$ & $NA$ & $  1.423$ & $  4.01$ & $0$ & $41.85$ \\ 
-   & Europe and North America & $312$ & $0.651$ & $  0.645$ & $  0.48$ & $0$ & $1$ \\ 
-   & Region - Africa & $7$ & $0.015$ & $  0.012$ & $  0.11$ & $0$ & $1$ \\ 
-   & Region - Asia & $128$ & $0.267$ & $  0.282$ & $  0.45$ & $0$ & $1$ \\ 
-   & Region - Europe & $241$ & $0.503$ & $  0.501$ & $  0.50$ & $0$ & $1$ \\ 
-   & Region - Latin America & $22$ & $0.046$ & $  0.042$ & $  0.20$ & $0$ & $1$ \\ 
-   & Region - North America & $71$ & $0.148$ & $  0.143$ & $  0.35$ & $0$ & $1$ \\ 
-   & Region - Oceania & $10$ & $0.021$ & $  0.019$ & $  0.14$ & $0$ & $1$ \\ 
+ & PM density (country) &  &  &   0.411 &   1.23 & 0.00077 & 27.26 \\ 
+   & Pop. (millions) within 10km &  &  &   1.322 &   1.69 & 0.000087 & 10.81 \\ 
+   & Pop. (millions) country &  &  & 156.197 & 287.82 & 0.037 & 1412.36 \\ 
+   & Nbr PM within 10km &  &  &   1.601 &   2.97 & 0 & 15 \\ 
+   & PM density (10km) &  &  &   1.423 &   4.01 & 0 & 41.85 \\ 
+   & Europe and North America & 312 & 0.651 &   0.645 &   0.48 & 0 & 1 \\ 
+   & Region - Africa & 7 & 0.015 &   0.012 &   0.11 & 0 & 1 \\ 
+   & Region - Asia & 128 & 0.267 &   0.282 &   0.45 & 0 & 1 \\ 
+   & Region - Europe & 241 & 0.503 &   0.501 &   0.50 & 0 & 1 \\ 
+   & Region - Latin America & 22 & 0.046 &   0.042 &   0.20 & 0 & 1 \\ 
+   & Region - North America & 71 & 0.148 &   0.143 &   0.35 & 0 & 1 \\ 
+   & Region - Oceania & 10 & 0.021 &   0.019 &   0.14 & 0 & 1 \\ 
    \hline
@@
 \subsubsection*{Hazard rate and Age Dependence}
-\label{sec:org01e6edd}
 
@@
 \centering
-\includegraphics[width=16cm]{../figures/p_hazard.png}
+\includegraphics[width=16cm]{../figures/p_hazard.pdf}
 \caption{\label{fig:p_hazard}Private Museum hazard function}
@@
 \centering
-\includegraphics[width=14cm]{../figures/p_surv.png}
+\includegraphics[width=14cm]{../figures/p_surv.pdf}
 \caption{\label{fig:p_surv}Private Museum Survival probability}
@@
 \subsubsection*{Regression Results}
-\label{sec:org4878b83}
 
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Sun Apr  7 15:01:01 2024
+% Mon Apr 15 11:32:02 2024
 \begin{table}[ht]
 \centering
-\begin{tabular}{p{0mm}ll}
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
   \hline 
@@
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & $.22 \; (0.37)$ \\ 
-   & Gender - Couple & $.14 \; (0.36)$ \\ 
-   & Founder died & $.28 \; (0.53)$ \\ 
+ & Gender - Female & .22 \; (0.37) \\ 
+   & Gender - Couple & .14 \; (0.36) \\ 
+   & Founder died & .28 \; (0.53) \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & $.71 \; (0.48)$ \\ 
-   & Self-Identification - Collection & $.14 \; (0.59)$ \\ 
-   & Self-Identification - Other & $1.32 \; (0.38)^{***}$ \\ 
-   & AN Ranking - Included & $.50 \; (0.38)$ \\ 
-   & AN Ranking - Dropped & $.82 \; (0.52)$ \\ 
-   & Founder name in Museum name & $-.35 \; (0.33)$ \\ 
-   & MOW inclusion & $-.90 \; (0.40)^{*}$ \\ 
+ & Self-Identification - Foundation & .71 \; (0.48) \\ 
+   & Self-Identification - Collection & .14 \; (0.59) \\ 
+   & Self-Identification - Other & 1.32 \; (0.38)^{***} \\ 
+   & AN Ranking - Included & .50 \; (0.38) \\ 
+   & AN Ranking - Dropped & .82 \; (0.52) \\ 
+   & Founder name in Museum name & -.35 \; (0.33) \\ 
+   & MOW inclusion & -.90 \; (0.40)^{*} \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density (country) & $.56 \; (0.42)$ \\ 
-   & PM density$^{2}$ (country) & $-.02 \; (0.02)$ \\ 
-   & Pop. (millions) within 10km & $.29 \; (0.11)^{**}$ \\ 
-   & Nbr PM within 10km & $.30 \; (0.09)^{***}$ \\ 
-   & Nbr PM (10km) * Pop (10km) & $-.10 \; (0.04)^{**}$ \\ 
+ & PM density (country) & .56 \; (0.42) \\ 
+   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .29 \; (0.11)^{**} \\ 
+   & Nbr PM within 10km & .30 \; (0.09)^{***} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
    \hline
- & Museum-years & $6423$ \\ 
-   & Closures & $52$ \\ 
-   & log. Likelihood & $-253.41$ \\ 
-   & AIC & $536.82$ \\ 
-   & BIC & $566.09$ \\ 
+ & Museum-years & 6423 \\ 
+   & Closures & 52 \\ 
+   & log. Likelihood & -253.41 \\ 
+   & AIC & 536.82 \\ 
+   & BIC & 566.09 \\ 
    \hline 
@@
 \paragraph*{Control Variables}
-\label{sec:org75141bd}
 
@@
 \paragraph*{Identity Variables}
-\label{sec:orge692d76}
 
@@
 \paragraph*{Organizational transformation}
-\label{sec:orge8aaa4f}
 
@@
 \paragraph*{Competition}
-\label{sec:orgd4359d4}
+
 \begin{figure}[htbp]
 \centering
-\includegraphics[width=18cm]{../figures/p_pred_popprxcnt.png}
+\includegraphics[width=18cm]{../figures/p_pred_popprxcnt.pdf}
 \caption{\label{fig:p_pred_popprxcnt}Predicted Avg. Hazard Rate on Regional PM Density and Population}
@@
 \subsection*{Conclusion}
-\label{sec:org77289d2}
+
 TBD

### 2024-04-17 scripts/closing_main.R
some changes to gp_lngtdvelp

@@ -432,7 +432,7 @@ gp_lngtdvelp <- function(dt_pmyear) {
     ## categorical and binary variables: proportion
     dt_vrblinfo <- gc_vvs() %>% chuck("dt_vrblinfo")
     
-    dt_cat <- dt_pmyear[, .SD, .SDcols = c("ID", "year", dt_vrblinfo[vrbltype %in% c("cat","bin"),
+    dt_cat <- dt_pmyear[, .SD, .SDcols = c("ID", "year", dt_vrblinfo[vrbltype == "cat",
                                                                      achr(funique(vrbl))])] %>%
         melt(id.vars = c("ID", "year"), variable.name = "vrbl") %>%
         .[, .N, .(year, vrbl, value)] %>%
@@ -440,11 +440,13 @@ gp_lngtdvelp <- function(dt_pmyear) {
         .[, N := NULL]
 
     ## numeric variables: mean
-    dt_num <- dt_pmyear[, .SD, .SDcols = c("ID", "year", "closing",
-                                           dt_vrblinfo[vrbltype == "num" & !grepl("I\\(|:", vrbl),
+    dt_num <- dt_pmyear[, .SD, .SDcols = c("ID", "year", "closing", "age",
+                                           # # yeet squared/interactions
+                                           dt_vrblinfo[(vrbltype %in% c("bin", "num") & !grepl("I\\(|:", vrbl)),
                                                        achr(funique(vrbl))])] %>%
         .[, cnt := .N, year] %>% # set up count (gets meaned)
         .[, will_close := fifelse(any(closing == 1), 1, 0), ID] %>% # whether a museum will close
+        .[, first_year := fifelse(age == 1, 1, 0), ID] %>% 
         melt(id.vars = c("ID", "year"), variable.name = "vrbl") %>%
         .[, .(value_y = mean(value)), .(year, vrbl)] %>%
         .[, `:=`(value = vrbl)] %>%
@@ -460,7 +462,7 @@ gp_lngtdvelp <- function(dt_pmyear) {
     dt_viz_colored <- join(dt_viz, dt_color, on = c("vrbl", "value"))
     
     ## add labels for lines of categorical variables at end of line
-    dt_lbls <- dt_viz_colored[dt_vrblinfo[vrbltype %in% c("cat", "bin"), .(vrbl)], on = "vrbl"] %>%
[…]

### 2024-04-17 scripts/closing_main.R
move descriptive plots/tables to new descriptives.R file, other:
gt_coxzph to regression.R
overall cleanup

@@ -35,206 +35,6 @@ library(khroma)      # plotting
 
 ## ** functions
 
-## *** config functions
-
-## moved to jtls
-## gc_dirs <- function(dir_proj) {
-##     list(
-##         proj = dir_proj,
-##         figs = paste0(dir_proj, "figures/"),
-##         tbls = paste0(dir_proj, "tables/"),
-##         data = paste0(dir_proj, "data/"),
-##         code = paste0(dir_proj, "scripts/"),
-##         misc = paste0(dir_proj, "misc/")
-##     )
-## }
-
-
-
-## *** data generation
-
-
-
-
-
-
-
-
-
-
-## *** plotting
-
-
-
-
-
-
-
-
-## *** tables
-
-
-
-
-gt_coxzph <- function(rx) {
-    gw_fargs(match.call())
-    if (as.character(match.call()[[1]]) %in% fstd){browser()}
-    1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
-    
-    #' generate a table of the cox.zph result (whether hazards are proportional) 
-
-    coxzph_trfms <- list(km = "Kaplan-Meier", identity = "Identity", rank = "Rank")
-
-    ## generate the actual data
-    dt_coxzph_prep <- map(names(coxzph_trfms), ~cox.zph(rx, terms = F, transform = .x) %>%
-                                                   chuck("table") %>% adt(keep.rownames = "term") %>%
-                                                   .[, src := .x]) %>% list_rbind %>%
-                      .[, .(term, src, p)]
-
-    
-    ## merge with variable labels, cast to wide
-    dt_coxzph <- gc_vvs() %>% chuck("dt_termlbls") %>% .[dt_coxzph_prep, on = "term"] %>%
-        .[, p_fmtd := fmt_cell(coef = p, pvalue = p,  type = "coef-stars"), .(term, src)] %>%
-        dcast(term_lbl + vrblgrp + vrblgrp_lbl ~ src, value.var = "p_fmtd") %>%
-        .[order(vrblgrp)]
-
-    
-    ## arrange table that in a way that it is to be written to file
-    dt_coxzph_viz <- dt_coxzph[, c("term_lbl", names(coxzph_trfms)), with = F] %>%
-        cbind(grp_filler = "", .) %>% # add column in beginning for faking group indentation
-        .[, term_lbl := latexTranslate(term_lbl)]
-            
[…]

### 2024-04-17 scripts/descriptives.R

@@ -1,0 +1,147 @@
+
+gp_lngtdvelp <- function(dt_pmyear) {
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
+    
+    ## categorical and binary variables: proportion
+    dt_vrblinfo <- gc_vvs() %>% chuck("dt_vrblinfo")
+    
+    dt_cat <- dt_pmyear[, .SD, .SDcols = c("ID", "year", dt_vrblinfo[vrbltype == "cat",
+                                                                     achr(funique(vrbl))])] %>%
+        melt(id.vars = c("ID", "year"), variable.name = "vrbl") %>%
+        .[, .N, .(year, vrbl, value)] %>%
+        .[, value_y := N/sum(N), .(year, vrbl)] %>%
+        .[, N := NULL]
+
+    ## numeric variables: mean
+    dt_num <- dt_pmyear[, .SD, .SDcols = c("ID", "year", "closing", "age",
+                                           # # yeet squared/interactions
+                                           dt_vrblinfo[(vrbltype %in% c("bin", "num") & !grepl("I\\(|:", vrbl)),
+                                                       achr(funique(vrbl))])] %>%
+        .[, cnt := .N, year] %>% # set up count (gets meaned)
+        .[, will_close := fifelse(any(closing == 1), 1, 0), ID] %>% # whether a museum will close
+        .[, first_year := fifelse(age == 1, 1, 0), ID] %>% 
+        melt(id.vars = c("ID", "year"), variable.name = "vrbl") %>%
+        .[, .(value_y = mean(value)), .(year, vrbl)] %>%
+        .[, `:=`(value = vrbl)] %>%
+        .[vrbl != "year"] # don't need avg year, is just year
+
+    dt_viz <- rbind(dt_cat, dt_num)
+        
+    ## set colors based on variable value
+    dt_color <- dt_viz[, .(vrbl, value)] %>% funique %>%
+        .[, lnbr := 1:.N, vrbl]
+    
+
+    dt_viz_colored <- join(dt_viz, dt_color, on = c("vrbl", "value"))
+    
+    ## add labels for lines of categorical variables at end of line
+    dt_lbls <- dt_viz_colored[dt_vrblinfo[vrbltype == "cat", .(vrbl)], on = "vrbl"] %>%
+        .[, .SD[which.max(year)], .(vrbl, value)]
+    
+    ## library(ggrepel)
[…]

### 2024-04-17 scripts/regression.R

@@ -805,28 +805,14 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         r_pop4 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + mow +
                             slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
                             proxcnt10*popm_circle10,
-                       dt_pmyear),
+                       dt_pmyear)
 
-        r_pop4_wyr = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + mow +
-                            slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-                            proxcnt10*popm_circle10 + year + I(year^2),
-                       copy(dt_pmyear)[, year := year - 2010]),
+        ## r_pop4_wyr = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + mow +
+        ##                     slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
+        ##                     proxcnt10*popm_circle10 + year + reg6,
+        ##                    dt_pmyear)
+                       
         
-        r_wsize1 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + mow +
-                            slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-                            proxcnt10*popm_circle10 + PC1,
-                         dt_pmyear),
-        
-
-        r_wsize2 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + mow +
-                            slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-                            proxcnt10*popm_circle10 + PC2,
-                         dt_pmyear),
-        
-        r_wsize3 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + mow +
-                            slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-                            proxcnt10*popm_circle10 + PC1 + PC2,
-                         dt_pmyear)
 
[…]

### 2024-04-22 scripts/cfg.R
add time_period variables (5 year spells), but inclusion not worth it

@@ -175,6 +175,7 @@ gc_vvs <- function() {
         PC2                       = "PC2 (Support)",
         year                      = "year",
         "I(year^2)"               = "year^2",
+        time_period               = "Time Period (5 years)",
         GLOBAL                    = "Global") # from cox.zph
     
     l_vrblgrps <- list(# variable groups
@@ -187,7 +188,7 @@ gc_vvs <- function() {
         envir    = .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
                       west, reg6,
                       pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10",
-                      year, "I(year^2)"),
+                      year, "I(year^2)",  time_period),
         misc     = .c(GLOBAL)
     )
 
@@ -196,7 +197,7 @@ gc_vvs <- function() {
     vrbls_tv <- .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
                    founder_dead, 
                    an_inclusion, pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10",
-                   year, "I(year^2)",
+                   year, "I(year^2)", time_period,
                    exhbany, exhbrollany, 
                    exhbqntl_cy, exhbqntl_year, "I(exhbqntl_year^2)", exhbprop_top10_log, exhbprop_top10_utf,
                    exhbqntl_roll, "I(exhbqntl_roll^2)")
@@ -209,7 +210,7 @@ gc_vvs <- function() {
                  year, "I(year^2)",
                  exhbqntl_cy, exhbqntl_year, "I(exhbqntl_year^2)",
                  exhbprop_top10_log, exhbprop_top10_utf, exhbqntl_roll, "I(exhbqntl_roll^2)"),
-        cat = .c(gender, slfidfcn, reg6, an_inclusion))
+        cat = .c(gender, slfidfcn, reg6, an_inclusion, time_period))
 
 
     l_vrblgrp_lbls <- list(# variable group labels
@@ -266,8 +267,12 @@ gc_vvs <- function() {
         list(vrbl = "reg6", term = "reg6OC",    term_lbl = "Region - Oceania"),
         list(vrbl = "an_inclusion", term = "an_inclusionincluded",     term_lbl = "AN Ranking - Included"),
[…]

### 2024-04-22 scripts/closing_main.R

@@ -160,6 +160,7 @@ l_pca_dimred_woclosed <- gl_pca_dimred_closed_imputed(dt_pmdb, dt_pmx)
 dt_pmtiv <- gd_pmtiv(dt_pmx, l_pca_dimred_woclosed) # time invariant variables
 
 
+
 dt_pmyear_prep <- gd_pmyear_prep(dt_pmx, dt_pmtiv, c_lvrs) # combine all data sources, as complete as possible
 dt_pmyear <- gd_pmyear(dt_pmyear_prep, c_lvrs) # trim down dt to no NAs
 
@@ -169,7 +170,7 @@ dt_pmcpct <- gd_pmcpct(dt_pmyear) # time-invariant variables (UoA PM, not pm-yea
 
 l_mdls <- gl_mdls(dt_pmyear, dt_pmcpct) # generate models
                                         # set model names for t_reg_coxph
-l_mdlnames_coxph <- c("r_pop4") #, "r_pop4_wyr")
+l_mdlnames_coxph <- c("r_pop4")# , "r_pop4_wyr")
 ## l_mdlnames_coxph <- c("r_pop4", paste0("r_wsize", 3:1))
 ## c("r_more", paste0("r_pop", c(1, 3:6)))
 ## "r_woaf", "r_waf_year", "r_waf_roll", "r_waf_roll2")

### 2024-04-22 scripts/regression.R

@@ -413,7 +413,8 @@ gd_pmyear_prep <- function(dt_pmx, dt_pmtiv, c_lvrs = c_lvrs) {
         .[, age := year - year_opened] %>% # set age
         ## founder death: 1 if year > deathyear, else 0 (before death or not dead at all)
         .[, founder_dead := fifelse(!is.na(deathyear),fifelse(year > deathyear, 1, 0), 0)] %>% 
-        .[, `:=`(tstart = age, tstop = age+1)] # set survival time interval variables
+        .[, `:=`(tstart = age, tstop = age+1)] %>% # set survival time interval variables
+        .[, time_period := as.factor(paste0("tp", 5*(floor(year/5))))]
         
 
     ## get country population data
@@ -544,6 +545,11 @@ gd_pmyear <- function(dt_pmyear_prep, c_lvrs) {
     dt_pmyear_lagfiltered <- na.omit(dt_pm_lagged, cols = vrbls_tolag)
 
     dt_pmyear_trimmed <- dt_pmyear_lagfiltered[year >= START_YEAR]
+
+    ## yeet unused time period factors, if it exists
+    if ("time_period" %in% names(dt_pmyear_trimmed)) {
+        dt_pmyear_trimmed[, time_period := factor(time_period)]
+    }
 
     
     attr(dt_pmyear_trimmed, "gnrtdby") <- as.character(match.call()[[1]])
@@ -916,12 +922,15 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         r_pop4 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
                             slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
                             proxcnt10*popm_circle10 + exhbrollany,
-                       dt_pmyear)
+                       dt_pmyear),
 
-        ## r_pop4_wyr = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
-        ##                     slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-        ##                     proxcnt10*popm_circle10 + year + reg6,
-        ##                    copy(dt_pmyear)[, reg6 := factor(reg6, labels = c("OC", "NALUL","EU","AS", "LA", "AF"))])
+        
+
+        r_pop4_wyr = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
[…]

### 2024-04-22 texts/paper_closing.tex
some more testing, just freely writing

@@
-% Created 2024-04-16 di 12:30
+% Created 2024-04-22 ma 19:57
 % Intended LaTeX compiler: pdflatex
@@
 \subsection*{Private museums}
+
+Investigating the survival prospects of private museum furthermore illucidates the long-term development of the organizational form as a whole.
+While the composition of private museums is not only influenced by closures, but also by foundings, analysing the former provides insights in the sustainability of
+
+Given the non-significant gender difference, it can be expected that (unless given a strong increase in founding by women) the population of private museums will continue to remain a dominated affair\footnote{The point estimates, which are higher for women and couples, albeit not significantly so, even point towards a slight expansion of the proportion of museums established by men.}
+The role of the founder is two sided.
+Death and exclusion from a prestigious ranking are not associated with a higher risk of closure, which indicates that private museums have attained a substantial degree of institutionalization.
+On the other hand, self-identifying as an institution which is not a museum, foundation or collection possibly reflects a kind of founder attitudes which substantially influences survival chances.
+Founders who are less interested in establish institutions might be more inclined to choose a name which less reflects this ambition. 
+One way of conceptualizing this distinction might then be that whereas involuntary, externally imposed events are less able to close museums of otherwise motivated founders, some founders might from the very beginning voluntarily decide to not establish a museum that is intended for perpetuity.
+
+However, this group is somewhat small.
+Of the XXX museums included in the database, XXX do not carry the term museum, foundation or collection.
+Thus given this low share, and the corresponding  higher closing rate, a possible future for the private museum population might be increased institutionalization and consolidation of relatively robust organizations.
+The effects of location might be seen
+On the one hand, museum location is chosen by the founder at the time of founding (or rather, several years in advance).
+This gives founders substantial choice in the size and composition of the potential audience who will be able to easily assess the museum.
+On the other hand, collectors are less able to influence what plans other collectors might have.
+What may have been at one point been identified as a promising location without substantial competition may turn out to be a much less fertile ground as soon as other collectors start eyeing the same region for their own private museum projects.
+In particular private museum in rural locations with low population densities seem to be at risk when other museums open in the neighborhood. 
+This is not to say that private museums cannot endure in areas with low population densities. 
+In fact, at low numbers of private museums in the neighborhood their survival prospects are better than those located in larger cities.
+These larger cities with low private museum counts are possibly also characterized by lower numbers of other cultural institutions as well as an audience less interested in postmaterial art consumption.
+
+The lack of a relation between temporary exhibitions and survival prospect is somewhat unexpected.
+It was expected that as temporary exhibitions constitute one of the main tasks of a museums operations, organizing them would benefit a museum financially (via visitor fees) and symbolically (via prestige of other art field actors, which might be developed into further contacts), leading to higher survival chances\footnote{Furthermore, the ability to organization exhibitions likely reflects museum resources, which should also enhance survival.}
+However, organizing exhibitions does not seem to bestow benefits for the museums which organize them, nor do organizations seem to be organized only by established/sustainable/secure organizations.
+One possibility for this discrepancy could be that exhibitions are expensive, and whatever benefits gained from them are offset by the associated costs.
+One might see in this association again the importance of the founder:
+Founders who are committed to their museums will keep them alive, regardless of whether or not they plan to organize temporary exhibitions.
 
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon Apr 15 11:30:07 2024
+% Fri Apr 19 19:04:41 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 275 & 0.574 &   0.593 &   0.49 & 0 & 1 \\ 
-   & Gender - Female & 76 & 0.159 &   0.169 &   0.37 & 0 & 1 \\ 
-   & Gender - Couple & 128 & 0.267 &   0.238 &   0.43 & 0 & 1 \\ 
-   & Founder died & 58 & 0.121 &   0.098 &   0.30 & 0 & 1 \\ 
+ & Gender - Male & 274 & 0.573 & 5.9e-01 &   0.49 & 0 & 1 \\ 
+   & Gender - Female & 76 & 0.159 & 1.7e-01 &   0.38 & 0 & 1 \\ 
+   & Gender - Couple & 128 & 0.268 & 2.4e-01 &   0.43 & 0 & 1 \\ 
+   & Founder died & 57 & 0.119 & 9.3e-02 &   0.29 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 178 & 0.372 &   0.410 &   0.49 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 101 & 0.211 &   0.189 &   0.39 & 0 & 1 \\ 
-   & Self-Identification - Collection & 74 & 0.154 &   0.140 &   0.35 & 0 & 1 \\ 
-   & Self-Identification - Other & 126 & 0.263 &   0.261 &   0.44 & 0 & 1 \\ 
-   & Founder name in Museum name & 229 & 0.478 &   0.488 &   0.50 & 0 & 1 \\ 
-   & MOW inclusion & 91 & 0.190 &   0.304 &   0.46 & 0 & 1 \\ 
-   & AN Ranking - Not Included &  &  &   0.797 &   0.40 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  &   0.150 &   0.36 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  &   0.054 &   0.23 & 0 & 1 \\ 
-   & PC1 (Size) & 76.0366391388584 & 0.159 &   0.138 &   1.88 & -6.4 & 2.62 \\ 
-   & PC2 (Support) & 58.6628793020593 & 0.122 &   0.179 &   1.49 & -5 & 2.74 \\ 
+ & Self-Identification - Museum & 177 & 0.370 & 4.0e-01 &   0.49 & 0 & 1 \\ 
+   & Self-Identification - Foundation & 101 & 0.211 & 1.9e-01 &   0.39 & 0 & 1 \\ 
+   & Self-Identification - Collection & 74 & 0.155 & 1.4e-01 &   0.35 & 0 & 1 \\ 
+   & Self-Identification - Other & 126 & 0.264 & 2.6e-01 &   0.44 & 0 & 1 \\ 
+   & Founder name in Museum name & 228 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
+   & MOW inclusion & 91 & 0.190 & 2.8e-01 &   0.45 & 0 & 1 \\ 
+   & AN Ranking - Not Included &  &  & 8.0e-01 &   0.40 & 0 & 1 \\ 
+   & AN Ranking - Included &  &  & 1.5e-01 &   0.36 & 0 & 1 \\ 
+   & AN Ranking - Dropped &  &  & 5.6e-02 &   0.23 & 0 & 1 \\ 
+   & Exhibition any &  &  & 6.5e-01 &   0.48 & 0 & 1 \\ 
+   & Exhibition any last 5 years &  &  & 4.7e-01 &   0.50 & 0 & 1 \\ 
+   & PC1 (Size) & 74.6913323980041 & 0.156 & 1.3e-01 &   1.88 & -6.4 & 2.62 \\ 
+   & PC2 (Support) & 58.6876842646085 & 0.123 & 1.6e-01 &   1.50 & -5 & 2.74 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density (country) &  &  &   0.411 &   1.23 & 0.00077 & 27.26 \\ 
-   & Pop. (millions) within 10km &  &  &   1.322 &   1.69 & 0.000087 & 10.81 \\ 
-   & Pop. (millions) country &  &  & 156.197 & 287.82 & 0.037 & 1412.36 \\ 
-   & Nbr PM within 10km &  &  &   1.601 &   2.97 & 0 & 15 \\ 
-   & PM density (10km) &  &  &   1.423 &   4.01 & 0 & 41.85 \\ 
-   & Europe and North America & 312 & 0.651 &   0.645 &   0.48 & 0 & 1 \\ 
-   & Region - Africa & 7 & 0.015 &   0.012 &   0.11 & 0 & 1 \\ 
-   & Region - Asia & 128 & 0.267 &   0.282 &   0.45 & 0 & 1 \\ 
-   & Region - Europe & 241 & 0.503 &   0.501 &   0.50 & 0 & 1 \\ 
-   & Region - Latin America & 22 & 0.046 &   0.042 &   0.20 & 0 & 1 \\ 
-   & Region - North America & 71 & 0.148 &   0.143 &   0.35 & 0 & 1 \\ 
-   & Region - Oceania & 10 & 0.021 &   0.019 &   0.14 & 0 & 1 \\ 
+ & PM density (country) &  &  & 4.3e-01 &   1.28 & 0.00077 & 27.26 \\ 
+   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.70 & 0.000087 & 10.81 \\ 
+   & Pop. (millions) country &  &  & 1.6e+02 & 297.59 & 0.037 & 1412.36 \\ 
+   & Nbr PM within 10km &  &  & 1.7e+00 &   3.07 & 0 & 15 \\ 
+   & PM density (10km) &  &  & 1.5e+00 &   4.15 & 0 & 41.85 \\ 
+   & Europe and North America & 311 & 0.651 & 6.5e-01 &   0.48 & 0 & 1 \\ 
+   & Region - Africa & 7 & 0.015 & 1.2e-02 &   0.11 & 0 & 1 \\ 
+   & Region - Asia & 128 & 0.268 & 2.8e-01 &   0.45 & 0 & 1 \\ 
+   & Region - Europe & 241 & 0.504 & 5.1e-01 &   0.50 & 0 & 1 \\ 
+   & Region - Latin America & 22 & 0.046 & 4.4e-02 &   0.20 & 0 & 1 \\ 
+   & Region - North America & 70 & 0.146 & 1.4e-01 &   0.35 & 0 & 1 \\ 
+   & Region - Oceania & 10 & 0.021 & 1.9e-02 &   0.14 & 0 & 1 \\ 
+   & year &  &  & 2.0e+03 &   5.75 & 2000 & 2021 \\ 
    \hline
@@
 
-Overall the entire life span, the average hazard rate is 0.78\%, which allows comparison to other studies of NPO closure.
+Overall the entire life span, the average hazard rate is 0.77\%, which allows comparison to other studies of NPO closure.
 While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})
@@
 places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
-While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.78\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
+While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.77\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
 It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon Apr 15 11:32:02 2024
+% Mon Apr 22 19:37:32 2024
 \begin{table}[ht]
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
   \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_wyr}\\ 
  \hline
-  \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .22 \; (0.37) \\ 
-   & Gender - Couple & .14 \; (0.36) \\ 
-   & Founder died & .28 \; (0.53) \\ 
-   \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .71 \; (0.48) \\ 
-   & Self-Identification - Collection & .14 \; (0.59) \\ 
-   & Self-Identification - Other & 1.32 \; (0.38)^{***} \\ 
-   & AN Ranking - Included & .50 \; (0.38) \\ 
-   & AN Ranking - Dropped & .82 \; (0.52) \\ 
-   & Founder name in Museum name & -.35 \; (0.33) \\ 
-   & MOW inclusion & -.90 \; (0.40)^{*} \\ 
-   \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .56 \; (0.42) \\ 
-   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .29 \; (0.11)^{**} \\ 
-   & Nbr PM within 10km & .30 \; (0.09)^{***} \\ 
-   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
+  \multicolumn{4}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & .16 \; (0.37) & .16 \; (0.37) \\ 
+   & Gender - Couple & .20 \; (0.36) & .13 \; (0.37) \\ 
+   & Founder died & -.06 \; (0.57) & -.02 \; (0.56) \\ 
+   \multicolumn{4}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .93 \; (0.49) & .83 \; (0.48) \\ 
+   & Self-Identification - Collection & .34 \; (0.59) & .36 \; (0.59) \\ 
+   & Self-Identification - Other & 1.45 \; (0.39)^{***} & 1.38 \; (0.39)^{***} \\ 
+   & AN Ranking - Included & .26 \; (0.38) & .22 \; (0.38) \\ 
+   & AN Ranking - Dropped & .81 \; (0.51) & .66 \; (0.52) \\ 
+   & Founder name in Museum name & -.44 \; (0.33) & -.42 \; (0.33) \\ 
+   & Exhibition any & .13 \; (0.33) &  \\ 
+   & Exhibition any last 5 years &  & .39 \; (0.32) \\ 
+   \multicolumn{4}{l}{\textbf{Environment}} \\ 
+ & Time Period 2005-2009 &  & .40 \; (1.16) \\ 
+   & Time Period 2010-2014 &  & 1.28 \; (1.04) \\ 
+   & Time Period 2015-2019 &  & 1.43 \; (1.03) \\ 
+   & Time Period 2020-2024 &  & 1.51 \; (1.05) \\ 
+   & PM density (country) & .63 \; (0.45) & .52 \; (0.51) \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .32 \; (0.11)^{**} & .30 \; (0.12)^{**} \\ 
+   & Nbr PM within 10km & .29 \; (0.09)^{**} & .26 \; (0.09)^{**} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} & -.09 \; (0.04)^{**} \\ 
    \hline
- & Museum-years & 6423 \\ 
-   & Closures & 52 \\ 
-   & log. Likelihood & -253.41 \\ 
-   & AIC & 536.82 \\ 
-   & BIC & 566.09 \\ 
+ & Museum-years & 5862 & 5862 \\ 
+   & Closures & 51 & 51 \\ 
+   & log. Likelihood & -246.02 & -241.64 \\ 
+   & AIC & 522.03 & 521.28 \\ 
+   & BIC & 551.01 & 557.99 \\ 
    \hline 
- \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
 \end{tabular}
@@
 Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research.
+
+environment can be measured more
+\begin{itemize}
+\item geocoding of other institutiosn
+\item tax incentives
+\item government spending
+\end{itemize}
+-> this might futher specify the niches in which PMs can endure
 \end{document}

### 2024-04-22 scripts/regression.R

@@ -921,7 +921,7 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         
         r_pop4 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
                             slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-                            proxcnt10*popm_circle10 + exhbrollany,
+                            proxcnt10*popm_circle10 + exhbany,
                        dt_pmyear),
 
         
@@ -930,6 +930,7 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
                             slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
                             proxcnt10*popm_circle10 + exhbrollany + time_period,
                            dt_pmyear)
+                           # dt_pmyear[iso3c != "KOR"])
          ## copy(dt_pmyear)[, reg6 := factor(reg6, labels = c("OC", "NALUL","EU","AS", "LA", "AF"))])
                        
         

### 2024-04-23 texts/paper_closing.tex
add table of self-ID examples

@@
 
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Tue Apr 23 17:09:15 2024
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrll}
+  \hline 
+ \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
+ \hline
+ Museum & 177 & Museum & Museum Kampa, Museum Barberini \\ 
+  Foundation & 101 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
+  Collection &  74 & Collection & The Farjam Collection, Sammlung Boros \\ 
+  None &  56 & Other & The Bunker, The Broad \\ 
+  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
+  Art space &  12 & Other & El Espacio 23, Qiao Space \\ 
+  Gallery &  11 & Other & Saatchi Gallery, Galerie C15 \\ 
+  House / villa &  10 & Other & Villa La Fleur, Casa Daros Rio \\ 
+  Institute &   9 & Other & Instituto Inhotim, Woods Art Institute \\ 
+  Kunsthalle &   7 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
+  Park / garden &   4 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
+   \hline
+\end{tabular}
+\caption{Selfidentification} 
+\label{tbl:t_selfid}
+\end{table}
+
 Two measures are constructed that aim to capture an effect of legitimacy on closing.
-First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent).
+First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
 Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might very well shape expectations and influence forms of engagement.

### 2024-04-23 scripts/cfg.R

@@ -26,7 +26,12 @@ gc_tbls <- function(c_tblargs) {
         t_sumstats = list(
             dt_pmyear = quote(dt_pmyear),
             dt_pmcpct = quote(dt_pmcpct),
-            caption = "Summary Statistics")
+            caption = "Summary Statistics"),
+        t_selfid = list(
+            dt_pmx = quote(dt_pmx),
+            dt_pmyear = quote(dt_pmyear),
+            caption = "Selfidentification"
+        )
     )
 
     

### 2024-04-23 scripts/descriptives.R

@@ -152,3 +152,80 @@ gt_sumstats <- function(dt_pmyear, dt_pmcpct) {
     
 
 }
+
+
+gt_selfid <- function(dt_pmx, dt_pmyear) {
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
+    1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
+    gw_fargs(match.call())
+    #' @param dt_pmx for name
+    #' @param dt_pmyear for only using those that are used eventually
+
+    
+    ## manually set some examples
+    l_examples <- list(
+        "Museum" = c("Museum Kampa", "Museum Barberini", "Kunstmuseum Walter", "Rubin Museum Of Art"),
+        "None" = c("The Bunker", "The Broad", "Magasin III", "Tank Shanghai"), # can't have empty name
+        "Foundation" = c("Marciano Art Foundation", "Hill Art Foundation", "Luma Foundation", "Kunststiftung Poll"),
+        "Collection" = c("The Farjam Collection", "Sammlung Boros", "Collezione Gori", "de la Cruz Collection"),
+        ## "Castle" = c("Kasteel Wijlre Estate", "Castello Di Ama"),
+        "Center" = c("Dairy Art Centre", "Art Center Nabi", "Faena Art Center", "Storm King Art Center"),
+        "Kunsthalle" = c("Kunsthalle Würth", "G2 Kunsthalle", "Kunsthalle Hgn", "Kunsthalle Messmer"),
+        "Institute" = c("Instituto Inhotim", "Woods Art Institute", "Instituto Figueiredo Ferraz"),
+        "House / villa" = c("Villa La Fleur", "Casa Daros Rio", "Kunst(Zeug)Haus", "La Maison Rouge"),
+        "Art space" = c("El Espacio 23", "Qiao Space", "Space*C", "Yarat Art Space"),
+        "Gallery" = c("Saatchi Gallery", "Galerie C15", "Galeria EGO", "Scrap Metal Gallery"),
+        "Park / garden" = c("Schlosspark Eyebesfeld", "Il Giardino dei Lauri", "Skulpturenpark Waldfrieden")
+        ## "Wine estate" = c("Donum Estate",
+    )
+
+    nbr_examples <- 2
+
+    ## convert to 
+    dt_examples <- imap(l_examples,
+                        ~data.table(slfidfcn = .y,
[…]

### 2024-04-23 scripts/cfg.R
add dummies for great recession and Covid

@@ -181,6 +181,8 @@ gc_vvs <- function() {
         year                      = "year",
         "I(year^2)"               = "year^2",
         time_period               = "Time Period (5 years)",
+        covid                     = "Covid Pandemic (2020/21)",
+        recession                 = "Great Recession (2008/09)",
         GLOBAL                    = "Global") # from cox.zph
     
     l_vrblgrps <- list(# variable groups
@@ -191,9 +193,9 @@ gc_vvs <- function() {
                       exhbqntl_year, "I(exhbqntl_year^2)",
                       exhbprop_top10_log, exhbprop_top10_utf, exhbqntl_roll, "I(exhbqntl_roll^2)"), 
         envir    = .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
-                      west, reg6,
+                      west, reg6, 
                       pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10",
-                      year, "I(year^2)",  time_period),
+                      year, "I(year^2)",  time_period, covid, recession),
         misc     = .c(GLOBAL)
     )
 
@@ -205,11 +207,12 @@ gc_vvs <- function() {
                    year, "I(year^2)", time_period,
                    exhbany, exhbrollany, 
                    exhbqntl_cy, exhbqntl_year, "I(exhbqntl_year^2)", exhbprop_top10_log, exhbprop_top10_utf,
-                   exhbqntl_roll, "I(exhbqntl_roll^2)")
+                   exhbqntl_roll, "I(exhbqntl_roll^2)",
+                   covid, recession)
 
     ## specify variable type: binary, numeric, categorical
     l_vrbltypes <- list(        
-        bin = .c(founder_dead, muem_fndr_name, mow, west, exhbany, exhbrollany),
+        bin = .c(founder_dead, muem_fndr_name, mow, west, exhbany, exhbrollany, covid, recession),
         num = .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
                  pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10", PC1, PC2,
                  year, "I(year^2)",

### 2024-04-23 scripts/closing_main.R

@@ -170,7 +170,7 @@ dt_pmcpct <- gd_pmcpct(dt_pmyear) # time-invariant variables (UoA PM, not pm-yea
 
 l_mdls <- gl_mdls(dt_pmyear, dt_pmcpct) # generate models
                                         # set model names for t_reg_coxph
-l_mdlnames_coxph <- c("r_pop4")# , "r_pop4_wyr")
+l_mdlnames_coxph <- c("r_pop4" , "r_pop4_wyr", "r_pop4_wcrises")
 ## l_mdlnames_coxph <- c("r_pop4", paste0("r_wsize", 3:1))
 ## c("r_more", paste0("r_pop", c(1, 3:6)))
 ## "r_woaf", "r_waf_year", "r_waf_roll", "r_waf_roll2")

### 2024-04-23 scripts/regression.R

@@ -414,7 +414,9 @@ gd_pmyear_prep <- function(dt_pmx, dt_pmtiv, c_lvrs = c_lvrs) {
         ## founder death: 1 if year > deathyear, else 0 (before death or not dead at all)
         .[, founder_dead := fifelse(!is.na(deathyear),fifelse(year > deathyear, 1, 0), 0)] %>% 
         .[, `:=`(tstart = age, tstop = age+1)] %>% # set survival time interval variables
-        .[, time_period := as.factor(paste0("tp", 5*(floor(year/5))))]
+        .[, time_period := as.factor(paste0("tp", 5*(floor(year/5))))] %>%
+        .[, covid := fifelse(year %in% c(2020, 2021), 1, 0)] %>%
+        .[, recession := fifelse(year %in% c(2008, 2009), 1, 0)]
         
 
     ## get country population data
@@ -902,6 +904,8 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         ## some regional covariates
         r_reg6 = coxph(Surv(age, closing) ~ reg6, dt_pmcpct), # doesn't like to convert 
 
+        r_garbage = coxph(Surv(age, closing) ~ west + age, dt_pmcpct),
+
         ## compare cpct and long (year) data
         r_west_cpct = coxph(Surv(age, closing) ~ west, dt_pmcpct),
         r_west_year = coxph(Surv(age, closing) ~ west, dt_pmyear),
@@ -921,15 +925,22 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         
         r_pop4 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
                             slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-                            proxcnt10*popm_circle10 + exhbany,
+                            proxcnt10*popm_circle10 + exhbany ,
                        dt_pmyear),
 
         
 
         r_pop4_wyr = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
                             slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-                            proxcnt10*popm_circle10 + exhbrollany + time_period,
-                           dt_pmyear)
+                            proxcnt10*popm_circle10 + exhbany + covid,
+                           dt_pmyear),
+
[…]

### 2024-04-23 scripts/cfg.R
test again different density specifications, but keep pop4

@@ -164,6 +164,7 @@ gc_vvs <- function() {
         pmdens_circle10           = "PM density (10km)",
         "I(pmdens_circle10^2)"    = "PM density^2 (10km)",
         "proxcnt10:popm_circle10" = "Nbr PM (10km) * Pop (10km)",
+        "popm_circle10:I(proxcnt10^2)" = "Nbr PM (10km) * Pop^2 (10km)",
         west                      = "Europe and North America",
         reg6                      = "Region",
         an_inclusion              = "ArtNews Ranking inclusion",
@@ -181,8 +182,8 @@ gc_vvs <- function() {
         year                      = "year",
         "I(year^2)"               = "year^2",
         time_period               = "Time Period (5 years)",
-        covid                     = "Covid Pandemic (2020/21)",
         recession                 = "Great Recession (2008/09)",
+        covid                     = "Covid Pandemic (2020/21)",
         GLOBAL                    = "Global") # from cox.zph
     
     l_vrblgrps <- list(# variable groups
@@ -193,7 +194,7 @@ gc_vvs <- function() {
                       exhbqntl_year, "I(exhbqntl_year^2)",
                       exhbprop_top10_log, exhbprop_top10_utf, exhbqntl_roll, "I(exhbqntl_roll^2)"), 
         envir    = .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
-                      west, reg6, 
+                      west, reg6, "popm_circle10:I(proxcnt10^2)",
                       pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10",
                       year, "I(year^2)",  time_period, covid, recession),
         misc     = .c(GLOBAL)
@@ -204,7 +205,7 @@ gc_vvs <- function() {
     vrbls_tv <- .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
                    founder_dead, 
                    an_inclusion, pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10",
-                   year, "I(year^2)", time_period,
+                   year, "I(year^2)", time_period, "popm_circle10:I(proxcnt10^2)",
                    exhbany, exhbrollany, 
[…]

### 2024-04-23 scripts/closing_main.R

@@ -170,7 +170,7 @@ dt_pmcpct <- gd_pmcpct(dt_pmyear) # time-invariant variables (UoA PM, not pm-yea
 
 l_mdls <- gl_mdls(dt_pmyear, dt_pmcpct) # generate models
                                         # set model names for t_reg_coxph
-l_mdlnames_coxph <- c("r_pop4" , "r_pop4_wyr", "r_pop4_wcrises")
+l_mdlnames_coxph <- c("r_pop4")#, "r_pop5", "r_pop42")#  , ",r_pop4_wyr", "r_pop4_wcrises")
 ## l_mdlnames_coxph <- c("r_pop4", paste0("r_wsize", 3:1))
 ## c("r_more", paste0("r_pop", c(1, 3:6)))
 ## "r_woaf", "r_waf_year", "r_waf_roll", "r_waf_roll2")

### 2024-04-23 scripts/regression.R

@@ -904,7 +904,7 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         ## some regional covariates
         r_reg6 = coxph(Surv(age, closing) ~ reg6, dt_pmcpct), # doesn't like to convert 
 
-        r_garbage = coxph(Surv(age, closing) ~ west + age, dt_pmcpct),
+        ## r_garbage = coxph(Surv(age, closing) ~ west + age, dt_pmcpct),
 
         ## compare cpct and long (year) data
         r_west_cpct = coxph(Surv(age, closing) ~ west, dt_pmcpct),
@@ -925,20 +925,30 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         
         r_pop4 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
                             slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-                            proxcnt10*popm_circle10 + exhbany ,
+                            proxcnt10*popm_circle10 + exhbany + recession + covid,
                        dt_pmyear),
+
+        ## r_pop42 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
+        ##                     slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
+        ##                     proxcnt10*popm_circle10 + I(proxcnt10^2)*popm_circle10 + exhbany + recession + covid,
+        ##                dt_pmyear),
+
+        ## r_pop5 = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
+        ##                     slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
+        ##                     pmdens_circle10 + I(pmdens_circle10^2) + exhbany + recession + covid,
+        ##                dt_pmyear)
 
         
 
-        r_pop4_wyr = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
-                            slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
-                            proxcnt10*popm_circle10 + exhbany + covid,
-                           dt_pmyear),
+        ## r_pop4_wyr = coxph(Surv(tstart, tstop, closing) ~ gender + pmdens_cry + I(pmdens_cry^2) + 
+        ##                     slfidfcn + founder_dead + muem_fndr_name + an_inclusion +
[…]

### 2024-04-23 texts/paper_closing.tex
some more notes which need to be written out

@@
-% Created 2024-04-22 ma 19:57
+% Created 2024-04-23 di 20:31
 % Intended LaTeX compiler: pdflatex
@@
 In this paper, I address this gap by investigating the closure event of members of this new organizational form.
-This exercise does not only provide insights into private museums in particular, but also more generally into processes of organizational identity, especially regarding legitimation and reputation.
+Analysis which factors are associated with museum closures provides insight not only into the event of closing, but also into the ongoing processes of a private museums, such as dependency relationships.
+Furthermore, analyzing which museums survive allows to make informed speculations on the future of this recently emerged organizational form.
+
+\subsection*{private museum 3 crisis}
+
+Museums, including private museums, might be relatively resilient \cite{Geller_Salamon_2010_resilience}: 
+tightening belt, fundraising, entrepreneurial strategies, downsizing
+The form of museums also implies commitment of resources, larger than that of other NPOs, which in turn provides capabilities, e.g. staff that is able to search for alternative revenue sources.
+
+\subsection*{Private museums relationships}
+
+A private museum is entangled in a number of dependencies.
+A crucial one is the relationship to the founder, without whom the private museum would not exist.
+Founders often control some aspects of management/operations.
+While the exact power relationships within museums are hard to observe due to the lack of transparency, which makes it in particular to assess the role of third parties, it is plausible to assume that they cannot exist against the wishes of the founder.
+Next to exhibiting the founder's collection, they likely also to a large extent dependent on continued financial contributions of the founder, as museums are chronically unprofitable (which is evidenced by their high share of NPOs or publicly owned/run museums, rather than for-profit companies).
+While the lack of transparency again makes it hard to systematically assess the financial importance of founder contributions to the existence of museums, \textbf{anecdotal} evidence suggests it to be substantial \parencite{Velthuis_Gera_forthcoming_fragility}.
+
+Furthermore, private museums, as (non-profit) organizations, is deeply entangled with its environment.
+Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations are likely factors that contribute to its viability and hence longevity.
+While some of these aspects can be influenced by the founder (in particular the available audience, via being able to decide a location and the extent to which a museum should organize exhibitions), other are less so.
+In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
+The image that these parties have of the private museum might be substantial importance in guiding their decision-making.
 
@@
 Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
-Understandability \parencite{Glynn_Abzug_2002_names} might thus be limited if an organization is atypical \parencite{Rosch_1975_family}, i.e. displays an unusual combination of features.
-In the case of private museums, such cases might be combinations of features from house museums (e.g. accessibility only by appointment) with full-service museums (e.g. extensive activities). 
 Next to "hard" organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate.
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Apr 19 19:04:41 2024
+% Tue Apr 23 17:09:14 2024
 \begin{table}[ht]
@@
    & year &  &  & 2.0e+03 &   5.75 & 2000 & 2021 \\ 
+   & Time Period 2000-2004 &  &  & 1.0e-01 &   0.30 & 0 & 1 \\ 
+   & Time Period 2005-2009 &  &  & 1.7e-01 &   0.37 & 0 & 1 \\ 
+   & Time Period 2010-2014 &  &  & 2.6e-01 &   0.44 & 0 & 1 \\ 
+   & Time Period 2015-2019 &  &  & 3.3e-01 &   0.47 & 0 & 1 \\ 
+   & Time Period 2020-2024 &  &  & 1.5e-01 &   0.35 & 0 & 1 \\ 
    \hline
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon Apr 22 19:37:32 2024
+% Tue Apr 23 20:19:31 2024
 \begin{table}[ht]
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
   \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_wyr}\\ 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
  \hline
-  \multicolumn{4}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .16 \; (0.37) & .16 \; (0.37) \\ 
-   & Gender - Couple & .20 \; (0.36) & .13 \; (0.37) \\ 
-   & Founder died & -.06 \; (0.57) & -.02 \; (0.56) \\ 
-   \multicolumn{4}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .93 \; (0.49) & .83 \; (0.48) \\ 
-   & Self-Identification - Collection & .34 \; (0.59) & .36 \; (0.59) \\ 
-   & Self-Identification - Other & 1.45 \; (0.39)^{***} & 1.38 \; (0.39)^{***} \\ 
-   & AN Ranking - Included & .26 \; (0.38) & .22 \; (0.38) \\ 
-   & AN Ranking - Dropped & .81 \; (0.51) & .66 \; (0.52) \\ 
-   & Founder name in Museum name & -.44 \; (0.33) & -.42 \; (0.33) \\ 
-   & Exhibition any & .13 \; (0.33) &  \\ 
-   & Exhibition any last 5 years &  & .39 \; (0.32) \\ 
-   \multicolumn{4}{l}{\textbf{Environment}} \\ 
- & Time Period 2005-2009 &  & .40 \; (1.16) \\ 
-   & Time Period 2010-2014 &  & 1.28 \; (1.04) \\ 
-   & Time Period 2015-2019 &  & 1.43 \; (1.03) \\ 
-   & Time Period 2020-2024 &  & 1.51 \; (1.05) \\ 
-   & PM density (country) & .63 \; (0.45) & .52 \; (0.51) \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .32 \; (0.11)^{**} & .30 \; (0.12)^{**} \\ 
-   & Nbr PM within 10km & .29 \; (0.09)^{**} & .26 \; (0.09)^{**} \\ 
-   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} & -.09 \; (0.04)^{**} \\ 
+  \multicolumn{3}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & .16 \; (0.37) \\ 
+   & Gender - Couple & .17 \; (0.36) \\ 
+   & Founder died & -.06 \; (0.57) \\ 
+   \multicolumn{3}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .91 \; (0.49) \\ 
+   & Self-Identification - Collection & .33 \; (0.59) \\ 
+   & Self-Identification - Other & 1.44 \; (0.39)^{***} \\ 
+   & AN Ranking - Included & .27 \; (0.38) \\ 
+   & AN Ranking - Dropped & .76 \; (0.52) \\ 
+   & Founder name in Museum name & -.41 \; (0.33) \\ 
+   & Exhibition any & .13 \; (0.33) \\ 
+   \multicolumn{3}{l}{\textbf{Environment}} \\ 
+ & PM density (country) & .59 \; (0.46) \\ 
+   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .31 \; (0.11)^{**} \\ 
+   & Nbr PM within 10km & .28 \; (0.09)^{**} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
+   & Great Recession (2008/09) & -1.21 \; (1.02) \\ 
+   & Covid Pandemic (2020/21) & .27 \; (0.34) \\ 
    \hline
- & Museum-years & 5862 & 5862 \\ 
-   & Closures & 51 & 51 \\ 
-   & log. Likelihood & -246.02 & -241.64 \\ 
-   & AIC & 522.03 & 521.28 \\ 
-   & BIC & 551.01 & 557.99 \\ 
+ & Museum-years & 5862 \\ 
+   & Closures & 51 \\ 
+   & log. Likelihood & -244.54 \\ 
+   & AIC & 523.08 \\ 
+   & BIC & 555.92 \\ 
    \hline 
- \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
 \end{tabular}

### 2024-05-03 scripts/closing_main.R
task update, more doc comments

@@ -140,7 +140,7 @@ if ("memoised" %!in% class(gd_mow_info)) {
 START_YEAR <- 2000
 END_YEAR <- 2021
 
-
+# levers: configuration options
 c_lvrs <- list(
     dtti = c("af_size"),
     ## dtti = c(""),

### 2024-05-03 scripts/cfg.R
adjust founder death variable labels to three stages

@@ -213,13 +213,13 @@ gc_vvs <- function() {
 
     ## specify variable type: binary, numeric, categorical
     l_vrbltypes <- list(        
-        bin = .c(founder_dead, muem_fndr_name, mow, west, exhbany, exhbrollany, covid, recession),
+        bin = .c(muem_fndr_name, mow, west, exhbany, exhbrollany, covid, recession),
         num = .c(pmdens_cry, "I(pmdens_cry^2)", popm_circle10, popm_country, proxcnt10, "I(proxcnt10^2)",
                  pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10", PC1, PC2,
                  year, "I(year^2)", "popm_circle10:I(proxcnt10^2)",
                  exhbqntl_cy, exhbqntl_year, "I(exhbqntl_year^2)",
                  exhbprop_top10_log, exhbprop_top10_utf, exhbqntl_roll, "I(exhbqntl_roll^2)"),
-        cat = .c(gender, slfidfcn, reg6, an_inclusion, time_period))
+        cat = .c(gender, founder_dead, slfidfcn, reg6, an_inclusion, time_period))
 
 
     l_vrblgrp_lbls <- list(# variable group labels
@@ -263,7 +263,10 @@ gc_vvs <- function() {
     l_ctgterm_lbls <- list(# labels of terms of categorical variables
         list(vrbl = "gender", term = "genderF",      term_lbl = "Gender - Female"),
         list(vrbl = "gender", term = "gendercouple", term_lbl = "Gender - Couple"),
-        list(vrbl = "gender", term = "genderM",      term_lbl = "Gender - Male"),        
+        list(vrbl = "gender", term = "genderM",      term_lbl = "Gender - Male"),
+        list(vrbl = "founder_dead", term = "founder_deadalive", term_lbl = "Founder - alive"),
+        list(vrbl = "founder_dead", term = "founder_deadrecently_dead", term_lbl = "Founder - died recently"),
+        list(vrbl = "founder_dead", term = "founder_deadlong_dead", term_lbl = "Founder - died 2+ years ago"),
         list(vrbl = "slfidfcn", term = "slfidfcnmuseum",     term_lbl = "Self-Identification - Museum"),
         list(vrbl = "slfidfcn", term = "slfidfcnfoundation", term_lbl = "Self-Identification - Foundation"),
         list(vrbl = "slfidfcn", term = "slfidfcncollection", term_lbl = "Self-Identification - Collection"),

### 2024-05-03 scripts/regression.R

@@ -423,7 +423,7 @@ gd_pmyear_prep <- function(dt_pmx, dt_pmtiv, c_lvrs = c_lvrs) {
                                     fifelse(year %between% list(deathyear, deathyear + 2), "recently_dead", 
                                             fifelse(year > deathyear + 2, "long_dead", "alive")),
                                     "alive")] %>%
-        .[, founder_dead := factor(founder_dead, levels = c("long_dead", "alive", "recently_dead"))] %>% 
+        .[, founder_dead := factor(founder_dead, levels = c("alive", "recently_dead", "long_dead"))] %>% 
         .[, `:=`(tstart = age, tstop = age+1)] %>% # set survival time interval variables
         .[, time_period := as.factor(paste0("tp", 5*(floor(year/5))))] %>%
         .[, covid := fifelse(year %in% c(2020, 2021), 1, 0)] %>%

### 2024-05-03 texts/paper_closing.tex
paper update after PMDB update

@@
-% Created 2024-04-23 di 20:31
+% Created 2024-05-03 vr 10:56
 % Intended LaTeX compiler: pdflatex
@@
 
+resource-based: lack of audience, or many other people competing for audience
+\cite{Velthuis_Gera_forthcoming_fragility}:
+p.23: In other cases, the location of the museum is a factor in limited visitor interest. On the
+one hand, private museums located in metropolitan art centers tend to face competition over
+visitors  from  well-established  other  museums  in  the  vicinity.  On  the  other  hand,  private
+museums located outside of those centers can be confronted with a small local audience, and
+difficulties in attracting visitors from afar.
+
 \textbf{Hypothesis 3}: A private museum is more likely to close in a more competitive environment.
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Apr 23 17:09:15 2024
+% Fri May  3 10:55:27 2024
 \begin{table}[ht]
@@
  \hline
- Museum & 177 & Museum & Museum Kampa, Museum Barberini \\ 
-  Foundation & 101 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
-  Collection &  74 & Collection & The Farjam Collection, Sammlung Boros \\ 
-  None &  56 & Other & The Bunker, The Broad \\ 
+ Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
+  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
+  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
+  None &  64 & Other & The Bunker, The Broad \\ 
   Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
-  Art space &  12 & Other & El Espacio 23, Qiao Space \\ 
-  Gallery &  11 & Other & Saatchi Gallery, Galerie C15 \\ 
-  House / villa &  10 & Other & Villa La Fleur, Casa Daros Rio \\ 
-  Institute &   9 & Other & Instituto Inhotim, Woods Art Institute \\ 
-  Kunsthalle &   7 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
-  Park / garden &   4 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
+  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
+  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
+  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
+  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
+  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
+  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
    \hline
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Apr 23 17:09:14 2024
+% Fri May  3 10:55:26 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 274 & 0.573 & 5.9e-01 &   0.49 & 0 & 1 \\ 
-   & Gender - Female & 76 & 0.159 & 1.7e-01 &   0.38 & 0 & 1 \\ 
-   & Gender - Couple & 128 & 0.268 & 2.4e-01 &   0.43 & 0 & 1 \\ 
-   & Founder died & 57 & 0.119 & 9.3e-02 &   0.29 & 0 & 1 \\ 
+ & Gender - Male & 294 & 0.584 & 6.0e-01 &   0.49 & 0 & 1 \\ 
+   & Gender - Female & 79 & 0.157 & 1.7e-01 &   0.37 & 0 & 1 \\ 
+   & Gender - Couple & 130 & 0.258 & 2.3e-01 &   0.42 & 0 & 1 \\ 
+   & Founder - alive & 440 & 0.875 & 9.0e-01 &   0.30 & 0 & 1 \\ 
+   & Founder - died recently & 17 & 0.034 & 1.9e-02 &   0.13 & 0 & 1 \\ 
+   & Founder - died 2+ years ago & 46 & 0.091 & 7.9e-02 &   0.27 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 177 & 0.370 & 4.0e-01 &   0.49 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 101 & 0.211 & 1.9e-01 &   0.39 & 0 & 1 \\ 
-   & Self-Identification - Collection & 74 & 0.155 & 1.4e-01 &   0.35 & 0 & 1 \\ 
-   & Self-Identification - Other & 126 & 0.264 & 2.6e-01 &   0.44 & 0 & 1 \\ 
-   & Founder name in Museum name & 228 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
-   & MOW inclusion & 91 & 0.190 & 2.8e-01 &   0.45 & 0 & 1 \\ 
+ & Self-Identification - Museum & 190 & 0.378 & 4.1e-01 &   0.49 & 0 & 1 \\ 
+   & Self-Identification - Foundation & 104 & 0.207 & 1.9e-01 &   0.39 & 0 & 1 \\ 
+   & Self-Identification - Collection & 69 & 0.137 & 1.3e-01 &   0.34 & 0 & 1 \\ 
+   & Self-Identification - Other & 140 & 0.278 & 2.7e-01 &   0.45 & 0 & 1 \\ 
+   & Founder name in Museum name & 240 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
+   & MOW inclusion & 92 & 0.183 & 2.7e-01 &   0.45 & 0 & 1 \\ 
    & AN Ranking - Not Included &  &  & 8.0e-01 &   0.40 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  & 1.5e-01 &   0.36 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  & 5.6e-02 &   0.23 & 0 & 1 \\ 
-   & Exhibition any &  &  & 6.5e-01 &   0.48 & 0 & 1 \\ 
-   & Exhibition any last 5 years &  &  & 4.7e-01 &   0.50 & 0 & 1 \\ 
-   & PC1 (Size) & 74.6913323980041 & 0.156 & 1.3e-01 &   1.88 & -6.4 & 2.62 \\ 
-   & PC2 (Support) & 58.6876842646085 & 0.123 & 1.6e-01 &   1.50 & -5 & 2.74 \\ 
+   & AN Ranking - Included &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
+   & AN Ranking - Dropped &  &  & 5.3e-02 &   0.23 & 0 & 1 \\ 
+   & Exhibition any &  &  & 6.3e-01 &   0.48 & 0 & 1 \\ 
+   & Exhibition any last 5 years &  &  & 4.6e-01 &   0.50 & 0 & 1 \\ 
+   & PC1 (Size) & 112.930441195886 & 0.225 & 1.8e-01 &   1.90 & -6.5 & 2.61 \\ 
+   & PC2 (Support) & 90.555299883145 & 0.180 & 2.0e-01 &   1.52 & -5.1 & 2.71 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density (country) &  &  & 4.3e-01 &   1.28 & 0.00077 & 27.26 \\ 
-   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.70 & 0.000087 & 10.81 \\ 
-   & Pop. (millions) country &  &  & 1.6e+02 & 297.59 & 0.037 & 1412.36 \\ 
-   & Nbr PM within 10km &  &  & 1.7e+00 &   3.07 & 0 & 15 \\ 
-   & PM density (10km) &  &  & 1.5e+00 &   4.15 & 0 & 41.85 \\ 
-   & Europe and North America & 311 & 0.651 & 6.5e-01 &   0.48 & 0 & 1 \\ 
-   & Region - Africa & 7 & 0.015 & 1.2e-02 &   0.11 & 0 & 1 \\ 
-   & Region - Asia & 128 & 0.268 & 2.8e-01 &   0.45 & 0 & 1 \\ 
-   & Region - Europe & 241 & 0.504 & 5.1e-01 &   0.50 & 0 & 1 \\ 
-   & Region - Latin America & 22 & 0.046 & 4.4e-02 &   0.20 & 0 & 1 \\ 
-   & Region - North America & 70 & 0.146 & 1.4e-01 &   0.35 & 0 & 1 \\ 
-   & Region - Oceania & 10 & 0.021 & 1.9e-02 &   0.14 & 0 & 1 \\ 
-   & year &  &  & 2.0e+03 &   5.75 & 2000 & 2021 \\ 
+ & PM density (country) &  &  & 4.5e-01 &   1.26 & 0.00077 & 27.26 \\ 
+   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.68 & 0.000087 & 10.81 \\ 
+   & Pop. (millions) country &  &  & 1.6e+02 & 292.68 & 0.037 & 1412.36 \\ 
+   & Nbr PM within 10km &  &  & 1.8e+00 &   3.14 & 0 & 16 \\ 
+   & PM density (10km) &  &  & 1.7e+00 &   4.93 & 0 & 76.37 \\ 
+   & Europe and North America & 320 & 0.636 & 6.4e-01 &   0.48 & 0 & 1 \\ 
+   & Region - Africa & 8 & 0.016 & 1.2e-02 &   0.11 & 0 & 1 \\ 
+   & Region - Asia & 142 & 0.282 & 2.9e-01 &   0.45 & 0 & 1 \\ 
+   & Region - Europe & 248 & 0.493 & 5.0e-01 &   0.50 & 0 & 1 \\ 
+   & Region - Latin America & 23 & 0.046 & 4.2e-02 &   0.20 & 0 & 1 \\ 
+   & Region - North America & 72 & 0.143 & 1.4e-01 &   0.34 & 0 & 1 \\ 
+   & Region - Oceania & 10 & 0.020 & 1.9e-02 &   0.13 & 0 & 1 \\ 
+   & year &  &  & 2.0e+03 &   5.72 & 2000 & 2021 \\ 
    & Time Period 2000-2004 &  &  & 1.0e-01 &   0.30 & 0 & 1 \\ 
@@
    & Time Period 2015-2019 &  &  & 3.3e-01 &   0.47 & 0 & 1 \\ 
-   & Time Period 2020-2024 &  &  & 1.5e-01 &   0.35 & 0 & 1 \\ 
+   & Time Period 2020-2024 &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
+   & Great Recession (2008/09) &  &  & 7.6e-02 &   0.27 & 0 & 1 \\ 
+   & Covid Pandemic (2020/21) &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
    \hline
@@
 
-Overall the entire life span, the average hazard rate is 0.77\%, which allows comparison to other studies of NPO closure.
+Overall the entire life span, the average hazard rate is 0.87\%, which allows comparison to other studies of NPO closure.
 While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})
@@
 \begin{table}[htbp]
-\caption{\label{tbl:litreview}Hazard rates in studies of museums art Art NPOs}
+\caption{\label{tbl:litreview}Hazard rates in studies of museums and art NPOs}
 \centering
-\begin{tabular}{llll}
+\begin{tabular}{lll}
 \hline
-study & population & avg. hazard rate & org years\\
+study & population & avg. hazard rate\\
 \hline
-\cite{Hager_2001_vulnerability} & Art Museums & 2.4\% & \\
-\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\% & \\
+\cite{Hager_2001_vulnerability} & Art Museums & 2.4\%\\
+\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\%\\
+\cite{Bowen_1994_charitable} & Museums & 1.1\%\\
 \hline
-\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\% & \\
-\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\% & \\
+\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\%\\
+\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\%\\
 \hline
@@
 places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
-While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.77\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
+While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.87\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
 It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
@@
 \cite{Clifford_2018_reinforcing} & Charities & 2\%-5\% & Reg. of Charities (UK)\\
-\cite{Mayer_2022_slimmer} & public charities & 0.17\% & IRS\\
+\cite{Mayer_2022_simmer} & public charities & 0.17\% & IRS\\
 \hline
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Apr 23 20:19:31 2024
+% Fri May  3 10:55:34 2024
 \begin{table}[ht]
@@
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .16 \; (0.37) \\ 
-   & Gender - Couple & .17 \; (0.36) \\ 
-   & Founder died & -.06 \; (0.57) \\ 
+ & Gender - Female & .02 \; (0.34) \\ 
+   & Gender - Couple & -.10 \; (0.32) \\ 
+   & Founder - died recently & 1.09 \; (0.61) \\ 
+   & Founder - died 2+ years ago & -.06 \; (0.55) \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .91 \; (0.49) \\ 
-   & Self-Identification - Collection & .33 \; (0.59) \\ 
-   & Self-Identification - Other & 1.44 \; (0.39)^{***} \\ 
-   & AN Ranking - Included & .27 \; (0.38) \\ 
-   & AN Ranking - Dropped & .76 \; (0.52) \\ 
-   & Founder name in Museum name & -.41 \; (0.33) \\ 
-   & Exhibition any & .13 \; (0.33) \\ 
+ & Self-Identification - Foundation & .25 \; (0.42) \\ 
+   & Self-Identification - Collection & -.46 \; (0.54) \\ 
+   & Self-Identification - Other & 1.12 \; (0.31)^{***} \\ 
+   & AN Ranking - Included & .25 \; (0.35) \\ 
+   & AN Ranking - Dropped & .51 \; (0.50) \\ 
+   & Founder name in Museum name & .09 \; (0.28) \\ 
+   & Exhibition any & -.22 \; (0.27) \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .59 \; (0.46) \\ 
-   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .31 \; (0.11)^{**} \\ 
-   & Nbr PM within 10km & .28 \; (0.09)^{**} \\ 
-   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
-   & Great Recession (2008/09) & -1.21 \; (1.02) \\ 
-   & Covid Pandemic (2020/21) & .27 \; (0.34) \\ 
+ & PM density (country) & .63 \; (0.35) \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
+   & Great Recession (2008/09) & -1.61 \; (1.01) \\ 
+   & Covid Pandemic (2020/21) & .39 \; (0.29) \\ 
    \hline
- & Museum-years & 5862 \\ 
-   & Closures & 51 \\ 
-   & log. Likelihood & -244.54 \\ 
-   & AIC & 523.08 \\ 
-   & BIC & 555.92 \\ 
+ & Museum-years & 6096 \\ 
+   & Closures & 68 \\ 
+   & log. Likelihood & -338.36 \\ 
+   & AIC & 712.73 \\ 
+   & BIC & 752.68 \\ 
    \hline 

### 2024-05-31 scripts/closing_main.R
add model generating function, mow naming convention

@@ -32,6 +32,7 @@ library(boot)            # bootstrapping for instantaneous hazard SE calculation
 library(marginaleffects) # for condmef plots (conditional marginal effects)
 library(texreg, include.only = c("screenreg", "texreg")) ## inspection of results
 library(Hmisc, include.only = "latexTranslate")  # latexTranslate
+library(stringr)         # for str_count, makes MOW naming convention processing easier
 
 
 ## LOCS <- list(PROJDIR = "/home/johannes/Dropbox/phd/papers/closing/")
@@ -249,6 +250,7 @@ gdtbl("t_reg_coxph")
 
 
 print("everything is DONE")
+stop("everything is DONE")
 
 ## longitudinal development of variables
 
@@ -280,5 +282,8 @@ dt_selfid_mission %>%
     geom_col(position = position_dodge())
     
 
-## library(stringr)
-## str_count
+
+
+
+
+

### 2024-05-31 scripts/descriptives.R

@@ -241,6 +241,7 @@ gt_selfid <- function(dt_pmx, dt_pmyear) {
 ## ** numbers
 
 gn_mow_prop_museum <- function() {
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
     #' generates info on how many MOWs museums have "museum" in their name
     
     l_form_strs <- list(

### 2024-05-31 scripts/regression.R

@@ -1103,7 +1103,7 @@ gp_hazard <- function(dt_pmcpct, cutwidth, bw.smooth) {
 
     leg_labels <- c("gamma" = "Epanechnikov-Kernel (5 years bandwidth)",
                     "epi" = sprintf("Piecewise-Constant (%s years)", cutwidth))
-
+    
 
     ggplot() +
         geom_step(copy(dt_pehaz)[src=="w1"][, src := "epi"], # awkward renaming 
@@ -1280,6 +1280,49 @@ gc_pmdb_tests <- function(dt_pmx, dt_pmyear, dt_pmcpct) {
 
 }
 
+gf_coxph_close <- function(vrbls_to_add = NULL, vrbls_to_yeet = NULL) {
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
+    1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
+    
+    #' generate coxph model formula
+    #' @param vrbls_to_add vector of variables to add
+    #' @param vrbls_to_yeet vector of variables to remove
+
+    vrbls_base <- c("gender",
+                    "pmdens_cry",
+                    "I(pmdens_cry^2)", 
+                    "slfidfcn",
+                    "founder_dead",
+                    "muem_fndr_name",
+                    "an_inclusion",
+                    "proxcnt10",
+                    "popm_circle10",
+                    "proxcnt10:popm_circle10",
+                    "exhbany",
+                    "recession",
+                    "covid")
+
+
+    if (len(intersect(vrbls_to_add, vrbls_to_yeet)) > 0) {stop("can't add and yeet the same")}
+    
+
+    vrbls_touse <- setdiff(vrbls_base, vrbls_to_yeet) %>%
+        union(vrbls_to_add)
+    
+
+    f_coxph_close <- sprintf("Surv(tstart, tstop, closing) ~ %s", paste(vrbls_touse, collapse = " + ")) %>%
+        as.formula
+
+    return(f_coxph_close)
+
+}
+
+
+
+
+    
+
+
 gl_mdls <- function(dt_pmyear, dt_pmcpct) {
     gw_fargs(match.call())
 
@@ -1309,28 +1352,19 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         ##                dt_pmyear),
 
         
[…]

### 2024-05-31 texts/paper_closing.tex
minor lit review and text updates (latex export)

@@
-% Created 2024-05-03 vr 10:56
+% Created 2024-05-30 do 10:16
 % Intended LaTeX compiler: pdflatex
@@
  pdfsubject={},
- pdfcreator={Emacs 29.2 (Org mode 9.6.26)}, 
+ pdfcreator={Emacs 29.3 (Org mode 9.6.26)}, 
  pdflang={English}}
@@
 
-\subsection*{private museum 3 crisis}
+\subsection*{lack of regulation -> museums are relatively free as long as they have money}
 
-Museums, including private museums, might be relatively resilient \cite{Geller_Salamon_2010_resilience}: 
-tightening belt, fundraising, entrepreneurial strategies, downsizing
-The form of museums also implies commitment of resources, larger than that of other NPOs, which in turn provides capabilities, e.g. staff that is able to search for alternative revenue sources.
+Museums are subject to relatively little regulation (the term "museum" is not a legally protected term and can be generally used without certification \parencite{Museumsbund_ICOMDE_2006_standards,Moore_2022_best,Lister_2023_marketing}.
+Museum associations on the national (e.g.
+American Alliance of Museums (AAM) for the United States, Museumsbund for Germany) or international (International council of museums, ICOM) level exist, which aim to standardize e.g.
+museum setup and operations, such as in relations to ethics \parencite{ICOM_2016_ethics} or sustainability \parencite{Bickersteth_2016_environment}.
+Membership for institutions is voluntary, and in practice limited:
+ICOM has around 3,000 institutional members \parencite{ICOM_2020_report19}, a relatively small fraction of the over 104,000 museums estimated to exist globally \parencite{UNESCO_2021_covid}.
+\footnote{The absence of clear criteria what constitutes a museum prevents standardized data collection which would be necessary to generate exact numbers.}
+National associations fare somewhat better, with e.g.
+the AAM representing over 4,000 of the country's 35,000 museums \parencite{LOC_2019_AAM}, and the German Museumsbund representing over 1,300 \parencite{Museumsbund_2024_mitgliedmuseen} of Germany's 7,120 museums \parencite{IMF_2024_museumsstatistik}.
+Even among its members promoting standards appears difficult, as shown in the establishment of the museum definition:
+After an ICOM proposal was rejected in 2019 after heated debates, an 18-month, four-round deliberation process involving 126 national committees was required to agree on a new definition by 2022 \parencite{Robinson_2021_debating,Seymour_2022_definition}.
 
@@
 
-\subsection*{Private museums}
-
-Investigating the survival prospects of private museum furthermore illucidates the long-term development of the organizational form as a whole.
-While the composition of private museums is not only influenced by closures, but also by foundings, analysing the former provides insights in the sustainability of
-
-Given the non-significant gender difference, it can be expected that (unless given a strong increase in founding by women) the population of private museums will continue to remain a dominated affair\footnote{The point estimates, which are higher for women and couples, albeit not significantly so, even point towards a slight expansion of the proportion of museums established by men.}
-The role of the founder is two sided.
-Death and exclusion from a prestigious ranking are not associated with a higher risk of closure, which indicates that private museums have attained a substantial degree of institutionalization.
-On the other hand, self-identifying as an institution which is not a museum, foundation or collection possibly reflects a kind of founder attitudes which substantially influences survival chances.
-Founders who are less interested in establish institutions might be more inclined to choose a name which less reflects this ambition. 
-One way of conceptualizing this distinction might then be that whereas involuntary, externally imposed events are less able to close museums of otherwise motivated founders, some founders might from the very beginning voluntarily decide to not establish a museum that is intended for perpetuity.
-
-However, this group is somewhat small.
-Of the XXX museums included in the database, XXX do not carry the term museum, foundation or collection.
-Thus given this low share, and the corresponding  higher closing rate, a possible future for the private museum population might be increased institutionalization and consolidation of relatively robust organizations.
-The effects of location might be seen
-On the one hand, museum location is chosen by the founder at the time of founding (or rather, several years in advance).
-This gives founders substantial choice in the size and composition of the potential audience who will be able to easily assess the museum.
-On the other hand, collectors are less able to influence what plans other collectors might have.
-What may have been at one point been identified as a promising location without substantial competition may turn out to be a much less fertile ground as soon as other collectors start eyeing the same region for their own private museum projects.
-In particular private museum in rural locations with low population densities seem to be at risk when other museums open in the neighborhood. 
-This is not to say that private museums cannot endure in areas with low population densities. 
-In fact, at low numbers of private museums in the neighborhood their survival prospects are better than those located in larger cities.
-These larger cities with low private museum counts are possibly also characterized by lower numbers of other cultural institutions as well as an audience less interested in postmaterial art consumption.
-
-The lack of a relation between temporary exhibitions and survival prospect is somewhat unexpected.
-It was expected that as temporary exhibitions constitute one of the main tasks of a museums operations, organizing them would benefit a museum financially (via visitor fees) and symbolically (via prestige of other art field actors, which might be developed into further contacts), leading to higher survival chances\footnote{Furthermore, the ability to organization exhibitions likely reflects museum resources, which should also enhance survival.}
-However, organizing exhibitions does not seem to bestow benefits for the museums which organize them, nor do organizations seem to be organized only by established/sustainable/secure organizations.
-One possibility for this discrepancy could be that exhibitions are expensive, and whatever benefits gained from them are offset by the associated costs.
-One might see in this association again the importance of the founder:
-Founders who are committed to their museums will keep them alive, regardless of whether or not they plan to organize temporary exhibitions.
-
 \subsection*{Theoretical framework}
 
-As a substantial literature on organizational survival exists,
+As a substantial literature on organizational survival exists, thus
 
@@
 
-An identity that is legitimate (understandable) and favorable (positive) has been shown to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
+An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
 As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
@@
 Furthermore, identity of a private museum may be influenced by the identity of persons most closely affiliated with it, in particular the identity of its founders.
-Given that founders are the very reason behind the existence of these organizations, and sometimes plan these as their personal legacies \parencite{Walker_2019_collector}, founder status gains or losses may very well reflect on the wider organization and affect its survival propspects.
+Given that founders are the very reason behind the existence of these organizations, and sometimes plan these as their personal legacies \parencite{Walker_2019_collector}, founder status gains or losses may reflect on the wider organization and affect its survival propspects.
 
@@
 
+\subsubsection*{Shocks}
+
+External shocks can
+
+Museums, including private museums, might be relatively resilient \cite{Geller_Salamon_2010_resilience}: 
+tightening belt, fundraising, entrepreneurial strategies, downsizing
+The form of museums also implies commitment of resources, larger than that of other NPOs, which in turn provides capabilities, e.g. staff that is able to search for alternative revenue sources.
+
+\subsubsection*{Size}
+
+Where
+
 \subsubsection*{Other predictors of organizational survival}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri May  3 10:55:27 2024
+% Mon May 27 11:25:43 2024
 \begin{table}[ht]
@@
 First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
-Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might very well shape expectations and influence forms of engagement.
+Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might shape expectations and influence forms of engagement.
 In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums.
 
-Secondly, a binary predictor measures whether the museum is included in the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55.000 museums.
-While the exact criteria of the research process leading to the MOW database are not known, it is plausible that museums who correspond to an ideal-typical museum are more likely to be included.
-Assuming that museums are seen similarly by the creators of the MOW database and other audiences, inclusion in the MOW database constitutes a proxy for adherence to museum standards.
+To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55.000 museums, are analyzed.
+In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial naming convention.
+
+prevalence of museum founders to include the term museum in the name of their institution\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum}.
 
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri May  3 10:55:26 2024
+% Mon May 27 11:25:41 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 294 & 0.584 & 6.0e-01 &   0.49 & 0 & 1 \\ 
-   & Gender - Female & 79 & 0.157 & 1.7e-01 &   0.37 & 0 & 1 \\ 
-   & Gender - Couple & 130 & 0.258 & 2.3e-01 &   0.42 & 0 & 1 \\ 
-   & Founder - alive & 440 & 0.875 & 9.0e-01 &   0.30 & 0 & 1 \\ 
-   & Founder - died recently & 17 & 0.034 & 1.9e-02 &   0.13 & 0 & 1 \\ 
-   & Founder - died 2+ years ago & 46 & 0.091 & 7.9e-02 &   0.27 & 0 & 1 \\ 
+ & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
+   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
+   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
+   & Founder - alive &  &  & 0.903 & 0.30 & 0 & 1 \\ 
+   & Founder - died recently &  &  & 0.019 & 0.13 & 0 & 1 \\ 
+   & Founder - died 2+ years ago &  &  & 0.079 & 0.27 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 190 & 0.378 & 4.1e-01 &   0.49 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 104 & 0.207 & 1.9e-01 &   0.39 & 0 & 1 \\ 
-   & Self-Identification - Collection & 69 & 0.137 & 1.3e-01 &   0.34 & 0 & 1 \\ 
-   & Self-Identification - Other & 140 & 0.278 & 2.7e-01 &   0.45 & 0 & 1 \\ 
-   & Founder name in Museum name & 240 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
-   & MOW inclusion & 92 & 0.183 & 2.7e-01 &   0.45 & 0 & 1 \\ 
-   & AN Ranking - Not Included &  &  & 8.0e-01 &   0.40 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  & 5.3e-02 &   0.23 & 0 & 1 \\ 
-   & Exhibition any &  &  & 6.3e-01 &   0.48 & 0 & 1 \\ 
-   & Exhibition any last 5 years &  &  & 4.6e-01 &   0.50 & 0 & 1 \\ 
-   & PC1 (Size) & 112.930441195886 & 0.225 & 1.8e-01 &   1.90 & -6.5 & 2.61 \\ 
-   & PC2 (Support) & 90.555299883145 & 0.180 & 2.0e-01 &   1.52 & -5.1 & 2.71 \\ 
+ & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
+   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
+   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
+   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
+   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
+   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
+   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
+   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
+   & Exhibition any &  &  & 0.630 & 0.48 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density (country) &  &  & 4.5e-01 &   1.26 & 0.00077 & 27.26 \\ 
-   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.68 & 0.000087 & 10.81 \\ 
-   & Pop. (millions) country &  &  & 1.6e+02 & 292.68 & 0.037 & 1412.36 \\ 
-   & Nbr PM within 10km &  &  & 1.8e+00 &   3.14 & 0 & 16 \\ 
-   & PM density (10km) &  &  & 1.7e+00 &   4.93 & 0 & 76.37 \\ 
-   & Europe and North America & 320 & 0.636 & 6.4e-01 &   0.48 & 0 & 1 \\ 
-   & Region - Africa & 8 & 0.016 & 1.2e-02 &   0.11 & 0 & 1 \\ 
-   & Region - Asia & 142 & 0.282 & 2.9e-01 &   0.45 & 0 & 1 \\ 
-   & Region - Europe & 248 & 0.493 & 5.0e-01 &   0.50 & 0 & 1 \\ 
-   & Region - Latin America & 23 & 0.046 & 4.2e-02 &   0.20 & 0 & 1 \\ 
-   & Region - North America & 72 & 0.143 & 1.4e-01 &   0.34 & 0 & 1 \\ 
-   & Region - Oceania & 10 & 0.020 & 1.9e-02 &   0.13 & 0 & 1 \\ 
-   & year &  &  & 2.0e+03 &   5.72 & 2000 & 2021 \\ 
-   & Time Period 2000-2004 &  &  & 1.0e-01 &   0.30 & 0 & 1 \\ 
-   & Time Period 2005-2009 &  &  & 1.7e-01 &   0.37 & 0 & 1 \\ 
-   & Time Period 2010-2014 &  &  & 2.6e-01 &   0.44 & 0 & 1 \\ 
-   & Time Period 2015-2019 &  &  & 3.3e-01 &   0.47 & 0 & 1 \\ 
-   & Time Period 2020-2024 &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
-   & Great Recession (2008/09) &  &  & 7.6e-02 &   0.27 & 0 & 1 \\ 
-   & Covid Pandemic (2020/21) &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
+ & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
+   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
+   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
+   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
+   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
+   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
+   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
+   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
+   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
+   & Time Period 2000-2004 &  &  & 0.101 & 0.30 & 0 & 1 \\ 
+   & Time Period 2005-2009 &  &  & 0.166 & 0.37 & 0 & 1 \\ 
+   & Time Period 2010-2014 &  &  & 0.258 & 0.44 & 0 & 1 \\ 
+   & Time Period 2015-2019 &  &  & 0.331 & 0.47 & 0 & 1 \\ 
+   & Time Period 2020-2024 &  &  & 0.145 & 0.35 & 0 & 1 \\ 
+   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
+   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
    \hline
@@
 
-Overall the entire life span, the average hazard rate is 0.87\%, which allows comparison to other studies of NPO closure.
+Overall the entire life span, the average hazard rate is 0.90\%, which allows comparison to other studies of NPO closure.
 While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})
@@
 places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
-While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.87\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
+While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.90\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
 It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri May  3 10:55:34 2024
+% Mon May 27 11:25:51 2024
 \begin{table}[ht]
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
   \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_woenv}\\ 
  \hline
-  \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .02 \; (0.34) \\ 
-   & Gender - Couple & -.10 \; (0.32) \\ 
-   & Founder - died recently & 1.09 \; (0.61) \\ 
-   & Founder - died 2+ years ago & -.06 \; (0.55) \\ 
-   \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .25 \; (0.42) \\ 
-   & Self-Identification - Collection & -.46 \; (0.54) \\ 
-   & Self-Identification - Other & 1.12 \; (0.31)^{***} \\ 
-   & AN Ranking - Included & .25 \; (0.35) \\ 
-   & AN Ranking - Dropped & .51 \; (0.50) \\ 
-   & Founder name in Museum name & .09 \; (0.28) \\ 
-   & Exhibition any & -.22 \; (0.27) \\ 
-   \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .63 \; (0.35) \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
-   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
-   & Great Recession (2008/09) & -1.61 \; (1.01) \\ 
-   & Covid Pandemic (2020/21) & .39 \; (0.29) \\ 
+  \multicolumn{4}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & .02 \; (0.34) & .10 \; (0.34) \\ 
+   & Gender - Couple & -.10 \; (0.32) & -.15 \; (0.32) \\ 
+   & Founder - died recently & 1.09 \; (0.61) & 1.03 \; (0.61) \\ 
+   & Founder - died 2+ years ago & -.06 \; (0.55) & -.19 \; (0.56) \\ 
+   \multicolumn{4}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .25 \; (0.42) & .44 \; (0.41) \\ 
+   & Self-Identification - Collection & -.46 \; (0.54) & .00 \; (0.50) \\ 
+   & Self-Identification - Other & 1.12 \; (0.31)^{***} & 1.04 \; (0.30)^{***} \\ 
+   & AN Ranking - Included & .25 \; (0.35) & .26 \; (0.35) \\ 
+   & AN Ranking - Dropped & .51 \; (0.50) & .52 \; (0.49) \\ 
+   & Founder name in Museum name & .09 \; (0.28) & .06 \; (0.28) \\ 
+   & Exhibition any & -.22 \; (0.27) & -.22 \; (0.27) \\ 
+   \multicolumn{4}{l}{\textbf{Environment}} \\ 
+ & PM density (country) & .63 \; (0.35) &  \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) &  \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} &  \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  \\ 
+   & Great Recession (2008/09) & -1.61 \; (1.01) &  \\ 
+   & Covid Pandemic (2020/21) & .39 \; (0.29) &  \\ 
    \hline
- & Museum-years & 6096 \\ 
-   & Closures & 68 \\ 
-   & log. Likelihood & -338.36 \\ 
-   & AIC & 712.73 \\ 
-   & BIC & 752.68 \\ 
+ & Museum-years & 6096 & 6096 \\ 
+   & Closures & 68 & 68 \\ 
+   & log. Likelihood & -338.36 & -351.64 \\ 
+   & AIC & 712.73 & 725.28 \\ 
+   & BIC & 752.68 & 749.69 \\ 
    \hline 
- \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
 \end{tabular}
@@
 
+\subsection*{Discussion}
+
+Investigating the survival prospects of private museum furthermore illucidates the long-term development of the organizational form as a whole, as it provides insights into factors related to variation of sustainability and thereby into trends in composition.
+
+Given the non-significant gender difference, it can be expected that (unless given a strong increase in founding by women) the population of private museums will continue to remain a man-dominated affair.
+This finding also provides no evidence that female founders face gender-specific challenges that decrease the survival prospects of their private museums.
+
+The lack of a relation between temporary exhibitions and survival prospect is somewhat unexpected.
+It was expected that as temporary exhibitions constitute one of the main tasks of a museums operations, organizing them would benefit a museum financially (via visitor fees) and symbolically (via prestige of other art field actors, which might be developed into further contacts), leading to higher survival chances\footnote{Furthermore, the ability to organization exhibitions likely reflects museum resources, which should also enhance survival.}
+However, organizing exhibitions does not seem to bestow benefits for the museums which organize them, nor do organizations seem to be organized only by established/sustainable/secure organizations.
+One possibility for this discrepancy could be that exhibitions are expensive, and whatever benefits gained from them are offset by the associated costs.
+One might see in this association again the importance of the founder:
+Founders who are committed to their museums will keep them alive, regardless of whether or not they plan to organize temporary exhibitions.
+
+\subsubsection*{founder}
+
 \subsection*{Conclusion}
@@
 One way in which this can happen is when other parties, such as local governments other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
-Sometimes this involves changes in the composition of the board of directors, with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum, often to an extent that it no longer fits the working definition.
-Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was often not feasible to determine the date of such transitions\footnote{As a consequence of this, they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing.
+Sometimes this involves changes in the composition of the board of directors (or equivalent), with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum to an extent that it no longer fits the working definition.
+Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to generally determine the date of such transitions\footnote{As a consequence of this, they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing.
 However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
-Primarily this was due to the intransparency of these organizations, as well as the gradual process.
+The main issues that made the determination of the date impossible was the intransparency of these organizations (\texttt{event in the past, no track of organizational history}), as well as the gradual process.
 As the presence of non-founder members does not categorically exclude a museum from being categorized as private museum as long as third-party influence is limited, this influence can grow until the museum bears little resemblance to its former self.
@@
 -> this might futher specify the niches in which PMs can endure
+
+Museum characteristics might influence closing to a larger extent than has been considered here.
+For example, museum size, facilities, as well as marketing and outreach activities might be related to long-term survival prospect.
+For example, museums with more XXX might be more expensive to run, but on the other hand attract higher visitor numbers, cooperations and sponsorships. \texttt{liability of smallness}
+Furthermore, having XXX might reflect founder commitment/resources.
+While the original data collection included assessing various museum characteristics, such as XXX, it became clear that desk research was
+Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Internet archive, \texttt{subdomains} were archived much less frequently, and sometimes inaccessible despite being archived due to changes in webtechnology (such as flash).
+While it would be possible to
+absence of evidence as evidence of absence
+
+\textbf{supplementary material}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
+\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population}
+\end{figure}
 \end{document}

### 2024-05-31 scripts/regression.R
add model facet labels if multiple models are passed to pred_X plots

@@ -1975,14 +1975,18 @@ gp_pred_popprxcnt <- function(l_mdlnames, l_mdls, dt_pmyear) {
     ## plot_comparisons(l_mdls$r_pop4, variables = list(popm_circle10 = c(1,5)),
     ## condition = "proxcnt10", type  = "lp")
     
-    l_lbls <- sprintf("%sm pop. (%sth perc.)", l_popm_circle10_qntls, l_quantile_probs*100) %>%
-        setNames(l_popm_circle10_qntls)
+    ## set up labels: has to be vector
+    l_lbls <- c(
+        sprintf("%sm pop. (%sth perc.)", l_popm_circle10_qntls, l_quantile_probs*100) %>%
+        setNames(paste0("facet",l_popm_circle10_qntls)),
+        setNames(l_mdlnames, l_mdlnames)) %>% unlist
 
-    
 
-    p_pred_popprxnct <- dt_predres_mult %>% copy %>% .[, popm_circle10_mult := as.character(popm_circle10)] %>%
+    p_pred_popprxnct <- dt_predres_mult %>% copy %>%
+        .[, popm_circle10_mult := as.character(popm_circle10)] %>% # set up merging column
         ## .[popm_circle10_mult == 209] %>% print(n=40)
         .[dt_popm_circle10_fltr, on = "popm_circle10_mult"] %>%
+        .[, facet_popm_circle10 := paste0("facet", popm_circle10_mult)] %>%
         .[proxcnt10 < 12] %>% 
         ## .[popm_circle10_mult %in% l_popm_circle10_qntls] %>% 
         ## p_pred_popprxnct <- dt_predres_mult[popm_circle10*10 %in% c(1, 15, 30, 50)] %>% 
@@ -2009,7 +2013,8 @@ gp_pred_popprxcnt <- function(l_mdlnames, l_mdls, dt_pmyear) {
     if (len(l_mdlnames) > 1) {
         
         p_pred_popprxnct <- p_pred_popprxnct +
-            facet_grid(src~popm_circle10_mult, scales = "free", labeller = as_labeller(l_lbls))
+            facet_grid(src~facet_popm_circle10, scales = "free", labeller = as_labeller(l_lbls))
+    
         
     } else if (len(l_mdlnames) == 1) {
 
@@ -2044,10 +2049,12 @@ gp_pred_proxcntpop <- function(l_mdlnames, l_mdls, dt_pmyear) {
         as.character
 
[…]

### 2024-06-19 scripts/cfg.R
add number of museums to regression table

@@ -348,6 +348,7 @@ gc_vvs <- function() {
     
     ## information for gofs
     c_gof <- list(
+        list(gof_name = "nunits", digits = 0, gof_lbl = "Museums"),
         list(gof_name = "nobs",   digits = 0, gof_lbl = "Museum-years"),
         list(gof_name = "nevent", digits = 0, gof_lbl = "Closures"),
         list(gof_name = "logLik", digits = 2, gof_lbl = "log. Likelihood"),

### 2024-06-19 scripts/regression.R

@@ -2170,10 +2170,23 @@ gt_reg_coxph <- function(l_mdls, l_mdlnames) {
 
     l_mdls_slct <- map(l_mdlnames, ~chuck(l_mdls, .x))
 
-    l_mdlres <- map2(l_mdls_slct, l_mdlnames, ~gd_reg_coxph(.x, .y))
+    l_mdlres <- map2(l_mdls_slct, l_mdlnames, ~gd_reg_coxph(.x, .y, unit_name = "ID"))
+
+    ## gd_reg_coxph(l_mdls_slct[[2]], l_mdlnames[[2]], unit_name = "ID")
 
     dt_coef <- map(l_mdlres, ~chuck(.x, "dt_coef")) %>% rbindlist
     dt_gof <- map(l_mdlres, ~chuck(.x, "dt_gof")) %>% rbindlist
+
+    ## see how many units there are: use convention that model data.table is called "dt_"
+    ## and that unit has name ID
+    ## this is super not solid
+    ## l_call_objs <- rx %>% chuck("call") %>% as.list
+    ## dt_str <- l_call_objs[which(substring(l_call_objs, 1,3) == "dt_")]
+    ## dt_str <- "dt_pmyear[year > 2010]"
+    ## eval(parse(text = dt_str))
+    
+    
+    ## dt_mdl <- get(dt_str)
 
     c_vvs <- gc_vvs()
 

### 2024-06-19 scripts/cfg.R
add separate table for models with different time configs
models: default, time period, year opened, both

@@ -39,7 +39,11 @@ gc_tbls <- function(c_tblargs) {
         t_reg_coxph_timeslice = list(
             l_mdls = quote(l_mdls),
             l_mdlnames = quote(l_mdlnames_timeslice),
-            caption = "Cox PH regression results with different time slices")        
+            caption = "Cox PH regression results with different time slices"),
+        t_reg_coxph_timecfg = list(
+            l_mdls = quote(l_mdls),
+            l_mdlnames = quote(l_mdlnames_timecfg),
+            caption = "Cox PH regression results with different time configurations")
     )
 
     

### 2024-06-19 scripts/closing_main.R

@@ -180,8 +180,11 @@ dt_pmcpct <- gd_pmcpct(dt_pmyear) # time-invariant variables (UoA PM, not pm-yea
 
 
 l_mdls <- gl_mdls(dt_pmyear, dt_pmcpct) # generate models
-                                        # set model names for t_reg_coxph
-l_mdlnames_coxph <- list("r_pop4", "r_pop4_wyo", "r_pop4_wtp", "r_pop4_wyotp")
+## set model names for t_reg_coxph
+
+l_mdlnames_coxph <- list("r_pop4")
+
+
 
 
 ## "r_smol")#, "r_pop5", "r_pop42")#  , ",r_pop4_wyr", "r_pop4_wcrises")
@@ -198,6 +201,8 @@ l_mdlnames_coxph_density <- list("r_pop4", "r_wocryside", "r_onlycryside", "r_po
 ## compare whether patterns change if only recent data is used
 l_mdlnames_timeslice <- list("r_pop4", "r_2005", "r_2010", "r_2015")
 
+## check whether patterns depend on itme configuration (time period, year_opened, both)
+l_mdlnames_timecfg <- list("r_pop4", "r_pop4_wyo", "r_pop4_wtp", "r_pop4_wyotp")
 
 
 

### 2024-06-19 scripts/regression.R

@@ -2203,6 +2203,7 @@ gt_reg_coxph <- function(l_mdls, l_mdlnames) {
 
 gt_reg_coxph_density <- gt_reg_coxph
 gt_reg_coxph_timeslice <- gt_reg_coxph
+gt_reg_coxph_timecfg <- gt_reg_coxph
 
 
 gt_coxzph <- function(rx) {

### 2024-06-19 scripts/regression.R
fix bug that renamed year_opened to year_opened_[, which breaks jtls

@@ -509,9 +509,13 @@ gd_pmyear_prep <- function(dt_pmx, dt_pmtiv, c_lvrs = c_lvrs) {
 
 
     ## combine with time-invariant variables
-    dt_pmyear_wtiv <- join(dt_pmyear_waf,
+    dt_pmyear_wtiv <- join(dt_pmyear_waf, 
                            copy(dt_pmtiv)[, `:=`(iso3c=NULL, name = NULL)], ## yeet non-essential columns
-                           on = "ID") 
+                           on = "ID",
+                           drop.dup.cols = "x") # don't use year_opened from dt_pmyear_waf, but from dt_pmtiv
+
+    ## dt_pmyear_wtiv[, .SD, .SDcols = patterns("year_opened")] %>% setnames(c("x1", "x2")) %>%
+    ##     .[, diff := x1-x2] %>% .[, .N, diff]
 
     if (any(is.na(dt_pmyear_wtiv$mow))) {stop("some MOW is NA")}
 

### 2024-06-19 scripts/closing_main.R
minor cleaning

@@ -261,7 +261,7 @@ gdtbl("t_reg_coxph")
 ## gd_reg_coxph(l_mdls$r_more, "r_more")
 
 
-print("everything is DONE")
+
 stop("everything is DONE")
 
 ## longitudinal development of variables

### 2024-06-19 texts/paper_closing.tex
new latex version with new tables

@@
-% Created 2024-05-30 do 10:16
+% Created 2024-06-19 wo 11:22
 % Intended LaTeX compiler: pdflatex
@@
 
-\section*{Identity and the closure of private art museums}
+\section*{It's so over/Short-lived legacies: The closure of private art museums}
 
@@
 While the lack of transparency again makes it hard to systematically assess the financial importance of founder contributions to the existence of museums, \textbf{anecdotal} evidence suggests it to be substantial \parencite{Velthuis_Gera_forthcoming_fragility}.
+\textcite{Adam_2021_rise}
+\begin{itemize}
+\item pandemic potentially
+\item long-term funding
+\item motivations may change
+\item difficulties not anticipated
+\end{itemize}
 
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon May 27 11:25:43 2024
+% Fri May 31 14:28:54 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon May 27 11:25:41 2024
+% Fri May 31 14:28:52 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon May 27 11:25:51 2024
+% Sat Jun  8 13:10:23 2024
 \begin{table}[ht]
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
   \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_woenv}\\ 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_wyo} & \multicolumn{1}{l}{r\_pop4\_wtp} & \multicolumn{1}{l}{r\_pop4\_wyotp}\\ 
  \hline
-  \multicolumn{4}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .02 \; (0.34) & .10 \; (0.34) \\ 
-   & Gender - Couple & -.10 \; (0.32) & -.15 \; (0.32) \\ 
-   & Founder - died recently & 1.09 \; (0.61) & 1.03 \; (0.61) \\ 
-   & Founder - died 2+ years ago & -.06 \; (0.55) & -.19 \; (0.56) \\ 
-   \multicolumn{4}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .25 \; (0.42) & .44 \; (0.41) \\ 
-   & Self-Identification - Collection & -.46 \; (0.54) & .00 \; (0.50) \\ 
-   & Self-Identification - Other & 1.12 \; (0.31)^{***} & 1.04 \; (0.30)^{***} \\ 
-   & AN Ranking - Included & .25 \; (0.35) & .26 \; (0.35) \\ 
-   & AN Ranking - Dropped & .51 \; (0.50) & .52 \; (0.49) \\ 
-   & Founder name in Museum name & .09 \; (0.28) & .06 \; (0.28) \\ 
-   & Exhibition any & -.22 \; (0.27) & -.22 \; (0.27) \\ 
-   \multicolumn{4}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .63 \; (0.35) &  \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) &  \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} &  \\ 
-   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  \\ 
-   & Great Recession (2008/09) & -1.61 \; (1.01) &  \\ 
-   & Covid Pandemic (2020/21) & .39 \; (0.29) &  \\ 
+  \multicolumn{6}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & .02 \; (0.34) & .04 \; (0.34) & .03 \; (0.34) & .04 \; (0.34) \\ 
+   & Gender - Couple & -.10 \; (0.32) & -.13 \; (0.32) & -.12 \; (0.32) & -.12 \; (0.32) \\ 
+   & Founder - died recently & 1.09 \; (0.61) & 1.05 \; (0.62) & 1.09 \; (0.62) & 1.08 \; (0.62) \\ 
+   & Founder - died 2+ years ago & -.06 \; (0.55) & -.05 \; (0.55) & -.03 \; (0.55) & -.04 \; (0.55) \\ 
+   \multicolumn{6}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .25 \; (0.42) & .22 \; (0.42) & .22 \; (0.42) & .22 \; (0.42) \\ 
+   & Self-Identification - Collection & -.46 \; (0.54) & -.52 \; (0.54) & -.53 \; (0.54) & -.53 \; (0.54) \\ 
+   & Self-Identification - Other & 1.12 \; (0.31)^{***} & 1.12 \; (0.31)^{***} & 1.12 \; (0.31)^{***} & 1.12 \; (0.31)^{***} \\ 
+   & AN Ranking - Included & .25 \; (0.35) & .29 \; (0.36) & .30 \; (0.36) & .30 \; (0.36) \\ 
+   & AN Ranking - Dropped & .51 \; (0.50) & .39 \; (0.50) & .41 \; (0.50) & .40 \; (0.50) \\ 
+   & Founder name in Museum name & .09 \; (0.28) & .12 \; (0.28) & .11 \; (0.28) & .11 \; (0.28) \\ 
+   & Exhibition any & -.22 \; (0.27) & -.20 \; (0.27) & -.20 \; (0.27) & -.20 \; (0.27) \\ 
+   & Opening year &  & .12 \; (0.04)^{**} &  & .03 \; (0.10) \\ 
+   \multicolumn{6}{l}{\textbf{Environment}} \\ 
+ & Time Period 2005-2009 &  &  & .46 \; (1.16) & .30 \; (1.25) \\ 
+   & Time Period 2010-2014 &  &  & 1.55 \; (1.04) & 1.22 \; (1.42) \\ 
+   & Time Period 2015-2019 &  &  & 2.12 \; (1.02)^{*} & 1.63 \; (1.77) \\ 
+   & Time Period 2020-2024 &  &  & 2.14 \; (1.04)^{*} & 1.54 \; (2.06) \\ 
+   & PM density (country) & .63 \; (0.35) & .58 \; (0.40) & .59 \; (0.40) & .59 \; (0.40) \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .26 \; (0.09)^{**} & .26 \; (0.09)^{**} & .26 \; (0.09)^{**} \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} & .23 \; (0.08)^{**} & .23 \; (0.08)^{**} & .23 \; (0.08)^{**} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.08 \; (0.03)^{**} & -.08 \; (0.03)^{**} & -.08 \; (0.03)^{**} \\ 
+   & Great Recession (2008/09) & -1.61 \; (1.01) & -1.00 \; (1.04) &  &  \\ 
+   & Covid Pandemic (2020/21) & .39 \; (0.29) & -.36 \; (0.35) &  &  \\ 
    \hline
- & Museum-years & 6096 & 6096 \\ 
-   & Closures & 68 & 68 \\ 
-   & log. Likelihood & -338.36 & -351.64 \\ 
-   & AIC & 712.73 & 725.28 \\ 
-   & BIC & 752.68 & 749.69 \\ 
+ & Museums & 503 & 503 & 503 & 503 \\ 
+   & Museum-years & 6096 & 6096 & 6096 & 6096 \\ 
+   & Closures & 68 & 68 & 68 & 68 \\ 
+   & log. Likelihood & -338.36 & -332.02 & -331.91 & -331.85 \\ 
+   & AIC & 712.73 & 702.04 & 703.82 & 705.70 \\ 
+   & BIC & 752.68 & 744.21 & 748.21 & 752.31 \\ 
    \hline 
- \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
 \end{tabular}
@@
 \end{figure}
+
+covid effect may take longer to be effective
 \end{document}

### 2024-06-19 texts/paper_closing.tex
new tables after adding t_timeslice/t_timecfg

--- 2024-05-31 texts/paper_closing.tex
@@
-% Created 2024-05-30 do 10:16
+% Created 2024-06-19 wo 12:22
 % Intended LaTeX compiler: pdflatex
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon May 27 11:25:43 2024
+% Wed Jun 19 12:18:06 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon May 27 11:25:41 2024
+% Wed Jun 19 12:18:05 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
-   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
-   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
-   & Founder - alive &  &  & 0.903 & 0.30 & 0 & 1 \\ 
-   & Founder - died recently &  &  & 0.019 & 0.13 & 0 & 1 \\ 
-   & Founder - died 2+ years ago &  &  & 0.079 & 0.27 & 0 & 1 \\ 
+ & Gender - Male & 294 & 0.584 & 6.0e-01 &  0.49 & 0 & 1 \\ 
+   & Gender - Female & 79 & 0.157 & 1.7e-01 &  0.37 & 0 & 1 \\ 
+   & Gender - Couple & 130 & 0.258 & 2.3e-01 &  0.42 & 0 & 1 \\ 
+   & Founder - alive &  &  & 9.0e-01 &  0.30 & 0 & 1 \\ 
+   & Founder - died recently &  &  & 1.9e-02 &  0.13 & 0 & 1 \\ 
+   & Founder - died 2+ years ago &  &  & 7.9e-02 &  0.27 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
-   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
-   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
-   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
-   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
-   & Exhibition any &  &  & 0.630 & 0.48 & 0 & 1 \\ 
+ & Self-Identification - Museum & 190 & 0.378 & 4.1e-01 &  0.49 & 0 & 1 \\ 
+   & Self-Identification - Foundation & 104 & 0.207 & 1.9e-01 &  0.39 & 0 & 1 \\ 
+   & Self-Identification - Collection & 69 & 0.137 & 1.3e-01 &  0.34 & 0 & 1 \\ 
+   & Self-Identification - Other & 140 & 0.278 & 2.7e-01 &  0.45 & 0 & 1 \\ 
+   & Founder name in Museum name & 240 & 0.477 & 4.8e-01 &  0.50 & 0 & 1 \\ 
+   & AN Ranking - Not Included &  &  & 8.0e-01 &  0.40 & 0 & 1 \\ 
+   & AN Ranking - Included &  &  & 1.4e-01 &  0.35 & 0 & 1 \\ 
+   & AN Ranking - Dropped &  &  & 5.3e-02 &  0.23 & 0 & 1 \\ 
+   & Exhibition any &  &  & 6.3e-01 &  0.48 & 0 & 1 \\ 
+   & Opening year &  &  & 2.0e+03 & 11.10 & 1960 & 2020 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
-   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
-   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
-   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
-   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
-   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
-   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
-   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
-   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
-   & Time Period 2000-2004 &  &  & 0.101 & 0.30 & 0 & 1 \\ 
-   & Time Period 2005-2009 &  &  & 0.166 & 0.37 & 0 & 1 \\ 
-   & Time Period 2010-2014 &  &  & 0.258 & 0.44 & 0 & 1 \\ 
-   & Time Period 2015-2019 &  &  & 0.331 & 0.47 & 0 & 1 \\ 
-   & Time Period 2020-2024 &  &  & 0.145 & 0.35 & 0 & 1 \\ 
-   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
-   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
+ & PM density (country) &  &  & 4.5e-01 &  1.26 & 0.00077 & 27.26 \\ 
+   & Pop. (millions) within 10km &  &  & 1.3e+00 &  1.68 & 0.000087 & 10.81 \\ 
+   & Nbr PM within 10km &  &  & 1.8e+00 &  3.14 & 0 & 16 \\ 
+   & Region - Africa & 8 & 0.016 & 1.2e-02 &  0.11 & 0 & 1 \\ 
+   & Region - Asia & 142 & 0.282 & 2.9e-01 &  0.45 & 0 & 1 \\ 
+   & Region - Europe & 248 & 0.493 & 5.0e-01 &  0.50 & 0 & 1 \\ 
+   & Region - Latin America & 23 & 0.046 & 4.2e-02 &  0.20 & 0 & 1 \\ 
+   & Region - North America & 72 & 0.143 & 1.4e-01 &  0.34 & 0 & 1 \\ 
+   & Region - Oceania & 10 & 0.020 & 1.9e-02 &  0.13 & 0 & 1 \\ 
+   & Time Period 2000-2004 &  &  & 1.0e-01 &  0.30 & 0 & 1 \\ 
+   & Time Period 2005-2009 &  &  & 1.7e-01 &  0.37 & 0 & 1 \\ 
+   & Time Period 2010-2014 &  &  & 2.6e-01 &  0.44 & 0 & 1 \\ 
+   & Time Period 2015-2019 &  &  & 3.3e-01 &  0.47 & 0 & 1 \\ 
+   & Time Period 2020-2024 &  &  & 1.4e-01 &  0.35 & 0 & 1 \\ 
+   & Great Recession (2008/09) &  &  & 7.6e-02 &  0.27 & 0 & 1 \\ 
+   & Covid Pandemic (2020/21) &  &  & 1.4e-01 &  0.35 & 0 & 1 \\ 
    \hline
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon May 27 11:25:51 2024
+% Wed Jun 19 12:18:22 2024
 \begin{table}[ht]
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
   \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_woenv}\\ 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
  \hline
-  \multicolumn{4}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .02 \; (0.34) & .10 \; (0.34) \\ 
-   & Gender - Couple & -.10 \; (0.32) & -.15 \; (0.32) \\ 
-   & Founder - died recently & 1.09 \; (0.61) & 1.03 \; (0.61) \\ 
-   & Founder - died 2+ years ago & -.06 \; (0.55) & -.19 \; (0.56) \\ 
-   \multicolumn{4}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .25 \; (0.42) & .44 \; (0.41) \\ 
-   & Self-Identification - Collection & -.46 \; (0.54) & .00 \; (0.50) \\ 
-   & Self-Identification - Other & 1.12 \; (0.31)^{***} & 1.04 \; (0.30)^{***} \\ 
-   & AN Ranking - Included & .25 \; (0.35) & .26 \; (0.35) \\ 
-   & AN Ranking - Dropped & .51 \; (0.50) & .52 \; (0.49) \\ 
-   & Founder name in Museum name & .09 \; (0.28) & .06 \; (0.28) \\ 
-   & Exhibition any & -.22 \; (0.27) & -.22 \; (0.27) \\ 
-   \multicolumn{4}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .63 \; (0.35) &  \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) &  \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} &  \\ 
-   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  \\ 
-   & Great Recession (2008/09) & -1.61 \; (1.01) &  \\ 
-   & Covid Pandemic (2020/21) & .39 \; (0.29) &  \\ 
+  \multicolumn{3}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & .02 \; (0.34) \\ 
+   & Gender - Couple & -.10 \; (0.32) \\ 
+   & Founder - died recently & 1.09 \; (0.61) \\ 
+   & Founder - died 2+ years ago & -.06 \; (0.55) \\ 
+   \multicolumn{3}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .25 \; (0.42) \\ 
+   & Self-Identification - Collection & -.46 \; (0.54) \\ 
+   & Self-Identification - Other & 1.12 \; (0.31)^{***} \\ 
+   & AN Ranking - Included & .25 \; (0.35) \\ 
+   & AN Ranking - Dropped & .51 \; (0.50) \\ 
+   & Founder name in Museum name & .09 \; (0.28) \\ 
+   & Exhibition any & -.22 \; (0.27) \\ 
+   \multicolumn{3}{l}{\textbf{Environment}} \\ 
+ & PM density (country) & .63 \; (0.35) \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
+   & Great Recession (2008/09) & -1.61 \; (1.01) \\ 
+   & Covid Pandemic (2020/21) & .39 \; (0.29) \\ 
    \hline
- & Museum-years & 6096 & 6096 \\ 
-   & Closures & 68 & 68 \\ 
-   & log. Likelihood & -338.36 & -351.64 \\ 
-   & AIC & 712.73 & 725.28 \\ 
-   & BIC & 752.68 & 749.69 \\ 
+ & Museums & 503 \\ 
+   & Museum-years & 6096 \\ 
+   & Closures & 68 \\ 
+   & log. Likelihood & -338.36 \\ 
+   & AIC & 712.73 \\ 
+   & BIC & 752.68 \\ 
    \hline 
- \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
 \end{tabular}

### 2024-06-19 scripts/cfg.R
add hazard by calendar time

@@ -91,6 +91,11 @@ gc_plts <- function() {
                 bw.smooth = 5,
                 width = 16,
                 height = 9),
+            p_hazard_time = list(
+                dt_pmyear = quote(dt_pmyear),
+                caption = "Private Museum hazard function by year",
+                width = 16,
+                height = 9),
             p_agedens = list(
                 dt_pmcpct = quote(dt_pmcpct),
                 caption = "Age distribution of private museums",

### 2024-06-19 scripts/regression.R

@@ -1142,6 +1142,31 @@ gp_hazard <- function(dt_pmcpct, cutwidth, bw.smooth) {
     
 }
 
+gp_hazard_time <- function(dt_pmyear) {
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
+    1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
+
+    ## get data
+    dt_vis <- dt_pmyear %>% copy %>%
+        .[, .(mean_closing = mean(closing), .N, nbr_closed = sum(closing)), year] %>%
+        .[, str_annotate := sprintf("%s/%s", nbr_closed, N)] 
+
+        ## .[, year2 := as.integer(floor(year/2)*2)] %>%
+    ## .[, .(mean_closing = mean(mean_closing)), year2] %>%
+    dt_vis %>% 
+        ggplot(aes(x=year, y=mean_closing)) +
+        geom_line() +
+        geom_point() +
+        geom_text_repel(dt_vis[year %in% c(2006, 2011, 2015, 2020, 2021)], mapping = aes(label = str_annotate)) +
+        labs(y = "hazard")
+    ## geom_smooth()
+
+    
+    
+
+}
+
+
 gp_agedens <- function(dt_pmcpct) {
     gw_fargs(match.call())
     if (as.character(match.call()[[1]]) %in% fstd){browser()}

### 2024-06-19 scripts/regression.R
minor adjustments to p_hazard_time

@@ -1157,7 +1157,8 @@ gp_hazard_time <- function(dt_pmyear) {
         ggplot(aes(x=year, y=mean_closing)) +
         geom_line() +
         geom_point() +
-        geom_text_repel(dt_vis[year %in% c(2006, 2011, 2015, 2020, 2021)], mapping = aes(label = str_annotate)) +
+        geom_label_repel(dt_vis[year %in% c(2006, 2011, 2015, 2018, 2020, 2021)],
+                        mapping = aes(label = str_annotate)) +
         labs(y = "hazard")
     ## geom_smooth()
 

### 2024-08-29 scripts/closing_main.R
more descriptive nbrs

@@ -62,6 +62,8 @@ gd_nbrs <- function() {
              nbr_fmt = dt_pmdb[museum_status %in% c("private museum", "closed"), .N]),
         list(nbr_name = "pmx_n",
              nbr_fmt = dt_pmx[, .N]),
+        list(nbr_name = "n_founder_dead",
+             nbr_fmt = dt_pmyear[founder_dead == "recently_dead", fnunique(ID)]),
         list(nbr_name = "pm_open_from2021",
              nbr_fmt = dt_pmdb[year_opened >= 2021 & museum_status %in% c("private museum", "closed"), .N]),
         list(nbr_name = "pm_n_used",
@@ -76,7 +78,7 @@ gd_nbrs <- function() {
     
     dt_pehaz <- gd_pehaz(dt_pmcpct, cutwidth = 2)[src == "w1"]
 
-    dt_meanhaz <- map(c(2, 4, 5, 10, 20, 30, 40, 100),
+    dt_meanhaz <- map(c(2, 4, 5, 8, 10, 20, 30, 40, 100),
                       ~list(upper_bound = .x, mean_haz = dt_pehaz[age < .x, mean(est)])) %>%
         rbindlist %>%
         .[, .(nbr_name = sprintf("meanhaz_upto_%s", upper_bound),
@@ -90,16 +92,25 @@ gd_nbrs <- function() {
               nbr_fmt = sprintf("%s%%", format(nbr*100, digits = 2, nsmall = 2)),
               grp = "meanhaz")]
 
+    ## median life expectancy assuming constant hazard for first 8 and 8 onwards
+    dt_med_life_expect <- data.table(
+        nbr_fmt = log((0.5/(1-dt_pehaz[age < 8, mean(est)])^8),
+                      base = 1-dt_pehaz[age %between% c(8, 30), mean(est)]) %>%
+            round %>% as.character,
+        nbr_name = "median_life_expectancy",
+        grp = "meanhaz")
+
     ## hazards by year
-    dt_yearhaz <- dt_pmyear[, .(rate_closing = sum(closing)/.N), year]
+    dt_yearhaz <- dt_pmyear[, .(.N, rate_closing = sum(closing)/.N), year]
     
     ## what is good selection of slices?
     ## setting slice lengths, then generating for each slice length all the periods?
     ## but is mess wiht last period (2020+) in most cases
     ## just do some manually
 
-    dt_nbr_yearhaz <- data.table(year_id = c("all", "upto2010", "from2010"),
[…]

### 2024-08-29 scripts/closing_playground.R

@@ -277,5 +277,23 @@ data.table(
     ## .[year == 1990, total := 2481] %>%
     ## .[,  cumsum(exits)]
     .[, total := 2484 + 271 - cumsum(exits)]
+
+
+
     
     
+## * liability of newness
+
+dt_pmyear[, .(.N, N_unique = fnunique(ID), N_closed = sum(closing)), floor(year_opened/5)*5] %>%
+    .[, prop_closed := N_closed/N_unique] %>%
+    ggplot(aes(x=floor, y=prop_closed)) + geom_col()
+
+## hmm that's not it, that's just general survival (older have had more time to die -> more of them are dead)
+
+## let's do it the other way around: look at 2010-2021 period, see which proportion of those who entered there have died
+
+dt_pmyear[year >= 2015, .(entered = fnunique(ID), closed = sum(closing)), floor(year_opened/10)*10] %>%
+    .[, prop_closed := closed/entered] %>%
+    ggplot(aes(x=floor, y=prop_closed)) + geom_col()
+
+dt_pmyear[year >= 2010 & year_opened %between% c(1990, 1999), fnunique(ID)]

### 2024-08-29 texts/paper_closing.tex
new tex version

@@
-% Created 2024-06-19 wo 12:22
+% Created 2024-08-29 do 15:35
 % Intended LaTeX compiler: pdflatex
@@
  pdfsubject={},
- pdfcreator={Emacs 29.3 (Org mode 9.6.26)}, 
+ pdfcreator={Emacs 29.4 (Org mode 9.7.9)}, 
  pdflang={English}}
@@
 
-\section*{It's so over/Short-lived legacies: The closure of private art museums}
+\section*{It's so over}
 
@@
 Furthermore, analyzing which museums survive allows to make informed speculations on the future of this recently emerged organizational form.
+\subsection*{Private museums definition}
 
-\subsection*{lack of regulation -> museums are relatively free as long as they have money}
+\bigbreak
+\noindent
+Private museums:
+\begin{itemize}
+\item founded by collector -> needs to have amassed substantial art collection
+\item building of its own, limited public/corporate funding, has to be visitable -> requires substantial resources
+\end{itemize}
+\subsection*{Private museums dependencies}
 
-Museums are subject to relatively little regulation (the term "museum" is not a legally protected term and can be generally used without certification \parencite{Museumsbund_ICOMDE_2006_standards,Moore_2022_best,Lister_2023_marketing}.
-Museum associations on the national (e.g.
-American Alliance of Museums (AAM) for the United States, Museumsbund for Germany) or international (International council of museums, ICOM) level exist, which aim to standardize e.g.
-museum setup and operations, such as in relations to ethics \parencite{ICOM_2016_ethics} or sustainability \parencite{Bickersteth_2016_environment}.
-Membership for institutions is voluntary, and in practice limited:
-ICOM has around 3,000 institutional members \parencite{ICOM_2020_report19}, a relatively small fraction of the over 104,000 museums estimated to exist globally \parencite{UNESCO_2021_covid}.
-\footnote{The absence of clear criteria what constitutes a museum prevents standardized data collection which would be necessary to generate exact numbers.}
-National associations fare somewhat better, with e.g.
-the AAM representing over 4,000 of the country's 35,000 museums \parencite{LOC_2019_AAM}, and the German Museumsbund representing over 1,300 \parencite{Museumsbund_2024_mitgliedmuseen} of Germany's 7,120 museums \parencite{IMF_2024_museumsstatistik}.
-Even among its members promoting standards appears difficult, as shown in the establishment of the museum definition:
-After an ICOM proposal was rejected in 2019 after heated debates, an 18-month, four-round deliberation process involving 126 national committees was required to agree on a new definition by 2022 \parencite{Robinson_2021_debating,Seymour_2022_definition}.
+Private museums have been argued to be highly dependent on their founder for their continuing existence, as museums generally cannot cover expenses via revenues from ticket prices, museum shops and cafes.
+The \textcite{IMLS_2008_funding} found that for non-profit American art museums, less than half (48.1\%) the revenues come from earned income, leaving substantial gaps in the budgets that are filled by a mix of private donations (23.0\%), investment (18.5\%) and government support (10.4\%) (p.27).
+Outside of the United States, the reliance on revenue streams beyond operations is even larger:
+German museums have had on average only 27\% of their expenses covered by operations \parencite[p.233]{Martin_1993_museen}, and even the more market-oriented NPOs in the cultural sector draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
 
-\subsection*{Private museums relationships}
+Given that operating at "the margin of financial sustainability" is the "ordinary condition" for cultural NPOs, \cite[p.2]{Licci_BaraldiBonini_2024_sustainability}, it is not surprising that costs have been listed as a primary reason for private museum closure:
+\textcite{Adam_2021_rise} argues that "most of the cases of defunct private museums come back to the issue of cost" (p.79); a sentiment shared by \textcite{Walker_2019_collector} who notes that "private institutions struggle to contain escalating costs that are associated with running a museum" (p.234).
+In other studies, "insufficient funding, high maintenance costs and lack of strong government support" \parencite[p.7]{Zennaro_2017_shanghai}.
+or a "shortage of fundings and interruptions in cash \parencite[p.45]{Song_2008_private}  were central reasons that forced private museums to close.
+In a systematic review of closing reasons given in newspapers, magazines, social media accounts and personal exchange, \textcite{Velthuis_Gera_2024_fragility} find financial issues as the most commonly mentioned reasons for private museum closing.
+Scholars have traced the closure of private museums to numerous types of declining financial situations, such as bankruptcies \parencite{Velthuis_Gera_2024_fragility,Liu_2019_identities,DeNigris_2018_museums}, costly legal battles \parencite{Velthuis_Gera_2024_fragility}, stock devaluations \parencite{Walker_2019_collector}, failing auction sales \parencite{Bechtler_Imhof_2018_future} or lack of government support \parencite{Zennaro_2017_shanghai,Velthuis_Gera_2024_fragility}.
+\subsubsection*{diversification}
 
-A private museum is entangled in a number of dependencies.
-A crucial one is the relationship to the founder, without whom the private museum would not exist.
-Founders often control some aspects of management/operations.
-While the exact power relationships within museums are hard to observe due to the lack of transparency, which makes it in particular to assess the role of third parties, it is plausible to assume that they cannot exist against the wishes of the founder.
-Next to exhibiting the founder's collection, they likely also to a large extent dependent on continued financial contributions of the founder, as museums are chronically unprofitable (which is evidenced by their high share of NPOs or publicly owned/run museums, rather than for-profit companies).
-While the lack of transparency again makes it hard to systematically assess the financial importance of founder contributions to the existence of museums, \textbf{anecdotal} evidence suggests it to be substantial \parencite{Velthuis_Gera_forthcoming_fragility}.
-\textcite{Adam_2021_rise}
-\begin{itemize}
-\item pandemic potentially
-\item long-term funding
-\item motivations may change
-\item difficulties not anticipated
-\end{itemize}
+A central reason for financial vulnerability has been argued to be the crucial reliance on the single founder, who, as the iniators of their private museums, likely have contribute a large part of their institution's non-operating income \parencite{Frey_Meier_2002_beyeler}:
+\textcite{Adam_2021_rise} argues that "ultimately, many of these failures demonstrate the fragility of spaces that rely on a single founder, whose motivations and financial stability may change, or who may not have realised the difficulties inherent in establishing their own art space" (p.82).
+\textcite{Velthuis_Gera_2024_fragility} similarly argue that "because of their funding models and reliance on a sole founder, [private museums] are inherently fragile organizations" (p.1).
+\textcite{Bechtler_Imhof_2018_future} also characterize "the dependency on single individuals only" as one of main reasons that "make these private museums fragile" (p.53).
+\cite{StylianouLambert_etal_2014_museums} also characterizes many private institutions as "small individual museums that depend too much on their creators to guarantee their sustainability" (p.582).
+Beyond a direct financial component, private museums have been also
+characterized as fragile since they can only rely on their founder for "taste", "vision and drive" \parencite[p.77]{Adam_2021_rise}, "passion" \parencite[p.234]{Walker_2019_collector} or "skills and knowledge" \parencite[p.580]{StylianouLambert_etal_2014_museums}.
+The link between diversification and mortality, i.e.
+higher survival chances for more diversified organizations, has been found for non-profit organizations more generally \parencite{Fernandez_2007_dissolution,Bielefeld_1994_survival,Hager_2001_vulnerability,Lu_Shon_Zhang_2019_dissolution}\footnote{An larger literature exists shows a link between diversification and measures of financial health and sustainability besides survival \parencite{Licci_BaraldiBonini_2024_sustainability}}; it is thus plausible to apply to museums as well.
 
-Furthermore, private museums, as (non-profit) organizations, is deeply entangled with its environment.
+Lack of diversification is then argued to pose a problem in particular in the case of the founder's death:
+\textcite{Walker_2019_collector} argues that "the death of the original founder and creator can [\ldots{}] place the future of private museums and collections in jeopardy" as "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museums indefinitely" (p.234).
+\textcite{Bechtler_Imhof_2018_future} argue that in order to ensure museum longevity, "flexible, easily adapted designs for private museums" are necessary "to reduce the financial burden on their heirs" (p.188).
+\textcite{Adam_2021_rise} argues that succession introduces strains in financial aspects ("Collectors’ successors may not look kindly on what may well be a money pit when [\ldots{}] they will have to pick up the bills", p.77), which also concerns an aesthetic dimension ("the nature of contemporary art is to be fresh and new, but what is ‘fresh and new’ for the founder might seem ‘old hat’ to their heirs", p.76).
+\textcite{Velthuis_Gera_2024_fragility} similarly argue that "the founder’s death will almost inevitably have a direct impact on the financial health of the museum" (p.10).
+\cite{StylianouLambert_etal_2014_museums}, after discussing a case of a private museum whose owner "does not believe that anyone else could love the museum as much as she does", argues that this "generates questions regarding the cultural sustainability of small private museums in cases where their initiators are not able to care for them any longer" (p.580).
+
+While private museums are thus generally characterized as fragile, it is not always clear in relation to whom.
+Among the most explicit is \textcite{Walker_2019_collector}, who characterizes public institutions as relatively stable (which constitutes the reason why private collectors aim to form cooperations with them); \textcite{Bechtler_Imhof_2018_future} implicitly also highlight the longevity of state-run institutions.
+However, no systematic data is used to estimate public museum longevity, and while some
+remarks are made that public spending cuts might result in problems for public museum operations (p.XX), the overall characterization of them remains as immortal \parencite{Frey_Meier_2002_beyeler}.
+Responsible for the characterization of private museums as fragile might also be implicit reliance on the ICOM definition \parencite{ICOM_2024_definition} of museums as "permanent institutions", according to which every closing is indicative of fragility.
+So far a third comparison has been absent, namely that to other non-profit museums which are not initiated and run by a single collector, but by a wider group of founders or foundations.
+As these share with private museums a common organizational form of the non-profit organization or foundation  and a similarly harsh environment, yet and differ primarily in regards to their diversification, i.e.
+their reliance on a single founder as central authority and income stream, they provide a effective way of investigating the effect of diversification on museum survival.
+
+\textbf{Hypothesis 1}: Private museums have higher closing chance than non-profit museums generally.
+
+\textbf{Hypothesis 2}: A founder's death increases the risk of closing.
+\textbf{Hypothesis 2}: Reliance on the founder is the mechanism through which PMs are exposed to higher closing risk, thus founder-related variables can be used to predict closing.
+
+While the low diversification, i.e.
+the centrality of the founder for museum finances, has been argued to constitute the key feature of private museum vulnerability, it is also important to consider the other ways in which private museums, as (non-profit) organizations, are entangled with their environments.
 Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations are likely factors that contribute to its viability and hence longevity.
@@
 In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
-The image that these parties have of the private museum might be substantial importance in guiding their decision-making.
+\paragraph*{Competition}
 
-\subsection*{Theoretical framework}
+mechanism: losing motivation?
 
-As a substantial literature on organizational survival exists, thus
+Private museums have been characterized as highly competitive.
+While some self-descriptions focus on collaborative aspect, previous studies have highlighted how private museums compete with public museums over art works, audiences, sponsoring and donors \parencite[p.4]{Kolbe_etal_2022_privatemuseum}.
+So far the primary interest of investigating competition has been to evaluate whether private museums pose a threat to art provision by public institutions.
+However, less focus has been given to the fact that operating in a competitive environment may also have consequences for the private museums themselves, in particular their survival aspects.
+While private museums presumably depend on their founder to a large extent, income from tickets and facilities, as well sponsorships and public support possibly also constitute other non-negligible revenue streams.
+While competition directly has not yet been investigated as a cause for private museum closing, a possible mechanism of competition, "insufficient interest from the public", has been identified as the second most mentioned closure reason by \textcite[p.6]{Velthuis_Gera_2024_fragility}.
+Lack of interest by the public can be a consequence of multiple processes.
+While competition is one such processes, and applies if nearby competing institutions capture large portions of the audience, lack of interest can also result from a lack of audience (in the absence of competing institutions), which may be the case for private museums located in sparsely populated areas \parencite{Foster_2015_cube}.
+In both these cases, the resources that a private museum is able to receive from actors in its environment are limited.
 
-\subsubsection*{Identity and the survival prospects of non-profit organizations}
+Previous research into non-profit dissolution has often investigated competition as a cause of closure, with both qualitative and quantitative studies indeed identifying competition as a frequent closure reason.
+Qualitative studies which trace the history and/or closing reasons for each organization individually have highlighted competition over funding.
+\textcite{Hager_1999_demise} reports that "both individual donations/subscriptions and community and corporate grants tended to go to the singular, most reputable arts organizations of their types", resulting in "strong competitive pressures" for the vast majority of organizations (ibid.).
+Similarly, \textcite{HernandezOrtiz_2022_discontinuity} found that an "[increasingly] crowded niche increased the competition and limited [NPOs'] access to resources and clients" (p.116) with an informant stating that "there was less money to go around and more organizations seeking the money [\ldots{}] we had a full-time grant writer, we were always applying for grants.
+But there are so many organizations applying for the same grants" (ibid.).
+Quantitative studies have identified a relation between competition and non-profit closing primarily via measuring competition over density \cite{Park_Shon_Lu_2021_mortality,Haugh_etal_2021_nascent,Lu_Shon_Zhang_2019_dissolution}, with higher number of non-profits increasing the chance of non-profit dissolution.
 
+\textbf{Hypothesis 3}: A private museum is more likely to close in a more competitive environment.
+\paragraph*{Identity}
+
+The mere availability of audiences and other potential donors might however not be sufficient if a museum is not perceived as deserving support; i.e. if its identity is found lacking. 
 An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
 As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
-Even for non-profit organizations such as museums, which do not produce tangible goods (a domain where identity-related effects are present, e.g.
+Even for non-profit organizations such as museums, which do not produce tangible goods (a domain where identity-related effects are especially prevalent, e.g.
 \cite{Hsu_2015_granted,Bogaert_etal_2014_ecological}), a clear and positive identity might be helpful in a number of ways:
@@
 The empirical record of the link between identity and survival for non-profit organizations is mixed: 
-For example \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close.
-However, other studies find limited impact of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
+For example \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close, and \textcite{HernandezOrtiz_2022_discontinuity} observes a declining image or reputation as a cause of closure in a number of non-profits (p.115).
+However, other studies find little to no effect of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
 Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
@@
 \noindent
-\textbf{Hypothesis 1}: Private museums with identities more understandable, legitimate and favorable are less likely to close.
+\textbf{Hypothesis 4}: Private museums with identities more understandable and favorable are less likely to close.
 
-\subsubsection*{Organizational transformation}
-
-\textcite{Carroll_Khessina_2019_demography} argue that transformation of core features of organizations such as changes in technology or authority can have divergent consequences. 
-On the one hand, it can disrupt internal routines as well as external customer relations by decreasing (perceived) reliability and accountability as the change upsets established perceptions, which can lead to higher mortality.
-On the other hand, organizational transformation can be necessary to adapt to a changing environment, and hence be beneficial for survival.
-
-In the case of private museums, the death of the founder might constitute a substantial transformation as authority has to be reconfigured.
-Abandonment by insiders (such as divorce of directors) has been argued to contribute to NPO closure \parencite{Duckles_Hager_Galaskiewicz_2005_close}.\footnote{Conflict is similarly argued to contribute to closure but is not testable with the current data.}
-Even if plans have been made for a handover, the new leaders might not share the same commitment to art as the original founder, potentially decreasing museum sustainability. 
-In the case of private museums, founder death has been speculated to pose a challenge to their sustainability as "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museum indefinitely" \parencite[p.234]{Walker_2019_collector}.
-However, existing research has not found a straightforward effect of founder death on museum closure \parencite{Velthuis_Gera_forthcoming_fragility,Velthuis_etal_2023_boom}.
-Nevertheless as previous research has relied primarily on descriptive statistics, investigating founder death in a multivariate survival model allows to investigate the effect of founder death with higher precision.
-\bigbreak
-\noindent
-\textbf{Hypothesis 2}: A private museum is more likely to close after the death of the founder.
-
-\subsubsection*{Competition}
-
-needs to write out: 
-\begin{itemize}
-\item \cite{Hager_1999_demise}:
-\begin{itemize}
-\item p.173: Ten organizations cited an inability to compete as a proximate cause for closure, making it the most popular proximate cause of organizational closure.
-\item p.173: Both [art organizations] noted that the majority of the community’s arts dollars, both individual donations/subscriptions and community and corporate grants, tended to go to the singular, most reputable arts organizations of their types (e.g.
-museums, orchestras, dance troupes) in the metro area.
-Other arts organizations faced strong competitive pressures from these flagship organizations, a factor which caused the demise of Organizations 276 and 293
-\end{itemize}
-\item \cite{Lecy_2010_nonprofit}:
-\begin{itemize}
-\item p.27: The analysis shows that a period of rapid sector expansion – a period where many additional resources are being poured into the sector – creates a more competitive environment as evidenced by higher rates of organizational mortality.
-\end{itemize}
-\item \cite{Park_Shon_Lu_2021_mortality}
-\begin{itemize}
-\item p.844: Furthermore, nonprofits that run their business in a county with greater organizational density and population size are more likely to dissolve, which implies that competition, as well as demand for service, prevents nonprofits from surviving
-\end{itemize}
-\item \cite{HernandezOrtiz_2022_discontinuity}
-\begin{itemize}
-\item p.116:  A crowded niche increased the competition and limited their access to resources and clients.
-As reported by informant of organization \#C07: "Well, there was less money to go around and more organizations seeking the money.
-Here we have the same, the same group of people that were supporting the organization, you know, donating to it and that only goes so far.
-So, we had a full-time grant writer, we were always applying for grants.
-But there are so many organizations applying for the same grants".
-(P31, Pos.
-49-51)
-\end{itemize}
-\item \cite{Lu_Shon_Zhang_2019_dissolution}
-\begin{itemize}
-\item p.43: For example, nonprofits operating in a more competitive environment with a higher degree of organizational density would experience a higher chance of dissolution.
-\end{itemize}
-\item \cite{Haugh_etal_2021_nascent}:
-\begin{itemize}
-\item p.1227: SEs are likely to compete with non-profit organizations for grants,donations, and programme-related investments.
-Second,both SEs and non-profit organizations serve the disadvantaged and socially excluded and thus may also compete for service users.
-Although collaboration between SEs and charities could increase the supply of services to those in need (Smiddy 2010), they compete with each other for resources and beneficiaries.
-The more similar the resource needs and markets served, the greater the competition between the organizational forms (Baum and Haveman 1997).
-Hence, the population density ofregistered non-profit organizations will thus have a detrimental effect on SE survival.
-\end{itemize}
-\end{itemize}
-
-resource-based: lack of audience, or many other people competing for audience
-\cite{Velthuis_Gera_forthcoming_fragility}:
-p.23: In other cases, the location of the museum is a factor in limited visitor interest. On the
-one hand, private museums located in metropolitan art centers tend to face competition over
-visitors  from  well-established  other  museums  in  the  vicinity.  On  the  other  hand,  private
-museums located outside of those centers can be confronted with a small local audience, and
-difficulties in attracting visitors from afar.
-
-\textbf{Hypothesis 3}: A private museum is more likely to close in a more competitive environment.
-
-\subsubsection*{Shocks}
-
-External shocks can
-
-Museums, including private museums, might be relatively resilient \cite{Geller_Salamon_2010_resilience}: 
-tightening belt, fundraising, entrepreneurial strategies, downsizing
-The form of museums also implies commitment of resources, larger than that of other NPOs, which in turn provides capabilities, e.g. staff that is able to search for alternative revenue sources.
-
-\subsubsection*{Size}
-
-Where
-
-\subsubsection*{Other predictors of organizational survival}
-
-\paragraph*{Age}
-
-The age of an organization is considered in different ways to be related to closing.
-What started with liability of newness \parencite{Stinchcombe_1965_structure}, which posited that organizational mortality decreases over time due to acquisition of capabilities and connections, has lead to a number of extensions \parencite{Carroll_Khessina_2019_demography,Hannan_1998_mortality}:
-Liability of adolescence argues that shortly after foundings organizations can still draw on endowments, the expiration of which leads to a peak of mortality some time after opening.
-While according to this view mortality still decreases after the peak as the organization becomes more established, other perspectives argue also for a positive relationship between age and mortality:
-According to the liability of obsolescence paradigm the environment changes faster than organizations which are seen as relatively constrained by inertia, which therefore leads to declining fitness and survival chances.
-Similar, according to "liability of senescence" capabilities/routines/coalitions can constrain the actions of organizations.
-Given such conflicting predictions, \textcite{Carroll_Khessina_2019_demography} propose to model age dependence with piece-wise constant hazard models (rather than parametric models) to estimate age-specific effects which can, but do not have to, indicate a relationship between age and mortality.
-
+It is however necessary to consider that in particular the name of a museum might be associated with a museum's survival via identity, but also reflect founder intentions regarding the institutions longevity.
+This is discussed in more detail below.
+Furthermore, inferring the status of the museum via the reputaton of the founder again explores the extent to which the founder is a figure of central importance for the private museum.
 \subsection*{Data and Methods}
 
-\subsubsection*{Dependent Variable}
+A newly constructed database, assembled from different sources,  is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
+Currently, the database includes 548 museums (of which 451 are currently open, the remainder having closed or transformed into other organizational forms).
+Using this database, in particular year of opening and, if available, closing, it is possible to reconstruct the life course of the each institution with museum-year as the unit of analysis.
+This data allows to conduct survival analysis (also known as event history analysis), the most common statistical technique to investigate hazard rates and identify mortality-assocated covariates \parencite{Moore_2015_survival,Allison_2014_event}.
 
-A newly constructed database, assembled from different sources,  is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
-First, existing databases of private art museums are harmonized.
-Secondly, the online presences of 14 English art publications were exhaustively searched for any mention of private museums.
-After identifying unique institutions, data on these organizations was collected such as opening year, closing year (of those which closed) and founder information.
-Currently, the database includes 547 museums (of which 446 are currently open, the remainder having closed or transformed into other organizational forms).
-Using this database allows to reconstruct the lifecourse of the each institution with the the unit of analysis as museum-year:
-The main dependenent variable is thus an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
+Hypothesis 1 (comparing closing risk between private museums and other, more diversified institutions) ideally would use a complete population of museums to identify the effect of institutional form on closing rate.
+However, as no institutions are maintaining museum databases on a global scale, I use existing quantitative studies of museum closure to compare to these  private museums in terms of their closing rates.
+This non-parametric method estimates the hazard rate as the conditional probability of exiting at time t\textsubscript{i} given being alive as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at time \(t_i\) and \(d_i\) as the number of exits at time \(t_i\)), and the survival function as the product of these conditional probabilities as \(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\).
+
+Hypothesis 2 to 4, which differentiate the private museum population according to a number of risk factors, are investigated via Cox proportional hazard models. 
+The main dependenent variable is here indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
 Typically for survival data, museums that do not close during the observation period are right-censored, i.e. for such museums the dependent variable is zero for all years.
+The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
+Partial maximum likelihood estimation allows calculating \(\beta\) without defining the baseline hazard rate, which therefore is not constrained to a parametric form \parencite{Moore_2015_survival}.
+\subsubsection*{Main Predictors (Cox Proportional Hazards Model)}
 
-\subsubsection*{Main Predictors}
+\paragraph*{Founder death}
 
+A measure of founder death is constructed as a time-varying covariate, which can take the values of the founder being alive, having deceased recently (the year in question and the year after that), and having been deceased for more than 2 years.
+While it would have been possible to model founder death as a binary variable, two separate stages of death allows to separately investigate the short- and long-term impacts.
 \paragraph*{Legitimacy}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Wed Jun 19 12:18:06 2024
+% Wed Aug 28 11:41:43 2024
 \begin{table}[ht]
@@
 prevalence of museum founders to include the term museum in the name of their institution\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum}.
-
 \paragraph*{Reputation}
@@
 to exclude the possibility that an association is observed which is present due to founders being dropped from the ranking as a consequence of the closure of their museum.
-
-\paragraph*{Organizational transformation}
-
-A measure of founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder.
-
 \paragraph*{Competition}
@@
 To be able to estimate both competition and demand/audience/population separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two.
-
 \subsubsection*{Control variables}
@@
 
+External shocks might interrupt operations, which reduces income from tickets, as well as make other donors more hesitant to commit money in uncertain times.
+However, museums, including private museums, might also be relatively resilient as they can adopt measures such as tightening their belt, additional fundraising, and expanding their marketing efforts \parencite{Geller_Salamon_2010_resilience}, which might bolster their resilience.
+To account for two prevalent shocks in the recent decades, the Great Recession and the Covid-19 pandemic, I thus include two dummy variables for 2008/2009 and 2020/2021; respectively.
 \subsubsection*{Analytical framework}
@@
 Secondly, we use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
-The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
-Partial maximum likelihood estimation allows calculating \(\beta\) without defining the baseline hazard rate, which therefore is not constrained to a parametric form. 
-Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.
-
 \subsection*{Results}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Wed Jun 19 12:18:05 2024
+% Wed Aug 28 11:41:41 2024
 \begin{table}[ht]
@@
 
-In total, 479 private museums are included in the database, 53 of them have closed.
-6903 museum-years are observed; table \ref{tbl:t_sumstats} shows summary statistics for all variables.
+In total, 523 private museums are included in the dataset which are either open or have closed\footnote{This does not include 25 institutions which were private museums at some point and have since been transformed into other organizational forms; these cases are discussed in the limitations.}.
+A small number of museums are excluded, in particular three museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), as well as two which closed before 2000 as they fall outside the period under investigation.
+This leaves 503 private museums at risk, of which 68 have closed.
+6096 museum-years are observed; table \ref{tbl:t_sumstats} shows summary statistics for all variables.
+\subsubsection*{Calendar Year hazard}
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=16cm]{../figures/p_hazard_time.pdf}
+\caption{\label{fig:p_hazard_time}Private Museum hazard function by year}
+\end{figure}
+
+While typically in survival analysis closing risk is seen as a function of age, previous studies have not done so, instead focusing on average yearly closing rates.
+To ensure comparability with these, I first analyze closing rates the same, and discuss age-related closing rate below.
+Summary yearly closing results in an average closing rate of 0.84\%; i.e.
+on average each year 0.84\% of the private museum population closes (weighing the yearly mortality rate by number of museums at risk results in an estimate of 1.12\%).
+It is worth pointing out however that closing rates appear to vary substantially over time (figure \ref{fig:p_hazard_time}); with an average closing rate of 0.21\% from 2000 to 2010 (with only 4 closures taking place in that time period), and a rate of 1.36\% from 2010 onwards.
+
+While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})\footnote{IRS data is not without limitations, such as only being required from larger organizations, misreporting, and the difficulty of inferring closing from non-filing.
+Nevertheless, it constitutes the most fine-grained data source to investigate non-profit survival}.
+None of these focus specifically on art museums (\textcite{Hager_2001_vulnerability} focuses on Art NPOs, \textcite{Bowen_1994_charitable} and \cite{Gordon_etal_2013_insolvency} on NPOs generally), but report survival estimates by organizational form, including museums.
+\textcite{Bowen_1994_charitable} reports average annual exit rates for all 501(c)(3) museums in the 1981-1991 time period of 1.1\% (p.103)
+\textcite{Gordon_etal_2013_insolvency} observes 35 closures over the years of 2000-2003 with 5,167 "firm-years" (p.368), resulting in an annual "average insolvency rate" of 0.68\% (p.377).
+Some of this difference may be explained by higher shares of smaller organizations in \textcite{Bowen_1994_charitable}, where NPOs of any size are included, whereas \textcite{Gordon_etal_2013_insolvency} excluded NPOs with operational revenues below 150,000 USD by, as smaller non-profits are at higher risk of closing \parencite{Harrison_Laincz_2008_nonprofit,Helmig_Ingerfurth_Pinz_2013_nonprofit}.
+Focusing directly on Art museums, rather than museum generally, \textcite{Hager_2001_vulnerability} observes 42 closures over a period of 4 years (1994-1997) from a starting populaton of 448 (p.383).
+As his way of delineating the population (having "filed an annual Form 990 tax return with the IRS for the 1990, 1991, or 1992 tax year", p.380) does not rule out that some closings took place in 1991, 1992 or 1993\footnote{In particular it is unclear why 1993 is not treated as belonging to the observation period}, attributing some closings to these years is likely appropriate, and presumably roughly equivalent to assuming an observation period of five (rather than four) years, which corresponds to an average yearly closing rate of \(1-\sqrt[5]{406/448}\) = 1.9\%\footnote{So far it is hard to tell why art museums appear to have higher closing rates than museums generally.
+According to \textcite{IMLS_2008_funding}, art museums have above-average reliance on earned income (46.1\% compared to 43.7\% on average, p.26), and \textcite{Bowen_1994_charitable} argue that a higher reliance on income is associated with exit rates (p.102), but it is questionable whether such an a small difference in percent earned can explain a 1.7-2.7 times higher closing risk.
+Similarly, while art museums do not have the largest coffers (in particular museums of natural history and science are substantially larger \cite{IMLS_2008_funding,Bowen_1994_charitable}), art museums have substantially higher incomes than the history museums (which are more frequent), historical societies and botanical gardens \parencite{IMLS_2008_funding} as well as "other museums" with more specialized and/or local focuses \parencite{Bowen_1994_charitable}.
+Especially the larger number of history museums, and the more restrictive inclusion by \textcite{Hager_2001_vulnerability} in comparison to \textcite{Bowen_1994_charitable} make the higher mortality rate for art museums than museums generally puzzling.}
+
+\begin{table}[htbp]
+\caption{\label{tbl:litreview}Hazard rates in studies of museums and art NPOs}
+\centering
+\begin{tabular}{lll}
+\hline
+Study & Population & Average Yearly Closings\\
+\hline
+\cite{Hager_2001_vulnerability} & Art Museums & 1.9\%\\
+\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\%\\
+\cite{Bowen_1994_charitable} & Museums & 1.1\%\\
+current study & Private Art Museums & 0.84\% (overall)\\
+ &  & 1.36\% (2010-2021)\\
+ &  & 1.12\% (weighted)\\
+\hline
+\end{tabular}
+\end{table}
+
+Results are summarized in table \ref{tbl:litreview}.
+Average annual closing rates fall within closing rates found in previous studies, and even the 2010-2021 time periods with higher risk is below the general estimate for art museums by \textcite{Hager_2001_vulnerability}.
+There is thus overall little support to the idea that private museums are exposed to higher closing risk than museums, thus refuting Hypothesis 1.
 \subsubsection*{Hazard rate and Age Dependence}
@@
 
+Next to average yearly closing rates, private museum closing can also investigated over its age (unfortunately, no comparison to previous studies can be done as age-dependent mortality estimates are not reported).
 Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
-The hazard rate doubles over the first 10 years from approximately 0.45\% to 0.9\%, at which value it approximately stays constant for the next 20 years, after which it appears to decline.
-However, the decline after thirty years is presumably less certain as very few private museums have already reached this age.
+The hazard rate increases strongly from 0.10\% in the first two years, to 0.69\% in the first 5 years, to 1.20\% at year 8, around which it then fluctuates, leading to an average hazard of 1.16\% for the first 30 years.
+\footnote{While it is possible to calculate the average hazard over longer periods (e.g.
+the overall average hazard rate is 0.90\%), for ages above 30 only few observations are available, which make these predictions rather uncertain.}
+The increase in the first years is likely due to what has been called "initial resource endowments" in organizational research \cite{Carroll_Khessina_2019_demography,Hannan_1998_mortality} (not to be confused with the practice of a particular endowment for e.g.
+a museum REF, i.e.
+a stock of money, often invested in stocks, whose capital gains are used for operations).
+As the establishment of a museum requires considerable resources, their founders appear to allocate enough resources to keep the risk of closure small in the first years after opening.
+Given that founders are likely aware that their endeavor is unlikely to generate a profit, they are not vulnerable to the liability of newness \parencite{Stinchcombe_1965_structure}.
 
-The increase in the first years is likely due to endowments: As the establishment of a museum requires considerable resources, their founders appear to allocate enough resources to keep the risk of closure small in the first years after opening.
-Given that founders are likely aware that their endeavor is unlikely to generate a profit, they are not vulnerable to the liability of newness \parencite{Stinchcombe_1965_structure}.
-The relative stability of the hazard rate after ten years has no correspondence in classical theories on age dependence:
-While an increase in mortality as observed here is predicted by the idea of "liability of adolescence" \parencite{Carroll_Khessina_2019_demography}, this framework also predicts a decline in mortality after a peak due to becoming established.
-Furthermore, while "liability of obsolescence" and "liability of senescence" (ibid.) predict higher mortality for older organizations due to mismatch with the environment and inertia (inflexible internal routines), it seems questionable whether museums would have reached obsolescence or senescence already after ten years.
-Furthermore, the applicability of obsolescence and senescence might be limited for non-profit organizations.
-
-Overall the entire life span, the average hazard rate is 0.90\%, which allows comparison to other studies of NPO closure.
-While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})
-
-\begin{table}[htbp]
-\caption{\label{tbl:litreview}Hazard rates in studies of museums and art NPOs}
-\centering
-\begin{tabular}{lll}
-\hline
-study & population & avg. hazard rate\\
-\hline
-\cite{Hager_2001_vulnerability} & Art Museums & 2.4\%\\
-\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\%\\
-\cite{Bowen_1994_charitable} & Museums & 1.1\%\\
-\hline
-\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\%\\
-\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\%\\
-\hline
-\end{tabular}
-\end{table}
-
-\textcite{Hager_2001_vulnerability} and \textcite{Gordon_etal_2013_insolvency} both study NPOs more generally, but report survival estimates by organizational form.
-Both these studies also report substantial variation in hazard rates between organizational forms.
-While these comparisons indicate that private museums have dissolution rates lower or similar to museums and non-profit organizations generally, more research is needed to establish the comparability of these hazard rates.
-
-Comparison to other forms of nonprofit organizations reported by \parencite{Gordon_etal_2013_insolvency}
-places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
-While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.90\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
-It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
-In fact, lower dissolution rates are only reported for historical societies (0.5\%) and libraries (0.2\%).
-
-\begin{table}[htbp]
-\caption{\label{tbl:litreview2}Hazard rates in studies of NPOs}
-\centering
-\begin{tabular}{llll}
-\hline
-study & population & avg. hazard rate & data source\\
-\hline
-\cite{Gordon_etal_2013_insolvency} & NPOs & 1.58\% & IRS\\
-\cite{Hager_Galaskiewicz_Larson_2007_liability} & NPOs & 1.25\% & own data\\
-\cite{Clifford_2018_reinforcing} & Charities & 2\%-5\% & Reg. of Charities (UK)\\
-\cite{Mayer_2022_simmer} & public charities & 0.17\% & IRS\\
-\hline
-\end{tabular}
-\end{table}
-
+Such analysis can be used to estimate the average life expectancy of a private museum.
+While only a fraction of all opened museums has closed (68 out of 503), under the assumption of average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, median life expectancy can be estimated as 52 years.
+On first sight such findings seems to differ from a previous quantitative analysis of the database, which argued that "the median number of years that private museums were open before they closed is 10 years" \parencite[p.5]{Velthuis_Gera_2024_fragility}, as previously only closed museums were considered.
+To contribute to this 
 \subsubsection*{Regression Results}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Wed Jun 19 12:18:22 2024
+% Wed Aug 28 11:41:53 2024
 \begin{table}[ht]
@@
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & .02 \; (0.34) \\ 
-   & Gender - Couple & -.10 \; (0.32) \\ 
-   & Founder - died recently & 1.09 \; (0.61) \\ 
-   & Founder - died 2+ years ago & -.06 \; (0.55) \\ 
+ & Gender - Female & -.01 \; (0.34) \\ 
+   & Gender - Couple & -.11 \; (0.32) \\ 
+   & Founder - died recently & 1.06 \; (0.61) \\ 
+   & Founder - died 2+ years ago & -.09 \; (0.55) \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .25 \; (0.42) \\ 
-   & Self-Identification - Collection & -.46 \; (0.54) \\ 
-   & Self-Identification - Other & 1.12 \; (0.31)^{***} \\ 
-   & AN Ranking - Included & .25 \; (0.35) \\ 
-   & AN Ranking - Dropped & .51 \; (0.50) \\ 
-   & Founder name in Museum name & .09 \; (0.28) \\ 
-   & Exhibition any & -.22 \; (0.27) \\ 
+ & Self-Identification - Foundation & .21 \; (0.41) \\ 
+   & Self-Identification - Collection & -.44 \; (0.54) \\ 
+   & Self-Identification - Other & 1.09 \; (0.30)^{***} \\ 
+   & AN Ranking - Included & .18 \; (0.34) \\ 
+   & AN Ranking - Dropped & .47 \; (0.50) \\ 
+   & Founder name in Museum name & .07 \; (0.28) \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .63 \; (0.35) \\ 
+ & PM density (country) & .62 \; (0.35) \\ 
    & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
+   & Pop. (millions) within 10km & .27 \; (0.10)^{**} \\ 
+   & Nbr PM within 10km & .27 \; (0.08)^{***} \\ 
    & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
-   & Great Recession (2008/09) & -1.61 \; (1.01) \\ 
-   & Covid Pandemic (2020/21) & .39 \; (0.29) \\ 
+   & Great Recession (2008/09) & -1.59 \; (1.01) \\ 
+   & Covid Pandemic (2020/21) & .40 \; (0.29) \\ 
    \hline
@@
    & Closures & 68 \\ 
-   & log. Likelihood & -338.36 \\ 
-   & AIC & 712.73 \\ 
-   & BIC & 752.68 \\ 
+   & log. Likelihood & -338.69 \\ 
+   & AIC & 711.39 \\ 
+   & BIC & 749.12 \\ 
    \hline 
@@
 Table \ref{tbl:t_reg_coxph} shows the results of Cox proportional hazard regression model.
-
+Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.
 \paragraph*{Control Variables}
@@
 While generally organizations whose name include the name of their founder might be more centered around the founder, and hence display higher inertia, making them less able to adapt to changing environments, these results indicate that it does not seem to be case for private museums.
-
 \paragraph*{Identity Variables}
@@
 Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (not statistically significant) and by founders who were included at some point but are no longer included (not statistically significant).
-
 \paragraph*{Organizational transformation}
@@
 This possibly indicates that private museums might be less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
-
 \paragraph*{Competition}
@@
 Furthermore, these "rural" museums see an increase in the risk of closing for each additional private museum present within 10 kilometers, whereas the risk of closing decreases with  each additional private museum in the local environment for museums in more urban areas.
-
 \subsection*{Discussion}
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
+\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population}
+\end{figure}
+
 The lack of a relation between temporary exhibitions and survival prospect is somewhat unexpected.
@@
 Founders who are committed to their museums will keep them alive, regardless of whether or not they plan to organize temporary exhibitions.
-
 \subsubsection*{founder}
@@
 
-TBD
+Private museum have been characterized as fragile institutions due to their reliance on a single founder.
+However, my analysis finds neither a higher substantially higher mortality rates for private museums compared to (art) museums generally, nor a conclusive relationship between museum closure and a number of founder characteristics, such as founder gender, death, exclusion from the Artnews collector ranking or inclusion of founder name in the museum name.
+While Self-identification and audience/competition are significantly associated with higher mortality, and possibly reflect or influence founder motivations, they are also subject to alternative mechanisms, namely devaluation by third parties and competition, respectively (self-identification furthermore concerns a relatively small group of institutions).
+Furthermore, even if they reflect founder motivations, these are likely cases of voluntary closure; there is thus no large evidence that private museums are at a higher risk of unvoluntary closure than more diversified museums as a consequence of their reliance on a single founder.
+
+A possible explanation of the characterization of private museums as fragile might be due to the focus on case studies, which disregards the much larger population who don't experience closing.
+Due to the "private museum boom", some museums will experience closing over a period of around two decades even if the underlying closing probability is low.
+
+It cannot be stated whether private museums experience higher mortality rates than publicly funded museums (for which European countries would be the most natural comparison).
+While public museums have been characterized to some extent as very stable due to government picking up deficits \parencite{Meier_Frey_2003_faces,Bechtler_Imhof_2018_future}, \textcite{Walker_2019_collector} argues that due to declining cultural spending even public museums might face hard times.
+While national public flagship institutions will likely remain sufficiently funded to survive, this might not be the case for the vast majority of smaller museums in less touristic regions who rely on limited municipal funding, as \textcite{StylianouLambert_etal_2014_museums} demonstrates for a number of smaller publicly funded ethnography museums in Cyprus.
+Without access to museum register comparable to the IRS/NCCS datasets, such questions regarding the relation between type of ownership and survival remain speculative.
 
@@
 \end{sloppypar}
-
 \subsubsection*{Limitations}
@@
 Sometimes this involves changes in the composition of the board of directors (or equivalent), with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum to an extent that it no longer fits the working definition.
-Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to generally determine the date of such transitions\footnote{As a consequence of this, they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing.
+Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to generally determine the date of such transitions\footnote{Consequently they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing.
 However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
@@
 Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research. 
+\paragraph*{closing reasons not as rich as previous studies}
+
+The extent to which closing factors are investigated does not reach the level of detail by \cite{Velthuis_Gera_2024_fragility}, who investigate each closing separately.
+On the other hand, the inclusion of the museums who do not close results in a more more complete comparatison. 
+A research approach that would combine the strengths of both approaches could for example consist of leveraging additional data sources, such as financial histories of founder companies to investigate financial issues or search engine results, media reports or social media posts to assess interest from the public.
+
+founder age bracket
 
@@
 \item government spending
+\item government: political changes, censorship, persecution
 \end{itemize}
 -> this might futher specify the niches in which PMs can endure
+
+remain intransparent
 
@@
 Furthermore, having XXX might reflect founder commitment/resources.
-While the original data collection included assessing various museum characteristics, such as XXX, it became clear that desk research was
+While the original data collection included the measurement of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear in the process that desk research was unsuitable to construct reliabile indicators from these findings due to difficulty in assessing them in many cases.
 Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Internet archive, \texttt{subdomains} were archived much less frequently, and sometimes inaccessible despite being archived due to changes in webtechnology (such as flash).
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
-\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population}
-\end{figure}
+covid effect may take longer to be effective
+\subsubsection*{future research}
 
-covid effect may take longer to be effective
+The US register data on NPO tax filings constitutes a promising source for data for museum research (while this data source has seen frequent usage in non-profit management, it remains underexploited in the field of museum research).
+While the United States private museum population with XX museums and YY closings might not be sufficient to test whether private museums have a a higher closing risks than other museums, it still hosts a large population of museums.
+Thus this data can be used to establish average mortality estimates for museums generally as well as different types of museums, which can be compared to those observed for private museums globally. 
+Its furthermore a rich source of financial data
+
+egmus doesn't have that
 \end{document}

### 2024-09-02 texts/paper_closing.tex
export with new numbers, rewritten sections (hypotheses, founder death)

@@
-% Created 2024-08-29 do 15:35
+% Created 2024-08-31 za 13:35
 % Intended LaTeX compiler: pdflatex
@@
 \textcite{Adam_2021_rise} argues that "most of the cases of defunct private museums come back to the issue of cost" (p.79); a sentiment shared by \textcite{Walker_2019_collector} who notes that "private institutions struggle to contain escalating costs that are associated with running a museum" (p.234).
-In other studies, "insufficient funding, high maintenance costs and lack of strong government support" \parencite[p.7]{Zennaro_2017_shanghai}.
-or a "shortage of fundings and interruptions in cash \parencite[p.45]{Song_2008_private}  were central reasons that forced private museums to close.
-In a systematic review of closing reasons given in newspapers, magazines, social media accounts and personal exchange, \textcite{Velthuis_Gera_2024_fragility} find financial issues as the most commonly mentioned reasons for private museum closing.
-Scholars have traced the closure of private museums to numerous types of declining financial situations, such as bankruptcies \parencite{Velthuis_Gera_2024_fragility,Liu_2019_identities,DeNigris_2018_museums}, costly legal battles \parencite{Velthuis_Gera_2024_fragility}, stock devaluations \parencite{Walker_2019_collector}, failing auction sales \parencite{Bechtler_Imhof_2018_future} or lack of government support \parencite{Zennaro_2017_shanghai,Velthuis_Gera_2024_fragility}.
+In other studies, "insufficient funding, high maintenance costs and lack of strong government support" \parencite[p.7]{Zennaro_2017_shanghai}, a "shortage of fundings and interruptions in cash" \parencite[p.45]{Song_2008_private}, bankruptcies \parencite{Velthuis_Gera_2024_fragility,Liu_2019_identities,DeNigris_2018_museums}, costly legal battles \parencite{Velthuis_Gera_2024_fragility}, stock devaluations \parencite{Walker_2019_collector} or failing auction sales \parencite{Bechtler_Imhof_2018_future} were central reasons that forced private museums to close.
+In a systematic review of closing reasons given in newspapers, magazines, social media accounts and personal exchanges, \textcite{Velthuis_Gera_2024_fragility} find financial issues as the most commonly mentioned reasons for private museum closing.
 \subsubsection*{diversification}
 
-A central reason for financial vulnerability has been argued to be the crucial reliance on the single founder, who, as the iniators of their private museums, likely have contribute a large part of their institution's non-operating income \parencite{Frey_Meier_2002_beyeler}:
+A central reason for financial vulnerability has been argued to be the crucial reliance on the single founder, who, as the iniators of their private museums, likely have to contribute a large part of their institution's non-operating income \parencite{Frey_Meier_2002_beyeler}:
 \textcite{Adam_2021_rise} argues that "ultimately, many of these failures demonstrate the fragility of spaces that rely on a single founder, whose motivations and financial stability may change, or who may not have realised the difficulties inherent in establishing their own art space" (p.82).
@@
 \cite{StylianouLambert_etal_2014_museums} also characterizes many private institutions as "small individual museums that depend too much on their creators to guarantee their sustainability" (p.582).
-Beyond a direct financial component, private museums have been also
-characterized as fragile since they can only rely on their founder for "taste", "vision and drive" \parencite[p.77]{Adam_2021_rise}, "passion" \parencite[p.234]{Walker_2019_collector} or "skills and knowledge" \parencite[p.580]{StylianouLambert_etal_2014_museums}.
+Beyond a direct financial component, private museums have been also been characterized as fragile since they can only rely on their founder for "taste", "vision and drive" \parencite[p.77]{Adam_2021_rise}, "passion" \parencite[p.234]{Walker_2019_collector} or "skills and knowledge" \parencite[p.580]{StylianouLambert_etal_2014_museums}.
 The link between diversification and mortality, i.e.
@@
 \cite{StylianouLambert_etal_2014_museums}, after discussing a case of a private museum whose owner "does not believe that anyone else could love the museum as much as she does", argues that this "generates questions regarding the cultural sustainability of small private museums in cases where their initiators are not able to care for them any longer" (p.580).
+
+Overall, two related arguments emerge from the current literature:
+First, individual private museums rely on heavily on their founders for survival; events that interrupt the founders ability to provide resources are therefore associated with a highler likelihood of closing.
+Second, due to their low diversification (high reliance on the founder), private museums have are more fragile than museums where single individuals are not comparably central figures.
 
@@
 
-\textbf{Hypothesis 2}: A founder's death increases the risk of closing.
-\textbf{Hypothesis 2}: Reliance on the founder is the mechanism through which PMs are exposed to higher closing risk, thus founder-related variables can be used to predict closing.
+\textbf{Hypothesis 2}: Reliance on the founder is the mechanism through which PMs are exposed to a higher closing risk, thus founder-related variables predict closing, in particular
+\begin{itemize}
+\item \textbf{Hypothesis 2a}: Private museums are more likely to close after the death of the founder.
+\item \textbf{Hypothesis 2b}: Private museums are more likely to close after their founder is excluded from a prestigious ranking.
+\item \textbf{Hypothesis 2c}: Private museums which carry their founder's name in the museum name are more likely to close.
+\end{itemize}
 
@@
 \cite{Hsu_2015_granted,Bogaert_etal_2014_ecological}), a clear and positive identity might be helpful in a number of ways:
-In particular in the context of private museums, decline of legitimacy or reputation could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
+In the context of private museums, decline of legitimacy or reputation could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
 
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Wed Aug 28 11:41:43 2024
+% Fri Aug 30 12:00:47 2024
 \begin{table}[ht]
@@
 On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
+Women constitute a minority of the private museums founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would have a greater difficulties in securing resources third parties, presumably primarily governments and corporate sponsors.
+However, women may also be particularly associated with philanthropic initiatives (unlike e.g.
+corporate activities, \cite{Milam_2013_artgirls}) to such an extent that devaluation of female initiatives may not necessarily be present.
+
 Centrality of the founder's vision is measured via the proxy of whether the name of the founder is included in the name of the museum.
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Wed Aug 28 11:41:41 2024
+% Fri Aug 30 12:00:46 2024
 \begin{table}[ht]
@@
    & Founder - alive &  &  & 9.0e-01 &  0.30 & 0 & 1 \\ 
-   & Founder - died recently &  &  & 1.9e-02 &  0.13 & 0 & 1 \\ 
-   & Founder - died 2+ years ago &  &  & 7.9e-02 &  0.27 & 0 & 1 \\ 
+   & Founder - died recently &  &  & 1.3e-02 &  0.11 & 0 & 1 \\ 
+   & Founder - died 2+ years ago &  &  & 8.4e-02 &  0.28 & 0 & 1 \\ 
+   & Founder died &  &  & 9.7e-02 &  0.30 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
@@
 
-Next to average yearly closing rates, private museum closing can also investigated over its age (unfortunately, no comparison to previous studies can be done as age-dependent mortality estimates are not reported).
+Next to average yearly closing rates, private museum closing can also be investigated over its age (unfortunately, no comparison to previous studies can be done as age-dependent mortality estimates are not reported).
 Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
@@
 the overall average hazard rate is 0.90\%), for ages above 30 only few observations are available, which make these predictions rather uncertain.}
+
 The increase in the first years is likely due to what has been called "initial resource endowments" in organizational research \cite{Carroll_Khessina_2019_demography,Hannan_1998_mortality} (not to be confused with the practice of a particular endowment for e.g.
@@
 Such analysis can be used to estimate the average life expectancy of a private museum.
-While only a fraction of all opened museums has closed (68 out of 503), under the assumption of average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, median life expectancy can be estimated as 52 years.
+While only a fraction of all opened museums has closed (68 out of 503), under the assumption of average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, median life expectancy can be estimated as approximately 52 years.
 On first sight such findings seems to differ from a previous quantitative analysis of the database, which argued that "the median number of years that private museums were open before they closed is 10 years" \parencite[p.5]{Velthuis_Gera_2024_fragility}, as previously only closed museums were considered.
-To contribute to this 
+Focusing on the entire population of private museums instead, this analysis provides additional insights into the expected longevity of private art museums.
 \subsubsection*{Regression Results}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Wed Aug 28 11:41:53 2024
+% Fri Aug 30 12:00:45 2024
 \begin{table}[ht]
@@
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & -.01 \; (0.34) \\ 
-   & Gender - Couple & -.11 \; (0.32) \\ 
-   & Founder - died recently & 1.06 \; (0.61) \\ 
-   & Founder - died 2+ years ago & -.09 \; (0.55) \\ 
+ & Gender - Female & -.04 \; (0.34) \\ 
+   & Gender - Couple & -.14 \; (0.32) \\ 
+   & Founder died & .28 \; (0.43) \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .21 \; (0.41) \\ 
-   & Self-Identification - Collection & -.44 \; (0.54) \\ 
+ & Self-Identification - Foundation & .20 \; (0.41) \\ 
+   & Self-Identification - Collection & -.45 \; (0.54) \\ 
    & Self-Identification - Other & 1.09 \; (0.30)^{***} \\ 
-   & AN Ranking - Included & .18 \; (0.34) \\ 
-   & AN Ranking - Dropped & .47 \; (0.50) \\ 
-   & Founder name in Museum name & .07 \; (0.28) \\ 
+   & AN Ranking - Included & .19 \; (0.34) \\ 
+   & AN Ranking - Dropped & .46 \; (0.50) \\ 
+   & Founder name in Museum name & .05 \; (0.28) \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .62 \; (0.35) \\ 
+ & PM density (country) & .65 \; (0.34) \\ 
    & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .27 \; (0.10)^{**} \\ 
-   & Nbr PM within 10km & .27 \; (0.08)^{***} \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
    & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
    & Great Recession (2008/09) & -1.59 \; (1.01) \\ 
-   & Covid Pandemic (2020/21) & .40 \; (0.29) \\ 
+   & Covid Pandemic (2020/21) & .42 \; (0.29) \\ 
    \hline
@@
    & Closures & 68 \\ 
-   & log. Likelihood & -338.69 \\ 
-   & AIC & 711.39 \\ 
-   & BIC & 749.12 \\ 
+   & log. Likelihood & -339.68 \\ 
+   & AIC & 711.35 \\ 
+   & BIC & 746.87 \\ 
    \hline 
@@
 
-Table \ref{tbl:t_reg_coxph} shows the results of Cox proportional hazard regression model.
+To investigate which covariates are associated with increased risk of closing, table \ref{tbl:t_reg_coxph} shows the results of Cox proportional hazard regression model.
 Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.
@@
 
-Neither gender nor inclusion of founder name is significantly associated with mortality rates.
+Neither gender nor external shocks (the Great Recession and the Covid-19 Pandemic) are associated with higher closing rates.
+
+inclusion of founder name is significantly associated with mortality rates.
 While generally organizations whose name include the name of their founder might be more centered around the founder, and hence display higher inertia, making them less able to adapt to changing environments, these results indicate that it does not seem to be case for private museums.
+\paragraph*{Founder dependence}
+
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Fri Aug 30 12:08:04 2024
+\begin{table}[ht]
+\centering
+\begin{tabular}{rD{)}{)}{8)3}D{)}{)}{8)3}}
+  \hline 
+ \multicolumn{1}{l}{Recent death length} & \multicolumn{1}{l}{Recently dead} & \multicolumn{1}{l}{Long dead}\\ 
+ \hline
+   1 & .97 \; (1.02) & .19 \; (0.46) \\ 
+    2 & 1.37 \; (0.61)^{*} & -.16 \; (0.55) \\ 
+    3 & 1.06 \; (0.61) & -.09 \; (0.55) \\ 
+    4 & .83 \; (0.61) & -.02 \; (0.55) \\ 
+    5 & .62 \; (0.61) & .07 \; (0.55) \\ 
+    6 & .50 \; (0.61) & .13 \; (0.55) \\ 
+    7 & .87 \; (0.49) & -.51 \; (0.75) \\ 
+    8 & .80 \; (0.49) & -.45 \; (0.75) \\ 
+    9 & .91 \; (0.46)^{*} & -1.11 \; (1.03) \\ 
+   10 & .83 \; (0.46) & -1.03 \; (1.03) \\ 
+   11 & .78 \; (0.46) & -.98 \; (1.03) \\ 
+   12 & .71 \; (0.46) & -.90 \; (1.03) \\ 
+   \hline
+\end{tabular}
+\caption{Cox PH regression results wiht different death configurations} 
+\label{tbl:t_reg_coxph_deathcfg}
+\end{table}
+
+The death of the founder is not associated with a significant difference in private museum closure, i.e. museums are not significantly more likely to close after their founder has died.
+It is in principle possible to construct an alternative measure of founder death by splitting the time after the death in a short-term and long-term period; the short-term period might then capture the disruption by the founder, whereas the long-term period would only be reached by museums who have successfully acquired alternative funding models and are hence relatively viable.
+However, the choice of choosing a cut-off point between the short- and long-term periods is relatively arbitrary.
+
+Table \ref{tbl:t_reg_coxph_deathcfg} shows coefficients of both periods with different cut-off points.
+While the coefficient in the short-term period is consistently higher than both the overall death coefficient and the long-term period coefficients, so far the evidence is inconclusive as only few cases are statistically significant\footnote{P-values are not adjusted for multiple tests}.
+Considering the underlying numbers supports this:
+While 47 private museums have seen the death of their founders, only 3 of these have closed in the following 5 years; observing statistical significance in some configurations of founder death time more likely reflect random clustering than an underlying pattern.
+\textbf{Effect sizes}:
+\begin{itemize}
+\item death overall
+\item short-term death
+\end{itemize}
+stress how few people it is
+
+This possibly indicates that private museums might be less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
+
+The reputation of the founder is not statistically related to closure. 
+Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (not statistically significant) and by founders who were included at some point but are no longer included (not statistically significant).
 \paragraph*{Identity Variables}
@@
 However, as founders can choose the name of their museum arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.
-
-Museums included in the Museum of the World Database are \(e\)\textsuperscript{-0.88} = 0.41 (p < 0.05) times as likely to close than museums which are not, yet this result might be produced by different mechanisms.
-On the one hand, it might reflect that larger and richer institutions are both more likely to be noticed by the MOW and more likely to survive (MOW inclusion would then be a proxy for resources).
-On the other hand, similar to unconventional naming patterns, lack of inclusion in the MOW could be an indicator of deviance from museum standards, which could increase the unfamiliarity of the museum vis-a-vis third parties, reducing the chance of survival-enhancing interactions.
-
-The reputation of the founder is not statistically related to closure. 
-Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (not statistically significant) and by founders who were included at some point but are no longer included (not statistically significant).
-\paragraph*{Organizational transformation}
-
-The death of the founder is not associated with a significant difference in private museum closure, i.e. museums are not significantly more likely to close after their founder has died.
-This possibly indicates that private museums might be less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
 \paragraph*{Competition}

### 2024-09-02 scripts/cfg.R
add founder-death survival comparison

@@ -159,7 +159,14 @@ gc_plts <- function() {
                 caption = paste0("Predicted Avg. Hazard Rate from Regional PM Density and Population",
                                  " (without proxcnt < 2 & popm_circle10 <2)"),
                 width = 18,
-                height = 10),        
+                height = 10),
+
+            p_surv_death = list(
+                l_mdls = quote(l_mdls),
+                name_mainmdl = "r_pop4",
+                caption = "Comparison of Survival Estimates by Founder Death (95% CI)",
+                width = 18,
+                height = 10),
             p_lngtdvelp = list(
                 dt_pmyear = quote(dt_pmyear),
                 caption = "Composition of private museum population",

### 2024-09-02 scripts/closing_playground.R

@@ -316,24 +316,7 @@ dt_new <- expand.grid(founder_dead_binary = c(0,1), age = seq(0,30), closing = 0
 
 ## predicted effect of founder death
 
-dt_pred_prep <- cbind(
-        dt_pmyear[, lapply(.SD, Mode), # categorical/binary variables: use mode
-                  .SDcols = gc_vvs()$dt_vrblinfo[vrbltype %in% c("bin", "cat"), achr(vrbl)]],
-        dt_pmyear[, lapply(.SD, median), .SDcols = c("pmdens_cry", "year", "proxcnt10", "popm_circle10")])
 
-dt_pred_prep2 <- rbind(dt_pred_prep, dt_pred_prep) %>%
-    .[2, founder_dead_binary := 1]
-
-gd_pred("r_pop4", l_mdls, dt_pred_prep2, measure = "surv", year_range = 10)
-
-
-map(1:30, ~gd_pred("r_pop4", l_mdls, dt_pred_prep2, measure = "surv", year_range = .x) %>%
-              .[, `:=`(age = .x, founder_dead_binary = c(0,1))]) %>% rbindlist %>%
-    .[, founder_dead_binary := factor(founder_dead_binary)] %>% 
-    ggplot(aes(x=age, y=est, ymax = upper, ymin=lower, group = founder_dead_binary,
-               color = founder_dead_binary, linetype = founder_dead_binary)) +
-    geom_step() +
-    geom_ribbon(alpha = 0.1, stat = "stepribbon")
 
 
 

### 2024-09-02 scripts/regression.R

@@ -2219,6 +2219,49 @@ gp_condmef <- function(mdlname, l_mdls, dt_pmyear) {
 ##     ggplot(aes(x=proxcnt10, y=popm_circle10, color = factor(museum_status))) +
 ##     geom_jitter(size = 0.8, width = 0.2)
 
+gp_surv_death <- function(l_mdls, name_mainmdl) {
+    #' generate survival plot by death/alive
+    #' @param l_mdls list of models
+    #' @param name_mainmdl name of the main model
+    if (as.character(match.call()[[1]]) %in% fstd){browser()}
+    1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
+
+    ## set up the data to predict
+    dt_pred_prep <- cbind(
+        dt_pmyear[, lapply(.SD, Mode), # categorical/binary variables: use mode
+                  .SDcols = gc_vvs()$dt_vrblinfo[vrbltype %in% c("bin", "cat"), achr(vrbl)]],
+        dt_pmyear[, lapply(.SD, median), .SDcols = c("pmdens_cry", "year", "proxcnt10", "popm_circle10")])
+
+    ## assing one as dead
+    dt_pred_prep2 <- rbind(dt_pred_prep, dt_pred_prep) %>%
+        .[2, founder_dead_binary := 1]
+
+    ## predict for 30 years
+    dt_pred_vis <- map(1:30, ~gd_pred("r_pop4", l_mdls, dt_pred_prep2, measure = "surv", year_range = .x) %>%
+                  .[, `:=`(age = .x, founder_dead_binary = c(0,1))]) %>% rbindlist %>%
+                  .[, founder_dead_binary := factor(founder_dead_binary)]
+
+    leg_labels <- c("0" = "Alive", "1" = "Dead")
+
+    dt_pred_vis %>% 
+        ggplot(aes(x=age, y=est, ymax = upper, ymin=lower, group = founder_dead_binary,
+                   color = founder_dead_binary, linetype = founder_dead_binary)) +                   
+        geom_step(linewidth = 0.8) +
+        geom_ribbon(alpha = 0.1, stat = "stepribbon", show.legend = F, linewidth = 0.2) +
+        guides(color = guide_legend(title = "Founder status"),
+               linetype = guide_legend(title = "Founder status")) +
+        scale_color_manual(values = c("0" = "blue", "1" = "red"), labels = leg_labels) +
[…]

### 2024-09-02 scripts/closing_main.R
expand death nbrs

@@ -122,6 +122,22 @@ gd_nbrs <- function() {
     
     
     dt_mow_prop_museum <- gn_mow_prop_museum()
+
+    ## ---------- regression coefs ---------
+
+    dt_coefs <- gd_reg_coxph(l_mdls$r_pop4, "r_pop4") %>% chuck("dt_coef")
+
+    dt_coefnbrs <- list(
+        list(nbr_name = "coef_death",
+             nbr_fmt = dt_coefs[term =="founder_dead_binary", format(coef, digits =2, nsmall = 2)]),
+        list(nbr_name = "coef_death_exp",
+             nbr_fmt = dt_coefs[term =="founder_dead_binary", format(exp(coef), digits =2, nsmall = 2)]),
+        list(nbr_name = "coef_death_perc",
+             nbr_fmt = dt_coefs[term =="founder_dead_binary", format((exp(coef)-1)*100, digits =2, nsmall = 0)])
+        ) %>% rbindlist %>% .[, grp := "coefs"]
+    
+    
+
     
         
     ## plots: yanking (insertion) and in-text referencing
@@ -134,7 +150,8 @@ gd_nbrs <- function() {
     dt_nbrs_cbnd <- Reduce(rbind, list(dt_descs, dt_meanhaz, dt_meanhaz_later, dt_med_life_expect,
                                        dt_nbr_yearhaz,
                                        dt_ynkplt, dt_refplt, dt_reftbl,
-                                       dt_mow_prop_museum))
+                                       dt_mow_prop_museum,
+                                       dt_coefnbrs))
 
     
     return(dt_nbrs_cbnd)

### 2024-09-05 scripts/cfg.R
all kinds of label fixes, (also model inclusion)

@@ -248,7 +248,7 @@ gc_vvs <- function() {
     
 
     ## group variables thematically, add also labels
-
+    
     l_vrbl_lbls <- list( # variable labels
         gender                    = "Founder Gender",
         founder_dead1             = "Founder died",
@@ -268,14 +268,14 @@ gc_vvs <- function() {
         "I(pmdens_circle10_log^2)"= "PM density (10km, log^2)",
         "proxcnt10:popm_circle10" = "Nbr PM (10km) * Pop (10km)",
         
-        proxcnt10_log             = "Nbr PM^2 within 10km (log)",
+        proxcnt10_log             = "Nbr PM within 10km (log)",
         popm_circle10_log         = "Pop. (millions) within 10km (log)",
         
         
         "popm_circle10:I(proxcnt10^2)"    = "Nbr PM^2 (10km) * Pop (10km)",
-        "proxcnt10_log:popm_circle10_log" = "Nbr PM^2 (10km, log) * Pop (10km, log)",
-        "popm_circle10:proxcnt10_log"     = "Nbr PM^2 (10km, log) * Pop (10km)",
-        "proxcnt10:popm_circle10_log"     = "Nbr PM^2 (10km) * Pop (10km, log)",
+        "proxcnt10_log:popm_circle10_log" = "Nbr PM (10km, log) * Pop (10km, log)",
+        "popm_circle10:proxcnt10_log"     = "Nbr PM (10km, log) * Pop (10km)",
+        "proxcnt10:popm_circle10_log"     = "Nbr PM (10km) * Pop (10km, log)",
         
                 
 

### 2024-09-05 scripts/closing_main.R

@@ -270,7 +270,7 @@ l_mdls <- gl_mdls(dt_pmyear, dt_pmcpct) # generate models
 
 l_mdlnames_coxph <- list("r_pop4")
 
-l_mdlnames_dens <- list("r_pop4", "r_comp1", "r_pmdens1", "r_pmdens3", "r_pmdens_aud1", "r_pmdens_aud2")
+l_mdlnames_dens <- list("r_pop4", "r_comp1", "r_pmdens1", "r_pmdens2", "r_pmdens3", "r_pmdens_aud1", "r_pmdens_aud2")
 
 ## "r_smol")#, "r_pop5", "r_pop42")#  , ",r_pop4_wyr", "r_pop4_wcrises")
 ## l_mdlnames_coxph <- c("r_pop4", paste0("r_wsize", 3:1))

### 2024-09-05 scripts/regression.R

@@ -1965,9 +1965,9 @@ gp_pred_heatmap <- function(mdlname, l_mdls, dt_pmyear, vx, vy, add_cross) {
                  length = unit(8, "pt"),
                  sides = "tr") +  
         scale_fill_YlOrBr(reverse = T, range = c(0, 0.88), scale_name = "jj",
-                          name = "Closing change\nwithin 20 years") +
+                          name = "Closing chance\nwithin 20 years") +
         scale_color_YlOrBr(reverse = T, range = c(0, 0.88), scale_name = "jj",
-                           name = "Closing change\nwithin 20 years") +
+                           name = "Closing chance\nwithin 20 years") +
         theme_bw() +
         scale_y_continuous(expand = expansion(add = c(0, 0.5))) +
         scale_x_continuous(expand = expansion(add = c(0, 0.5))) + 

### 2024-09-05 scripts/cfg.R
rework alt_heatmap height and legend for more compactness

@@ -194,7 +194,7 @@ gc_plts <- function() {
                 dt_pmyear = quote(dt_pmyear),
                 caption = "Prediction Heatmap of Alternative model specifications",
                 width = 18,
-                height = 10),
+                height = 15),
             p_surv_death = list(
                 l_mdls = quote(l_mdls),
                 name_mainmdl = "r_pop4",

### 2024-09-05 scripts/regression.R

@@ -1484,7 +1484,9 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         r_pmdens2 = coxph(gf_coxph_close(
             vrbls_to_add = "pmdens_circle10_log",
             vrbls_to_yeet = c("proxcnt10", "popm_circle10", "proxcnt10:popm_circle10")), dt_pmyear),
-            
+
+        ## this does not really make sense:
+        ## no good reason why density defined as pop/pm should be quadratic
         r_pmdens3 = coxph(gf_coxph_close(
             vrbls_to_add = c("pmdens_circle10", "I(pmdens_circle10^2)"),
             vrbls_to_yeet = c("proxcnt10", "popm_circle10", "proxcnt10:popm_circle10")), dt_pmyear),
@@ -2019,6 +2021,17 @@ gp_pred_heatmap_alt <- function(l_mdls, dt_pmyear) {
     #' for the models in l_mdlnames
     #' to quickly check different specifications
 
+    theme_heatmap_alt <- function() {
+
+        theme(legend.position = "bottom",
+              axis.title.x = element_text(size = 11, margin = margin(0,0,0,0)),
+              legend.spacing = unit(0, "pt"),
+              legend.key.height = unit(8, "pt"),
+              legend.box.spacing = unit(3, "pt"),
+              legend.margin = margin(0,0,0,0))
+    }
+
+
     p_pred_heatmap_comp1 <- gp_pred_heatmap(
         mdlname = "r_comp1",
         l_mdls = l_mdls,
@@ -2027,7 +2040,7 @@ gp_pred_heatmap_alt <- function(l_mdls, dt_pmyear) {
         add_cross = T,
         dt_pmyear = dt_pmyear) +
         labs(title = "popm_circle10 (log)") +
-        theme(legend.key.height = unit(0.5, "cm"))
+        theme_heatmap_alt()
 
     p_pred_heatmap_pop42 <- gp_pred_heatmap(
         mdlname = "r_pop42",
@@ -2037,7 +2050,7 @@ gp_pred_heatmap_alt <- function(l_mdls, dt_pmyear) {
         add_cross = T,
         dt_pmyear = dt_pmyear) +
         labs(title = "base + proxcnt10^2") +
-        theme(legend.key.height = unit(0.5, "cm"))
+        theme_heatmap_alt()
 
 
[…]

### 2024-09-05 texts/sup_materials.tex
update sup materials, also include tex version

% Created 2024-09-05 do 11:15
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

\usepackage[hyphens]{url}                
\usepackage{hyperref}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{pdflscape}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[section]{placeins}
\usepackage{dirtree}
\usepackage{siunitx}
\usepackage{afterpage}
\usepackage{pdflscape}
\usepackage{svg}

\usepackage{booktabs}
\usepackage{dcolumn}

\usepackage{bibentry}

\sisetup{detect-all}

\sloppy
\usepackage{scalerel,stackengine}

\stackMath
\newcommand\reallywidehat[1]{%
\savestack{\tmpbox}{\stretchto{%
  \scaleto{%
    \scalerel*[\widthof{\ensuremath{#1}}]{\kern-.6pt\bigwedge\kern-.6pt}%
    {\rule[-\textheight/2]{1ex}{\textheight}}%WIDTH-LIMITED BIG WEDGE
  }{\textheight}% 
}{0.5ex}}%
\stackon[1pt]{#1}{\tmpbox}%
}

\usepackage{caption}
\usepackage[draft]{todonotes}

\captionsetup{skip=0pt}
\usepackage[utf8]{inputenc}
\usepackage[style=apa, backend=biber]{biblatex} 
\usepackage[english, american]{babel}
\DeclareLanguageMapping{american}{american-apa}
\DeclareFieldFormat{apacase}{#1}

\usepackage[T1]{fontenc}
\usepackage{csquotes}

\addbibresource{/home/johannes/Dropbox/references.bib}
\addbibresource{/home/johannes/Dropbox/references2.bib}

\usepackage{floatrow}

\usepackage{listings}
\usepackage{xcolor}
\usepackage{colortbl}

\lstset{
  language=R,                    
  basicstyle=\footnotesize,      
  numbers=left,                  
  numberstyle=\tiny\color{gray}, 
  stepnumber=1,                  
  numbersep=5pt,                 
  backgroundcolor=\color{white}, 
  showspaces=false,              
  showstringspaces=false,        
  showtabs=false,                
  frame=single,                  
  rulecolor=\color{black},       
  tabsize=2,                     
  captionpos=b,                  
  breaklines=true,               
  breakatwhitespace=false,       
  title=\lstname,                
  keywordstyle=\color{red},     
  commentstyle=\color{blue},  
  stringstyle=\color{violet},     
  escapeinside={\%*}{*)},        
  morekeywords={*,...}           
}

% \usepackage{crimson}
% \usepackage{microtype}

% \usepackage{helvet}
% \renewcommand{\familydefault}{\sfdefault}

\usepackage{tgtermes} % times font

\usepackage{fancyhdr}
\usepackage{setspace}
\onehalfspacing
\usepackage{longtable}
\usepackage{subfig}
% \usepackage[a4paper, total={18cm, 24cm}]{geometry}
\usepackage[a4paper, margin=2.5cm]{geometry}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\maketitle}{}

\usepackage{enumitem}
\setlist[itemize]{topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt}

\usepackage{multicol}
\setlength\multicolsep{0pt}

\newlist{propertyList}{itemize}{1}
\setlist[propertyList]{
  label=\textbullet,
  noitemsep,
  leftmargin=10pt,
  before=\begin{multicols}{3},
  after=\end{multicols}
  }

% \cfoot {Johannes Aengenheyster}
\rfoot {\thepage}

\listfiles

\setlength{\parindent}{1.2cm}
\author{Johannes }
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes },
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.4 (Org mode 9.7.9)}, 
 pdflang={English}}
\begin{document}

\section*{Supplementary online materials}

\subsection*{Alternative competition specifications}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Thu Sep  5 09:54:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pmdens1} & \multicolumn{1}{l}{r\_pmdens2} & \multicolumn{1}{l}{r\_audience1} & \multicolumn{1}{l}{r\_audience\_log1}\\ 
 \hline
  \multicolumn{7}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & .00 \; (0.33) & -.05 \; (0.33) & -.00 \; (0.33) & -.11 \; (0.33) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.22 \; (0.32) & -.18 \; (0.32) & -.21 \; (0.32) & -.23 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & .19 \; (0.43) & .25 \; (0.43) & .18 \; (0.43) & .08 \; (0.43) \\ 
   \multicolumn{7}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .36 \; (0.40) & .33 \; (0.40) & .37 \; (0.40) & .44 \; (0.40) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -.09 \; (0.50) & -.20 \; (0.51) & -.05 \; (0.51) & .05 \; (0.51) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.03 \; (0.30)^{***} & 1.12 \; (0.31)^{***} & 1.05 \; (0.30)^{***} & 1.13 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .24 \; (0.34) & .17 \; (0.35) & .23 \; (0.34) & .18 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .45 \; (0.50) & .31 \; (0.50) & .45 \; (0.49) & .47 \; (0.49) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .10 \; (0.28) & .14 \; (0.28) & .10 \; (0.28) & .07 \; (0.28) \\ 
   \multicolumn{7}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .50 \; (0.32) & .41 \; (0.34) & .55 \; (0.33) & .73 \; (0.31)^{*} \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.03 \; (0.03) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  &  &  &  \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} &  &  &  &  \\ 
   & PM density (10km) &  & -.00 \; (0.03) &  &  &  \\ 
   & PM density (10km, log) &  &  & .29 \; (0.15) &  &  \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  &  &  &  \\ 
   & Local Audience per PM &  &  &  & .10 \; (0.14) &  \\ 
   & Local Audience per PM (log) &  &  &  &  & .28 \; (0.09)^{**} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.65 \; (1.01) & -1.64 \; (1.01) & -1.65 \; (1.01) & -1.63 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .44 \; (0.29) & .46 \; (0.29) & .43 \; (0.29) & .42 \; (0.29) \\ 
   \hline
 & Museums & 503 & 503 & 503 & 503 & 503 \\ 
   & Museum-years & 6096 & 6096 & 6096 & 6096 & 6096 \\ 
   & Closures & 68 & 68 & 68 & 68 & 68 \\ 
   & log. Likelihood & -339.68 & -347.93 & -346.18 & -347.72 & -342.93 \\ 
   & AIC & 711.35 & 723.85 & 720.35 & 723.44 & 713.86 \\ 
   & BIC & 746.87 & 754.93 & 751.42 & 754.51 & 744.93 \\ 
   \hline 
 \multicolumn{7}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Alternative specification of environment} 
\label{tbl:t_reg_coxph_env}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_heatmap_alt.pdf}
\caption{\label{fig:p_pred_heatmap_alt}Prediction Heatmap of Alternative model specifications}
\end{figure}

Alternative Specifications of competition exist.
First, it is possible to argue that the primary mechanism through which private museums compete with each other is by limiting each other's audience.
This specification leads to the construction of the Audience variable, which describes the number of people in the 10 km surrounding by the number of private museums present.
Under this assumption, the situation of a private museum which is alone in an environment of 1 million people is equivalent to one in an environment of 3 million people with 2 other private museums, as each museums is "assigned" a pool of 1 million people.
Secondly, one might argue that the competition between private museums is scaled by the amount of people, which corresponds to specifying competition as the number of other private museums per (million) population.
In this case, the absence of other private museums assumes absence of competition, regardless of the audience size.

These while it would be possible for these different specifications to lead to similar interpretations, in practice they diverge substantially (table \ref{tbl:t_reg_coxph_env}).
Using Private museum density (model 2 and 3 for linear and log-transformed audience, figure \ref{fig:p_pred_heatmap_alt} bottom left), the general conclusion would be that (logged) competition increases mortality as predicted closing chance is highest in areas of low population and large private museum populations.
However, using audience (models 4 and 5, figure \ref{fig:p_pred_heatmap_alt} bottom right) leads to the opposite conclusion, as higher audience is associated with higher mortality; predicted closing chance is highest for areas of low numbers of private museums and large populations.
While it is beyond the scope of the paper to explore the origin of these diverging perspectives in detail, it is worth pointing out that the main specification of private interacted private museum and population counts captures both of these relationships, which arguably makes it preferable for its encompassingness.
\subsection*{Alternative sample specifications}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Thu Sep  5 11:13:39 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_wocryside} & \multicolumn{1}{l}{r\_onlycryside} & \multicolumn{1}{l}{r\_pop42}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & .21 \; (0.44) & -1.07 \; (0.78) & -.01 \; (0.34) \\ 
   & Gender - Couple & -.14 \; (0.32) & .07 \; (0.52) & -.27 \; (0.46) & -.12 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & -.19 \; (0.77) & .58 \; (0.59) & .29 \; (0.43) \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & 1.02 \; (0.65) & .31 \; (0.58) & .18 \; (0.41) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & .95 \; (0.71) & -18.23 \; (4781.88) & -.50 \; (0.55) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.95 \; (0.51)^{***} & .67 \; (0.46) & 1.09 \; (0.31)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & -.32 \; (0.48) & .55 \; (0.58) & .18 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .18 \; (0.73) & -.06 \; (0.85) & .47 \; (0.50) \\ 
   & Founder name in Museum name & .05 \; (0.28) & -.30 \; (0.42) & .24 \; (0.44) & .04 \; (0.28) \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & -1.16 \; (2.52) & .88 \; (0.44)^{*} & .67 \; (0.34)^{*} \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & 1.33 \; (2.38) & -.04 \; (0.02) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .17 \; (0.17) & 1.69 \; (0.81)^{*} & .20 \; (0.12) \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .19 \; (0.10) & .64 \; (1.06) & .22 \; (0.20) \\ 
   & Nbr PM$^{2}$ within 10km &  &  &  & .01 \; (0.02) \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.07 \; (0.04)^{*} & -.54 \; (1.83) & -.02 \; (0.09) \\ 
   & Nbr PM$^{2}$ (10km) * Pop (10km) &  &  &  & -.01 \; (0.01) \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -18.42 \; (5245.29) & -.75 \; (1.04) & -1.59 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .30 \; (0.41) & .46 \; (0.47) & .45 \; (0.29) \\ 
   \hline
 & Museums & 503 & 219 & 283 & 503 \\ 
   & Museum-years & 6096 & 2265 & 3311 & 6096 \\ 
   & Closures & 68 & 35 & 28 & 68 \\ 
   & log. Likelihood & -339.68 & -139.36 & -116.47 & -338.79 \\ 
   & AIC & 711.35 & 310.72 & 264.94 & 713.59 \\ 
   & BIC & 746.87 & 335.60 & 286.25 & 753.54 \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox PH models of different local density specifications} 
\label{tbl:t_reg_coxph_density}
\end{table}

To investigate the robustness of the coefficients across different values, table \ref{tbl:t_reg_coxph_density} shows how coefficients according to sample restrictions. 
In model 1, only museums are included which are located in areas with the highest value combination of number and private museums and population, i.e. museums located in an environment of less than 2 million people and 0 or 1 other private museums (the "countryside").
In model 2, the "countryside" is excluded.
However, both these models are not reliable, as they do not properly converge (indicated by extremely large coefficients in both models).
\end{document}

### 2024-09-05 scripts/closing_main.R
reorder model order

@@ -280,7 +280,7 @@ l_mdlnames_dens <- list("r_pop4", "r_comp1", "r_pmdens1", "r_pmdens2", "r_pmdens
 
 
 ## compare whether proxcnt/popm_circle10 patterns are stable across data ranges
-l_mdlnames_coxph_density <- list("r_pop4", "r_wocryside", "r_onlycryside", "r_pop42") 
+l_mdlnames_coxph_density <- list("r_pop4", "r_onlycryside", "r_wocryside", "r_pop42") 
 
 ## compare whether patterns change if only recent data is used
 l_mdlnames_timeslice <- list("r_pop4", "r_2005", "r_2010", "r_2015")

### 2024-09-05 scripts/descriptives.R
minor spacing out due to debugging

@@ -120,7 +120,9 @@ gt_sumstats <- function(dt_pmyear, dt_pmcpct) {
         .[, min_fmtd := format(min, digits = 2, scientific = F, trim = F), .I] %>% # row-wise min for small mins
         .[, max_fmtd := format(max, digits = 2, scientific = F, trim = F,
                                nsmall = fifelse(max %% 1 == 0, 0, 2)), .I] %>% # non-Ints: two decimal places
-        .[, .(grp_filler = "", term_lbl, pm_sum = as.character(pm_sum),
+        .[, .(grp_filler = "",
+              term_lbl,
+              pm_sum = as.character(pm_sum),
               pm_mean = format(pm_mean, digits=2, trim = T),
               mean = format(mean, digits = 2, trim = F),
               sd = format(sd, digits = 2, trim = F),

### 2024-09-06 texts/paper_closing.tex
latest latex export: rewritten results section

@@
-% Created 2024-08-31 za 13:35
+% Created 2024-09-06 vr 09:44
 % Intended LaTeX compiler: pdflatex
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Aug 30 12:00:47 2024
+% Thu Sep  5 13:08:13 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Aug 30 12:00:46 2024
+% Thu Sep  5 13:08:11 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 294 & 0.584 & 6.0e-01 &  0.49 & 0 & 1 \\ 
-   & Gender - Female & 79 & 0.157 & 1.7e-01 &  0.37 & 0 & 1 \\ 
-   & Gender - Couple & 130 & 0.258 & 2.3e-01 &  0.42 & 0 & 1 \\ 
-   & Founder - alive &  &  & 9.0e-01 &  0.30 & 0 & 1 \\ 
-   & Founder - died recently &  &  & 1.3e-02 &  0.11 & 0 & 1 \\ 
-   & Founder - died 2+ years ago &  &  & 8.4e-02 &  0.28 & 0 & 1 \\ 
-   & Founder died &  &  & 9.7e-02 &  0.30 & 0 & 1 \\ 
+ & Gender - Male & 294 & 0.584 &    0.604 &  0.49 & 0 & 1 \\ 
+   & Gender - Female & 79 & 0.157 &    0.166 &  0.37 & 0 & 1 \\ 
+   & Gender - Couple & 130 & 0.258 &    0.231 &  0.42 & 0 & 1 \\ 
+   & Founder - alive &  &  &    0.903 &  0.30 & 0 & 1 \\ 
+   & Founder - died recently &  &  &    0.013 &  0.11 & 0 & 1 \\ 
+   & Founder - died 2+ years ago &  &  &    0.084 &  0.28 & 0 & 1 \\ 
+   & Founder died &  &  &    0.097 &  0.30 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 190 & 0.378 & 4.1e-01 &  0.49 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 104 & 0.207 & 1.9e-01 &  0.39 & 0 & 1 \\ 
-   & Self-Identification - Collection & 69 & 0.137 & 1.3e-01 &  0.34 & 0 & 1 \\ 
-   & Self-Identification - Other & 140 & 0.278 & 2.7e-01 &  0.45 & 0 & 1 \\ 
-   & Founder name in Museum name & 240 & 0.477 & 4.8e-01 &  0.50 & 0 & 1 \\ 
-   & AN Ranking - Not Included &  &  & 8.0e-01 &  0.40 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  & 1.4e-01 &  0.35 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  & 5.3e-02 &  0.23 & 0 & 1 \\ 
-   & Exhibition any &  &  & 6.3e-01 &  0.48 & 0 & 1 \\ 
-   & Opening year &  &  & 2.0e+03 & 11.10 & 1960 & 2020 \\ 
+ & Self-Identification - Museum & 190 & 0.378 &    0.408 &  0.49 & 0 & 1 \\ 
+   & Self-Identification - Foundation & 104 & 0.207 &    0.189 &  0.39 & 0 & 1 \\ 
+   & Self-Identification - Collection & 69 & 0.137 &    0.130 &  0.34 & 0 & 1 \\ 
+   & Self-Identification - Other & 140 & 0.278 &    0.274 &  0.45 & 0 & 1 \\ 
+   & Founder name in Museum name & 240 & 0.477 &    0.477 &  0.50 & 0 & 1 \\ 
+   & AN Ranking - Not Included &  &  &    0.802 &  0.40 & 0 & 1 \\ 
+   & AN Ranking - Included &  &  &    0.144 &  0.35 & 0 & 1 \\ 
+   & AN Ranking - Dropped &  &  &    0.053 &  0.23 & 0 & 1 \\ 
+   & Exhibition any &  &  &    0.630 &  0.48 & 0 & 1 \\ 
+   & Opening year &  &  & 2001.493 & 11.10 & 1960 & 2020 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density (country) &  &  & 4.5e-01 &  1.26 & 0.00077 & 27.26 \\ 
-   & Pop. (millions) within 10km &  &  & 1.3e+00 &  1.68 & 0.000087 & 10.81 \\ 
-   & Nbr PM within 10km &  &  & 1.8e+00 &  3.14 & 0 & 16 \\ 
-   & Region - Africa & 8 & 0.016 & 1.2e-02 &  0.11 & 0 & 1 \\ 
-   & Region - Asia & 142 & 0.282 & 2.9e-01 &  0.45 & 0 & 1 \\ 
-   & Region - Europe & 248 & 0.493 & 5.0e-01 &  0.50 & 0 & 1 \\ 
-   & Region - Latin America & 23 & 0.046 & 4.2e-02 &  0.20 & 0 & 1 \\ 
-   & Region - North America & 72 & 0.143 & 1.4e-01 &  0.34 & 0 & 1 \\ 
-   & Region - Oceania & 10 & 0.020 & 1.9e-02 &  0.13 & 0 & 1 \\ 
-   & Time Period 2000-2004 &  &  & 1.0e-01 &  0.30 & 0 & 1 \\ 
-   & Time Period 2005-2009 &  &  & 1.7e-01 &  0.37 & 0 & 1 \\ 
-   & Time Period 2010-2014 &  &  & 2.6e-01 &  0.44 & 0 & 1 \\ 
-   & Time Period 2015-2019 &  &  & 3.3e-01 &  0.47 & 0 & 1 \\ 
-   & Time Period 2020-2024 &  &  & 1.4e-01 &  0.35 & 0 & 1 \\ 
-   & Great Recession (2008/09) &  &  & 7.6e-02 &  0.27 & 0 & 1 \\ 
-   & Covid Pandemic (2020/21) &  &  & 1.4e-01 &  0.35 & 0 & 1 \\ 
+ & PM density (country) &  &  &    0.450 &  1.26 & 0.00077 & 27.26 \\ 
+   & Pop. (millions) within 10km &  &  &    1.337 &  1.68 & 0.000087 & 10.81 \\ 
+   & Nbr PM within 10km &  &  &    1.778 &  3.14 & 0 & 16 \\ 
+   & PM density (10km, log) &  &  &    0.527 &  0.79 & 0 & 4.35 \\ 
+   & Nbr PM within 10km (log) &  &  &    0.613 &  0.82 & 0 & 2.83 \\ 
+   & Pop. (millions) within 10km (log) &  &  &   -0.893 &  1.97 & -9.3 & 2.38 \\ 
+   & Local Audience per PM &  &  &    0.567 &  0.86 & 0.000087 & 8.16 \\ 
+   & Local Audience per PM (log) &  &  &   -1.505 &  1.64 & -9.3 & 2.10 \\ 
+   & Region - Africa & 8 & 0.016 &    0.012 &  0.11 & 0 & 1 \\ 
+   & Region - Asia & 142 & 0.282 &    0.292 &  0.45 & 0 & 1 \\ 
+   & Region - Europe & 248 & 0.493 &    0.497 &  0.50 & 0 & 1 \\ 
+   & Region - Latin America & 23 & 0.046 &    0.042 &  0.20 & 0 & 1 \\ 
+   & Region - North America & 72 & 0.143 &    0.138 &  0.34 & 0 & 1 \\ 
+   & Region - Oceania & 10 & 0.020 &    0.019 &  0.13 & 0 & 1 \\ 
+   & Time Period 2000-2004 &  &  &    0.101 &  0.30 & 0 & 1 \\ 
+   & Time Period 2005-2009 &  &  &    0.166 &  0.37 & 0 & 1 \\ 
+   & Time Period 2010-2014 &  &  &    0.258 &  0.44 & 0 & 1 \\ 
+   & Time Period 2015-2019 &  &  &    0.331 &  0.47 & 0 & 1 \\ 
+   & Time Period 2020-2024 &  &  &    0.145 &  0.35 & 0 & 1 \\ 
+   & Great Recession (2008/09) &  &  &    0.076 &  0.27 & 0 & 1 \\ 
+   & Covid Pandemic (2020/21) &  &  &    0.145 &  0.35 & 0 & 1 \\ 
    \hline
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Aug 30 12:00:45 2024
+% Thu Sep  5 13:08:31 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Aug 30 12:08:04 2024
+% Thu Sep  5 13:08:17 2024
 \begin{table}[ht]
@@
 
-The death of the founder is not associated with a significant difference in private museum closure, i.e. museums are not significantly more likely to close after their founder has died.
-It is in principle possible to construct an alternative measure of founder death by splitting the time after the death in a short-term and long-term period; the short-term period might then capture the disruption by the founder, whereas the long-term period would only be reached by museums who have successfully acquired alternative funding models and are hence relatively viable.
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=18cm]{../figures/p_surv_death.pdf}
+\caption{\label{fig:p_surv_death}Comparison of Survival Estimates by Founder Death (95\% CI)}
+\end{figure}
+
+The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e. museums are not significantly more likely to close after their founder has died.
+While the point estimate is positive (0.280, corresponding to a  32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that despite the cumulative character even decade-long survival times do not differ substantially (figure \ref{fig:p_surv_death}).
+
+It is in principle possible to construct an alternative measure of founder death by partioning the time after the death in a short-term and long-term period; the short-term period might then capture the disruption by the founder, whereas the long-term period would only be reached by museums who have successfully acquired alternative funding models and are hence relatively viable.
 However, the choice of choosing a cut-off point between the short- and long-term periods is relatively arbitrary.
@@
 Table \ref{tbl:t_reg_coxph_deathcfg} shows coefficients of both periods with different cut-off points.
-While the coefficient in the short-term period is consistently higher than both the overall death coefficient and the long-term period coefficients, so far the evidence is inconclusive as only few cases are statistically significant\footnote{P-values are not adjusted for multiple tests}.
-Considering the underlying numbers supports this:
-While 47 private museums have seen the death of their founders, only 3 of these have closed in the following 5 years; observing statistical significance in some configurations of founder death time more likely reflect random clustering than an underlying pattern.
-\textbf{Effect sizes}:
-\begin{itemize}
-\item death overall
-\item short-term death
-\end{itemize}
-stress how few people it is
-
-This possibly indicates that private museums might be less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
+While the coefficient in the short-term period is consistently higher than both the overall death coefficient and the long-term period coefficients, so far the evidence is inconclusive as only few cases are statistically significant\footnote{P-values are also not adjusted for multiple tests}.
+Furthermore, such a shock passes quickly relative to the median life-time of museums of 52 years, thus "giving" the founder death little time to lead to many museum closures. 
+Considering the numbers underlying the death effect estimates illustrates the uncertainty of the determning the effect of the death of the founder on aclosing: 
+While 47 private museums have seen the death of their founders, only 3 of these have closed in the following 5 years; given such low numbers it cannot be ruled out that the statistical significance in a few configurations of founder death time results from random fluctuations rather than an underlying pattern.
 
 The reputation of the founder is not statistically related to closure. 
-Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (not statistically significant) and by founders who were included at some point but are no longer included (not statistically significant).
-\paragraph*{Identity Variables}
+Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (21\% elevated closing risk) and by founders who were included at some point but are no longer included (58\% elevated closing risk), however none of the differences are statistically significant.
+It is also worth to point out that the order of the categories does not fully correspond to the expected order, according to which museums whose collectors are not included would be more likely to close than collectors who are.
+However, as all differences are not statistically significant, there is no strong evidence that this reflects unexpected status mechanisms rather than randomness.
+it nevertheless provides some evidence that status matters; as in particular the loss of status appears to be substantially associated with museum closure.
 
-Museums which include the term "museum" in their name are the least likely to close, while those with the term "foundation" or "collection" have higher closure rates (but not significantly higher).
-Museums which include neither of these are the most likely to close, and have mortality rates more than three times as high (\(e\)\textsuperscript{1.18} = 3.25, p<0.01) than institutions including the term "museum".
-The usage of unconventional names might reflect adherence to museum standards which makes museums more understandable and familiar to third parties (e.g.
-audiences, other museums, companies or the government) and thereby facilitates interactions which are beneficial for long-term survival (e.g.
-attracting visitors, cooperations, sponsorships or subsidies).
-However, as founders can choose the name of their museum arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.
+Museums whose name contain the name of the founder face a non-significantly 4.9\% elevated risk of closure, which indicates that there is little evidence that founders face greater difficulties to secure a long-term future for their museums by choosing to emphasize their personal contribution.
+It might have been expected that such central positioning of the founder might limit longevity by disincentivizing contributions by other parties.
+However, as the direct mechanism of declining contributions cannot be observed, its absence cannot be assumed either.
+It might be the case that other parties do indeed feel less inclined to contribute but that these gaps are filled by a stronger commitment of the founder, who having committed her name to the enterprise, wants to keep her museum open event at great costs.
+\subparagraph*{founder conclusion}
+
+Taken together, the inability to explain private museum closing with the death of founder, her exclusion from a prestitious ranking and the presence of her name in the museum's name question the hypothesized central role of the founder.
+In other words, so far little evidence points to founders constituting a substantial source of involuntary closing risk.
 \paragraph*{Competition}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=18cm]{../figures/p_condmef.pdf}
+\caption{\label{fig:p_condmef}Conditional effects of Regional PM Density and Population}
+\end{figure}
 
@@
 
-Country-level Environmental variables show no association with mortality.
-However, at the local level the number of private museum and population density predicts survival chances as the main effects of population number of private museums as well as its interaction is significant.
-Figure \ref{fig:p_pred_popprxcnt} shows predicted average hazard rates for different conditions of regional PM density and population numbers.
-Museums located in sparsely populated areas have (at low PM densities) lower hazard rates than museums in more densely populated areas. 
-Furthermore, these "rural" museums see an increase in the risk of closing for each additional private museum present within 10 kilometers, whereas the risk of closing decreases with  each additional private museum in the local environment for museums in more urban areas.
+Country-level measures of the private museum population show a marginally significant association with mortality (b=0.648, p=0.058).
+While these results provide a support for evidence of competition on the country level leading to closure, it is worth noting that the observed relationship does not correspond to the generally accepted non-monotonic relationship between density and closures (as the linear term is positive, and the squared term not significant at p = 0.22), which postulates that density increases at low densities reduce closing risk (corresponding to a negative linear coefficient), and increases at high numbers increase risk (corresponding to a positive squard term).
+
+At the local level, the number of private museum and population numbers predict survival chances as the main effects of population and number of private museums as well as its interaction are significant.
+The particular pattern is complex:
+As both main terms are positive and the interaction negative, at low values increases in either variable are associated with increases in mortality (figure \ref{fig:p_condmef}).
+Thus, for population values of 0 to 2.97 million people, an increase in the number of private museums corresponds to an increase in mortality (bottom half of figure \ref{fig:p_pred_heatmap}), which provides support for the view that competition leads to museum closure, in particular as this range includes 5056 museums years, or 83\% of the dataset.
+Yet at the same time, at low private museums numbers (0 to 3 private museums), increases in population also increase mortality; this range also includes a large number of museum-years (4960 museum years; 81\% of the data).
+Such a relationship is unexpected insofar as it is unclear why a larger potential audience would be associated with a higher risk of closure.\footnote{Alternative approaches of modeling competition are discussed in the supplementary materials, but cannot answer this question.}
+A possible explanation might be that collectors in less densely populated areas are more committed than those in less populated areas precisely because they know they cannot count visitors to contribute substantially.
+Alternatively, areas with high population and low private museum numbers might more generally lack cultural infrastructure; which one could see supported by closures in Jakarta, Istanbul and Mexico City, but less so by closings in Paris, Tokyo or Madrid.
+Low private museums indicating lack of cultural infrastructure might also explain the decrease in mortality associated with increases in private museum numbers at high population values (figure \ref{fig:p_pred_heatmap}, upper half), as such pattern does not correspond to that predicted by competition.
+More in line with expectation is however the association between increases of population numbers and lower mortality at higher numbers of private museums (right half), as it indicates that audiences can facilitate museum survival.
+
+Taken together, figure \ref{fig:p_pred_heatmap} indicates two niches as particular supportive of private museum survival, on the one hand remote areas with low population and no competing private museums, and on the other densely populated areas with at least some other private museums.
+
+While not all associations correspond to predictions made by resource dependence, the most direct measurement of increased competition, number of private museums in the local surrounding, is associated with higher closing chances for a large part of the sample, which in turn supports the substantial role of competition.
+\paragraph*{Identity Variables}
+
+Museums which include the term "collections" in their name are the least likely to close (0.63 times the rate of museums with the name "museum", while those with the term foundation experience 23\% elevated closure rates (but not significantly higher).
+However, institutions which include neither of these are the most likely to close, and have mortality rates almost three times as high (198\%) than institutions including the term "museum".
+The usage of unconventional names might reflect adherence to museum standards which makes museums more understandable and familiar to third parties (e.g.
+audiences, other museums, companies or the government) and thereby facilitates interactions which are beneficial for long-term survival (e.g.
+attracting visitors, cooperations, sponsorships or subsidies).
+However, as founders can choose the name of their museum arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.
+Some support for the latter interpretaton is given by the fact that two of the three museums for which \textcite{Velthuis_Gera_2024_fragility} identify a temporal intention as the closing reason do not self-identify as museum, collection or foundation.
+A temporal intentions are however the exceptions among closing reasons identified by \textcite{Velthuis_Gera_2024_fragility} (p.6), and as similarly only a small fraction of private museum chooses such a name (140 museums, or 28\%), the overall proportion of these types of voluntary closures compared to all closures is presumably limited.
 \subsection*{Discussion}
@@
 \includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
-\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population}
+\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population (at available values)}
 \end{figure}
@@
 
+It has been widely argued that the death of the founder would lead to his or her private museum to close, while this analysis has not found conclusive evidence for this relationship.
+It is important to keep in mind that the lack of observing a clear relationship between the death of the founder and museum closure does not imply that no relationship exists.
+It is possible that previous scholars who argued for such an association have correctly identified the dependency relationships in private museums, which will become visible once more founder deaths have occurred.
+At the same time, it is possible that private museums are indeed generally less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
 \subsection*{Conclusion}

### 2024-09-06 texts/sup_materials.tex
include timeslice table in sup_materials

@@
-% Created 2024-09-05 do 11:15
+% Created 2024-09-06 vr 15:46
 % Intended LaTeX compiler: pdflatex
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Sep  5 09:54:41 2024
+% Fri Sep  6 15:29:56 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Sep  5 11:13:39 2024
+% Fri Sep  6 15:29:49 2024
 \begin{table}[ht]
@@
   \hline 
- \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_wocryside} & \multicolumn{1}{l}{r\_onlycryside} & \multicolumn{1}{l}{r\_pop42}\\ 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_onlycryside} & \multicolumn{1}{l}{r\_wocryside} & \multicolumn{1}{l}{r\_pop42}\\ 
  \hline
   \multicolumn{6}{l}{\textbf{Founder}} \\ 
- & Gender - Female & -.04 \; (0.34) & .21 \; (0.44) & -1.07 \; (0.78) & -.01 \; (0.34) \\ 
-   & Gender - Couple & -.14 \; (0.32) & .07 \; (0.52) & -.27 \; (0.46) & -.12 \; (0.32) \\ 
-   & Founder died & .28 \; (0.43) & -.19 \; (0.77) & .58 \; (0.59) & .29 \; (0.43) \\ 
+ & Gender - Female & -.04 \; (0.34) & -1.07 \; (0.78) & .21 \; (0.44) & -.01 \; (0.34) \\ 
+   & Gender - Couple & -.14 \; (0.32) & -.27 \; (0.46) & .07 \; (0.52) & -.12 \; (0.32) \\ 
+   & Founder died & .28 \; (0.43) & .58 \; (0.59) & -.19 \; (0.77) & .29 \; (0.43) \\ 
    \multicolumn{6}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .20 \; (0.41) & 1.02 \; (0.65) & .31 \; (0.58) & .18 \; (0.41) \\ 
-   & Self-Identification - Collection & -.45 \; (0.54) & .95 \; (0.71) & -18.23 \; (4781.88) & -.50 \; (0.55) \\ 
-   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.95 \; (0.51)^{***} & .67 \; (0.46) & 1.09 \; (0.31)^{***} \\ 
-   & AN Ranking - Included & .19 \; (0.34) & -.32 \; (0.48) & .55 \; (0.58) & .18 \; (0.34) \\ 
-   & AN Ranking - Dropped & .46 \; (0.50) & .18 \; (0.73) & -.06 \; (0.85) & .47 \; (0.50) \\ 
-   & Founder name in Museum name & .05 \; (0.28) & -.30 \; (0.42) & .24 \; (0.44) & .04 \; (0.28) \\ 
+ & Self-Identification - Foundation & .20 \; (0.41) & .31 \; (0.58) & 1.02 \; (0.65) & .18 \; (0.41) \\ 
+   & Self-Identification - Collection & -.45 \; (0.54) & -18.23 \; (4781.88) & .95 \; (0.71) & -.50 \; (0.55) \\ 
+   & Self-Identification - Other & 1.09 \; (0.30)^{***} & .67 \; (0.46) & 1.95 \; (0.51)^{***} & 1.09 \; (0.31)^{***} \\ 
+   & AN Ranking - Included & .19 \; (0.34) & .55 \; (0.58) & -.32 \; (0.48) & .18 \; (0.34) \\ 
+   & AN Ranking - Dropped & .46 \; (0.50) & -.06 \; (0.85) & .18 \; (0.73) & .47 \; (0.50) \\ 
+   & Founder name in Museum name & .05 \; (0.28) & .24 \; (0.44) & -.30 \; (0.42) & .04 \; (0.28) \\ 
    \multicolumn{6}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .65 \; (0.34) & -1.16 \; (2.52) & .88 \; (0.44)^{*} & .67 \; (0.34)^{*} \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) & 1.33 \; (2.38) & -.04 \; (0.02) & -.03 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .17 \; (0.17) & 1.69 \; (0.81)^{*} & .20 \; (0.12) \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} & .19 \; (0.10) & .64 \; (1.06) & .22 \; (0.20) \\ 
+ & PM density (country) & .65 \; (0.34) & .88 \; (0.44)^{*} & -1.16 \; (2.52) & .67 \; (0.34)^{*} \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.04 \; (0.02) & 1.33 \; (2.38) & -.03 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & 1.69 \; (0.81)^{*} & .17 \; (0.17) & .20 \; (0.12) \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} & .64 \; (1.06) & .19 \; (0.10) & .22 \; (0.20) \\ 
    & Nbr PM$^{2}$ within 10km &  &  &  & .01 \; (0.02) \\ 
-   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.07 \; (0.04)^{*} & -.54 \; (1.83) & -.02 \; (0.09) \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.54 \; (1.83) & -.07 \; (0.04)^{*} & -.02 \; (0.09) \\ 
    & Nbr PM$^{2}$ (10km) * Pop (10km) &  &  &  & -.01 \; (0.01) \\ 
-   & Great Recession (2008/09) & -1.59 \; (1.01) & -18.42 \; (5245.29) & -.75 \; (1.04) & -1.59 \; (1.01) \\ 
-   & Covid Pandemic (2020/21) & .42 \; (0.29) & .30 \; (0.41) & .46 \; (0.47) & .45 \; (0.29) \\ 
+   & Great Recession (2008/09) & -1.59 \; (1.01) & -.75 \; (1.04) & -18.42 \; (5245.29) & -1.59 \; (1.01) \\ 
+   & Covid Pandemic (2020/21) & .42 \; (0.29) & .46 \; (0.47) & .30 \; (0.41) & .45 \; (0.29) \\ 
    \hline
- & Museums & 503 & 219 & 283 & 503 \\ 
-   & Museum-years & 6096 & 2265 & 3311 & 6096 \\ 
-   & Closures & 68 & 35 & 28 & 68 \\ 
-   & log. Likelihood & -339.68 & -139.36 & -116.47 & -338.79 \\ 
-   & AIC & 711.35 & 310.72 & 264.94 & 713.59 \\ 
-   & BIC & 746.87 & 335.60 & 286.25 & 753.54 \\ 
+ & Museums & 503 & 283 & 219 & 503 \\ 
+   & Museum-years & 6096 & 3311 & 2265 & 6096 \\ 
+   & Closures & 68 & 28 & 35 & 68 \\ 
+   & log. Likelihood & -339.68 & -116.47 & -139.36 & -338.79 \\ 
+   & AIC & 711.35 & 264.94 & 310.72 & 713.59 \\ 
+   & BIC & 746.87 & 286.25 & 335.60 & 753.54 \\ 
    \hline 
@@
 However, both these models are not reliable, as they do not properly converge (indicated by extremely large coefficients in both models).
+\subsection*{Alternative time range specifications}
+
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Fri Sep  6 15:29:50 2024
+\begin{table}[ht]
+\centering
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
+  \hline 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_2005} & \multicolumn{1}{l}{r\_2010} & \multicolumn{1}{l}{r\_2015}\\ 
+ \hline
+  \multicolumn{6}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & -.04 \; (0.34) & .00 \; (0.34) & .05 \; (0.34) & .31 \; (0.37) \\ 
+   & Gender - Couple & -.14 \; (0.32) & -.10 \; (0.32) & -.39 \; (0.35) & -.35 \; (0.40) \\ 
+   & Founder died & .28 \; (0.43) & .13 \; (0.46) & .34 \; (0.46) & -.22 \; (0.55) \\ 
+   \multicolumn{6}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .20 \; (0.41) & .25 \; (0.42) & .24 \; (0.43) & -.13 \; (0.48) \\ 
+   & Self-Identification - Collection & -.45 \; (0.54) & -.41 \; (0.54) & -.37 \; (0.55) & -.62 \; (0.60) \\ 
+   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.14 \; (0.31)^{***} & 1.15 \; (0.32)^{***} & .96 \; (0.35)^{**} \\ 
+   & AN Ranking - Included & .19 \; (0.34) & .17 \; (0.34) & .26 \; (0.35) & -.35 \; (0.49) \\ 
+   & AN Ranking - Dropped & .46 \; (0.50) & .22 \; (0.55) & .28 \; (0.55) & .13 \; (0.56) \\ 
+   & Founder name in Museum name & .05 \; (0.28) & .05 \; (0.28) & -.01 \; (0.29) & .46 \; (0.32) \\ 
+   \multicolumn{6}{l}{\textbf{Environment}} \\ 
+ & PM density (country) & .65 \; (0.34) & .70 \; (0.38) & .40 \; (0.45) & .25 \; (0.51) \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) & -.02 \; (0.03) & -.02 \; (0.06) \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} & .25 \; (0.10)^{**} & .24 \; (0.11)^{*} \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} & .25 \; (0.08)^{***} & .25 \; (0.08)^{***} & .23 \; (0.08)^{**} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.07 \; (0.03)^{*} \\ 
+   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.69 \; (1.01) &  &  \\ 
+   & Covid Pandemic (2020/21) & .42 \; (0.29) & .33 \; (0.29) & .28 \; (0.30) & .12 \; (0.31) \\ 
+   \hline
+ & Museums & 503 & 502 & 499 & 485 \\ 
+   & Museum-years & 6096 & 5483 & 4474 & 2901 \\ 
+   & Closures & 68 & 67 & 64 & 50 \\ 
+   & log. Likelihood & -339.68 & -329.47 & -304.28 & -217.32 \\ 
+   & AIC & 711.35 & 690.94 & 638.57 & 464.65 \\ 
+   & BIC & 746.87 & 726.22 & 670.95 & 493.33 \\ 
+   \hline 
+ \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+\end{tabular}
+\caption{Cox PH regression results with different time slices} 
+\label{tbl:t_reg_coxph_timeslice}
+\end{table}
+
+Table \ref{tbl:t_reg_coxph_timecfg} investigates whether relationships have substantially changed over time.
+However, subsetting the dataset to different year ranges shows general consistency of the main findings, in particular insignificant coefficients for the founder's death, gender, Artnews ranking variables, inclusion of founder name in museum name, positive and significant coefficients for self-identification as other, population and private museum numbers, and a significant negative interaction between private museum numbers and population.
 \end{document}

### 2024-09-06 texts/paper_closing.tex
many small improvements after first reading

@@
-% Created 2024-09-06 vr 09:44
+% Created 2024-09-06 vr 16:21
 % Intended LaTeX compiler: pdflatex
@@
 These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums operated and financed by the state, foundations or associations.
-While the emergence of this organizational form has attracted attention (cf.
-\cite{Kolbe_etal_2022_privatemuseum} for a literature review), the process of closure has received considerably less attention.
+While many aspects of this new organizational form has attracted attention, such as their emergence, relations to other institutions or impact on artist consecration (cf.
+\cite{Kolbe_etal_2022_privatemuseum} for a literature review), the process of closure has received considerably less attention
+Furthermore, the focus that has been given to questions of sustainability has been primarily conducted through case studies; beyond the exception of \textcite{Velthuis_Gera_2024_fragility} quantitative studies have been absent.
 In this paper, I address this gap by investigating the closure event of members of this new organizational form.
@@
 Furthermore, analyzing which museums survive allows to make informed speculations on the future of this recently emerged organizational form.
-\subsection*{Private museums definition}
+
+While a recent study by \textcite{Velthuis_Gera_2024_fragility} has investigated closing reasons of private museums, I extend/complement this study by using a more elaborate statistical model and additional data sources.
+In particular, I compare private museum closing rates to those of other museum populations, and analyze the risk associated with variables on the level of the founder, museum and environment. 
+Taken together, the results show that (at least so far) little evidence exists neither for private museums being overly dependend on their founder, nor having overall higher mortality rates than other non-profit museums.
+While little evidence points toward private museums being unvoluntarily at risk due to their low diversification, private museums may close due to environmental pressures, which exhibit a complex relationship which for most museums consists of competition from other private museums as well as, unexpectedly, large audiences.
+Finally, some limited evidence points towards a temporary intention by their founders from the very beginning as a potential reason for their closure.
+
+This study furthermore combines museum research with quantitative non-profit management literature, a link which has so far been weak. 
+\subsection*{Private museums definition and dependency relations}
+
+\subsubsection*{definition}
 
@@
 \noindent
-Private museums:
-\begin{itemize}
-\item founded by collector -> needs to have amassed substantial art collection
-\item building of its own, limited public/corporate funding, has to be visitable -> requires substantial resources
-\end{itemize}
-\subsection*{Private museums dependencies}
+While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{diMaggio_1982_boston,Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than e.g.
+loaning or donating their collection or opening museums as a group.
+This phenomenon of private collectors taking the initiative in setting up a museum of their own has become increasingly widespread, with around 80\% of currently open private museums having opened since 2000 \parencite{Velthuis_etal_2023_boom}.
+To be considered as a private museum for this study, a collector needs to have amassed a substantial art collection, which he exhibits in a building in a way that is accessible to the public, all while receiving limited public and corporate funding.
+The central role of the founder delimits a private museum from other organizational forms such as public museums supported by local or state governments, corporate museums run by companies or other non-profit museums operated by associations or foundations with more dispersed ownership and control.\footnote{Which is not to say that for an institution to be considered a private museum, it has to be legal personal ownership of the founder.
+Insted the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms; generally this has to be assessed on a case-by-case basis.}
 
-Private museums have been argued to be highly dependent on their founder for their continuing existence, as museums generally cannot cover expenses via revenues from ticket prices, museum shops and cafes.
+Due to the founders central role, private museums have been argued to be highly dependent on their founder for their continuing existence, as museums generally cannot cover expenses via revenues from ticket prices, museum shops and cafes:
 The \textcite{IMLS_2008_funding} found that for non-profit American art museums, less than half (48.1\%) the revenues come from earned income, leaving substantial gaps in the budgets that are filled by a mix of private donations (23.0\%), investment (18.5\%) and government support (10.4\%) (p.27).
 Outside of the United States, the reliance on revenue streams beyond operations is even larger:
-German museums have had on average only 27\% of their expenses covered by operations \parencite[p.233]{Martin_1993_museen}, and even the more market-oriented NPOs in the cultural sector draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
+German museums in the 1990s covered on average only 27\% of their expenses covered by operations \parencite[p.233]{Martin_1993_museen}, and even the more market-oriented NPOs in the cultural sector draws around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
 
-Given that operating at "the margin of financial sustainability" is the "ordinary condition" for cultural NPOs, \cite[p.2]{Licci_BaraldiBonini_2024_sustainability}, it is not surprising that costs have been listed as a primary reason for private museum closure:
+Given that operating at "the margin of financial sustainability" is the "ordinary condition" for cultural NPOs, \parencite[p.2]{Licci_BaraldiBonini_2024_sustainability}, it is not surprising that costs have been listed as a primary reason for private museum closure:
 \textcite{Adam_2021_rise} argues that "most of the cases of defunct private museums come back to the issue of cost" (p.79); a sentiment shared by \textcite{Walker_2019_collector} who notes that "private institutions struggle to contain escalating costs that are associated with running a museum" (p.234).
@@
 \textcite{Bechtler_Imhof_2018_future} also characterize "the dependency on single individuals only" as one of main reasons that "make these private museums fragile" (p.53).
-\cite{StylianouLambert_etal_2014_museums} also characterizes many private institutions as "small individual museums that depend too much on their creators to guarantee their sustainability" (p.582).
+\cite{StylianouLambert_etal_2014_museums} also characterize many private institutions as "small individual museums that depend too much on their creators to guarantee their sustainability" (p.582).
 Beyond a direct financial component, private museums have been also been characterized as fragile since they can only rely on their founder for "taste", "vision and drive" \parencite[p.77]{Adam_2021_rise}, "passion" \parencite[p.234]{Walker_2019_collector} or "skills and knowledge" \parencite[p.580]{StylianouLambert_etal_2014_museums}.
 The link between diversification and mortality, i.e.
-higher survival chances for more diversified organizations, has been found for non-profit organizations more generally \parencite{Fernandez_2007_dissolution,Bielefeld_1994_survival,Hager_2001_vulnerability,Lu_Shon_Zhang_2019_dissolution}\footnote{An larger literature exists shows a link between diversification and measures of financial health and sustainability besides survival \parencite{Licci_BaraldiBonini_2024_sustainability}}; it is thus plausible to apply to museums as well.
+higher survival chances for more diversified organizations, has been found for non-profit organizations more generally \parencite{Fernandez_2007_dissolution,Bielefeld_1994_survival,Hager_2001_vulnerability,Lu_Shon_Zhang_2019_dissolution}; it is thus plausible to apply to museums as well.
 
@@
 \textcite{Velthuis_Gera_2024_fragility} similarly argue that "the founder’s death will almost inevitably have a direct impact on the financial health of the museum" (p.10).
-\cite{StylianouLambert_etal_2014_museums}, after discussing a case of a private museum whose owner "does not believe that anyone else could love the museum as much as she does", argues that this "generates questions regarding the cultural sustainability of small private museums in cases where their initiators are not able to care for them any longer" (p.580).
+\cite{StylianouLambert_etal_2014_museums}, after discussing a case of a private museum whose owner "does not believe that anyone else could love the museum as much as she does", argue that this "generates questions regarding the cultural sustainability of small private museums in cases where their initiators are not able to care for them any longer" (p.580).
 
-Overall, two related arguments emerge from the current literature:
-First, individual private museums rely on heavily on their founders for survival; events that interrupt the founders ability to provide resources are therefore associated with a highler likelihood of closing.
-Second, due to their low diversification (high reliance on the founder), private museums have are more fragile than museums where single individuals are not comparably central figures.
+Overall, two related arguments emerge from the current literature on private museum sustainability:
+First, individual private museums heavily rely on their founders for survival; events that interrupt the founders ability to provide resources are therefore associated with a highler likelihood of closing.
+Second, due to their low diversification (high reliance on the founder), private museums are more fragile than museums where single individuals are not comparably central figures.
 
@@
 However, no systematic data is used to estimate public museum longevity, and while some
-remarks are made that public spending cuts might result in problems for public museum operations (p.XX), the overall characterization of them remains as immortal \parencite{Frey_Meier_2002_beyeler}.
-Responsible for the characterization of private museums as fragile might also be implicit reliance on the ICOM definition \parencite{ICOM_2024_definition} of museums as "permanent institutions", according to which every closing is indicative of fragility.
-So far a third comparison has been absent, namely that to other non-profit museums which are not initiated and run by a single collector, but by a wider group of founders or foundations.
-As these share with private museums a common organizational form of the non-profit organization or foundation  and a similarly harsh environment, yet and differ primarily in regards to their diversification, i.e.
+remarks are made that public spending cuts might result in problems for public museum operations (p.233), the overall characterization of them remains as immortal \parencite{Frey_Meier_2002_beyeler}.
+Responsible for the characterization of private museums as fragile might also be implicit reliance on the ICOM definition \parencite{ICOM_2024_definition} of museums as "permanent institutions" (according to which every closing is indicative of fragility), which is echoed by an interviewee of \textcite{Walker_2019_collector} who expresses (his perspective on) the prevalent perspective as "We assume museums are forever" (p.235).
+So far a third comparison has been absent, namely that to other non-profit museums which are not initiated and run by a single collector, but by a wider group of founders, foundations or associations.
+As these share with private museums a common organizational form of the non-profit organization or foundation  and the same harsh environment of the cultural sector where operations cannot sustain an organization, yet differ primarily in regards to their diversification, i.e.
 their reliance on a single founder as central authority and income stream, they provide a effective way of investigating the effect of diversification on museum survival.
@@
 Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations are likely factors that contribute to its viability and hence longevity.
-While some of these aspects can be influenced by the founder (in particular the available audience, via being able to decide a location and the extent to which a museum should organize exhibitions), other are less so.
+While some of these aspects can be influenced by the founder (in particular the museum's location and strategies) , other are less so.
 In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
@@
 Lack of interest by the public can be a consequence of multiple processes.
-While competition is one such processes, and applies if nearby competing institutions capture large portions of the audience, lack of interest can also result from a lack of audience (in the absence of competing institutions), which may be the case for private museums located in sparsely populated areas \parencite{Foster_2015_cube}.
+While competition is one such processes, and applies if nearby competing institutions capture large portions of the audience, lack of interest can also result from a lack of audience (in the absence of competing institutions), which may be the case for private museums located in sparsely populated areas.
 In both these cases, the resources that a private museum is able to receive from actors in its environment are limited.
@@
 But there are so many organizations applying for the same grants" (ibid.).
-Quantitative studies have identified a relation between competition and non-profit closing primarily via measuring competition over density \cite{Park_Shon_Lu_2021_mortality,Haugh_etal_2021_nascent,Lu_Shon_Zhang_2019_dissolution}, with higher number of non-profits increasing the chance of non-profit dissolution.
+Quantitative studies have identified a relation between competition and non-profit closing primarily via measuring competition over density \parencite{Park_Shon_Lu_2021_mortality,Haugh_etal_2021_nascent,Lu_Shon_Zhang_2019_dissolution}, with higher number of non-profits increasing the chance of non-profit dissolution.
 
@@
 
-The empirical record of the link between identity and survival for non-profit organizations is mixed: 
+The empirical record of the link between identity and survival for non-profit organizations however is mixed: 
 For example \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close, and \textcite{HernandezOrtiz_2022_discontinuity} observes a declining image or reputation as a cause of closure in a number of non-profits (p.115).
-However, other studies find little to no effect of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
+Nonetheless, other studies find little to no effect of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
+
 Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
 Next to "hard" organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate.
-However, the category of museums could be relatively flexible (for example, it is generally not subject to state regulation), which might result in a relatively high tolerance of diversity as "anything goes" and hence limited "devaluation" of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.
-
-Furthermore, identity of a private museum may be influenced by the identity of persons most closely affiliated with it, in particular the identity of its founders.
-Given that founders are the very reason behind the existence of these organizations, and sometimes plan these as their personal legacies \parencite{Walker_2019_collector}, founder status gains or losses may reflect on the wider organization and affect its survival propspects.
+However, the category of museums could be relatively flexible (for example, the term "museum" is generally not subject to state regulation in the US or Germany \parencite{Museumsbund_ICOMDE_2006_standards,Lister_2023_marketing}), which might result in a relatively high tolerance of diversity as "anything goes" and hence limited devaluation of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.
 
@@
 \noindent
-\textbf{Hypothesis 4}: Private museums with identities more understandable and favorable are less likely to close.
+\textbf{Hypothesis 4}: Private museums with more understandable identities, indicated by adherence to naming conventions, are less likely to close.
 
@@
 Furthermore, inferring the status of the museum via the reputaton of the founder again explores the extent to which the founder is a figure of central importance for the private museum.
-\subsection*{Data and Methods}
+\subsection*{Methods and Data}
 
@@
 However, as no institutions are maintaining museum databases on a global scale, I use existing quantitative studies of museum closure to compare to these private museums in terms of their closing rates.
-This non-parametric method estimates the hazard rate as the conditional probability of exiting at time t\textsubscript{i} given being alive as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at time \(t_i\) and \(d_i\) as the number of exits at time \(t_i\)), and the survival function as the product of these conditional probabilities as \(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\).
+This non-parametric method estimates the hazard rate as the conditional probability of exiting at time t\textsubscript{i} given being alive as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at time \(t_i\) and \(d_i\) as the number of exits at time \(t_i\)).
+Hazards can be calculated over calendar time (thus comparing closures in a given year to museums being open in that year) or over age (comparing closures at a given age to museums being open at that age), the latter is the more prevalent approach in survival analysis as it allows to calculate the survival function as the product of conditional survival probabilities as \(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\).
 
 Hypothesis 2 to 4, which differentiate the private museum population according to a number of risk factors, are investigated via Cox proportional hazard models. 
-The main dependenent variable is here indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
-Typically for survival data, museums that do not close during the observation period are right-censored, i.e. for such museums the dependent variable is zero for all years.
+The dependent variable is indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
+Typically for survival data, museums that do not close during the observation period are right-censored, i.e.
+for such museums the dependent variable is zero for all years as their closing has not been observed.
 The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
@@
 
-A measure of founder death is constructed as a time-varying covariate, which can take the values of the founder being alive, having deceased recently (the year in question and the year after that), and having been deceased for more than 2 years.
-While it would have been possible to model founder death as a binary variable, two separate stages of death allows to separately investigate the short- and long-term impacts.
+A measure of founder death is constructed as a time-varying covariate, which takes the value of 1 from the year of the founder's death onwards.
 \paragraph*{Legitimacy}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Sep  5 13:08:13 2024
+% Fri Sep  6 15:49:38 2024
 \begin{table}[ht]
@@
 To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55.000 museums, are analyzed.
-In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial naming convention.
-
-prevalence of museum founders to include the term museum in the name of their institution\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum}.
+In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum}.
 \paragraph*{Reputation}
@@
 To account for two prevalent shocks in the recent decades, the Great Recession and the Covid-19 pandemic, I thus include two dummy variables for 2008/2009 and 2020/2021; respectively.
-\subsubsection*{Analytical framework}
-
-First, I investigate the relationship between age and closing descriptively using hazard rates and the Kaplan-Meier survival function.
-This non-parametric method estimates the hazard rate as the conditional probability of exiting at time t\textsubscript{i} given being alive as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at time \(t_i\) and \(d_i\) as the number of exits at time \(t_i\)), and the survival function as the product of these conditional probabilities as \(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\).
-
-Secondly, we use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
 \subsection*{Results}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Sep  5 13:08:11 2024
+% Fri Sep  6 15:49:37 2024
 \begin{table}[ht]
@@
 In total, 523 private museums are included in the dataset which are either open or have closed\footnote{This does not include 25 institutions which were private museums at some point and have since been transformed into other organizational forms; these cases are discussed in the limitations.}.
+While around 20\% of private museums have opened before 2000, the retrospective data collection does not rule out the possibility that some institutions were missed, with such risks likely being higher for earlier time periods.
+To ensure that the effect of such missed museums is does not distort insights, the time range in question is limited to events between 2000-2021.
 A small number of museums are excluded, in particular three museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), as well as two which closed before 2000 as they fall outside the period under investigation.
@@
 
-While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})\footnote{IRS data is not without limitations, such as only being required from larger organizations, misreporting, and the difficulty of inferring closing from non-filing.
-Nevertheless, it constitutes the most fine-grained data source to investigate non-profit survival}.
-None of these focus specifically on art museums (\textcite{Hager_2001_vulnerability} focuses on Art NPOs, \textcite{Bowen_1994_charitable} and \cite{Gordon_etal_2013_insolvency} on NPOs generally), but report survival estimates by organizational form, including museums.
-\textcite{Bowen_1994_charitable} reports average annual exit rates for all 501(c)(3) museums in the 1981-1991 time period of 1.1\% (p.103)
-\textcite{Gordon_etal_2013_insolvency} observes 35 closures over the years of 2000-2003 with 5,167 "firm-years" (p.368), resulting in an annual "average insolvency rate" of 0.68\% (p.377).
-Some of this difference may be explained by higher shares of smaller organizations in \textcite{Bowen_1994_charitable}, where NPOs of any size are included, whereas \textcite{Gordon_etal_2013_insolvency} excluded NPOs with operational revenues below 150,000 USD by, as smaller non-profits are at higher risk of closing \parencite{Harrison_Laincz_2008_nonprofit,Helmig_Ingerfurth_Pinz_2013_nonprofit}.
-Focusing directly on Art museums, rather than museum generally, \textcite{Hager_2001_vulnerability} observes 42 closures over a period of 4 years (1994-1997) from a starting populaton of 448 (p.383).
-As his way of delineating the population (having "filed an annual Form 990 tax return with the IRS for the 1990, 1991, or 1992 tax year", p.380) does not rule out that some closings took place in 1991, 1992 or 1993\footnote{In particular it is unclear why 1993 is not treated as belonging to the observation period}, attributing some closings to these years is likely appropriate, and presumably roughly equivalent to assuming an observation period of five (rather than four) years, which corresponds to an average yearly closing rate of \(1-\sqrt[5]{406/448}\) = 1.9\%\footnote{So far it is hard to tell why art museums appear to have higher closing rates than museums generally.
-According to \textcite{IMLS_2008_funding}, art museums have above-average reliance on earned income (46.1\% compared to 43.7\% on average, p.26), and \textcite{Bowen_1994_charitable} argue that a higher reliance on income is associated with exit rates (p.102), but it is questionable whether such an a small difference in percent earned can explain a 1.7-2.7 times higher closing risk.
-Similarly, while art museums do not have the largest coffers (in particular museums of natural history and science are substantially larger \cite{IMLS_2008_funding,Bowen_1994_charitable}), art museums have substantially higher incomes than the history museums (which are more frequent), historical societies and botanical gardens \parencite{IMLS_2008_funding} as well as "other museums" with more specialized and/or local focuses \parencite{Bowen_1994_charitable}.
-Especially the larger number of history museums, and the more restrictive inclusion by \textcite{Hager_2001_vulnerability} in comparison to \textcite{Bowen_1994_charitable} make the higher mortality rate for art museums than museums generally puzzling.}
-
 \begin{table}[htbp]
-\caption{\label{tbl:litreview}Hazard rates in studies of museums and art NPOs}
+\caption{\label{tbl:litreview}Hazard rates in studies of museums survival}
 \centering
@@
 \cite{Gordon_etal_2013_insolvency} & Museums & 0.7\%\\
-\cite{Bowen_1994_charitable} & Museums & 1.1\%\\
+\cite{Bowen_etal_1994_charitable} & Museums & 1.1\%\\
 current study & Private Art Museums & 0.84\% (overall)\\
@@
 
-Results are summarized in table \ref{tbl:litreview}.
+\FloatBarrier
+
+While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})\footnote{IRS data is not without limitations, such as only being required from larger organizations, misreporting, and the difficulty of inferring closing from non-filing.
+Nevertheless, it constitutes the most fine-grained data source to investigate non-profit survival}.
+None of these focus on art museums exclusively (\textcite{Hager_2001_vulnerability} focuses on Art NPOs, \textcite{Bowen_etal_1994_charitable} and \textcite{Gordon_etal_2013_insolvency} on NPOs generally), but report survival estimates by organizational form, including museums.
+\textcite{Bowen_etal_1994_charitable} investigates the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
+\textcite{Gordon_etal_2013_insolvency} observes 35 closures over the years of 2000-2003 with 5,167 museum-years (p.368), resulting in an average annual closing rate of 0.68\% (p.377).
+Some of this difference may be explained by higher shares of smaller organizations in \textcite{Bowen_etal_1994_charitable}, where museums of any size are included, whereas \textcite{Gordon_etal_2013_insolvency} excluded NPOs with operational revenues below 150,000 USD by, as smaller non-profits are at higher risk of closing \parencite{Harrison_Laincz_2008_nonprofit,Helmig_Ingerfurth_Pinz_2013_nonprofit}.
+
+Focusing directly on Art museums, rather than museum generally as part of the wider focus on Art NPOs, \textcite{Hager_2001_vulnerability} observes 42 closures over a period of 4 years (1994-1997) from a starting populaton of 448 (p.383).
+As his way of delineating the population (having "filed an annual Form 990 tax return with the IRS for the 1990, 1991, or 1992 tax year", p.380) does not rule out that some closings took place in 1991, 1992 or 1993\footnote{In particular it is unclear why 1993 is not treated as belonging to the observation period}, attributing some closings to these years is likely appropriate, and presumably roughly equivalent to assuming an observation period of five (rather than four) years, which corresponds to an average yearly closing rate of \(1-(406/448)^{1/5}\) = 1.9\%.\footnote{So far it is hard to tell why art museums appear to have higher closing rates than museums generally.
+According to the \textcite{IMLS_2008_funding}, art museums have above-average reliance on earned income (46.1\% compared to 43.7\% on average, p.26), and \textcite{Bowen_etal_1994_charitable} argue that a higher reliance on income is associated with higher exit rates (p.102), but it is questionable whether such an a small difference in percent earned can explain a 1.7-2.7 times higher closing risk.
+Similarly, while art museums do not have the largest coffers (in particular museums of natural history and science are substantially larger \parencite{IMLS_2008_funding,Bowen_etal_1994_charitable}), art museums have substantially higher incomes than the history museums (which are more frequent), historical societies and botanical gardens \parencite{IMLS_2008_funding} as well as "other museums" with more specialized and/or local focuses \parencite{Bowen_etal_1994_charitable}.
+Especially the larger number of history museums, and the more restrictive inclusion by \textcite{Hager_2001_vulnerability} in comparison to \textcite{Bowen_etal_1994_charitable} make the higher mortality rate for art museums than museums generally puzzling.}
+
+Results are combined in table \ref{tbl:litreview}.
 Average annual closing rates fall within closing rates found in previous studies, and even the 2010-2021 time periods with higher risk is below the general estimate for art museums by \textcite{Hager_2001_vulnerability}.
-There is thus overall little support to the idea that private museums are exposed to higher closing risk than museums, thus refuting Hypothesis 1.
+There is thus overall little evidence that private museums are exposed to higher closing risk than non-profit museums generally, which provides little support for hypothesis 1.
 \subsubsection*{Hazard rate and Age Dependence}
@@
 
-Next to average yearly closing rates, private museum closing can also be investigated over its age (unfortunately, no comparison to previous studies can be done as age-dependent mortality estimates are not reported).
+Next to average yearly closing rates, private museum closing can also be investigated over its age (no comparison to previous studies can be done these did not report age-dependent mortality estimates).
 Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
@@
 the overall average hazard rate is 0.90\%), for ages above 30 only few observations are available, which make these predictions rather uncertain.}
-
-The increase in the first years is likely due to what has been called "initial resource endowments" in organizational research \cite{Carroll_Khessina_2019_demography,Hannan_1998_mortality} (not to be confused with the practice of a particular endowment for e.g.
-a museum REF, i.e.
-a stock of money, often invested in stocks, whose capital gains are used for operations).
-As the establishment of a museum requires considerable resources, their founders appear to allocate enough resources to keep the risk of closure small in the first years after opening.
-Given that founders are likely aware that their endeavor is unlikely to generate a profit, they are not vulnerable to the liability of newness \parencite{Stinchcombe_1965_structure}.
+The increase in the first years is likely explained by the fact that as the establishment of a museum requires considerable resources, their founders have allocated enough resources to keep the risk of closure minimal in the first years after opening.
 
@@
 While only a fraction of all opened museums has closed (68 out of 503), under the assumption of average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, median life expectancy can be estimated as approximately 52 years.
-On first sight such findings seems to differ from a previous quantitative analysis of the database, which argued that "the median number of years that private museums were open before they closed is 10 years" \parencite[p.5]{Velthuis_Gera_2024_fragility}, as previously only closed museums were considered.
+On first sight such findings seems to differ from a previous quantitative analysis of the same data used here, which argued that "the median number of years that private museums were open before they closed is 10 years" \parencite[p.5]{Velthuis_Gera_2024_fragility}, as previously only closed museums were considered.
 Focusing on the entire population of private museums instead, this analysis provides additional insights into the expected longevity of private art museums.
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Sep  5 13:08:31 2024
+% Fri Sep  6 15:49:55 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Sep  5 13:08:17 2024
+% Fri Sep  6 15:49:42 2024
 \begin{table}[ht]
@@
 While public museums have been characterized to some extent as very stable due to government picking up deficits \parencite{Meier_Frey_2003_faces,Bechtler_Imhof_2018_future}, \textcite{Walker_2019_collector} argues that due to declining cultural spending even public museums might face hard times.
-While national public flagship institutions will likely remain sufficiently funded to survive, this might not be the case for the vast majority of smaller museums in less touristic regions who rely on limited municipal funding, as \textcite{StylianouLambert_etal_2014_museums} demonstrates for a number of smaller publicly funded ethnography museums in Cyprus.
+While national public flagship institutions will likely remain sufficiently funded to survive, this might not be the case for the vast majority of smaller museums in less touristic regions who rely on limited municipal funding, as \textcite{StylianouLambert_etal_2014_museums} demonstrate for a number of smaller publicly funded ethnography museums in Cyprus.
 Without access to museum register comparable to the IRS/NCCS datasets, such questions regarding the relation between type of ownership and survival remain speculative.

### 2024-09-06 texts/paper_closing.tex
more minor improvements

@@
-% Created 2024-09-06 vr 16:21
+% Created 2024-09-06 vr 17:50
 % Intended LaTeX compiler: pdflatex
@@
 remarks are made that public spending cuts might result in problems for public museum operations (p.233), the overall characterization of them remains as immortal \parencite{Frey_Meier_2002_beyeler}.
-Responsible for the characterization of private museums as fragile might also be implicit reliance on the ICOM definition \parencite{ICOM_2024_definition} of museums as "permanent institutions" (according to which every closing is indicative of fragility), which is echoed by an interviewee of \textcite{Walker_2019_collector} who expresses (his perspective on) the prevalent perspective as "We assume museums are forever" (p.235).
+Responsible for the characterization of private museums as fragile might also be implicit reliance on the ICOM definition \parencite{ICOM_2024_definition} of museums as "permanent institutions" (according to which every closing is indicative of fragility), which is echoed by an interviewee of \textcite{Walker_2019_collector} who expresses (his perspective on) the prevalent perspective as "we assume museums are forever" (p.235).
 So far a third comparison has been absent, namely that to other non-profit museums which are not initiated and run by a single collector, but by a wider group of founders, foundations or associations.
@@
 the centrality of the founder for museum finances, has been argued to constitute the key feature of private museum vulnerability, it is also important to consider the other ways in which private museums, as (non-profit) organizations, are entangled with their environments.
-Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations are likely factors that contribute to its viability and hence longevity.
+Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations possibly constitute factors that contribute to its viability and hence longevity.
 While some of these aspects can be influenced by the founder (in particular the museum's location and strategies) , other are less so.
@@
 \paragraph*{Competition}
-
-mechanism: losing motivation?
 
@@
 Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
-Next to "hard" organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate.
-However, the category of museums could be relatively flexible (for example, the term "museum" is generally not subject to state regulation in the US or Germany \parencite{Museumsbund_ICOMDE_2006_standards,Lister_2023_marketing}), which might result in a relatively high tolerance of diversity as "anything goes" and hence limited devaluation of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.
+Next to material organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate.
+However, the category of museums could be relatively flexible (for example, the term "museum" is generally not subject to state regulation in the US or Germany \parencite{Museumsbund_ICOMDE_2006_standards,Lister_2023_marketing}), which might result in a relatively high tolerance of diversity and hence limited devaluation of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.
 
@@
 Using this database, in particular year of opening and, if available, closing, it is possible to reconstruct the life course of the each institution with museum-year as the unit of analysis.
+While around 20\% of private museums have opened before 2000, the retrospective data collection does not rule out the possibility that some institutions were missed, with such risks likely being higher for earlier time periods.
+To ensure that the effect of such missed museums is does not distort insights, the time range in question is limited to events between 2000-2021.
 This data allows to conduct survival analysis (also known as event history analysis), the most common statistical technique to investigate hazard rates and identify mortality-assocated covariates \parencite{Moore_2015_survival,Allison_2014_event}.
@@
 Women constitute a minority of the private museums founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would have a greater difficulties in securing resources third parties, presumably primarily governments and corporate sponsors.
-However, women may also be particularly associated with philanthropic initiatives (unlike e.g.
-corporate activities, \cite{Milam_2013_artgirls}) to such an extent that devaluation of female initiatives may not necessarily be present.
-
-Centrality of the founder's vision is measured via the proxy of whether the name of the founder is included in the name of the museum.
+However, women may also be particularly associated with philanthropic initiatives - in contrast to corporate activities \parencite{Milam_2013_artgirls} - to such an extent that devaluation of female initiatives may not necessarily be present.
 
@@
 In total, 523 private museums are included in the dataset which are either open or have closed\footnote{This does not include 25 institutions which were private museums at some point and have since been transformed into other organizational forms; these cases are discussed in the limitations.}.
-While around 20\% of private museums have opened before 2000, the retrospective data collection does not rule out the possibility that some institutions were missed, with such risks likely being higher for earlier time periods.
-To ensure that the effect of such missed museums is does not distort insights, the time range in question is limited to events between 2000-2021.
 A small number of museums are excluded, in particular three museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), as well as two which closed before 2000 as they fall outside the period under investigation.
@@
 6096 museum-years are observed; table \ref{tbl:t_sumstats} shows summary statistics for all variables.
-\subsubsection*{Calendar Year hazard}
+\subsubsection*{Comparing private museum hazard rates to previous studies}
 
@@
 To ensure comparability with these, I first analyze closing rates the same, and discuss age-related closing rate below.
-Summary yearly closing results in an average closing rate of 0.84\%; i.e.
+Summarizing yearly closing proportions results in an average closing rate of 0.84\%; i.e.
 on average each year 0.84\% of the private museum population closes (weighing the yearly mortality rate by number of museums at risk results in an estimate of 1.12\%).
@@
 \textcite{Gordon_etal_2013_insolvency} observes 35 closures over the years of 2000-2003 with 5,167 museum-years (p.368), resulting in an average annual closing rate of 0.68\% (p.377).
-Some of this difference may be explained by higher shares of smaller organizations in \textcite{Bowen_etal_1994_charitable}, where museums of any size are included, whereas \textcite{Gordon_etal_2013_insolvency} excluded NPOs with operational revenues below 150,000 USD by, as smaller non-profits are at higher risk of closing \parencite{Harrison_Laincz_2008_nonprofit,Helmig_Ingerfurth_Pinz_2013_nonprofit}.
+Some of this difference may be explained by higher shares of smaller organizations in \textcite{Bowen_etal_1994_charitable}, where museums of any size are included, whereas \textcite{Gordon_etal_2013_insolvency} excluded NPOs with operational revenues below 150,000 USD, as smaller non-profits are at higher risk of closing \parencite{Harrison_Laincz_2008_nonprofit,Helmig_Ingerfurth_Pinz_2013_nonprofit}.
 
 Focusing directly on Art museums, rather than museum generally as part of the wider focus on Art NPOs, \textcite{Hager_2001_vulnerability} observes 42 closures over a period of 4 years (1994-1997) from a starting populaton of 448 (p.383).
-As his way of delineating the population (having "filed an annual Form 990 tax return with the IRS for the 1990, 1991, or 1992 tax year", p.380) does not rule out that some closings took place in 1991, 1992 or 1993\footnote{In particular it is unclear why 1993 is not treated as belonging to the observation period}, attributing some closings to these years is likely appropriate, and presumably roughly equivalent to assuming an observation period of five (rather than four) years, which corresponds to an average yearly closing rate of \(1-(406/448)^{1/5}\) = 1.9\%.\footnote{So far it is hard to tell why art museums appear to have higher closing rates than museums generally.
+As his way of delineating the population (having "filed an annual Form 990 tax return with the IRS for the 1990, 1991, or 1992 tax year", p.380) does not rule out that some closings took place in 1991, 1992 or 1993\footnote{In particular it is unclear why 1993 is not treated as belonging to the observation period}, attributing some closings to these years is likely appropriate, and presumably roughly equivalent to assuming an observation period of five (rather than four) years, which corresponds to an average yearly closing rate of 1.9\%.\footnote{So far it is hard to tell why art museums appear to have higher closing rates than museums generally.
 According to the \textcite{IMLS_2008_funding}, art museums have above-average reliance on earned income (46.1\% compared to 43.7\% on average, p.26), and \textcite{Bowen_etal_1994_charitable} argue that a higher reliance on income is associated with higher exit rates (p.102), but it is questionable whether such an a small difference in percent earned can explain a 1.7-2.7 times higher closing risk.
@@
 Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
-The hazard rate increases strongly from 0.10\% in the first two years, to 0.69\% in the first 5 years, to 1.20\% at year 8, around which it then fluctuates, leading to an average hazard of 1.16\% for the first 30 years.
-\footnote{While it is possible to calculate the average hazard over longer periods (e.g.
-the overall average hazard rate is 0.90\%), for ages above 30 only few observations are available, which make these predictions rather uncertain.}
+The hazard rate increases strongly from 0.10\% in the first two years, to 0.69\% in the first 5 years, to 1.20\% at year 8, around which it then fluctuates, leading to an average hazard of 1.16\% for the first 30 years\footnote{While it is possible to calculate the average hazard over longer periods (e.g.
+the overall average hazard rate is 0.90\%), for ages above 30 only few observations are available, which make these predictions rather uncertain.}.
 The increase in the first years is likely explained by the fact that as the establishment of a museum requires considerable resources, their founders have allocated enough resources to keep the risk of closure minimal in the first years after opening.
@@
 
-The reputation of the founder is not statistically related to closure. 
+Other founder-level characteristics also do not indicate that founder-related variables are strongly associated to museum closure, as the coefficients of ARTnews ranking inclusion (measuring reputation) and inclusion of founder's name in the museum name are not statistically significant.
 Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (21\% elevated closing risk) and by founders who were included at some point but are no longer included (58\% elevated closing risk), however none of the differences are statistically significant.
@@
 However, as all differences are not statistically significant, there is no strong evidence that this reflects unexpected status mechanisms rather than randomness.
-it nevertheless provides some evidence that status matters; as in particular the loss of status appears to be substantially associated with museum closure.
-
-Museums whose name contain the name of the founder face a non-significantly 4.9\% elevated risk of closure, which indicates that there is little evidence that founders face greater difficulties to secure a long-term future for their museums by choosing to emphasize their personal contribution.
-It might have been expected that such central positioning of the founder might limit longevity by disincentivizing contributions by other parties.
-However, as the direct mechanism of declining contributions cannot be observed, its absence cannot be assumed either.
-It might be the case that other parties do indeed feel less inclined to contribute but that these gaps are filled by a stronger commitment of the founder, who having committed her name to the enterprise, wants to keep her museum open event at great costs.
-\subparagraph*{founder conclusion}
 
@@
 \caption{\label{fig:p_condmef}Conditional effects of Regional PM Density and Population}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=18cm]{../figures/p_pred_popprxcnt.pdf}
-\caption{\label{fig:p_pred_popprxcnt}Predicted Avg. Hazard Rate on Regional PM Density and Population}
 \end{figure}
@@
 Alternatively, areas with high population and low private museum numbers might more generally lack cultural infrastructure; which one could see supported by closures in Jakarta, Istanbul and Mexico City, but less so by closings in Paris, Tokyo or Madrid.
-Low private museums indicating lack of cultural infrastructure might also explain the decrease in mortality associated with increases in private museum numbers at high population values (figure \ref{fig:p_pred_heatmap}, upper half), as such pattern does not correspond to that predicted by competition.
+However, low private museums indicating lack of cultural infrastructure might also explain the decrease in mortality associated with increases in private museum numbers at high population values (figure \ref{fig:p_pred_heatmap}, upper half), as such pattern does not correspond to that predicted by competition.
 More in line with expectation is however the association between increases of population numbers and lower mortality at higher numbers of private museums (right half), as it indicates that audiences can facilitate museum survival.
@@
 
-While not all associations correspond to predictions made by resource dependence, the most direct measurement of increased competition, number of private museums in the local surrounding, is associated with higher closing chances for a large part of the sample, which in turn supports the substantial role of competition.
+While not all associations correspond to predictions made by resource dependence, the most direct measurement of increased competition, number of private museums in the local surrounding, is associated with higher closing chances for a large part of the sample, which in turn supports the substantial role of competition (H3).
 \paragraph*{Identity Variables}

### 2024-09-09 scripts/closing_main.R
update descriptive nbrs, combine in one paragraph

@@ -54,7 +54,14 @@ gd_nbrs <- function() {
         list(nbr_name = "pm_n_closed",   nbr_fmt = dt_pmyear[, sum(closing)]),
         list(nbr_name = "n_pmyears",     nbr_fmt = dt_pmyear[, .N]),
         list(nbr_name = "pmdb_n_nlpm",   nbr_fmt = dt_pmdb[museum_status == "no longer a private museum", .N]),
+        list(nbr_name = "pmdb_n_closed", nbr_fmt = dt_pmdb[museum_status == "closed", .N]),
         list(nbr_name = "pmdb_n",        nbr_fmt = dt_pmdb[museum_status %in% c("private museum", "closed"), .N]),
+        list(nbr_name = "pmdb_n_closed_NAclosingyear",
+             nbr_fmt = dt_pmdb[museum_status == "closed" & is.na(year_closed), .N]),
+        list(nbr_name = "pmdb_n_closed_before2k",
+             nbr_fmt = dt_pmdb[museum_status == "closed" & year_closed < 2000, .N]),
+        list(nbr_name = "pmdb_n_open_NAopeningyear",
+             nbr_fmt = dt_pmdb[museum_status %in% c("private museum", "closed") & is.na(year_opened), .N]),
         list(nbr_name = "pmx_n",         nbr_fmt = dt_pmx[, .N]),
         list(nbr_name = "n_founder_dead",nbr_fmt = dt_pmyear[founder_dead5 == "recently_dead", fnunique(ID)]),
         list(nbr_name = "pm_n_used",     nbr_fmt = dt_pmyear[, fnunique(ID)]),
@@ -344,6 +351,7 @@ l_mdlnames_comp <- c("r_pop4", "r_comp1", "r_audience1", "r_audience2", "r_audie
 ## combination of density/competition specifications
 l_mdlnames_env <- c("r_pop4", "r_pmdens1", "r_pmdens2", "r_audience1", "r_audience_log1")
 
+## improvement by adding variables
 dt_drop1 <- gd_drop1(l_mdls)
 
 ## ** number/figure/table export

### 2024-09-09 texts/paper_closing.tex
minor result rewriting

@@
-% Created 2024-09-06 vr 17:50
+% Created 2024-09-09 ma 10:48
 % Intended LaTeX compiler: pdflatex
@@
 
-\textbf{Hypothesis 2}: Reliance on the founder is the mechanism through which PMs are exposed to a higher closing risk, thus founder-related variables predict closing, in particular
+\textbf{Hypothesis 2}: Reliance on the founder is the mechanism through which PMs are exposed to a higher closing risk, thus founder-related variables predict closing, in particular: 
 \begin{itemize}
@@
 
-A newly constructed database, assembled from different sources, is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
-Currently, the database includes 548 museums (of which 451 are currently open, the remainder having closed or transformed into other organizational forms).
+A newly constructed database, assembled from a wide range of sources, is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
+Currently, the database includes 548 museums, of which 451 are currently open, 72 have closed and 25 have transformed into other organizational forms.\footnote{The 25 institutions which were private museums at some point and have since been transformed into other organizational forms are not included in this analysis and discussed in the limitations.}
 Using this database, in particular year of opening and, if available, closing, it is possible to reconstruct the life course of the each institution with museum-year as the unit of analysis.
-While around 20\% of private museums have opened before 2000, the retrospective data collection does not rule out the possibility that some institutions were missed, with such risks likely being higher for earlier time periods.
-To ensure that the effect of such missed museums is does not distort insights, the time range in question is limited to events between 2000-2021.
+While the database is not limited to private museums of a particular time period, due to the recency of the private museum boom in the last two decades 80\% of the museums included in it have opened after 2000.
+As the databse was constructed retrospectively from 2020 to 2022, I focus here on closing events from 2000 to 2021 to limit the possibility that some institutions were missed, as such risks are likely higher for earlier time periods.
+Furthermore, a small number of museums are excluded, in particular 2 museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), 1 museum the opening year of which could not be determined, as well as 2 which closed before 2000 thereby fall outside the period under investigation.
+This leaves 503 private museums at risk which have accumulated 6096 museum-years and 68 closures.
 This data allows to conduct survival analysis (also known as event history analysis), the most common statistical technique to investigate hazard rates and identify mortality-assocated covariates \parencite{Moore_2015_survival,Allison_2014_event}.
@@
 
-In total, 523 private museums are included in the dataset which are either open or have closed\footnote{This does not include 25 institutions which were private museums at some point and have since been transformed into other organizational forms; these cases are discussed in the limitations.}.
-A small number of museums are excluded, in particular three museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), as well as two which closed before 2000 as they fall outside the period under investigation.
-This leaves 503 private museums at risk, of which 68 have closed.
-6096 museum-years are observed; table \ref{tbl:t_sumstats} shows summary statistics for all variables.
+Table \ref{tbl:t_sumstats} shows summary statistics for all variables.
 \subsubsection*{Comparing private museum hazard rates to previous studies}
@@
 
-Neither gender nor external shocks (the Great Recession and the Covid-19 Pandemic) are associated with higher closing rates.
-
-inclusion of founder name is significantly associated with mortality rates.
-While generally organizations whose name include the name of their founder might be more centered around the founder, and hence display higher inertia, making them less able to adapt to changing environments, these results indicate that it does not seem to be case for private museums.
-\paragraph*{Founder dependence}
+Neither gender of the founder nor external shocks (the Great Recession and the Covid-19 Pandemic) are associated with significantly higher closing rates.
+\paragraph*{Founder dependence (H2)}
 
@@
 
-The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e. museums are not significantly more likely to close after their founder has died.
+The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e.
+museums are not significantly more likely to close after their founder has died, which provides little support to H2a.
 While the point estimate is positive (0.280, corresponding to a  32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that despite the cumulative character even decade-long survival times do not differ substantially (figure \ref{fig:p_surv_death}).
@@
 Other founder-level characteristics also do not indicate that founder-related variables are strongly associated to museum closure, as the coefficients of ARTnews ranking inclusion (measuring reputation) and inclusion of founder's name in the museum name are not statistically significant.
-Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (21\% elevated closing risk) and by founders who were included at some point but are no longer included (58\% elevated closing risk), however none of the differences are statistically significant.
+Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (21\% elevated closing risk) and by founders who were included at some point but are no longer included (58\% elevated closing risk).
+However as none of the differences are statistically significant, they provide little support for hypothesis 2b.
 It is also worth to point out that the order of the categories does not fully correspond to the expected order, according to which museums whose collectors are not included would be more likely to close than collectors who are.
@@
 
-Taken together, the inability to explain private museum closing with the death of founder, her exclusion from a prestitious ranking and the presence of her name in the museum's name question the hypothesized central role of the founder.
-In other words, so far little evidence points to founders constituting a substantial source of involuntary closing risk.
-\paragraph*{Competition}
+Museums whose name contain the name of the founder face a non-significantly 4.9\% elevated risk of closure, which indicates that there is little evidence that founders face greater difficulties to secure a long-term future for their museums by choosing to emphasize their personal contribution; thus providing no support for hypothesis 2c.
+A possible explanation might be that even when other parties do indeed feel less inclined to contribute, these gaps are filled by a stronger commitment of the founder, who having committed her name to the initiative, wants to keep the museum open event at great costs.
+
+Taken together, the inability to explain private museum closing with the death of founder, her exclusion from a prestitious ranking and the presence of her name in the museum's name question the hypothesized central role of the founder (Hypothesis 2).
+In other words, so far little evidence points to low diversification, i.e. reliance on founders, as a substantial source of involuntary closing risk for private museums.
+\paragraph*{Competition (H3)}
 
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
+\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population (at available values)}
+\end{figure}
+
 At the local level, the number of private museum and population numbers predict survival chances as the main effects of population and number of private museums as well as its interaction are significant.
-The particular pattern is complex:
+The particular pattern however is complex:
 As both main terms are positive and the interaction negative, at low values increases in either variable are associated with increases in mortality (figure \ref{fig:p_condmef}).
-Thus, for population values of 0 to 2.97 million people, an increase in the number of private museums corresponds to an increase in mortality (bottom half of figure \ref{fig:p_pred_heatmap}), which provides support for the view that competition leads to museum closure, in particular as this range includes 5056 museums years, or 83\% of the dataset.
+Thus, for population values of 0 to 2.97 million people, an increase in the number of private museums corresponds to an increase in mortality (bottom half of figure \ref{fig:p_pred_heatmap}), which provides support for hypothesis 3 according to which competition leads to museum closure, in particular as this range includes 5056 museums years, or 83\% of the dataset.
 Yet at the same time, at low private museums numbers (0 to 3 private museums), increases in population also increase mortality; this range also includes a large number of museum-years (4960 museum years; 81\% of the data).
 Such a relationship is unexpected insofar as it is unclear why a larger potential audience would be associated with a higher risk of closure.\footnote{Alternative approaches of modeling competition are discussed in the supplementary materials, but cannot answer this question.}
-A possible explanation might be that collectors in less densely populated areas are more committed than those in less populated areas precisely because they know they cannot count visitors to contribute substantially.
+A possible explanation might be that collectors in less densely populated areas are more committed than those in less populated areas precisely because they know they cannot count on visitors to contribute substantially.
 Alternatively, areas with high population and low private museum numbers might more generally lack cultural infrastructure; which one could see supported by closures in Jakarta, Istanbul and Mexico City, but less so by closings in Paris, Tokyo or Madrid.
@@
 While not all associations correspond to predictions made by resource dependence, the most direct measurement of increased competition, number of private museums in the local surrounding, is associated with higher closing chances for a large part of the sample, which in turn supports the substantial role of competition (H3).
-\paragraph*{Identity Variables}
+\paragraph*{Identity (H4)}
 
@@
 Investigating the survival prospects of private museum furthermore illucidates the long-term development of the organizational form as a whole, as it provides insights into factors related to variation of sustainability and thereby into trends in composition.
-
-Given the non-significant gender difference, it can be expected that (unless given a strong increase in founding by women) the population of private museums will continue to remain a man-dominated affair.
-This finding also provides no evidence that female founders face gender-specific challenges that decrease the survival prospects of their private museums.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
-\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population (at available values)}
-\end{figure}
 

### 2024-09-09 texts/sup_materials.tex
add extra models with AF variables to sup_materials

@@
-% Created 2024-09-06 vr 15:46
+% Created 2024-09-09 ma 11:38
 % Intended LaTeX compiler: pdflatex
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=18cm]{../figures/p_pred_heatmap_alt.pdf}
+\caption{\label{fig:p_pred_heatmap_alt}Prediction Heatmap of Alternative model specifications}
+\end{figure}
+
+Alternative Specifications of competition exist.
+First, it is possible to argue that the primary mechanism through which private museums compete with each other is by limiting each other's audience.
+This specification leads to the construction of the Audience variable, which describes the number of people in the 10 km surrounding by the number of private museums present.
+Under this assumption, the situation of a private museum which is alone in an environment of 1 million people is equivalent to one in an environment of 3 million people with 2 other private museums, as each museums is "assigned" a pool of 1 million people.
+Secondly, one might argue that the competition between private museums is scaled by the amount of people, which corresponds to specifying competition as the number of other private museums per (million) population.
+In this case, the absence of other private museums assumes absence of competition, regardless of the audience size.
+
+\begin{landscape}
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:29:56 2024
+% Fri Sep  6 15:49:47 2024
 \begin{table}[ht]
@@
 \end{table}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=18cm]{../figures/p_pred_heatmap_alt.pdf}
-\caption{\label{fig:p_pred_heatmap_alt}Prediction Heatmap of Alternative model specifications}
-\end{figure}
-
-Alternative Specifications of competition exist.
-First, it is possible to argue that the primary mechanism through which private museums compete with each other is by limiting each other's audience.
-This specification leads to the construction of the Audience variable, which describes the number of people in the 10 km surrounding by the number of private museums present.
-Under this assumption, the situation of a private museum which is alone in an environment of 1 million people is equivalent to one in an environment of 3 million people with 2 other private museums, as each museums is "assigned" a pool of 1 million people.
-Secondly, one might argue that the competition between private museums is scaled by the amount of people, which corresponds to specifying competition as the number of other private museums per (million) population.
-In this case, the absence of other private museums assumes absence of competition, regardless of the audience size.
+\end{landscape}
 
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:29:49 2024
+% Fri Sep  6 15:49:39 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:29:50 2024
+% Fri Sep  6 15:49:41 2024
 \begin{table}[ht]
@@
 
-Table \ref{tbl:t_reg_coxph_timecfg} investigates whether relationships have substantially changed over time.
+Table \ref{tbl:t_reg_coxph_timeslice} investigates whether relationships have substantially changed over time.
 However, subsetting the dataset to different year ranges shows general consistency of the main findings, in particular insignificant coefficients for the founder's death, gender, Artnews ranking variables, inclusion of founder name in museum name, positive and significant coefficients for self-identification as other, population and private museum numbers, and a significant negative interaction between private museum numbers and population.
+\subsection*{Inclusion of Exhibition data}
+
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Mon Sep  9 11:20:03 2024
+\begin{table}[ht]
+\centering
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
+  \hline 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_exhbany} & \multicolumn{1}{l}{r\_exhbroll}\\ 
+ \hline
+  \multicolumn{5}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & -.04 \; (0.34) & -.01 \; (0.34) & -.06 \; (0.34) \\ 
+   & Gender - Couple & -.14 \; (0.32) & -.12 \; (0.32) & -.15 \; (0.32) \\ 
+   & Founder died & .28 \; (0.43) & .31 \; (0.43) & .26 \; (0.43) \\ 
+   \multicolumn{5}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .20 \; (0.41) & .24 \; (0.42) & .17 \; (0.41) \\ 
+   & Self-Identification - Collection & -.45 \; (0.54) & -.47 \; (0.55) & -.42 \; (0.54) \\ 
+   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.13 \; (0.31)^{***} & 1.07 \; (0.30)^{***} \\ 
+   & AN Ranking - Included & .19 \; (0.34) & .26 \; (0.36) & .13 \; (0.35) \\ 
+   & AN Ranking - Dropped & .46 \; (0.50) & .50 \; (0.50) & .42 \; (0.50) \\ 
+   & Founder name in Museum name & .05 \; (0.28) & .07 \; (0.28) & .03 \; (0.28) \\ 
+   & Exhibition any &  & -.22 \; (0.27) &  \\ 
+   & Exhibition any last 5 years &  &  & .20 \; (0.26) \\ 
+   \multicolumn{5}{l}{\textbf{Environment}} \\ 
+ & PM density (country) & .65 \; (0.34) & .66 \; (0.35) & .65 \; (0.35) \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) & -.03 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} & .26 \; (0.08)^{***} & .27 \; (0.08)^{***} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} \\ 
+   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.60 \; (1.01) & -1.57 \; (1.01) \\ 
+   & Covid Pandemic (2020/21) & .42 \; (0.29) & .42 \; (0.29) & .41 \; (0.29) \\ 
+   \hline
+ & Museums & 503 & 503 & 503 \\ 
+   & Museum-years & 6096 & 6096 & 6096 \\ 
+   & Closures & 68 & 68 & 68 \\ 
+   & log. Likelihood & -339.68 & -339.34 & -339.38 \\ 
+   & AIC & 711.35 & 712.67 & 712.76 \\ 
+   & BIC & 746.87 & 750.41 & 750.50 \\ 
+   \hline 
+ \multicolumn{5}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+\end{tabular}
+\caption{Alternative specification: include Exhibition} 
+\label{tbl:t_reg_coxph_af}
+\end{table}
+
+It is also possible to include an indicator whether museums have had exhibitions of contemporary art.
+For this the database of Artfacts is used.
+It is not included in the main model as it might reflect resources (with larger museums being more likely to organize exhibitions), which would then influence the coefficients of other variables. 
+Controlling for the mechanism (or a proxy of it) would then lead to coefficients corresponding to comparisons where resources are equal.
+To investigate the role of exhibitions anyways, table \ref{tbl:t_reg_coxph_af} includes next to the main model two models with different exhibition specifications.
+"Exhibition any" is a time-invariant indicator measuring whether Artfacts has ever recorded this museum as organizating an exhibition, "Exhibition any last 5 years" is a time-varying variable indicating whether an exhibition has been taken place in the previous 5 years.
+Both coefficients are not significant, and do not substantially change the coefficients of other variables. 
 \end{document}

### 2024-09-09 scripts/cfg.R

@@ -59,6 +59,10 @@ gc_tbls <- function(c_tblargs) {
             l_mdls = quote(l_mdls),
             l_mdlnames = quote(l_mdlnames_env),
             caption = "Alternative specification of environment"),
+        t_reg_coxph_af = list(
+            l_mdls = quote(l_mdls),
+            l_mdlnames = quote(l_mdlnames_af),
+            caption = "Alternative specification: include Exhibition"),
         t_reg_coxph_timecfg = list(
             l_mdls = quote(l_mdls),
             l_mdlnames = quote(l_mdlnames_timecfg),

### 2024-09-09 scripts/closing_main.R

@@ -329,13 +329,6 @@ l_mdlnames_coxph <- list("r_pop4")
 
 l_mdlnames_dens <- list("r_pop4", "r_comp1", "r_pmdens1", "r_pmdens2", "r_pmdens3", "r_pmdens_aud1", "r_pmdens_aud2")
 
-## "r_smol")#, "r_pop5", "r_pop42")#  , ",r_pop4_wyr", "r_pop4_wcrises")
-## l_mdlnames_coxph <- c("r_pop4", paste0("r_wsize", 3:1))
-## c("r_more", paste0("r_pop", c(1, 3:6)))
-## "r_woaf", "r_waf_year", "r_waf_roll", "r_waf_roll2")
-## "r_waf_cy", "r_waf_proplog", "r_waf_prop", "r_waf_year_sqrd") 
-
-
 ## compare whether proxcnt/popm_circle10 patterns are stable across data ranges
 l_mdlnames_coxph_density <- list("r_pop4", "r_onlycryside", "r_wocryside", "r_pop42") 
 
@@ -350,6 +343,9 @@ l_mdlnames_comp <- c("r_pop4", "r_comp1", "r_audience1", "r_audience2", "r_audie
 
 ## combination of density/competition specifications
 l_mdlnames_env <- c("r_pop4", "r_pmdens1", "r_pmdens2", "r_audience1", "r_audience_log1")
+
+## including exhibition data (Artfacts)
+l_mdlnames_af <- c("r_pop4", "r_exhbany", "r_exhbroll")
 
 ## improvement by adding variables
 dt_drop1 <- gd_drop1(l_mdls)

### 2024-09-09 scripts/regression.R

@@ -1503,7 +1503,11 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
 
         r_pmdens_aud2 = coxph(gf_coxph_close(
             vrbls_to_add = "pmdens_circle10",
-            vrbls_to_yeet = c("popm_circle10", "proxcnt10:popm_circle10")), dt_pmyear)
+            vrbls_to_yeet = c("popm_circle10", "proxcnt10:popm_circle10")), dt_pmyear),
+
+        r_exhbany = coxph(gf_coxph_close(vrbls_to_add = "exhbany"), dt_pmyear),
+
+        r_exhbroll = coxph(gf_coxph_close(vrbls_to_add = "exhbrollany"), dt_pmyear)
         
 
         ## fullest model:
@@ -2385,6 +2389,7 @@ gt_reg_coxph_timecfg <- gt_reg_coxph
 gt_reg_coxph_comp <- gt_reg_coxph
 gt_reg_coxph_dens <- gt_reg_coxph
 gt_reg_coxph_env <- gt_reg_coxph
+gt_reg_coxph_af <- gt_reg_coxph
 
 gt_coxzph <- function(rx) {
     gw_fargs(match.call())

### 2024-09-09 texts/sup_materials.tex
move exhibitions to sup materials, expand there

@@
-% Created 2024-09-09 ma 11:38
+% Created 2024-09-09 ma 12:03
 % Intended LaTeX compiler: pdflatex
@@
 Controlling for the mechanism (or a proxy of it) would then lead to coefficients corresponding to comparisons where resources are equal.
+Alternatively, exhibitions could enhance the reputation of museums, as it might lead to higher recognition among third parties such as sponsors and governments of the public good the museum provides.
+Temporary exhibitions might also be a way to attract larger audiences, but as museum operations are unprofitable, the ticket revenues likely do not lead to a better financial situation.
 To investigate the role of exhibitions anyways, table \ref{tbl:t_reg_coxph_af} includes next to the main model two models with different exhibition specifications.

### 2024-09-10 scripts/closing_main.R
add egmus-based numbers

@@ -81,9 +81,33 @@ gd_nbrs <- function() {
         melt(id.vars = "slfidfcn") %>%
         .[, .(nbr_name = sprintf("%s_slfid_%s", variable, slfidfcn),
               nbr_fmt = format(value, digits = 2, nsmall = 0, trim = T))]
-
-
+    
     dt_descs <- rbind(dt_descs_prep1, dt_descs_prep2) %>% .[, grp := "descs"]
+
+    ## get EGMUS numbers
+    dt_egmus_subset <- gd_egmus() %>% 
+        .[, .SD[which.max(year)], country] %>%
+        .[year > 2014] %>%
+        .[, .SD, .SDcols = patterns("country|^year$|^own_|^inc_")]
+
+
+    ## ownership counts/percentages by form
+    dt_egmus_own <- melt(dt_egmus_subset, id.vars = "country", measure.vars = patterns("own_"),
+                         variable.name = "ownership") %>%
+        .[ownership != "own_ppp", .(own_cnt = sum(value, na.rm = T)), ownership] %>%
+        .[, own_perc := own_cnt*100/sum(own_cnt)] %>%
+        rbind(data.table(ownership = "own_ttl", own_cnt = sum(.[, own_cnt]), own_perc = 100)) %>%
+        melt(measure.vars = c("own_cnt", "own_perc")) %>%
+        .[, .(nbr_fmt = format(value, digits = 2)),
+          .(nbr_name = sprintf("%s_%s", ownership, gsub("own_", "", variable)))]
+    
+    ## income percentages by category
+    dt_egmus_inc <- dt_egmus_subset[, .(perc_entryfees = (inc_entryfees/inc_ttl)*100,
+                                        perc_subsidies = (inc_subsidies/inc_ttl)*100)] %>%
+        .[, map(.SD, ~mean(.x, na.rm = T))] %>% melt(measure.vars =  names(.)) %>%
+        .[, .(nbr_name = variable, nbr_fmt = format(value, digits = 2))]
+
+    dt_egmus_cbn <- rbind(dt_egmus_own, dt_egmus_inc)[, grp := "egmus"]
     
 
     ## calculate average hazard rate numbers, depending on maximum age
@@ -212,7 +236,7 @@ gd_nbrs <- function() {
     ## dt_ynktbl <- gc_ynktbl()
     dt_reftbl <- gc_reftbl()
 
[…]

### 2024-09-10 scripts/closing_playground.R

@@ -550,4 +550,17 @@ dt_pmdb[dt_pmyear[popm_circle10 > 3 & proxcnt10 < 4, .(year = max(year), closing
     .[, .(name, iso3c, closing, city, year, ID)] %>% print(n=30) %>%
     .[closing == 1]
 
-## Jakarta, Istanbul, Paris.. 
+## Jakarta, Istanbul, Paris..
+
+## * egmus
+dt_egmus <- gd_egmus()
+
+
+dt_egmus %>% names
+
+## look at 
+
+
+
+    
+    

### 2024-09-10 texts/paper_closing.tex
move conclusion paragraphs around, tryiing to find good angle

@@
-% Created 2024-09-09 ma 10:48
+% Created 2024-09-10 di 19:08
 % Intended LaTeX compiler: pdflatex
@@
 Outside of the United States, the reliance on revenue streams beyond operations is even larger:
-German museums in the 1990s covered on average only 27\% of their expenses covered by operations \parencite[p.233]{Martin_1993_museen}, and even the more market-oriented NPOs in the cultural sector draws around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
+German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table p.233}, with private museums requiring less support as operations provide around 47\% of their budget (ibid.), and even the more market-oriented NPOs in the cultural sector draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
+On a European level, only 12\% of museum incomes are generated by entry fees, whereas 69\% originate from subsidies \parencite{EGMUS_2024_complete.}\footnote{Own calculations from on EGMUS data, based on all countries with income data from 2015 onwards.}
 
@@
 
-On a national level, density of private museum is calculated as the number of private museums per million.
-On a local level, I use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
+On a national level, density of private museum is calculated as the number of private museums per million population.
+To measure competition on a local level, I first determine the coordinates of museum using the Google Maps API; the coordindates of museums which are not found that way (particularly those located in countries with limited Google presence such as South Korea, China and Russia) are searched manually (often using other map services such as Kakao Maps, Baidu Maps and Yandex Maps).
+For closed museums, which often are not included in the current map databases, coordinates are also determined via addresses mentioned on snapshots in the Wayback Machine.
+I then use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
 To be able to estimate both competition and demand/audience/population separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two.
@@
 
-Investigating the survival prospects of private museum furthermore illucidates the long-term development of the organizational form as a whole, as it provides insights into factors related to variation of sustainability and thereby into trends in composition.
+Previously the dozens of closures have been seen as indicator of their vulnerability and short-livedness \parencite{Adam_2020_close}, however this analysis shows the importance studying closing not in isolaton but in comparison to both non-closures and closures of comparable institutions.
+While the booming numbers of private museums themselves have received substantial attention, less consideration has been given to the fact that large populations can generate dozens of closures without requiring high closing rates, especially when cloures are considered over a span of several years or decades.
+In other words, the sheer size to which the private museum population has grown over the last decades has made it all but inevitable that some of them would close, and do so after only a few year.
+Based on the current analysis, private museums will continue to close in the years to come; at hazard rates of around 1\% on average a handful of closures every year are to be expected.
 
-The lack of a relation between temporary exhibitions and survival prospect is somewhat unexpected.
-It was expected that as temporary exhibitions constitute one of the main tasks of a museums operations, organizing them would benefit a museum financially (via visitor fees) and symbolically (via prestige of other art field actors, which might be developed into further contacts), leading to higher survival chances\footnote{Furthermore, the ability to organization exhibitions likely reflects museum resources, which should also enhance survival.}
-However, organizing exhibitions does not seem to bestow benefits for the museums which organize them, nor do organizations seem to be organized only by established/sustainable/secure organizations.
-One possibility for this discrepancy could be that exhibitions are expensive, and whatever benefits gained from them are offset by the associated costs.
-One might see in this association again the importance of the founder:
-Founders who are committed to their museums will keep them alive, regardless of whether or not they plan to organize temporary exhibitions.
-\subsubsection*{founder}
+Comparing private museums closures to closures of other organizational form advances our understanding of the sustainability of this new organizational form.
+While private museums do close, the comparison to previous studies of museum closing rates provides no evidence that dependence on single founders constitutes a less stable organizational form than reliance on less centralized foundations, associations or corporate sponsorship.
+Multiple reasons might be the at play that mitigate this risk of low diversification.
+First, it might take more commitment to open a museum as an individual or couple compared to less involved art patronage of being a board member in existing institutions or donating works, which would result in private museums founders being more motivated to secure the existence of their institutions.
+Furthermore, the centrality of the founder might leave little room to question who is responsible to provide additional funds in times of financial difficulties, whereas in organizations without a central figure each member may feel less responsible.
+It might also be such commitment that leads founder to plan the future of their museum to such an extent that their death is not significantly associated with unvoluntary closing.
 
-It has been widely argued that the death of the founder would lead to his or her private museum to close, while this analysis has not found conclusive evidence for this relationship.
-It is important to keep in mind that the lack of observing a clear relationship between the death of the founder and museum closure does not imply that no relationship exists.
-It is possible that previous scholars who argued for such an association have correctly identified the dependency relationships in private museums, which will become visible once more founder deaths have occurred.
-At the same time, it is possible that private museums are indeed generally less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
+However, it is necessary to consider that so far only a small fraction (47 museums, 9.3\%) of museums has experienced the death of their founder, one of the primary reasons hypothesized to lead to the private museum closure.
+While so far these museums have not seen substantially elevated closing risks, these estimates will become more precise as more founders pass away.
+As the currently large confidence interval (figure \ref{fig:p_surv_death}) for museums whose founders have died allows a wide range of survival chances, it is entirely possible that previous scholars have indeed correctly identified a key dependency (the current absence of evidence of it should not be taken as evidence of absence) and that therefore later analyses will a significantly association between founder death and closing risk as well as a higher average closing risk for private museums.
+At the same time, it is also possible that private museums are generally less dependent on a single person (or couple) than has been assumed, and have in fact become institutionalized to an extent that most heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
+
+While so far little evidence points toward low diversification, i.e.
+reliance on the founder, as a key vulnerability of private museums to unvoluntary closures, the centrality of the founder may be more pronounced in voluntary closures.
+Indicated by unconventional naming choice, a subset of founders might from the very beginning envision the museum as temporary.
+On the other hand, higher closing rates for unconventionally named museums might reflect absence of recognition and support by third parties in the environment.
+While the question of which mechanism explains the association between name and survival, the role of the environment can be clearly seen in terms of nearby institution counts and population measures, with both factors leading to higher closing rates.
+
+While overall private museum closing rates are generally not diverging from museums in general, and may even lie below the average, it has to be kept in mind that this comparison is based on American non-profit museums.
+To the best of my knowledge, currently no data sources exist that allow estimation of closing rates of (European) public, state-funded museums.
+While public museums have been characterized to some extent as very stable due to government picking up deficits \parencite{Meier_Frey_2003_faces,Bechtler_Imhof_2018_future}, \textcite{Walker_2019_collector} argues that due to declining cultural spending even public museums might face hard times.
+Most national public flagship institutions will presumably remain sufficiently funded to survive, however this might not be the case for the much larger of smaller museums in less touristic regions who rely on more limited municipal funding (49\% of the European museum population, \cite{EGMUS_2024_complete}), as \textcite{StylianouLambert_etal_2014_museums} explore for a number of smaller publicly funded ethnography museums in Cyprus.
+Yet without access to museum registers comparable to the IRS/NCCS datasets, questions regarding the relation between type of ownership and survival remain speculative.
+
 \subsection*{Conclusion}
@@
 Furthermore, even if they reflect founder motivations, these are likely cases of voluntary closure; there is thus no large evidence that private museums are at a higher risk of unvoluntary closure than more diversified museums as a consequence of their reliance on a single founder.
-
-A possible explanation of the characterization of private museums as fragile might be due to the focus on case studies, which disregards the much larger population who don't experience closing.
-Due to the "private museum boom", some museums will experience closing over a period of around two decades even if the underlying closing probability is low.
-
-It cannot be stated whether private museums experience higher mortality rates than publicly funded museums (for which European countries would be the most natural comparison).
-While public museums have been characterized to some extent as very stable due to government picking up deficits \parencite{Meier_Frey_2003_faces,Bechtler_Imhof_2018_future}, \textcite{Walker_2019_collector} argues that due to declining cultural spending even public museums might face hard times.
-While national public flagship institutions will likely remain sufficiently funded to survive, this might not be the case for the vast majority of smaller museums in less touristic regions who rely on limited municipal funding, as \textcite{StylianouLambert_etal_2014_museums} demonstrate for a number of smaller publicly funded ethnography museums in Cyprus.
-Without access to museum register comparable to the IRS/NCCS datasets, such questions regarding the relation between type of ownership and survival remain speculative.
-
-\begin{sloppypar}
-\printbibliography
-\end{sloppypar}
 \subsubsection*{Limitations}
@@
 egmus doesn't have that
+
+\begin{sloppypar}
+\printbibliography
+\end{sloppypar}
 \end{document}

### 2024-09-11 texts/paper_closing.tex
polish conclusion, minor section moves, add US nbrs

@@
-% Created 2024-09-10 di 19:08
+% Created 2024-09-11 wo 11:36
 % Intended LaTeX compiler: pdflatex
@@
 Neither gender of the founder nor external shocks (the Great Recession and the Covid-19 Pandemic) are associated with significantly higher closing rates.
+Given the non-significant gender difference, it can be expected that the population of private museums will continue to remain a man-dominated affair, unless a strong increase in museum founding by women takes place.
+At the same time, this finding also provides no evidence that female founders face gender-specific challenges, at least not to an extent that these decrease the survival prospects of their private museums.
+The insignificance of the coefficients of the external shocks indicate that museums are overall relatively resilient; possibly unlike other types of art organizations with lower assets and higher reliance on earned incomes \parencite[p.102]{Bowen_etal_1994_charitable}.
 \paragraph*{Founder dependence (H2)}
@@
 
+While so far little evidence points toward low diversification, i.e.
+reliance on the founder, as a key vulnerability of private museums to unvoluntary closures, the centrality of the founder may be more pronounced in voluntary closures.
+Indicated by unconventional naming choice, a subset of founders might from the very beginning envision the museum as temporary.
+On the other hand, higher closing rates for unconventionally named museums might reflect absence of recognition and support by third parties in the environment.
+A dimensions where the influence of the environment can however be ascertained with greater certainty is the role of audiences and other private museums.
+While the overall relationship is complex, for the majority of private museums increases in both variables are associated with higher closing rates.
+Whereas it is plausible that the association between higher institution counts and closing rates reflects competitive pressures, it is less obvious what may lay behind observing a positive association behind larger population and closing risk.
+\subsection*{Conclusion}
+
+\subsubsection*{Limitations}
+
 However, it is necessary to consider that so far only a small fraction (47 museums, 9.3\%) of museums has experienced the death of their founder, one of the primary reasons hypothesized to lead to the private museum closure.
@@
 
-While so far little evidence points toward low diversification, i.e.
-reliance on the founder, as a key vulnerability of private museums to unvoluntary closures, the centrality of the founder may be more pronounced in voluntary closures.
-Indicated by unconventional naming choice, a subset of founders might from the very beginning envision the museum as temporary.
-On the other hand, higher closing rates for unconventionally named museums might reflect absence of recognition and support by third parties in the environment.
-While the question of which mechanism explains the association between name and survival, the role of the environment can be clearly seen in terms of nearby institution counts and population measures, with both factors leading to higher closing rates.
+While overall private museum closing rates are generally not diverging from museums in general, it has to be kept in mind that this comparison is based on American non-profit museums.
+To my knowledge, currently no data sources exist that allow estimation of closing rates of (European) public, state-funded museums.
+Although I argue that the American non-profit museums serve as a better comparison to evaluate private museum surival rates than state-funded museums because the comparison allows to focus on the centrality of the founder, the contrast to public museums would still provide additional insights into the relationship between ownership and survival rates.
+While public museums have been characterized to some extent as very stable due to government picking up deficits \parencite{Meier_Frey_2003_faces,Bechtler_Imhof_2018_future}, \textcite{Walker_2019_collector} argues that due to declining cultural spending even public museums might face hard times.
+Most national public flagship institutions might remain sufficiently funded to survive, however this may not be the case for the much larger of smaller museums in less touristic regions who rely on more limited municipal funding (49\% of the European museum population, \cite{EGMUS_2024_complete}), as \textcite{StylianouLambert_etal_2014_museums} explore for a number of smaller publicly funded ethnography museums in Cyprus.
+Yet without access to museum registers comparable to the IRS/NCCS datasets, such questions of the relation between a wider range of organizational form and survival remain speculative.
 
-While overall private museum closing rates are generally not diverging from museums in general, and may even lie below the average, it has to be kept in mind that this comparison is based on American non-profit museums.
-To the best of my knowledge, currently no data sources exist that allow estimation of closing rates of (European) public, state-funded museums.
-While public museums have been characterized to some extent as very stable due to government picking up deficits \parencite{Meier_Frey_2003_faces,Bechtler_Imhof_2018_future}, \textcite{Walker_2019_collector} argues that due to declining cultural spending even public museums might face hard times.
-Most national public flagship institutions will presumably remain sufficiently funded to survive, however this might not be the case for the much larger of smaller museums in less touristic regions who rely on more limited municipal funding (49\% of the European museum population, \cite{EGMUS_2024_complete}), as \textcite{StylianouLambert_etal_2014_museums} explore for a number of smaller publicly funded ethnography museums in Cyprus.
-Yet without access to museum registers comparable to the IRS/NCCS datasets, questions regarding the relation between type of ownership and survival remain speculative.
-
-\subsection*{Conclusion}
-
-Private museum have been characterized as fragile institutions due to their reliance on a single founder.
-However, my analysis finds neither a higher substantially higher mortality rates for private museums compared to (art) museums generally, nor a conclusive relationship between museum closure and a number of founder characteristics, such as founder gender, death, exclusion from the Artnews collector ranking or inclusion of founder name in the museum name.
-While Self-identification and audience/competition are significantly associated with higher mortality, and possibly reflect or influence founder motivations, they are also subject to alternative mechanisms, namely devaluation by third parties and competition, respectively (self-identification furthermore concerns a relatively small group of institutions).
-Furthermore, even if they reflect founder motivations, these are likely cases of voluntary closure; there is thus no large evidence that private museums are at a higher risk of unvoluntary closure than more diversified museums as a consequence of their reliance on a single founder.
-\subsubsection*{Limitations}
+The primary mechanism that has been argued to lead to museum closure is financials, and while this study measures it indirectly, primarily through indicators on the level of the founder, museum and environment, the financial situation of a museum is not used directly.
+The primary reason for this is data availability.
+While centralized non-profit financial information is available for American non-profits through the IRS/NCCS files, the much larger private museum population in the rest of the world is not subject to similar reporting requirements.
+The effort to compile such information on a global scale ranges from extremely challenging (harmonizing different reporting standards, language barriers) to outright impossible for institutions who do not even (have to) report public financial information.
+Similarly, other museum characteristics, such as as museum size, facilities, as well as marketing and outreach activities might be related to long-term survival prospect\footnote{While the original data collection included the assessment of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear during data analysis that the data collected was unsuitable to construct accurate indicators from these findings due to difficulty in assessing them in many cases.
+Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Wayback machine, less central pages (such as those with information about facilities and activities), were archived much less frequently, and sometimes inaccessible despite being archived due to changes in webtechnology (such as the retirement of Adobe flash).}
+As such, private museums remain relatively intransparent, which does not prevent, but to some extent limits the identification of risk factors.
 
@@
 Sometimes this involves changes in the composition of the board of directors (or equivalent), with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum to an extent that it no longer fits the working definition.
-Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to generally determine the date of such transitions\footnote{Consequently they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing.
+Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to consistently determine the date of such transitions\footnote{Consequently they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing for at least some time.
 However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
-The main issues that made the determination of the date impossible was the intransparency of these organizations (\texttt{event in the past, no track of organizational history}), as well as the gradual process.
-As the presence of non-founder members does not categorically exclude a museum from being categorized as private museum as long as third-party influence is limited, this influence can grow until the museum bears little resemblance to its former self.
+The main issues that made the determination of the date impossible was the intransparency of these organizations, the gradual process of the transition, as well as that these events life often years or decades in the past.
 The possibility of other outcomes than surival and closures has been investigated for NPOs more generally
-\parencite{Searing_2020_zombies,HernandezOrtiz_2022_discontinuity,Helmig_Ingerfurth_Pinz_2013_nonprofit}, and for private museums specifically: 
+\parencite{Searing_2020_zombies,HernandezOrtiz_2022_discontinuity,Helmig_Ingerfurth_Pinz_2013_nonprofit}, and for private museums specifically on a case study basis: 
 \textcite{Walker_2019_collector} argues that in the case of Germany, private museum founders turn to the state to ensure the survival of their projects in the form of public-private partnerships.
 Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research.
-\paragraph*{closing reasons not as rich as previous studies}
 
-The extent to which closing factors are investigated does not reach the level of detail by \cite{Velthuis_Gera_2024_fragility}, who investigate each closing separately.
-On the other hand, the inclusion of the museums who do not close results in a more more complete comparatison. 
-A research approach that would combine the strengths of both approaches could for example consist of leveraging additional data sources, such as financial histories of founder companies to investigate financial issues or search engine results, media reports or social media posts to assess interest from the public.
-
-founder age bracket
-
-environment can be measured more
-\begin{itemize}
-\item geocoding of other institutiosn
-\item tax incentives
-\item government spending
-\item government: political changes, censorship, persecution
-\end{itemize}
--> this might futher specify the niches in which PMs can endure
-
-remain intransparent
-
-Museum characteristics might influence closing to a larger extent than has been considered here.
-For example, museum size, facilities, as well as marketing and outreach activities might be related to long-term survival prospect.
-For example, museums with more XXX might be more expensive to run, but on the other hand attract higher visitor numbers, cooperations and sponsorships. \texttt{liability of smallness}
-Furthermore, having XXX might reflect founder commitment/resources.
-While the original data collection included the measurement of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear in the process that desk research was unsuitable to construct reliabile indicators from these findings due to difficulty in assessing them in many cases.
-Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Internet archive, \texttt{subdomains} were archived much less frequently, and sometimes inaccessible despite being archived due to changes in webtechnology (such as flash).
-While it would be possible to
-absence of evidence as evidence of absence
-
-\textbf{supplementary material}
-
-covid effect may take longer to be effective
+While this study has already included measures of both the national and local environment, the ability to clearly observe spatial museum location allows to measure environmental influences in greater detail.
+For once, so far competition has been limited to other private museums, but geocoding of a wider range of institutions would lead to a more encompassing assessment of competitive and dynamics.
+Furthermore, including wider institutional changes such as tax incentives, government subsidies, but also political changes and censorship would lead to a more complete description of risk factors, and in more detail identify niches which are particularly suited for private museums.
 \subsubsection*{future research}
@@
 The US register data on NPO tax filings constitutes a promising source for data for museum research (while this data source has seen frequent usage in non-profit management, it remains underexploited in the field of museum research).
-While the United States private museum population with XX museums and YY closings might not be sufficient to test whether private museums have a a higher closing risks than other museums, it still hosts a large population of museums.
+While the United States private museum population with 70 museums and 9 closings might not be sufficient to test whether private museums have a a higher closing risks than other museums, it still hosts a large population of museums.
 Thus this data can be used to establish average mortality estimates for museums generally as well as different types of museums, which can be compared to those observed for private museums globally. 
-Its furthermore a rich source of financial data
-
-egmus doesn't have that
+The availability of financial data for American institutions through the NCCS/IRS may also provide tentative insights into the finances of private museums.
 

### 2024-09-11 scripts/closing_main.R

@@ -50,6 +50,8 @@ gd_nbrs <- function() {
     ## descripti nbrs
     dt_descs_prep1 <- list(
         list(nbr_name = "pmdb_n_all",    nbr_fmt = dt_pmdb[, .N]),
+        list(nbr_name = "pmdb_n_US",    nbr_fmt = dt_pmdb[iso3c == "USA", .N]),
+        list(nbr_name = "pmdb_n_closed_US",  nbr_fmt = dt_pmdb[iso3c == "USA" & museum_status == "closed", .N]),
         list(nbr_name = "pmdb_open_atm", nbr_fmt = dt_pmdb[museum_status == "private museum", .N]),
         list(nbr_name = "pm_n_closed",   nbr_fmt = dt_pmyear[, sum(closing)]),
         list(nbr_name = "n_pmyears",     nbr_fmt = dt_pmyear[, .N]),

### 2024-09-16 texts/paper_closing.tex
minor polishing, update tasks, send email, update sups

@@
-% Created 2024-09-11 wo 11:36
+% Created 2024-09-11 wo 15:33
 % Intended LaTeX compiler: pdflatex
@@
 
-\section*{It's so over}
+\section*{Stayin' Alive: The unexpected longevity of founder-centered private art museums}
 
@@
 While many aspects of this new organizational form has attracted attention, such as their emergence, relations to other institutions or impact on artist consecration (cf.
-\cite{Kolbe_etal_2022_privatemuseum} for a literature review), the process of closure has received considerably less attention
-Furthermore, the focus that has been given to questions of sustainability has been primarily conducted through case studies; beyond the exception of \textcite{Velthuis_Gera_2024_fragility} quantitative studies have been absent.
+\cite{Kolbe_etal_2022_privatemuseum} for a literature review), the process of closure has received considerably less attention.
+Furthermore, the focus that has been given to questions of sustainability has been primarily conducted through case studies; quantitative studies have been mostly absent.
 In this paper, I address this gap by investigating the closure event of members of this new organizational form.
@@
 While little evidence points toward private museums being unvoluntarily at risk due to their low diversification, private museums may close due to environmental pressures, which exhibit a complex relationship which for most museums consists of competition from other private museums as well as, unexpectedly, large audiences.
-Finally, some limited evidence points towards a temporary intention by their founders from the very beginning as a potential reason for their closure.
+Finally, private museums with unconventional names (in particular, without the term "museum" in the name) face a higher closing risk, which may indicate either a temporary intention by their founders from the very beginning and/or limited recognition by third parties as potential closing reasons.
 
@@
 Outside of the United States, the reliance on revenue streams beyond operations is even larger:
-German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table p.233}, with private museums requiring less support as operations provide around 47\% of their budget (ibid.), and even the more market-oriented NPOs in the cultural sector draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
-On a European level, only 12\% of museum incomes are generated by entry fees, whereas 69\% originate from subsidies \parencite{EGMUS_2024_complete.}\footnote{Own calculations from on EGMUS data, based on all countries with income data from 2015 onwards.}
+German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table p.233}, with private museums however requiring less support as operations provide around 47\% of their budget (ibid.), and even the more market-oriented NPOs in the cultural sector draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
+On a European level, only 12\% of museum incomes are generated by entry fees, whereas 69\% originate from subsidies \parencite{EGMUS_2024_complete}.\footnote{Own calculations from on EGMUS data, based on all countries with income data from 2015 onwards.}
 
@@
 \textcite{Bechtler_Imhof_2018_future} also characterize "the dependency on single individuals only" as one of main reasons that "make these private museums fragile" (p.53).
-\cite{StylianouLambert_etal_2014_museums} also characterize many private institutions as "small individual museums that depend too much on their creators to guarantee their sustainability" (p.582).
+\textcite{StylianouLambert_etal_2014_museums} also characterize many private institutions as "small individual museums that depend too much on their creators to guarantee their sustainability" (p.582).
 Beyond a direct financial component, private museums have been also been characterized as fragile since they can only rely on their founder for "taste", "vision and drive" \parencite[p.77]{Adam_2021_rise}, "passion" \parencite[p.234]{Walker_2019_collector} or "skills and knowledge" \parencite[p.580]{StylianouLambert_etal_2014_museums}.
@@
 \textcite{Velthuis_Gera_2024_fragility} similarly argue that "the founder’s death will almost inevitably have a direct impact on the financial health of the museum" (p.10).
-\cite{StylianouLambert_etal_2014_museums}, after discussing a case of a private museum whose owner "does not believe that anyone else could love the museum as much as she does", argue that this "generates questions regarding the cultural sustainability of small private museums in cases where their initiators are not able to care for them any longer" (p.580).
+\textcite{StylianouLambert_etal_2014_museums}, after discussing a case of a private museum whose owner "does not believe that anyone else could love the museum as much as she does", argue that this "generates questions regarding the cultural sustainability of small private museums in cases where their initiators are not able to care for them any longer" (p.580).
 
@@
 As the databse was constructed retrospectively from 2020 to 2022, I focus here on closing events from 2000 to 2021 to limit the possibility that some institutions were missed, as such risks are likely higher for earlier time periods.
-Furthermore, a small number of museums are excluded, in particular 2 museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), 1 museum the opening year of which could not be determined, as well as 2 which closed before 2000 thereby fall outside the period under investigation.
+Furthermore, a small number of museums are excluded, in particular 2 museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), 1 museum the opening year of which could not be determined, as well as 2 museums which closed before 2000 and thereby fall outside the period under investigation.
 This leaves 503 private museums at risk which have accumulated 6096 museum-years and 68 closures.
@@
 
-To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55.000 museums, are analyzed.
-In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum}.
+To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55,000 museums, are analyzed.
+In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum.}
 \paragraph*{Reputation}
@@
 
-While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})\footnote{IRS data is not without limitations, such as only being required from larger organizations, misreporting, and the difficulty of inferring closing from non-filing.
-Nevertheless, it constitutes the most fine-grained data source to investigate non-profit survival}.
+While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview}).\footnote{IRS data is not without limitations, such as only being required from larger organizations, misreporting, and the difficulty of inferring closing from non-filing.
+Nevertheless, it constitutes the most fine-grained data source to investigate non-profit survival}
 None of these focus on art museums exclusively (\textcite{Hager_2001_vulnerability} focuses on Art NPOs, \textcite{Bowen_etal_1994_charitable} and \textcite{Gordon_etal_2013_insolvency} on NPOs generally), but report survival estimates by organizational form, including museums.
@@
 While the coefficient in the short-term period is consistently higher than both the overall death coefficient and the long-term period coefficients, so far the evidence is inconclusive as only few cases are statistically significant\footnote{P-values are also not adjusted for multiple tests}.
-Furthermore, such a shock passes quickly relative to the median life-time of museums of 52 years, thus "giving" the founder death little time to lead to many museum closures. 
+Furthermore, such a shock passes quickly relative to the predicted median life time of museums of 52 years, thus "giving" the founder death little time to lead to many museum closures. 
 Considering the numbers underlying the death effect estimates illustrates the uncertainty of the determning the effect of the death of the founder on aclosing: 
@@
 Thus, for population values of 0 to 2.97 million people, an increase in the number of private museums corresponds to an increase in mortality (bottom half of figure \ref{fig:p_pred_heatmap}), which provides support for hypothesis 3 according to which competition leads to museum closure, in particular as this range includes 5056 museums years, or 83\% of the dataset.
-Yet at the same time, at low private museums numbers (0 to 3 private museums), increases in population also increase mortality; this range also includes a large number of museum-years (4960 museum years; 81\% of the data).
+Yet at the same time, at low private museums numbers (0 to 3 private museums, left half of figure \ref{fig:p_pred_heatmap}), increases in population also increase mortality; this range also includes a large number of museum-years (4960 museum years; 81\% of the data).
 Such a relationship is unexpected insofar as it is unclear why a larger potential audience would be associated with a higher risk of closure.\footnote{Alternative approaches of modeling competition are discussed in the supplementary materials, but cannot answer this question.}
@@
 Alternatively, areas with high population and low private museum numbers might more generally lack cultural infrastructure; which one could see supported by closures in Jakarta, Istanbul and Mexico City, but less so by closings in Paris, Tokyo or Madrid.
-However, low private museums indicating lack of cultural infrastructure might also explain the decrease in mortality associated with increases in private museum numbers at high population values (figure \ref{fig:p_pred_heatmap}, upper half), as such pattern does not correspond to that predicted by competition.
+However, low private museums numbers indicating lack of cultural infrastructure might also explain the decrease in mortality associated with increases in private museum numbers at high population values (figure \ref{fig:p_pred_heatmap}, upper half), as such pattern does not correspond to that predicted by competition.
 More in line with expectation is however the association between increases of population numbers and lower mortality at higher numbers of private museums (right half), as it indicates that audiences can facilitate museum survival.
@@
 A temporal intentions are however the exceptions among closing reasons identified by \textcite{Velthuis_Gera_2024_fragility} (p.6), and as similarly only a small fraction of private museum chooses such a name (140 museums, or 28\%), the overall proportion of these types of voluntary closures compared to all closures is presumably limited.
-\subsection*{Discussion}
+\subsection*{Discussion and Conclusion}
 
@@
 While the booming numbers of private museums themselves have received substantial attention, less consideration has been given to the fact that large populations can generate dozens of closures without requiring high closing rates, especially when cloures are considered over a span of several years or decades.
-In other words, the sheer size to which the private museum population has grown over the last decades has made it all but inevitable that some of them would close, and do so after only a few year.
+In other words, the sheer size to which the private museum population has grown over the last decades has made it all but inevitable that some of them would close, and do so after only a few years.
 Based on the current analysis, private museums will continue to close in the years to come; at hazard rates of around 1\% on average a handful of closures every year are to be expected.
@@
 Multiple reasons might be the at play that mitigate this risk of low diversification.
-First, it might take more commitment to open a museum as an individual or couple compared to less involved art patronage of being a board member in existing institutions or donating works, which would result in private museums founders being more motivated to secure the existence of their institutions.
+First, it might take more commitment to open a museum as an individual or couple compared to less involved art patronage of being a board member in existing institutions or donating works, which would result in private museums founders being more motivated to secure the continued existence of their institutions.
 Furthermore, the centrality of the founder might leave little room to question who is responsible to provide additional funds in times of financial difficulties, whereas in organizations without a central figure each member may feel less responsible.
@@
 On the other hand, higher closing rates for unconventionally named museums might reflect absence of recognition and support by third parties in the environment.
-A dimensions where the influence of the environment can however be ascertained with greater certainty is the role of audiences and other private museums.
+A dimension where the influence of the environment can however be ascertained with greater certainty is the role of audiences and other private museums.
 While the overall relationship is complex, for the majority of private museums increases in both variables are associated with higher closing rates.
 Whereas it is plausible that the association between higher institution counts and closing rates reflects competitive pressures, it is less obvious what may lay behind observing a positive association behind larger population and closing risk.
-\subsection*{Conclusion}
-
 \subsubsection*{Limitations}
 
-However, it is necessary to consider that so far only a small fraction (47 museums, 9.3\%) of museums has experienced the death of their founder, one of the primary reasons hypothesized to lead to the private museum closure.
+A number of limitations are worth considering:
+So far only a small fraction (47 museums, 9.3\%) of museums has experienced the death of their founder, one of the primary reasons hypothesized to lead to the private museum closure. 
 While so far these museums have not seen substantially elevated closing risks, these estimates will become more precise as more founders pass away.
-As the currently large confidence interval (figure \ref{fig:p_surv_death}) for museums whose founders have died allows a wide range of survival chances, it is entirely possible that previous scholars have indeed correctly identified a key dependency (the current absence of evidence of it should not be taken as evidence of absence) and that therefore later analyses will a significantly association between founder death and closing risk as well as a higher average closing risk for private museums.
+As the currently large confidence interval (figure \ref{fig:p_surv_death}) for museums whose founders have died allows a wide range of survival chances, it is entirely possible that previous scholars have indeed correctly identified a key dependency (the current absence of evidence of it should not be taken as evidence of absence) and that therefore later analyses will a significantly association between founder death and closing risk as well as a higher average closing risk for private museums.\footnote{Similarly, as 80\% of private museums have been founded in the new millenium, only a few museums have so far reached an age above 30 years, which makes the estimation of the age-dependent hazard for this age range highly speculative.}
 At the same time, it is also possible that private museums are generally less dependent on a single person (or couple) than has been assumed, and have in fact become institutionalized to an extent that most heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
@@
 
-The primary mechanism that has been argued to lead to museum closure is financials, and while this study measures it indirectly, primarily through indicators on the level of the founder, museum and environment, the financial situation of a museum is not used directly.
+The primary mechanism that has been argued to lead to museum closure is costs, and while this study measures it indirectly, primarily through indicators on the level of the founder, museum and environment, the financial situation of a museum is not used directly.
 The primary reason for this is data availability.
@@
 The effort to compile such information on a global scale ranges from extremely challenging (harmonizing different reporting standards, language barriers) to outright impossible for institutions who do not even (have to) report public financial information.
-Similarly, other museum characteristics, such as as museum size, facilities, as well as marketing and outreach activities might be related to long-term survival prospect\footnote{While the original data collection included the assessment of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear during data analysis that the data collected was unsuitable to construct accurate indicators from these findings due to difficulty in assessing them in many cases.
+Similarly, other museum characteristics which were not considered here, such as as museum size, facilities, as well as marketing and outreach activities, might be related to long-term survival prospects.\footnote{While the original data collection included the assessment of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear during data analysis that the data collected was unsuitable to construct accurate indicators from these findings due to difficulty in assessing them in many cases.
 Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Wayback machine, less central pages (such as those with information about facilities and activities), were archived much less frequently, and sometimes inaccessible despite being archived due to changes in webtechnology (such as the retirement of Adobe flash).}
@@
 However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms.
-One way in which this can happen is when other parties, such as local governments other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
+One way in which this can happen is when other parties, such as local governments, other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
 Sometimes this involves changes in the composition of the board of directors (or equivalent), with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum to an extent that it no longer fits the working definition.
-Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to consistently determine the date of such transitions\footnote{Consequently they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing for at least some time.
+Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to consistently determine the date of such transitions.\footnote{Consequently they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing for at least some time.
 However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
@@
 Furthermore, including wider institutional changes such as tax incentives, government subsidies, but also political changes and censorship would lead to a more complete description of risk factors, and in more detail identify niches which are particularly suited for private museums.
-\subsubsection*{future research}
-
-The US register data on NPO tax filings constitutes a promising source for data for museum research (while this data source has seen frequent usage in non-profit management, it remains underexploited in the field of museum research).
-While the United States private museum population with 70 museums and 9 closings might not be sufficient to test whether private museums have a a higher closing risks than other museums, it still hosts a large population of museums.
-Thus this data can be used to establish average mortality estimates for museums generally as well as different types of museums, which can be compared to those observed for private museums globally. 
-The availability of financial data for American institutions through the NCCS/IRS may also provide tentative insights into the finances of private museums.
 

### 2024-09-16 texts/sup_materials.tex
minor polishing, update tasks, send email, update sups

@@
-% Created 2024-09-09 ma 12:03
+% Created 2024-09-11 wo 13:29
 % Intended LaTeX compiler: pdflatex
@@
 \section*{Supplementary online materials}
+\label{sec:orgb29274c}
 
 \subsection*{Alternative competition specifications}
+\label{sec:org52f01e9}
 
@@
 \centering
-\includegraphics[width=18cm]{../figures/p_pred_heatmap_alt.pdf}
+\includegraphics[width=18cm]{../figures/p_pred_heatmap_alt.png}
 \caption{\label{fig:p_pred_heatmap_alt}Prediction Heatmap of Alternative model specifications}
@@
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
+\begin{tabular}{p{0mm}llllll}
   \hline 
@@
   \multicolumn{7}{l}{\textbf{Founder}} \\ 
- & Gender - Female & -.04 \; (0.34) & .00 \; (0.33) & -.05 \; (0.33) & -.00 \; (0.33) & -.11 \; (0.33) \\ 
-   & Gender - Couple & -.14 \; (0.32) & -.22 \; (0.32) & -.18 \; (0.32) & -.21 \; (0.32) & -.23 \; (0.32) \\ 
-   & Founder died & .28 \; (0.43) & .19 \; (0.43) & .25 \; (0.43) & .18 \; (0.43) & .08 \; (0.43) \\ 
+ & Gender - Female & $-.04 \; (0.34)$ & $.00 \; (0.33)$ & $-.05 \; (0.33)$ & $-.00 \; (0.33)$ & $-.11 \; (0.33)$ \\ 
+   & Gender - Couple & $-.14 \; (0.32)$ & $-.22 \; (0.32)$ & $-.18 \; (0.32)$ & $-.21 \; (0.32)$ & $-.23 \; (0.32)$ \\ 
+   & Founder died & $.28 \; (0.43)$ & $.19 \; (0.43)$ & $.25 \; (0.43)$ & $.18 \; (0.43)$ & $.08 \; (0.43)$ \\ 
    \multicolumn{7}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .20 \; (0.41) & .36 \; (0.40) & .33 \; (0.40) & .37 \; (0.40) & .44 \; (0.40) \\ 
-   & Self-Identification - Collection & -.45 \; (0.54) & -.09 \; (0.50) & -.20 \; (0.51) & -.05 \; (0.51) & .05 \; (0.51) \\ 
-   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.03 \; (0.30)^{***} & 1.12 \; (0.31)^{***} & 1.05 \; (0.30)^{***} & 1.13 \; (0.30)^{***} \\ 
-   & AN Ranking - Included & .19 \; (0.34) & .24 \; (0.34) & .17 \; (0.35) & .23 \; (0.34) & .18 \; (0.34) \\ 
-   & AN Ranking - Dropped & .46 \; (0.50) & .45 \; (0.50) & .31 \; (0.50) & .45 \; (0.49) & .47 \; (0.49) \\ 
-   & Founder name in Museum name & .05 \; (0.28) & .10 \; (0.28) & .14 \; (0.28) & .10 \; (0.28) & .07 \; (0.28) \\ 
+ & Self-Identification - Foundation & $.20 \; (0.41)$ & $.36 \; (0.40)$ & $.33 \; (0.40)$ & $.37 \; (0.40)$ & $.44 \; (0.40)$ \\ 
+   & Self-Identification - Collection & $-.45 \; (0.54)$ & $-.09 \; (0.50)$ & $-.20 \; (0.51)$ & $-.05 \; (0.51)$ & $.05 \; (0.51)$ \\ 
+   & Self-Identification - Other & $1.09 \; (0.30)^{***}$ & $1.03 \; (0.30)^{***}$ & $1.12 \; (0.31)^{***}$ & $1.05 \; (0.30)^{***}$ & $1.13 \; (0.30)^{***}$ \\ 
+   & AN Ranking - Included & $.19 \; (0.34)$ & $.24 \; (0.34)$ & $.17 \; (0.35)$ & $.23 \; (0.34)$ & $.18 \; (0.34)$ \\ 
+   & AN Ranking - Dropped & $.46 \; (0.50)$ & $.45 \; (0.50)$ & $.31 \; (0.50)$ & $.45 \; (0.49)$ & $.47 \; (0.49)$ \\ 
+   & Founder name in Museum name & $.05 \; (0.28)$ & $.10 \; (0.28)$ & $.14 \; (0.28)$ & $.10 \; (0.28)$ & $.07 \; (0.28)$ \\ 
    \multicolumn{7}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .65 \; (0.34) & .50 \; (0.32) & .41 \; (0.34) & .55 \; (0.33) & .73 \; (0.31)^{*} \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.03 \; (0.03) \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  &  &  &  \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} &  &  &  &  \\ 
-   & PM density (10km) &  & -.00 \; (0.03) &  &  &  \\ 
-   & PM density (10km, log) &  &  & .29 \; (0.15) &  &  \\ 
-   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  &  &  &  \\ 
-   & Local Audience per PM &  &  &  & .10 \; (0.14) &  \\ 
-   & Local Audience per PM (log) &  &  &  &  & .28 \; (0.09)^{**} \\ 
-   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.65 \; (1.01) & -1.64 \; (1.01) & -1.65 \; (1.01) & -1.63 \; (1.01) \\ 
-   & Covid Pandemic (2020/21) & .42 \; (0.29) & .44 \; (0.29) & .46 \; (0.29) & .43 \; (0.29) & .42 \; (0.29) \\ 
+ & PM density (country) & $.65 \; (0.34)$ & $.50 \; (0.32)$ & $.41 \; (0.34)$ & $.55 \; (0.33)$ & $.73 \; (0.31)^{*}$ \\ 
+   & PM density$^{2}$ (country) & $-.03 \; (0.02)$ & $-.02 \; (0.02)$ & $-.02 \; (0.02)$ & $-.02 \; (0.02)$ & $-.03 \; (0.03)$ \\ 
+   & Pop. (millions) within 10km & $.27 \; (0.09)^{**}$ & $NA$ & $NA$ & $NA$ & $NA$ \\ 
+   & Nbr PM within 10km & $.26 \; (0.08)^{***}$ & $NA$ & $NA$ & $NA$ & $NA$ \\ 
+   & PM density (10km) & $NA$ & $-.00 \; (0.03)$ & $NA$ & $NA$ & $NA$ \\ 
+   & PM density (10km, log) & $NA$ & $NA$ & $.29 \; (0.15)$ & $NA$ & $NA$ \\ 
+   & Nbr PM (10km) * Pop (10km) & $-.09 \; (0.03)^{**}$ & $NA$ & $NA$ & $NA$ & $NA$ \\ 
+   & Local Audience per PM & $NA$ & $NA$ & $NA$ & $.10 \; (0.14)$ & $NA$ \\ 
+   & Local Audience per PM (log) & $NA$ & $NA$ & $NA$ & $NA$ & $.28 \; (0.09)^{**}$ \\ 
+   & Great Recession (2008/09) & $-1.59 \; (1.01)$ & $-1.65 \; (1.01)$ & $-1.64 \; (1.01)$ & $-1.65 \; (1.01)$ & $-1.63 \; (1.01)$ \\ 
+   & Covid Pandemic (2020/21) & $.42 \; (0.29)$ & $.44 \; (0.29)$ & $.46 \; (0.29)$ & $.43 \; (0.29)$ & $.42 \; (0.29)$ \\ 
    \hline
- & Museums & 503 & 503 & 503 & 503 & 503 \\ 
-   & Museum-years & 6096 & 6096 & 6096 & 6096 & 6096 \\ 
-   & Closures & 68 & 68 & 68 & 68 & 68 \\ 
-   & log. Likelihood & -339.68 & -347.93 & -346.18 & -347.72 & -342.93 \\ 
-   & AIC & 711.35 & 723.85 & 720.35 & 723.44 & 713.86 \\ 
-   & BIC & 746.87 & 754.93 & 751.42 & 754.51 & 744.93 \\ 
+ & Museums & $503$ & $503$ & $503$ & $503$ & $503$ \\ 
+   & Museum-years & $6096$ & $6096$ & $6096$ & $6096$ & $6096$ \\ 
+   & Closures & $68$ & $68$ & $68$ & $68$ & $68$ \\ 
+   & log. Likelihood & $-339.68$ & $-347.93$ & $-346.18$ & $-347.72$ & $-342.93$ \\ 
+   & AIC & $711.35$ & $723.85$ & $720.35$ & $723.44$ & $713.86$ \\ 
+   & BIC & $746.87$ & $754.93$ & $751.42$ & $754.51$ & $744.93$ \\ 
    \hline 
@@
 \subsection*{Alternative sample specifications}
+\label{sec:org9b637b1}
 
@@
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
+\begin{tabular}{p{0mm}lllll}
   \hline 
@@
   \multicolumn{6}{l}{\textbf{Founder}} \\ 
- & Gender - Female & -.04 \; (0.34) & -1.07 \; (0.78) & .21 \; (0.44) & -.01 \; (0.34) \\ 
-   & Gender - Couple & -.14 \; (0.32) & -.27 \; (0.46) & .07 \; (0.52) & -.12 \; (0.32) \\ 
-   & Founder died & .28 \; (0.43) & .58 \; (0.59) & -.19 \; (0.77) & .29 \; (0.43) \\ 
+ & Gender - Female & $-.04 \; (0.34)$ & $-1.07 \; (0.78)$ & $.21 \; (0.44)$ & $-.01 \; (0.34)$ \\ 
+   & Gender - Couple & $-.14 \; (0.32)$ & $-.27 \; (0.46)$ & $.07 \; (0.52)$ & $-.12 \; (0.32)$ \\ 
+   & Founder died & $.28 \; (0.43)$ & $.58 \; (0.59)$ & $-.19 \; (0.77)$ & $.29 \; (0.43)$ \\ 
    \multicolumn{6}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .20 \; (0.41) & .31 \; (0.58) & 1.02 \; (0.65) & .18 \; (0.41) \\ 
-   & Self-Identification - Collection & -.45 \; (0.54) & -18.23 \; (4781.88) & .95 \; (0.71) & -.50 \; (0.55) \\ 
-   & Self-Identification - Other & 1.09 \; (0.30)^{***} & .67 \; (0.46) & 1.95 \; (0.51)^{***} & 1.09 \; (0.31)^{***} \\ 
-   & AN Ranking - Included & .19 \; (0.34) & .55 \; (0.58) & -.32 \; (0.48) & .18 \; (0.34) \\ 
-   & AN Ranking - Dropped & .46 \; (0.50) & -.06 \; (0.85) & .18 \; (0.73) & .47 \; (0.50) \\ 
-   & Founder name in Museum name & .05 \; (0.28) & .24 \; (0.44) & -.30 \; (0.42) & .04 \; (0.28) \\ 
+ & Self-Identification - Foundation & $.20 \; (0.41)$ & $.31 \; (0.58)$ & $1.02 \; (0.65)$ & $.18 \; (0.41)$ \\ 
+   & Self-Identification - Collection & $-.45 \; (0.54)$ & $-18.23 \; (4781.88)$ & $.95 \; (0.71)$ & $-.50 \; (0.55)$ \\ 
+   & Self-Identification - Other & $1.09 \; (0.30)^{***}$ & $.67 \; (0.46)$ & $1.95 \; (0.51)^{***}$ & $1.09 \; (0.31)^{***}$ \\ 
+   & AN Ranking - Included & $.19 \; (0.34)$ & $.55 \; (0.58)$ & $-.32 \; (0.48)$ & $.18 \; (0.34)$ \\ 
+   & AN Ranking - Dropped & $.46 \; (0.50)$ & $-.06 \; (0.85)$ & $.18 \; (0.73)$ & $.47 \; (0.50)$ \\ 
+   & Founder name in Museum name & $.05 \; (0.28)$ & $.24 \; (0.44)$ & $-.30 \; (0.42)$ & $.04 \; (0.28)$ \\ 
    \multicolumn{6}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .65 \; (0.34) & .88 \; (0.44)^{*} & -1.16 \; (2.52) & .67 \; (0.34)^{*} \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.04 \; (0.02) & 1.33 \; (2.38) & -.03 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & 1.69 \; (0.81)^{*} & .17 \; (0.17) & .20 \; (0.12) \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} & .64 \; (1.06) & .19 \; (0.10) & .22 \; (0.20) \\ 
-   & Nbr PM$^{2}$ within 10km &  &  &  & .01 \; (0.02) \\ 
-   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.54 \; (1.83) & -.07 \; (0.04)^{*} & -.02 \; (0.09) \\ 
-   & Nbr PM$^{2}$ (10km) * Pop (10km) &  &  &  & -.01 \; (0.01) \\ 
-   & Great Recession (2008/09) & -1.59 \; (1.01) & -.75 \; (1.04) & -18.42 \; (5245.29) & -1.59 \; (1.01) \\ 
-   & Covid Pandemic (2020/21) & .42 \; (0.29) & .46 \; (0.47) & .30 \; (0.41) & .45 \; (0.29) \\ 
+ & PM density (country) & $.65 \; (0.34)$ & $.88 \; (0.44)^{*}$ & $-1.16 \; (2.52)$ & $.67 \; (0.34)^{*}$ \\ 
+   & PM density$^{2}$ (country) & $-.03 \; (0.02)$ & $-.04 \; (0.02)$ & $1.33 \; (2.38)$ & $-.03 \; (0.02)$ \\ 
+   & Pop. (millions) within 10km & $.27 \; (0.09)^{**}$ & $1.69 \; (0.81)^{*}$ & $.17 \; (0.17)$ & $.20 \; (0.12)$ \\ 
+   & Nbr PM within 10km & $.26 \; (0.08)^{***}$ & $.64 \; (1.06)$ & $.19 \; (0.10)$ & $.22 \; (0.20)$ \\ 
+   & Nbr PM$^{2}$ within 10km & $NA$ & $NA$ & $NA$ & $.01 \; (0.02)$ \\ 
+   & Nbr PM (10km) * Pop (10km) & $-.09 \; (0.03)^{**}$ & $-.54 \; (1.83)$ & $-.07 \; (0.04)^{*}$ & $-.02 \; (0.09)$ \\ 
+   & Nbr PM$^{2}$ (10km) * Pop (10km) & $NA$ & $NA$ & $NA$ & $-.01 \; (0.01)$ \\ 
+   & Great Recession (2008/09) & $-1.59 \; (1.01)$ & $-.75 \; (1.04)$ & $-18.42 \; (5245.29)$ & $-1.59 \; (1.01)$ \\ 
+   & Covid Pandemic (2020/21) & $.42 \; (0.29)$ & $.46 \; (0.47)$ & $.30 \; (0.41)$ & $.45 \; (0.29)$ \\ 
    \hline
- & Museums & 503 & 283 & 219 & 503 \\ 
-   & Museum-years & 6096 & 3311 & 2265 & 6096 \\ 
-   & Closures & 68 & 28 & 35 & 68 \\ 
-   & log. Likelihood & -339.68 & -116.47 & -139.36 & -338.79 \\ 
-   & AIC & 711.35 & 264.94 & 310.72 & 713.59 \\ 
-   & BIC & 746.87 & 286.25 & 335.60 & 753.54 \\ 
+ & Museums & $503$ & $283$ & $219$ & $503$ \\ 
+   & Museum-years & $6096$ & $3311$ & $2265$ & $6096$ \\ 
+   & Closures & $68$ & $28$ & $35$ & $68$ \\ 
+   & log. Likelihood & $-339.68$ & $-116.47$ & $-139.36$ & $-338.79$ \\ 
+   & AIC & $711.35$ & $264.94$ & $310.72$ & $713.59$ \\ 
+   & BIC & $746.87$ & $286.25$ & $335.60$ & $753.54$ \\ 
    \hline 
@@
 \subsection*{Alternative time range specifications}
-
+\label{sec:org68f7010}
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
@@
   \multicolumn{6}{l}{\textbf{Founder}} \\ 
- & Gender - Female & -.04 \; (0.34) & .00 \; (0.34) & .05 \; (0.34) & .31 \; (0.37) \\ 
-   & Gender - Couple & -.14 \; (0.32) & -.10 \; (0.32) & -.39 \; (0.35) & -.35 \; (0.40) \\ 
-   & Founder died & .28 \; (0.43) & .13 \; (0.46) & .34 \; (0.46) & -.22 \; (0.55) \\ 
+ & Gender - Female & $-.04 \; (0.34)$ & $.00 \; (0.34)$ & $.05 \; (0.34)$ & $.31 \; (0.37)$ \\ 
+   & Gender - Couple & $-.14 \; (0.32)$ & $-.10 \; (0.32)$ & $-.39 \; (0.35)$ & $-.35 \; (0.40)$ \\ 
+   & Founder died & $.28 \; (0.43)$ & $.13 \; (0.46)$ & $.34 \; (0.46)$ & $-.22 \; (0.55)$ \\ 
    \multicolumn{6}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .20 \; (0.41) & .25 \; (0.42) & .24 \; (0.43) & -.13 \; (0.48) \\ 
-   & Self-Identification - Collection & -.45 \; (0.54) & -.41 \; (0.54) & -.37 \; (0.55) & -.62 \; (0.60) \\ 
-   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.14 \; (0.31)^{***} & 1.15 \; (0.32)^{***} & .96 \; (0.35)^{**} \\ 
-   & AN Ranking - Included & .19 \; (0.34) & .17 \; (0.34) & .26 \; (0.35) & -.35 \; (0.49) \\ 
-   & AN Ranking - Dropped & .46 \; (0.50) & .22 \; (0.55) & .28 \; (0.55) & .13 \; (0.56) \\ 
-   & Founder name in Museum name & .05 \; (0.28) & .05 \; (0.28) & -.01 \; (0.29) & .46 \; (0.32) \\ 
+ & Self-Identification - Foundation & $.20 \; (0.41)$ & $.25 \; (0.42)$ & $.24 \; (0.43)$ & $-.13 \; (0.48)$ \\ 
+   & Self-Identification - Collection & $-.45 \; (0.54)$ & $-.41 \; (0.54)$ & $-.37 \; (0.55)$ & $-.62 \; (0.60)$ \\ 
+   & Self-Identification - Other & $1.09 \; (0.30)^{***}$ & $1.14 \; (0.31)^{***}$ & $1.15 \; (0.32)^{***}$ & $.96 \; (0.35)^{**}$ \\ 
+   & AN Ranking - Included & $.19 \; (0.34)$ & $.17 \; (0.34)$ & $.26 \; (0.35)$ & $-.35 \; (0.49)$ \\ 
+   & AN Ranking - Dropped & $.46 \; (0.50)$ & $.22 \; (0.55)$ & $.28 \; (0.55)$ & $.13 \; (0.56)$ \\ 
+   & Founder name in Museum name & $.05 \; (0.28)$ & $.05 \; (0.28)$ & $-.01 \; (0.29)$ & $.46 \; (0.32)$ \\ 
    \multicolumn{6}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .65 \; (0.34) & .70 \; (0.38) & .40 \; (0.45) & .25 \; (0.51) \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) & -.02 \; (0.03) & -.02 \; (0.06) \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} & .25 \; (0.10)^{**} & .24 \; (0.11)^{*} \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} & .25 \; (0.08)^{***} & .25 \; (0.08)^{***} & .23 \; (0.08)^{**} \\ 
-   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.07 \; (0.03)^{*} \\ 
-   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.69 \; (1.01) &  &  \\ 
-   & Covid Pandemic (2020/21) & .42 \; (0.29) & .33 \; (0.29) & .28 \; (0.30) & .12 \; (0.31) \\ 
+ & PM density (country) & $.65 \; (0.34)$ & $.70 \; (0.38)$ & $.40 \; (0.45)$ & $.25 \; (0.51)$ \\ 
+   & PM density$^{2}$ (country) & $-.03 \; (0.02)$ & $-.03 \; (0.02)$ & $-.02 \; (0.03)$ & $-.02 \; (0.06)$ \\ 
+   & Pop. (millions) within 10km & $.27 \; (0.09)^{**}$ & $.27 \; (0.10)^{**}$ & $.25 \; (0.10)^{**}$ & $.24 \; (0.11)^{*}$ \\ 
+   & Nbr PM within 10km & $.26 \; (0.08)^{***}$ & $.25 \; (0.08)^{***}$ & $.25 \; (0.08)^{***}$ & $.23 \; (0.08)^{**}$ \\ 
+   & Nbr PM (10km) * Pop (10km) & $-.09 \; (0.03)^{**}$ & $-.09 \; (0.03)^{**}$ & $-.09 \; (0.03)^{**}$ & $-.07 \; (0.03)^{*}$ \\ 
+   & Great Recession (2008/09) & $-1.59 \; (1.01)$ & $-1.69 \; (1.01)$ & $NA$ & $NA$ \\ 
+   & Covid Pandemic (2020/21) & $.42 \; (0.29)$ & $.33 \; (0.29)$ & $.28 \; (0.30)$ & $.12 \; (0.31)$ \\ 
    \hline
- & Museums & 503 & 502 & 499 & 485 \\ 
-   & Museum-years & 6096 & 5483 & 4474 & 2901 \\ 
-   & Closures & 68 & 67 & 64 & 50 \\ 
-   & log. Likelihood & -339.68 & -329.47 & -304.28 & -217.32 \\ 
-   & AIC & 711.35 & 690.94 & 638.57 & 464.65 \\ 
-   & BIC & 746.87 & 726.22 & 670.95 & 493.33 \\ 
+ & Museums & $503$ & $502$ & $499$ & $485$ \\ 
+   & Museum-years & $6096$ & $5483$ & $4474$ & $2901$ \\ 
+   & Closures & $68$ & $67$ & $64$ & $50$ \\ 
+   & log. Likelihood & $-339.68$ & $-329.47$ & $-304.28$ & $-217.32$ \\ 
+   & AIC & $711.35$ & $690.94$ & $638.57$ & $464.65$ \\ 
+   & BIC & $746.87$ & $726.22$ & $670.95$ & $493.33$ \\ 
    \hline 
@@
 \subsection*{Inclusion of Exhibition data}
+\label{sec:org3423df8}
 
@@
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
+\begin{tabular}{p{0mm}llll}
   \hline 
@@
   \multicolumn{5}{l}{\textbf{Founder}} \\ 
- & Gender - Female & -.04 \; (0.34) & -.01 \; (0.34) & -.06 \; (0.34) \\ 
-   & Gender - Couple & -.14 \; (0.32) & -.12 \; (0.32) & -.15 \; (0.32) \\ 
-   & Founder died & .28 \; (0.43) & .31 \; (0.43) & .26 \; (0.43) \\ 
+ & Gender - Female & $-.04 \; (0.34)$ & $-.01 \; (0.34)$ & $-.06 \; (0.34)$ \\ 
+   & Gender - Couple & $-.14 \; (0.32)$ & $-.12 \; (0.32)$ & $-.15 \; (0.32)$ \\ 
+   & Founder died & $.28 \; (0.43)$ & $.31 \; (0.43)$ & $.26 \; (0.43)$ \\ 
    \multicolumn{5}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .20 \; (0.41) & .24 \; (0.42) & .17 \; (0.41) \\ 
-   & Self-Identification - Collection & -.45 \; (0.54) & -.47 \; (0.55) & -.42 \; (0.54) \\ 
-   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.13 \; (0.31)^{***} & 1.07 \; (0.30)^{***} \\ 
-   & AN Ranking - Included & .19 \; (0.34) & .26 \; (0.36) & .13 \; (0.35) \\ 
-   & AN Ranking - Dropped & .46 \; (0.50) & .50 \; (0.50) & .42 \; (0.50) \\ 
-   & Founder name in Museum name & .05 \; (0.28) & .07 \; (0.28) & .03 \; (0.28) \\ 
-   & Exhibition any &  & -.22 \; (0.27) &  \\ 
-   & Exhibition any last 5 years &  &  & .20 \; (0.26) \\ 
+ & Self-Identification - Foundation & $.20 \; (0.41)$ & $.24 \; (0.42)$ & $.17 \; (0.41)$ \\ 
+   & Self-Identification - Collection & $-.45 \; (0.54)$ & $-.47 \; (0.55)$ & $-.42 \; (0.54)$ \\ 
+   & Self-Identification - Other & $1.09 \; (0.30)^{***}$ & $1.13 \; (0.31)^{***}$ & $1.07 \; (0.30)^{***}$ \\ 
+   & AN Ranking - Included & $.19 \; (0.34)$ & $.26 \; (0.36)$ & $.13 \; (0.35)$ \\ 
+   & AN Ranking - Dropped & $.46 \; (0.50)$ & $.50 \; (0.50)$ & $.42 \; (0.50)$ \\ 
+   & Founder name in Museum name & $.05 \; (0.28)$ & $.07 \; (0.28)$ & $.03 \; (0.28)$ \\ 
+   & Exhibition any & $NA$ & $-.22 \; (0.27)$ & $NA$ \\ 
+   & Exhibition any last 5 years & $NA$ & $NA$ & $.20 \; (0.26)$ \\ 
    \multicolumn{5}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .65 \; (0.34) & .66 \; (0.35) & .65 \; (0.35) \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) & -.03 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} & .26 \; (0.08)^{***} & .27 \; (0.08)^{***} \\ 
-   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} \\ 
-   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.60 \; (1.01) & -1.57 \; (1.01) \\ 
-   & Covid Pandemic (2020/21) & .42 \; (0.29) & .42 \; (0.29) & .41 \; (0.29) \\ 
+ & PM density (country) & $.65 \; (0.34)$ & $.66 \; (0.35)$ & $.65 \; (0.35)$ \\ 
+   & PM density$^{2}$ (country) & $-.03 \; (0.02)$ & $-.03 \; (0.02)$ & $-.03 \; (0.02)$ \\ 
+   & Pop. (millions) within 10km & $.27 \; (0.09)^{**}$ & $.27 \; (0.09)^{**}$ & $.27 \; (0.10)^{**}$ \\ 
+   & Nbr PM within 10km & $.26 \; (0.08)^{***}$ & $.26 \; (0.08)^{***}$ & $.27 \; (0.08)^{***}$ \\ 
+   & Nbr PM (10km) * Pop (10km) & $-.09 \; (0.03)^{**}$ & $-.09 \; (0.03)^{**}$ & $-.09 \; (0.03)^{**}$ \\ 
+   & Great Recession (2008/09) & $-1.59 \; (1.01)$ & $-1.60 \; (1.01)$ & $-1.57 \; (1.01)$ \\ 
+   & Covid Pandemic (2020/21) & $.42 \; (0.29)$ & $.42 \; (0.29)$ & $.41 \; (0.29)$ \\ 
    \hline
- & Museums & 503 & 503 & 503 \\ 
-   & Museum-years & 6096 & 6096 & 6096 \\ 
-   & Closures & 68 & 68 & 68 \\ 
-   & log. Likelihood & -339.68 & -339.34 & -339.38 \\ 
-   & AIC & 711.35 & 712.67 & 712.76 \\ 
-   & BIC & 746.87 & 750.41 & 750.50 \\ 
+ & Museums & $503$ & $503$ & $503$ \\ 
+   & Museum-years & $6096$ & $6096$ & $6096$ \\ 
+   & Closures & $68$ & $68$ & $68$ \\ 
+   & log. Likelihood & $-339.68$ & $-339.34$ & $-339.38$ \\ 
+   & AIC & $711.35$ & $712.67$ & $712.76$ \\ 
+   & BIC & $746.87$ & $750.41$ & $750.50$ \\ 
    \hline 

### 2024-09-16 scripts/closing_main.R
pmdb update: gd_pmdb_excl rewrite, some new descriptives

@@ -305,8 +305,7 @@ source(paste0(c_dirs$code, "descriptives.R")) # descriptive tables/plots
 
 
 
-dt_pmdb_excl <- gd_pmdb_excl(only_pms = F) %>%
-    .[museum_status %in% c("private museum", "no longer a private museum", "closed")] # yeet bad PMs
+dt_pmdb_excl <- gd_pmdb_excl(sel = "any_ever_pm")    
 dt_pmdb <- gd_pmdb(dt_pmdb_excl, verbose = T)
 
 

### 2024-09-16 scripts/pmdb_update.R

@@ -1,6 +1,6 @@
 ## * update pmdb variables
 
-dt_pmdb_excl <- gd_pmdb_excl(only_pms = F)
+dt_pmdb_excl <- gd_pmdb_excl(sel =  "all")
 dt_pmdb <- gd_pmdb(dt_pmdb_excl, verbose = T)
 
 

### 2024-09-16 scripts/regression.R

@@ -132,7 +132,7 @@ gd_af_size <- function(dt_pmx) {
     
     ## check that NAs on iso3c are dealt with
     dt_pmdb_na_check <- join(dt_af_qntlprep[is.na(iso3c), .N, .(ID = PMDB_ID)] %>% na.omit,
-                             gd_pmdb_excl(only_pms = F)[, .(name, museum_status, ID)],
+                             gd_pmdb_excl(sel = "all")[, .(name, museum_status, ID)],
                              on = "ID")
     
     if (dt_pmdb_na_check[, any(museum_status %!in% c("no longer a private museum", "not open yet"))]) {

### 2024-09-26 texts/sup_materials.tex
include geographical models in supplementary materials

--- 2024-09-09 texts/sup_materials.tex
@@
-% Created 2024-09-09 ma 12:03
+% Created 2024-09-26 do 17:45
 % Intended LaTeX compiler: pdflatex
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:49:47 2024
+% Tue Sep 17 14:48:53 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:49:39 2024
+% Tue Sep 17 14:48:47 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:49:41 2024
+% Tue Sep 17 14:48:49 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Mon Sep  9 11:20:03 2024
+% Tue Sep 17 14:48:55 2024
 \begin{table}[ht]
@@
 Both coefficients are not significant, and do not substantially change the coefficients of other variables. 
+\subsection*{Inclusion of regional indicators}
+
+\begin{landscape}
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Thu Sep 26 17:45:22 2024
+\begingroup\small
+\begin{longtable}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
+  \hline 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_reg6} & \multicolumn{1}{l}{r\_regsub2} & \multicolumn{1}{l}{r\_regsub2\_samplecprn} & \multicolumn{1}{l}{r\_country} & \multicolumn{1}{l}{r\_country\_samplecprn}\\
+ \hline
+  \multicolumn{8}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & -.04 \; (0.34) & -.04 \; (0.34) & -.05 \; (0.37) & -.13 \; (0.36) & -.37 \; (0.46) & -.21 \; (0.44) \\ 
+   & Gender - Couple & -.14 \; (0.32) & -.14 \; (0.34) & -.09 \; (0.35) & -.07 \; (0.33) & .21 \; (0.43) & -.04 \; (0.39) \\ 
+   & Founder died & .28 \; (0.43) & .18 \; (0.44) & .07 \; (0.46) & .22 \; (0.44) & -.11 \; (0.58) & .25 \; (0.54) \\ 
+   \multicolumn{8}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .20 \; (0.41) & .34 \; (0.45) & .22 \; (0.47) & .14 \; (0.43) & .32 \; (0.68) & .50 \; (0.55) \\ 
+   & Self-Identification - Collection & -.45 \; (0.54) & -.34 \; (0.57) & -.54 \; (0.57) & -.45 \; (0.55) & -.73 \; (0.85) & -.51 \; (0.76) \\ 
+   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.18 \; (0.35)^{***} & .96 \; (0.36)^{**} & 1.13 \; (0.31)^{***} & 1.25 \; (0.57)^{*} & 1.53 \; (0.41)^{***} \\ 
+   & AN Ranking - Included & .19 \; (0.34) & .17 \; (0.36) & .10 \; (0.37) & .19 \; (0.35) & .10 \; (0.44) & .23 \; (0.41) \\ 
+   & AN Ranking - Dropped & .46 \; (0.50) & .42 \; (0.50) & .43 \; (0.51) & .43 \; (0.50) & .59 \; (0.62) & .47 \; (0.58) \\ 
+   & Founder name in Museum name & .05 \; (0.28) & .08 \; (0.29) & .18 \; (0.29) & .17 \; (0.29) & -.40 \; (0.41) & -.36 \; (0.37) \\ 
+   \multicolumn{8}{l}{\textbf{Environment}} \\ 
+ & Region - Asia &  & -1.24 \; (1.08) &  &  &  &  \\ 
+   & Region - Europe &  & -1.46 \; (1.06) &  &  &  &  \\ 
+   & Region - Latin America &  & -.66 \; (1.12) &  &  &  &  \\ 
+   & Region - North America &  & -1.11 \; (1.09) &  &  &  &  \\ 
+   & Region - Oceania &  & -.85 \; (1.27) &  &  &  &  \\ 
+   & UN Subregion - Eastern Europe &  &  & .04 \; (0.64) &  &  &  \\ 
+   & UN Subregion - Southern Europe &  &  & -1.06 \; (0.62) &  &  &  \\ 
+   & UN Subregion - Eastern Asia &  &  & -1.30 \; (0.69) &  &  &  \\ 
+   & UN Subregion - South-eastern Asia &  &  & .65 \; (0.79) &  &  &  \\ 
+   & UN Subregion - Western Europe &  &  & -.64 \; (0.54) &  &  &  \\ 
+   & UN Subregion - Latin America and the Caribbean &  &  & .45 \; (0.61) &  &  &  \\ 
+   & UN Subregion - Western Asia &  &  & .58 \; (0.58) &  &  &  \\ 
+   & UN Subregion - Northern Europe &  &  & .21 \; (0.58) &  &  &  \\ 
+   & Country - Greece &  &  &  &  & -.33 \; (1.10) &  \\ 
+   & Country - Germany &  &  &  &  & -.60 \; (0.65) &  \\ 
+   & Country - France &  &  &  &  & .49 \; (0.76) &  \\ 
+   & Country - South Korea &  &  &  &  & -.04 \; (0.79) &  \\ 
+   & Country - Japan &  &  &  &  & -.72 \; (1.21) &  \\ 
+   & Country - China &  &  &  &  & -1.36 \; (1.39) &  \\ 
+   & Country - Belgium &  &  &  &  & -.19 \; (1.15) &  \\ 
+   & Country - Brazil &  &  &  &  & 1.17 \; (0.77) &  \\ 
+   & Country - Italy &  &  &  &  & -.20 \; (0.73) &  \\ 
+   & Country - Spain &  &  &  &  & -.36 \; (0.86) &  \\ 
+   & Country - United Kingdom &  &  &  &  & .53 \; (0.74) &  \\ 
+   & Country - Switzerland &  &  &  &  & 1.34 \; (0.70) &  \\ 
+   & Country - Russia &  &  &  &  & .85 \; (0.74) &  \\ 
+   & PM density (country) & .65 \; (0.34) & .87 \; (0.36)^{*} & 1.73 \; (0.83)^{*} & .73 \; (0.34)^{*} &  &  \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.04 \; (0.03) & -.30 \; (0.27) & -.03 \; (0.02) &  &  \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .28 \; (0.10)^{**} & .41 \; (0.14)^{**} & .35 \; (0.10)^{***} & .42 \; (0.18)^{*} & .30 \; (0.12)^{*} \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} & .27 \; (0.08)^{***} & .26 \; (0.09)^{**} & .26 \; (0.08)^{***} & .48 \; (0.12)^{***} & .35 \; (0.09)^{***} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.09 \; (0.04)^{**} & -.09 \; (0.03)^{**} & -.16 \; (0.05)^{**} & -.11 \; (0.04)^{**} \\ 
+   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.58 \; (1.01) & -1.46 \; (1.01) & -1.51 \; (1.01) & -18.01 \; (4506.35) & -17.10 \; (3040.09) \\ 
+   & Covid Pandemic (2020/21) & .42 \; (0.29) & .42 \; (0.29) & .41 \; (0.31) & .40 \; (0.30) & .79 \; (0.35)^{*} & .64 \; (0.34) \\ 
+   \hline
+ & Museums & 503 & 503 & 476 & 476 & 373 & 373 \\ 
+   & Museum-years & 6096 & 6096 & 5819 & 5819 & 4610 & 4610 \\ 
+   & Closures & 68 & 68 & 65 & 65 & 45 & 45 \\ 
+   & log. Likelihood & -339.68 & -337.93 & -310.02 & -319.17 & -186.68 & -193.26 \\ 
+   & AIC & 711.35 & 717.87 & 668.04 & 670.35 & 427.37 & 414.51 \\ 
+   & BIC & 746.87 & 764.48 & 720.22 & 705.14 & 476.15 & 439.81 \\ 
+   \hline 
+ \multicolumn{8}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
+\hline
+\caption{Cox PH regression results with different region dummies included} 
+\label{tbl:t_reg_coxph_reg}
+\end{longtable}
+\endgroup
+\end{landscape}
+
+As private museum closing might depend on particular country- or region-level factors, table \ref{tbl:t_reg_coxph_reg} shows a number of Cox Proportional Hazard regression models results with different sets of dummy variables.
+In particular, dummy variables are added for UN region code (with a minor modification of splitting the Americas into North and Latin America according to the UN subregion codes and reference category of Africa), the UN subregion code itself (with reference category of Northern America), as well as country level (with reference category of United States).
+For models with country-dummies, country-level private museum density variables are removed as the high collinearity led to unreasonably high country-dummy estimates.
+As many countries and some UN subregions have too few private museums for the model to converge correctly, the dataset is reduced to include only regions or countries with 10 or more private museums (in the case of country2, 15 private museums).
+To identify whether any change in coefficients is due to addition of variables or exclusion of cases, a separate model with the same restricted sample but without region/country dummies is included.
+
+None of the models show a significant region or country dummy variables, nor substantial changes of the coefficients of the main predictors (a minor change is that the addition of country dummies results in a significant coefficient for the Covid-19 pandemic).
+While log-likelihood decreases by definition, model fit indices (AIC and BIC) that penalize inclusion of additional variables indicate worse fit for models with region/country dummies, except in the case of the AIC for the inclusion of UN subregion dummies, where a small improvement is observed.
+Taken together, these results indicate little support for an importance of time-invariant contextual factors on the level of the region or country on private museum survival. 
+\subsection*{Measurement of museum-level variables}
+
+\ref{fig:p_vrblcvrg_ratio}
+Figure \ref{fig:p_vrblcvrg_ratio} shows the variable coverage by whether a museum is open or closed at the status of data collection (2020-2022).
+Not only is coverage on most variables far from complete, which would already make it difficult to construct indicators of them, but variable coverage is substantially worse for closed museums than for open museums, especially variables related to the collection, operation, relations to other actors and social media.
+In principle it is possible to treat absence of evidence as evidence of absence, and assume that not measuring the presence of e.g.
+temporary exhibitions, educational events, restaurants or cooperations means that these are absent.
+
+Under this assumption, based on variables where an absence is a plausible value (i.e.
+not including variables such as floor size, collection size or opening times) a principal component analysis was performed.
+figure FIXME
+
+and the two first factors included in the regression results.
 \end{document}

### 2024-09-26 scripts/closing_main.R

@@ -373,8 +373,10 @@ l_mdlnames_env <- c("r_pop4", "r_pmdens1", "r_pmdens2", "r_audience1", "r_audien
 ## including exhibition data (Artfacts)
 l_mdlnames_af <- c("r_pop4", "r_exhbany", "r_exhbroll")
 
-l_mdlnames_reg <- c("r_pop4", "r_reg6", "r_regsub", "r_regsub2", "r_regsub2_samplecprn",
-                    "r_country", "r_country_samplecprn", "r_country2", "r_country2_samplecprn")
+l_mdlnames_reg <- c("r_pop4", "r_reg6", "r_regsub2", "r_regsub2_samplecprn",
+                    "r_country", "r_country_samplecprn") # "r_country2", "r_country2_samplecprn")
+
+
 
 ## improvement by adding variables
 dt_drop1 <- gd_drop1(l_mdls)

### 2024-09-26 scripts/regression.R

@@ -2439,7 +2439,15 @@ gt_reg_coxph_comp <- gt_reg_coxph
 gt_reg_coxph_dens <- gt_reg_coxph
 gt_reg_coxph_env <- gt_reg_coxph
 gt_reg_coxph_af <- gt_reg_coxph
-gt_reg_coxph_reg <- gt_reg_coxph
+
+
+gt_reg_coxph_reg <- function(l_mdls, l_mdlnames) {
+    c(gt_reg_coxph(l_mdls, l_mdlnames),
+      list(tabenv = "longtable", size = "small")) ## scalebox = 0.8), )
+}
+
+
+
 
 gt_coxzph <- function(rx) {
     gw_fargs(match.call())

### 2024-09-26 texts/paper_closing.tex
rewrite mortality comparison into descriptive results

@@
-% Created 2024-09-11 wo 15:33
+% Created 2024-09-26 do 18:56
 % Intended LaTeX compiler: pdflatex
@@
 A newly constructed database, assembled from a wide range of sources, is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
-Currently, the database includes 548 museums, of which 451 are currently open, 72 have closed and 25 have transformed into other organizational forms.\footnote{The 25 institutions which were private museums at some point and have since been transformed into other organizational forms are not included in this analysis and discussed in the limitations.}
+Currently, the database includes 550 museums, of which 453 are currently open, 72 have closed and 25 have transformed into other organizational forms.\footnote{The 25 institutions which were private museums at some point and have since been transformed into other organizational forms are not included in this analysis and discussed in the limitations.}
 Using this database, in particular year of opening and, if available, closing, it is possible to reconstruct the life course of the each institution with museum-year as the unit of analysis.
@@
 As the databse was constructed retrospectively from 2020 to 2022, I focus here on closing events from 2000 to 2021 to limit the possibility that some institutions were missed, as such risks are likely higher for earlier time periods.
-Furthermore, a small number of museums are excluded, in particular 2 museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), 1 museum the opening year of which could not be determined, as well as 2 museums which closed before 2000 and thereby fall outside the period under investigation.
+Furthermore, a small number of museums are excluded, in particular 2 museums for which the closing date could not be found, 17 museums which opened in 2021 and later (as survival analyses requires positive survival times), 1 museum the opening year of which could not be determined, as well as 2 museums which closed before 2000 and thereby fall outside the period under investigation.
 This leaves 503 private museums at risk which have accumulated 6096 museum-years and 68 closures.
 This data allows to conduct survival analysis (also known as event history analysis), the most common statistical technique to investigate hazard rates and identify mortality-assocated covariates \parencite{Moore_2015_survival,Allison_2014_event}.
-
-Hypothesis 1 (comparing closing risk between private museums and other, more diversified institutions) ideally would use a complete population of museums to identify the effect of institutional form on closing rate.
-However, as no institutions are maintaining museum databases on a global scale, I use existing quantitative studies of museum closure to compare to these private museums in terms of their closing rates.
-This non-parametric method estimates the hazard rate as the conditional probability of exiting at time t\textsubscript{i} given being alive as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at time \(t_i\) and \(d_i\) as the number of exits at time \(t_i\)).
-Hazards can be calculated over calendar time (thus comparing closures in a given year to museums being open in that year) or over age (comparing closures at a given age to museums being open at that age), the latter is the more prevalent approach in survival analysis as it allows to calculate the survival function as the product of conditional survival probabilities as \(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\).
 
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:49:38 2024
+% Tue Sep 17 14:48:46 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:49:37 2024
+% Tue Sep 17 14:48:45 2024
 \begin{table}[ht]
@@
 Table \ref{tbl:t_sumstats} shows summary statistics for all variables.
-\subsubsection*{Comparing private museum hazard rates to previous studies}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=16cm]{../figures/p_hazard_time.pdf}
-\caption{\label{fig:p_hazard_time}Private Museum hazard function by year}
-\end{figure}
-
-While typically in survival analysis closing risk is seen as a function of age, previous studies have not done so, instead focusing on average yearly closing rates.
-To ensure comparability with these, I first analyze closing rates the same, and discuss age-related closing rate below.
-Summarizing yearly closing proportions results in an average closing rate of 0.84\%; i.e.
-on average each year 0.84\% of the private museum population closes (weighing the yearly mortality rate by number of museums at risk results in an estimate of 1.12\%).
-It is worth pointing out however that closing rates appear to vary substantially over time (figure \ref{fig:p_hazard_time}); with an average closing rate of 0.21\% from 2000 to 2010 (with only 4 closures taking place in that time period), and a rate of 1.36\% from 2010 onwards.
-
-\begin{table}[htbp]
-\caption{\label{tbl:litreview}Hazard rates in studies of museums survival}
-\centering
-\begin{tabular}{lll}
-\hline
-Study & Population & Average Yearly Closings\\
-\hline
-\cite{Hager_2001_vulnerability} & Art Museums & 1.9\%\\
-\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\%\\
-\cite{Bowen_etal_1994_charitable} & Museums & 1.1\%\\
-current study & Private Art Museums & 0.84\% (overall)\\
- &  & 1.36\% (2010-2021)\\
- &  & 1.12\% (weighted)\\
-\hline
-\end{tabular}
-\end{table}
-
-\FloatBarrier
-
-While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview}).\footnote{IRS data is not without limitations, such as only being required from larger organizations, misreporting, and the difficulty of inferring closing from non-filing.
-Nevertheless, it constitutes the most fine-grained data source to investigate non-profit survival}
-None of these focus on art museums exclusively (\textcite{Hager_2001_vulnerability} focuses on Art NPOs, \textcite{Bowen_etal_1994_charitable} and \textcite{Gordon_etal_2013_insolvency} on NPOs generally), but report survival estimates by organizational form, including museums.
-\textcite{Bowen_etal_1994_charitable} investigates the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
-\textcite{Gordon_etal_2013_insolvency} observes 35 closures over the years of 2000-2003 with 5,167 museum-years (p.368), resulting in an average annual closing rate of 0.68\% (p.377).
-Some of this difference may be explained by higher shares of smaller organizations in \textcite{Bowen_etal_1994_charitable}, where museums of any size are included, whereas \textcite{Gordon_etal_2013_insolvency} excluded NPOs with operational revenues below 150,000 USD, as smaller non-profits are at higher risk of closing \parencite{Harrison_Laincz_2008_nonprofit,Helmig_Ingerfurth_Pinz_2013_nonprofit}.
-
-Focusing directly on Art museums, rather than museum generally as part of the wider focus on Art NPOs, \textcite{Hager_2001_vulnerability} observes 42 closures over a period of 4 years (1994-1997) from a starting populaton of 448 (p.383).
-As his way of delineating the population (having "filed an annual Form 990 tax return with the IRS for the 1990, 1991, or 1992 tax year", p.380) does not rule out that some closings took place in 1991, 1992 or 1993\footnote{In particular it is unclear why 1993 is not treated as belonging to the observation period}, attributing some closings to these years is likely appropriate, and presumably roughly equivalent to assuming an observation period of five (rather than four) years, which corresponds to an average yearly closing rate of 1.9\%.\footnote{So far it is hard to tell why art museums appear to have higher closing rates than museums generally.
-According to the \textcite{IMLS_2008_funding}, art museums have above-average reliance on earned income (46.1\% compared to 43.7\% on average, p.26), and \textcite{Bowen_etal_1994_charitable} argue that a higher reliance on income is associated with higher exit rates (p.102), but it is questionable whether such an a small difference in percent earned can explain a 1.7-2.7 times higher closing risk.
-Similarly, while art museums do not have the largest coffers (in particular museums of natural history and science are substantially larger \parencite{IMLS_2008_funding,Bowen_etal_1994_charitable}), art museums have substantially higher incomes than the history museums (which are more frequent), historical societies and botanical gardens \parencite{IMLS_2008_funding} as well as "other museums" with more specialized and/or local focuses \parencite{Bowen_etal_1994_charitable}.
-Especially the larger number of history museums, and the more restrictive inclusion by \textcite{Hager_2001_vulnerability} in comparison to \textcite{Bowen_etal_1994_charitable} make the higher mortality rate for art museums than museums generally puzzling.}
-
-Results are combined in table \ref{tbl:litreview}.
-Average annual closing rates fall within closing rates found in previous studies, and even the 2010-2021 time periods with higher risk is below the general estimate for art museums by \textcite{Hager_2001_vulnerability}.
-There is thus overall little evidence that private museums are exposed to higher closing risk than non-profit museums generally, which provides little support for hypothesis 1.
 \subsubsection*{Hazard rate and Age Dependence}
@@
 
-Next to average yearly closing rates, private museum closing can also be investigated over its age (no comparison to previous studies can be done these did not report age-dependent mortality estimates).
+Before discussing the regression models, I provide a descriptive account on private museum closure using the hazard and survival functions which describe variation the closing risk over the museum life-course.
+The hazard rate is a non-parametric function which describes the probability of exiting at age \(t_i\) (conditional on being alive) as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at age \(t_i\) and \(d_i\) as the number of exits at age \(t_i\)).
+The survival function is the product of these conditional probabilities (\(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\)) and describes the chance of surviving up to age \(t_i\).
+
 Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
@@
 Such analysis can be used to estimate the average life expectancy of a private museum.
-While only a fraction of all opened museums has closed (68 out of 503), under the assumption of average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, median life expectancy can be estimated as approximately 52 years.
-On first sight such findings seems to differ from a previous quantitative analysis of the same data used here, which argued that "the median number of years that private museums were open before they closed is 10 years" \parencite[p.5]{Velthuis_Gera_2024_fragility}, as previously only closed museums were considered.
-Focusing on the entire population of private museums instead, this analysis provides additional insights into the expected longevity of private art museums.
+While only a fraction of all opened museums has closed (68 out of 503), and even the complete survival function has not reached 0.5, under the assumption of average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, it is possible to predict the median life expectancy as approximately 52 years (yet as only around half of this range is observed for a large number of museums, the certainty of such measurement is clearly limited).
+
+It cannot be asserted with great certainty whether such a hazard rate and median survival time is substantially different from institutions of comparable size that differ only in whether they are set up by a private art collector.
+While a small number of studies has investigated museum closing rates, these have focused on the United States, likely primarily due to data availability reasons: 
+Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form data is publicly available \parencite{Lecy_2023_core,Lecy_2023_core}.
+This data source has been used by three studies to investigated museum closure, which calculate hazard rates not over age but over calendar year:
+\begin{itemize}
+\item \textcite{Bowen_etal_1994_charitable} investigate the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
+\item \textcite{Gordon_etal_2013_insolvency} observe 35 closures over the years of 2000-2003 with 5,167 museum-years (p.368), resulting in an average annual closing rate of 0.68\% (p.377).
+\item \textcite{Hager_2001_vulnerability} has conducted the only study specifically on art museums (NTEE code A51); he observes 42 closures over a period of four years (1994-1997) from a starting populaton of 448 (p.383), corresponding to an average yearly closing rate of 2.4\%, or around 1.9\% under the more realistic assumption of effectively using a five-year time period.
+\end{itemize}
+
+Construcing private museum closing rates in a similar manner (as average of proportion closed each calendar year, rather than at each age) results in average closing rates of 0.84\% overall, 1.36\% for the period 2010-2011 and 1.12\% when weighing yearly closing proportions by the number of museums at risk.
+Private museum closing rates thus do not appear substantially higher than the range of possible values established by previous studies, and in particular not higher than the closing rate of the most direct comparison group of art museums by \textcite{Hager_2001_vulnerability}.
+
+However, a number of limitations complicate such a comparison.
+First, this measure of overall museum closing rates cannot take museum-level variables into account, thus direct comparability hinges on the assumption that on private museums display a similar distribution of survival-relevant attributes to US non-profit museums.
+More specifically, private museums might have such disproportionately high assets and/or revenues that the appropriate comparison group would not be the entire (art) museum population, but rather only its in wealthiest half, third or quarter, which in turn could be characterized by substantially higher survival rates (such a size difference likely explains the difference between the hazard rates of \textcite{Gordon_etal_2013_insolvency} and \textcite{Bowen_etal_1994_charitable}, as the former only includes museums with operational revenues above 150,000 USD).
+Secondly, as previous studies have focused exclusively on the US, survival rates for non-profits in other countries might differ, for example in particular in Europe one possible reason might be more public support for non-profits.
+While additional analyses, reported in the supplementary materials, do not indicate a substantial influence of time-invariant country (or region) factors on private museum closing, mortality of other, non-private museums might be stronger influenced by these country-level factors.
+Thirdly, a number of limitations of form 990 data might lead to inaccurate mortality estimates in the first place.
+As closure is generally estimated from non-filing for a number of years, incorect closing assessments and mortality estimates can arise as organizations continue operations without filing, file but continue to exist only on paper, or transform, leading to records of multiple organizations while effectively only a single organization exists.
+Taken together, these factors substantially limit the extent to which a lack of difference in closing rates between private museum and American non-profit museums in general is indicative of similar sustainability of these different organizational populations.
 \subsubsection*{Regression Results}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:49:55 2024
+% Thu Sep 26 17:44:59 2024
 \begin{table}[ht]
@@
    \hline 
- \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
 \end{tabular}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep  6 15:49:42 2024
+% Tue Sep 17 14:48:50 2024
 \begin{table}[ht]

### 2024-09-27 texts/paper_closing.tex
further rewrite results

@@
-% Created 2024-09-26 do 18:56
+% Created 2024-09-27 vr 11:25
 % Intended LaTeX compiler: pdflatex
@@
 
-\bigbreak
-\noindent
 While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{diMaggio_1982_boston,Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than e.g.
@@
 Before discussing the regression models, I provide a descriptive account on private museum closure using the hazard and survival functions which describe variation the closing risk over the museum life-course.
-The hazard rate is a non-parametric function which describes the probability of exiting at age \(t_i\) (conditional on being alive) as \(h(t_i) = \frac{d_i}{n_i}\), (with \(n_i\) as the number of units at risk at age \(t_i\) and \(d_i\) as the number of exits at age \(t_i\)).
+The hazard rate is a non-parametric function which describes the probability of exiting at age \(t_i\) (conditional on being alive), in the context of museum-years as units of analysis it can be formulated as \(h(t_i) = \frac{d_i}{n_i}\), with \(n_i\) as the number of units at risk at age \(t_i\) and \(d_i\) as the number of exits at age \(t_i\).
 The survival function is the product of these conditional probabilities (\(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\)) and describes the chance of surviving up to age \(t_i\).
@@
 
-It cannot be asserted with great certainty whether such a hazard rate and median survival time is substantially different from institutions of comparable size that differ only in whether they are set up by a private art collector.
-While a small number of studies has investigated museum closing rates, these have focused on the United States, likely primarily due to data availability reasons: 
+Calculating such survival statistics allows (to a degree) to assess whether private museums differ in their longevity from comparable institutions.
+So far only a small number of studies has investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
 Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form data is publicly available \parencite{Lecy_2023_core,Lecy_2023_core}.
-This data source has been used by three studies to investigated museum closure, which calculate hazard rates not over age but over calendar year:
+This data has been used in many studies of non-profit populations, and constitutes an effective comparison group for private museums as both share the same organizational form (non-profit) and unprofitable cultural sector environment.
+So far three studies have used this data to investigate museum closure by calculating hazard rates not as a function of age age but of calendar year:
 \begin{itemize}
@@
 Construcing private museum closing rates in a similar manner (as average of proportion closed each calendar year, rather than at each age) results in average closing rates of 0.84\% overall, 1.36\% for the period 2010-2011 and 1.12\% when weighing yearly closing proportions by the number of museums at risk.
-Private museum closing rates thus do not appear substantially higher than the range of possible values established by previous studies, and in particular not higher than the closing rate of the most direct comparison group of art museums by \textcite{Hager_2001_vulnerability}.
+Private museum closing rates thus do not appear substantially higher than the range of possible values established by previous studies, and in particular not higher than the closing rate of the most direct comparison group of non-profit art museums by \textcite{Hager_2001_vulnerability}.
 
@@
 Secondly, as previous studies have focused exclusively on the US, survival rates for non-profits in other countries might differ, for example in particular in Europe one possible reason might be more public support for non-profits.
-While additional analyses, reported in the supplementary materials, do not indicate a substantial influence of time-invariant country (or region) factors on private museum closing, mortality of other, non-private museums might be stronger influenced by these country-level factors.
+While additional analyses, reported in the supplementary materials, do not indicate a substantial influence of time-invariant country (or region) factors on private museum closing, mortality of non-private museums might be stronger influenced by these country-level factors.
 Thirdly, a number of limitations of form 990 data might lead to inaccurate mortality estimates in the first place.
-As closure is generally estimated from non-filing for a number of years, incorect closing assessments and mortality estimates can arise as organizations continue operations without filing, file but continue to exist only on paper, or transform, leading to records of multiple organizations while effectively only a single organization exists.
+As closure is generally estimated from non-filing for a number of years, incorect closing assessments and mortality estimates can arise as organizations continue operations without filing, file but continue to exist only on paper, or transform thus producing records of several organizations while effectively only a single organization exists.
 Taken together, these factors substantially limit the extent to which a lack of difference in closing rates between private museum and American non-profit museums in general is indicative of similar sustainability of these different organizational populations.

### 2024-09-27 texts/paper_closing.tex
add diversification/reputation paragraphs, yeet comparison to non-PM, minor rephrasings

@@
-% Created 2024-09-27 vr 11:25
+% Created 2024-09-27 vr 16:13
 % Intended LaTeX compiler: pdflatex
@@
 Outside of the United States, the reliance on revenue streams beyond operations is even larger:
-German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table p.233}, with private museums however requiring less support as operations provide around 47\% of their budget (ibid.), and even the more market-oriented NPOs in the cultural sector draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
+German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table p.233}, with private museums however requiring less support as operations provide around 47\% of their budget (ibid.).
+In the Germany cultural sector, non-profit organizations more widely  draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
 On a European level, only 12\% of museum incomes are generated by entry fees, whereas 69\% originate from subsidies \parencite{EGMUS_2024_complete}.\footnote{Own calculations from on EGMUS data, based on all countries with income data from 2015 onwards.}
@@
 \textcite{Bechtler_Imhof_2018_future} also characterize "the dependency on single individuals only" as one of main reasons that "make these private museums fragile" (p.53).
-\textcite{StylianouLambert_etal_2014_museums} also characterize many private institutions as "small individual museums that depend too much on their creators to guarantee their sustainability" (p.582).
+\textcite{StylianouLambert_etal_2014_museums} similarly describe many private institutions as "small individual museums that depend too much on their creators to guarantee their sustainability" (p.582).
 Beyond a direct financial component, private museums have been also been characterized as fragile since they can only rely on their founder for "taste", "vision and drive" \parencite[p.77]{Adam_2021_rise}, "passion" \parencite[p.234]{Walker_2019_collector} or "skills and knowledge" \parencite[p.580]{StylianouLambert_etal_2014_museums}.
-The link between diversification and mortality, i.e.
-higher survival chances for more diversified organizations, has been found for non-profit organizations more generally \parencite{Fernandez_2007_dissolution,Bielefeld_1994_survival,Hager_2001_vulnerability,Lu_Shon_Zhang_2019_dissolution}; it is thus plausible to apply to museums as well.
+
+Existing research on private museum is conducted primarily by scholars of the art field or market as well as art historians.
+Nethertheless, the identification of the centrality of the founder as a critical source of vulnerability corresponds strongly to the finding in non-profit management of a relation between diversification and mortality \parencite{Tuckman_Chang_1991_vulnerability}.
+For example, \cite{Bielefeld_1994_survival} finds that nonprofits with a larger number of funding sources (e.g.
+from foundations, individuals, federated funders, corporations, trusts, government at federal, state, county and municipal level as well as self-generated sources such as dues, interests, and service revenue, p.31) are more likely to survive.
+Other studies have measured diversification as the Herfindahl Index (a measure of concentration) of income sources such as public support, program service revenues, dues and assessments, net fundraising income and profits from sale of inventory \parencite[p.381]{Hager_2001_vulnerability} or contributions, program service revenue, investment income, other revenues \parencite[p.37]{Lu_Shon_Zhang_2019_dissolution}, with both studies finding a positive association between diversification and survival; in the case of \cite{Hager_2001_vulnerability} also specifically for art museums.
+Next to diversification, volatility, i.e. fluctuation in revenue streams has been associated with mortality as well \parencite{Mayer_2022_simmer}.
+Despite limited reception of this research stream in the private museum literature, identifying the high reliance on the founder as a source of risk thus corresponds to management insights.
 
@@
 \textcite{Walker_2019_collector} argues that "the death of the original founder and creator can [\ldots{}] place the future of private museums and collections in jeopardy" as "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museums indefinitely" (p.234).
-\textcite{Bechtler_Imhof_2018_future} argue that in order to ensure museum longevity, "flexible, easily adapted designs for private museums" are necessary "to reduce the financial burden on their heirs" (p.188).
-\textcite{Adam_2021_rise} argues that succession introduces strains in financial aspects ("Collectors’ successors may not look kindly on what may well be a money pit when [\ldots{}] they will have to pick up the bills", p.77), which also concerns an aesthetic dimension ("the nature of contemporary art is to be fresh and new, but what is ‘fresh and new’ for the founder might seem ‘old hat’ to their heirs", p.76).
+\textcite{Bechtler_Imhof_2018_future} argue that in order to ensure private museum longevity, "flexible, easily adapted designs for private museums" are necessary "to reduce the financial burden on their heirs" (p.188).
+\textcite{Adam_2021_rise} argues that succession introduces financial strains as "collectors’ successors may not look kindly on what may well be a money pit when [\ldots{}] they will have to pick up the bills" (p.77), and also highlights the aesthetic dimension as "the nature of contemporary art is to be fresh and new, but what is ‘fresh and new’ for the founder might seem ‘old hat’ to their heirs".
+(p.76).
 \textcite{Velthuis_Gera_2024_fragility} similarly argue that "the founder’s death will almost inevitably have a direct impact on the financial health of the museum" (p.10).
@@
 
-Overall, two related arguments emerge from the current literature on private museum sustainability:
-First, individual private museums heavily rely on their founders for survival; events that interrupt the founders ability to provide resources are therefore associated with a highler likelihood of closing.
-Second, due to their low diversification (high reliance on the founder), private museums are more fragile than museums where single individuals are not comparably central figures.
+Private museums heavily rely on their founders for survival; events that interrupt the founders ability to provide resources are therefore associated with a highler likelihood of closing.
 
-While private museums are thus generally characterized as fragile, it is not always clear in relation to whom.
-Among the most explicit is \textcite{Walker_2019_collector}, who characterizes public institutions as relatively stable (which constitutes the reason why private collectors aim to form cooperations with them); \textcite{Bechtler_Imhof_2018_future} implicitly also highlight the longevity of state-run institutions.
-However, no systematic data is used to estimate public museum longevity, and while some
-remarks are made that public spending cuts might result in problems for public museum operations (p.233), the overall characterization of them remains as immortal \parencite{Frey_Meier_2002_beyeler}.
-Responsible for the characterization of private museums as fragile might also be implicit reliance on the ICOM definition \parencite{ICOM_2024_definition} of museums as "permanent institutions" (according to which every closing is indicative of fragility), which is echoed by an interviewee of \textcite{Walker_2019_collector} who expresses (his perspective on) the prevalent perspective as "we assume museums are forever" (p.235).
-So far a third comparison has been absent, namely that to other non-profit museums which are not initiated and run by a single collector, but by a wider group of founders, foundations or associations.
-As these share with private museums a common organizational form of the non-profit organization or foundation  and the same harsh environment of the cultural sector where operations cannot sustain an organization, yet differ primarily in regards to their diversification, i.e.
-their reliance on a single founder as central authority and income stream, they provide a effective way of investigating the effect of diversification on museum survival.
+\textbf{Hypothesis 1}: Events which disrupt the founder's ability to provide resources to their private museums increase the risk of closing, in particular:
 
-\textbf{Hypothesis 1}: Private museums have higher closing chance than non-profit museums generally.
+The death of the founder is a clearly financial and organizational disruption for the museum, and as previous research has seen it as a precursor of museum closure, a hypothesis can be formulated as: 
+\textbf{Hypothesis 1a}: Private museums are more likely to close after the death of the founder.
 
-\textbf{Hypothesis 2}: Reliance on the founder is the mechanism through which PMs are exposed to a higher closing risk, thus founder-related variables predict closing, in particular: 
-\begin{itemize}
-\item \textbf{Hypothesis 2a}: Private museums are more likely to close after the death of the founder.
-\item \textbf{Hypothesis 2b}: Private museums are more likely to close after their founder is excluded from a prestigious ranking.
-\item \textbf{Hypothesis 2c}: Private museums which carry their founder's name in the museum name are more likely to close.
-\end{itemize}
+A less obvious yet possibly impactful event that can jeopardize a founder's ability to sustain their museum and potentially shorten its lifespan is a decline of status of the collector within the art world.
+Recognition bestowed by prominent art world authorities confers the acknowledgment of "cultural expertise" \parencite[p.1486]{Braden_2016_recognition}, thus validating the collector-founder's refined taste, which constitutes a form symbolic capital that might yield tangible benefits \parencite{Bourdieu_1993_production}.
+This symbolic capital might provide opportunities to acquire material advantages such as collaborations with other institutions and access to broader audiences, ultimately bolstering the museum's longevity.
+
+In the face of a loss of recognition, the consequences can extend beyond the personal demotivation it may cause the founder.
+Such a decline could also curtail potential opportunities for cooperation with other institutions and limit the museum's reach to larger audiences, thus posing a risk to the museum's continued operation and survival in the long term.
+\textbf{Hypothesis 1b}: Private museums are more likely to close after a decline of their founder's status, measured by exclusion from a prestigious ranking.
 
@@
 While some of these aspects can be influenced by the founder (in particular the museum's location and strategies) , other are less so.
-In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
+In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship and funding choices, the influence of the individual founder is severely limited.
 \paragraph*{Competition}
@@
 Quantitative studies have identified a relation between competition and non-profit closing primarily via measuring competition over density \parencite{Park_Shon_Lu_2021_mortality,Haugh_etal_2021_nascent,Lu_Shon_Zhang_2019_dissolution}, with higher number of non-profits increasing the chance of non-profit dissolution.
+Thus, a hypothesis regarding competition can be formulated as:
 
@@
 
-The mere availability of audiences and other potential donors might however not be sufficient if a museum is not perceived as deserving support; i.e. if its identity is found lacking. 
+The mere availability of audiences and other potential donors might however not be sufficient if a museum is not perceived as deserving support; i.e. if its identity is perceived as inappropriate. 
 An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
@@
 \cite{Hsu_2015_granted,Bogaert_etal_2014_ecological}), a clear and positive identity might be helpful in a number of ways:
-In the context of private museums, decline of legitimacy or reputation could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
+In the context of private museums, a negative identity could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
 
@@
 
-It is however necessary to consider that in particular the name of a museum might be associated with a museum's survival via identity, but also reflect founder intentions regarding the institutions longevity.
-This is discussed in more detail below.
-Furthermore, inferring the status of the museum via the reputaton of the founder again explores the extent to which the founder is a figure of central importance for the private museum.
+It is however necessary to consider that in particular the name of a museum might be associated with a museum's survival via identity, but also reflect founder intentions regarding the institutions longevity; this possibility is discussed in more detail in the results section.
 \subsection*{Methods and Data}
@@
 
-Hypothesis 2 to 4, which differentiate the private museum population according to a number of risk factors, are investigated via Cox proportional hazard models. 
-The dependent variable is indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
+In particular, Cox proportional hazard models allows to identify the risk that a number of variables pose for a museum's chance of closing. 
+The dependent variable is an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
 Typically for survival data, museums that do not close during the observation period are right-censored, i.e.
@@
 Thirdly, a number of limitations of form 990 data might lead to inaccurate mortality estimates in the first place.
-As closure is generally estimated from non-filing for a number of years, incorect closing assessments and mortality estimates can arise as organizations continue operations without filing, file but continue to exist only on paper, or transform thus producing records of several organizations while effectively only a single organization exists.
+As closure is generally estimated from non-filing for a number of years, incorect closing assessments and mortality estimates can arise as organizations continue operations without filing, file but continue to exist only on paper, or transform thus producing records of several organizations while effectively only a single organization exists \parencite{Bielefeld_1994_survival}.
 Taken together, these factors substantially limit the extent to which a lack of difference in closing rates between private museum and American non-profit museums in general is indicative of similar sustainability of these different organizational populations.

### 2024-09-27 scripts/cfg.R
include PC for sup materials, minor rewrite of gc_tbls, add PC plts to gc_plts

@@ -16,14 +16,12 @@ gc_clgrphattrs <- function() {
 }
 
 gc_tbls <- function(c_tblargs) {
-    list(
+
+    l_tblcfgs_mnl <- list(
         t_coxzph = list(
             rx = quote(l_mdls$r_pop4),
             caption = "Z-test of proportional hazards"),
-        t_reg_coxph = list(
-            l_mdls = quote(l_mdls),
-            l_mdlnames = quote(l_mdlnames_coxph), # FIXME: gw_fargs should be able to handle vectors
-            caption = "Cox Proportional Hazards Regression Results"),
+        ## FIXME: gw_fargs should be able to handle vectors
         t_sumstats = list(
             dt_pmyear = quote(dt_pmyear),
             dt_pmcpct = quote(dt_pmcpct),
@@ -32,47 +30,43 @@ gc_tbls <- function(c_tblargs) {
             dt_pmx = quote(dt_pmx),
             dt_pmyear = quote(dt_pmyear),
             caption = "Selfidentification"),
-        t_reg_coxph_density = list(
-            l_mdls = quote(l_mdls),
-            l_mdlnames = quote(l_mdlnames_coxph_density),
-            caption = "Cox PH models of different local density specifications"),
-        t_reg_coxph_timeslice = list(
-            l_mdls = quote(l_mdls),
-            l_mdlnames = quote(l_mdlnames_timeslice),
-            caption = "Cox PH regression results with different time slices"),
         t_reg_coxph_deathcfg = list(
             l_mdls = quote(l_mdls),
-            ## l_mdlnames = quote(l_mdlnames_deathcfg),
-            caption = "Cox PH regression results wiht different death configurations"),
+            caption = "Cox PH regression results with different death configurations") ,
         t_drop1 = list(
             dt_drop1 = quote(dt_drop1),
-            caption = "Model Fit Improvement by Single Term Deletions"),
-        t_reg_coxph_comp = list(
-            l_mdls = quote(l_mdls),
-            l_mdlnames = quote(l_mdlnames_comp),
-            caption = "Alternative competition specifications"),
-        t_reg_coxph_dens = list(
-            l_mdls = quote(l_mdls),
-            l_mdlnames = quote(l_mdlnames_dens),
-            caption = "Alternative competition specifications"),
-        t_reg_coxph_env = list(
-            l_mdls = quote(l_mdls),
-            l_mdlnames = quote(l_mdlnames_env),
-            caption = "Alternative specification of environment"),
-        t_reg_coxph_af = list(
[…]

### 2024-09-27 scripts/closing_main.R

@@ -331,12 +331,13 @@ c_lvrs <- list(
 
 
 ## actual pm data
-## l_pca_dimred <- gl_pca_dimred(dt_pmdb)
+
 ## l_pca_dimred_woclosed <- gl_pca_dimred(dt_pmdb[museum_status != "closed"])
 
 dt_pmx <- gd_pmx(dt_pmdb) # extract of main variables
 
 ## generate PC cores, only use open PMs for loading calculation
+l_pca_dimred <- gl_pca_dimred(dt_pmdb)
 l_pca_dimred_woclosed <- gl_pca_dimred_closed_imputed(dt_pmdb, dt_pmx)
 
 dt_pmtiv <- gd_pmtiv(dt_pmx, l_pca_dimred_woclosed) # time invariant variables
@@ -353,7 +354,8 @@ l_mdls <- gl_mdls(dt_pmyear, dt_pmcpct) # generate models
 
 l_mdlnames_coxph <- list("r_pop4")
 
-l_mdlnames_dens <- list("r_pop4", "r_comp1", "r_pmdens1", "r_pmdens2", "r_pmdens3", "r_pmdens_aud1", "r_pmdens_aud2")
+l_mdlnames_dens <- list("r_pop4", "r_comp1", "r_pmdens1",
+                        "r_pmdens2", "r_pmdens3", "r_pmdens_aud1", "r_pmdens_aud2")
 
 ## compare whether proxcnt/popm_circle10 patterns are stable across data ranges
 l_mdlnames_coxph_density <- list("r_pop4", "r_onlycryside", "r_wocryside", "r_pop42") 
@@ -375,6 +377,8 @@ l_mdlnames_af <- c("r_pop4", "r_exhbany", "r_exhbroll")
 
 l_mdlnames_reg <- c("r_pop4", "r_reg6", "r_regsub2", "r_regsub2_samplecprn",
                     "r_country", "r_country_samplecprn") # "r_country2", "r_country2_samplecprn")
+
+l_mdlnames_dimred <- c("r_pop4", "r_pc1", "r_pc2", "r_pcboth") # dimred for supplementary materials
 
 
 

### 2024-09-27 scripts/regression.R

@@ -1517,8 +1517,8 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
             vrbls_to_add = "pmdens_circle10",
             vrbls_to_yeet = c("popm_circle10", "proxcnt10:popm_circle10")), dt_pmyear),
 
+        ## include artfacts variables
         r_exhbany = coxph(gf_coxph_close(vrbls_to_add = "exhbany"), dt_pmyear),
-
         r_exhbroll = coxph(gf_coxph_close(vrbls_to_add = "exhbrollany"), dt_pmyear),
 
         
@@ -1548,11 +1548,15 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         r_regsub2_samplecprn = coxph(gf_coxph_close(),
                           dt_pmyear[, .SD[sum(fnunique(ID)) > 10], regsub] %>% droplevels),
 
-
         
         ## r_regsub3 = coxph(gf_coxph_close(vrbls_to_add = "regsub"),
         ##                   dt_pmyear[, .SD[sum(fnunique(ID)) > 100], regsub] %>% droplevels),
-        r_reg6 = coxph(gf_coxph_close(vrbls_to_add = "reg6"), dt_pmyear)
+        r_reg6 = coxph(gf_coxph_close(vrbls_to_add = "reg6"), dt_pmyear),
+
+        ## include PC
+        r_pc1 = coxph(gf_coxph_close(vrbls_to_add = "PC1"), dt_pmyear),
+        r_pc2 = coxph(gf_coxph_close(vrbls_to_add = "PC2"), dt_pmyear),
+        r_pcboth = coxph(gf_coxph_close(vrbls_to_add = c("PC1", "PC2")), dt_pmyear)
 
 
 
@@ -2397,7 +2401,7 @@ gt_reg_coxph <- function(l_mdls, l_mdlnames) {
     1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;1;
     gw_fargs(match.call())
 
-
+    
     l_mdls_slct <- map(l_mdlnames, ~chuck(l_mdls, .x))
 
     l_mdlres <- map2(l_mdls_slct, l_mdlnames, ~gd_reg_coxph(.x, .y, unit_name = "ID"))
[…]

### 2024-09-27 scripts/cfg.R
include pca plots/tbls in nbrs, adjust nbrs/farg_calls/callgraph.dot

@@ -59,7 +59,7 @@ gc_tbls <- function(c_tblargs) {
     l_tblcfgs_coxph <- split(dt_cfg_prep, 1:nrow(dt_cfg_prep)) %>%
         lapply(\(x) list(# tblname = paste0("t_reg_coxph", x$tblname),
                         ## l_mdlnames = sym(paste0("l_mdlnames_",x$l_mdlnames)),
-                        l_mdlnames = get(paste0("l_mdlnames_",x$l_mdlnames)),
+                        l_mdlnames = sym(paste0("l_mdlnames_",x$l_mdlnames)),
                         l_mdls = sym("l_mdls"),
                         caption = x$caption)) %>%
         setNames(paste0("t_reg_coxph", dt_cfg_prep$tblname))

### 2024-09-27 scripts/closing_main.R

@@ -361,10 +361,10 @@ l_mdlnames_dens <- list("r_pop4", "r_comp1", "r_pmdens1",
 l_mdlnames_coxph_density <- list("r_pop4", "r_onlycryside", "r_wocryside", "r_pop42") 
 
 ## compare whether patterns change if only recent data is used
-l_mdlnames_timeslice <- list("r_pop4", "r_2005", "r_2010", "r_2015")
+l_mdlnames_timeslice <- c("r_pop4", "r_2005", "r_2010", "r_2015")
 
 ## check whether patterns depend on itme configuration (time period, year_opened, both)
-l_mdlnames_timecfg <- list("r_pop4", "r_pop4_wyo", "r_pop4_wtp", "r_pop4_wyotp")
+l_mdlnames_timecfg <- c("r_pop4", "r_pop4_wyo", "r_pop4_wtp", "r_pop4_wyotp")
 
 ## alternative competition specficication
 l_mdlnames_comp <- c("r_pop4", "r_comp1", "r_audience1", "r_audience2", "r_audience_log1", "r_audience_log2")

### 2024-09-27 texts/sup_materials.tex
add PC variables figures/tables/text to sup_materials

@@
-% Created 2024-09-26 do 17:45
+% Created 2024-09-27 vr 18:36
 % Intended LaTeX compiler: pdflatex
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Sep 17 14:48:53 2024
+% Fri Sep 27 17:51:29 2024
 \begin{table}[ht]
@@
    \hline 
- \multicolumn{7}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{7}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
 \end{tabular}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Sep 17 14:48:47 2024
+% Fri Sep 27 17:51:24 2024
 \begin{table}[ht]
@@
    \hline 
- \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
 \end{tabular}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Sep 17 14:48:49 2024
+% Fri Sep 27 17:51:26 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Sep 17 14:48:55 2024
+% Fri Sep 27 17:51:30 2024
 \begin{table}[ht]
@@
    \hline 
- \multicolumn{5}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
+ \multicolumn{5}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
 \end{tabular}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Sep 26 17:45:22 2024
+% Fri Sep 27 17:51:34 2024
 \begingroup\small
@@
 
-\ref{fig:p_vrblcvrg_ratio}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=18cm]{../figures/p_vrblcvrg_ratio.pdf}
+\caption{\label{fig:p_vrblcvrg_ratio}PMDB variable coverage (abs/rel prop) by museum status and variable group}
+\end{figure}
+
 Figure \ref{fig:p_vrblcvrg_ratio} shows the variable coverage by whether a museum is open or closed at the status of data collection (2020-2022).
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=18cm]{../figures/p_vrblcvrg_pca.pdf}
+\caption{\label{fig:p_vrblcvrg_pca}coverage of variables used in PCA}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=14cm]{../figures/p_pca_loadings.pdf}
+\caption{\label{fig:p_pca_loadings}loadings of first 2 PCs}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=16cm]{../figures/p_pca_scores.pdf}
+\caption{\label{fig:p_pca_scores}scores on first PCs}
+\end{figure}
+
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Fri Sep 27 18:04:16 2024
+\begin{table}[ht]
+\centering
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
+  \hline 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pc1} & \multicolumn{1}{l}{r\_pc2} & \multicolumn{1}{l}{r\_pcboth}\\ 
+ \hline
+  \multicolumn{6}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & -.04 \; (0.34) & .02 \; (0.34) & .38 \; (0.34) & .26 \; (0.34) \\ 
+   & Gender - Couple & -.14 \; (0.32) & .12 \; (0.33) & .20 \; (0.33) & .38 \; (0.34) \\ 
+   & Founder died & .28 \; (0.43) & 1.30 \; (0.45)^{**} & .73 \; (0.43) & 1.29 \; (0.44)^{**} \\ 
+   \multicolumn{6}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .20 \; (0.41) & -.08 \; (0.43) & .68 \; (0.43) & .38 \; (0.44) \\ 
+   & Self-Identification - Collection & -.45 \; (0.54) & -.68 \; (0.55) & -.41 \; (0.54) & -.50 \; (0.55) \\ 
+   & Self-Identification - Other & 1.09 \; (0.30)^{***} & .94 \; (0.31)^{**} & 1.04 \; (0.31)^{***} & .93 \; (0.31)^{**} \\ 
+   & AN Ranking - Included & .19 \; (0.34) & .59 \; (0.35) & .23 \; (0.35) & .33 \; (0.36) \\ 
+   & AN Ranking - Dropped & .46 \; (0.50) & .87 \; (0.53) & .25 \; (0.52) & .60 \; (0.55) \\ 
+   & Founder name in Museum name & .05 \; (0.28) & .09 \; (0.28) & -.01 \; (0.29) & .02 \; (0.29) \\ 
+   & PC1 (Size) &  & .88 \; (0.15)^{***} &  & .61 \; (0.14)^{***} \\ 
+   & PC2 (Support) &  &  & .86 \; (0.14)^{***} & .59 \; (0.15)^{***} \\ 
+   \multicolumn{6}{l}{\textbf{Environment}} \\ 
+ & PM density (country) & .65 \; (0.34) & .28 \; (0.35) & .50 \; (0.33) & .27 \; (0.34) \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.01 \; (0.02) & -.02 \; (0.03) & -.01 \; (0.03) \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .14 \; (0.10) & .33 \; (0.10)^{***} & .21 \; (0.11) \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} & .20 \; (0.07)^{**} & .23 \; (0.08)^{**} & .18 \; (0.08)^{*} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.07 \; (0.03)^{*} & -.08 \; (0.03)^{**} & -.06 \; (0.03)^{*} \\ 
+   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.76 \; (1.01) & -1.74 \; (1.01) & -1.82 \; (1.02) \\ 
+   & Covid Pandemic (2020/21) & .42 \; (0.29) & .64 \; (0.30)^{*} & .59 \; (0.30)^{*} & .69 \; (0.30)^{*} \\ 
+   \hline
+ & Museums & 503 & 503 & 503 & 503 \\ 
+   & Museum-years & 6096 & 6096 & 6096 & 6096 \\ 
+   & Closures & 68 & 68 & 68 & 68 \\ 
+   & log. Likelihood & -339.68 & -308.93 & -312.29 & -298.68 \\ 
+   & AIC & 711.35 & 651.85 & 658.59 & 633.37 \\ 
+   & BIC & 746.87 & 689.59 & 696.32 & 673.32 \\ 
+   \hline 
+ \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
+\end{tabular}
+\caption{Cox PH regression models with PCA factors of museum facilities} 
+\label{tbl:t_reg_coxph_dimred}
+\end{table}
+
 Under this assumption, based on variables where an absence is a plausible value (i.e.
-not including variables such as floor size, collection size or opening times) a principal component analysis was performed.
-figure FIXME
+not including variables such as floor size, collection size or opening times; figure \ref{fig:p_vrblcvrg_pca}) a principal component analysis was performed of which the first two factors are extracted with varimax rotation (figure \ref{fig:p_pca_loadings}).
+The first component appears to differentiate museums based on facilities (museumshop, restaurant) and institutional arrangements corresponding to larger institutions (sponsorship, donor program, temporary exhibitions), which makes it plausible that it reflects the size of an organization.
+The second dimension seems to measure the extent of artistic support, education and research.
+Figure \ref{fig:p_pca_scores} shows positioning of the museums on both dimensions. 
+Table \ref{tbl:t_reg_coxph_dimred} shows models with one or both of these components included:
+Both components are highly significantly associated with closing, improve model performance and change a number of main results, such as the coefficient of the death of the founder (significant when the first component is addded) and the main effect of local population (insignificant when the first component is addded), as well as the covid pandemic effect (significant in all model with principal components).
 
-and the two first factors included in the regression results.
+While it is plausible that larger organizations face a lower closing risk, I ultimately consider the coefficients are too large to be plausibly reflect primary an influence of institutional characteristics.
+While some size effect may exist, I consider it more plausible that this is indicator much more strongly reflects whether a museum is open or closed in the first place (as data collection was much more difficult for closed museums, the  measurement error is systematically related with the outcome variable), and therefore do not include it in the main regression model to avoid a circular rationale.
 \end{document}

### 2024-09-30 scripts/closing_playground.R
more search on protected term, no good solution
country dummies add something tho

@@ -571,3 +571,16 @@ dt_pmtiv[, .(subreg = countrycode(iso3c, "iso3c", "un.regionsub.code"),
 
 dt_pmtiv[, .N, iso3c][N > 10][, country_name := countrycode(iso3c, "iso3c", "country.name")] %>%
     .[, sprintf('list(vrbl = "iso3c", term = "iso3c%s", term_lbl = "Country - %s")', iso3c, country_name)] %>% cat(sep = "\n")
+
+## ** naming conventions by country
+
+dt_namconv <- dt_pmtiv[, .N, .(slfidfcn, iso3c)][, `:=`(prop = N/sum(N), N_ttl = sum(N)), iso3c]
+
+
+dt_namconv %>% dcast(iso3c + N_ttl ~ slfidfcn, value.var = "prop") %>% .[order(-N_ttl)]
+
+dt_namconv %>% copy %>%
+    .[N_ttl >= 10] %>% 
+    .[order(N_ttl)] %>% .[, iso3c := factor(iso3c, levels = unique(iso3c))] %>% # .[, iso3c] %>% 
+    ggplot(aes(x=prop, y=iso3c)) + geom_col() +
+    facet_grid(~slfidfcn)

### 2024-09-30 texts/sup_materials.tex
expand supplementary material

@@
-% Created 2024-09-27 vr 18:36
+% Created 2024-09-30 ma 14:08
 % Intended LaTeX compiler: pdflatex
@@
 While some size effect may exist, I consider it more plausible that this is indicator much more strongly reflects whether a museum is open or closed in the first place (as data collection was much more difficult for closed museums, the  measurement error is systematically related with the outcome variable), and therefore do not include it in the main regression model to avoid a circular rationale.
+\subsection*{Model improvement by variable addition}
+
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Fri Sep 27 17:51:21 2024
+\begin{table}[ht]
+\centering
+\begin{tabular}{llrD{.}{.}{5}}
+  \hline 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable dropped} & \multicolumn{1}{l}{AIC difference} & \multicolumn{1}{l}{Chisq}\\ 
+ \hline
+  \multicolumn{3}{l}{\textbf{Founder}} \\ 
+ & Founder Gender & 3.81 & .19 \\ 
+   & Founder died & 1.60 & .40 \\ 
+   \multicolumn{3}{l}{\textbf{Museum}} \\ 
+ & Self-Identification & -13.25 & 19.25^{***} \\ 
+   & Founder name in Museum name & 1.97 & .03 \\ 
+   & ArtNews Ranking inclusion & 3.00 & 1.00 \\ 
+   \multicolumn{3}{l}{\textbf{Environment}} \\ 
+ & PM density (country) & 0.85 & 3.15 \\ 
+   & PM density$^{2}$ (country) & -1.03 & 3.03 \\ 
+   & Pop. (millions) within 10km & -8.56 & 12.56^{**} \\ 
+   & Nbr PM within 10km & -9.28 & 13.28^{**} \\ 
+   & Nbr PM (10km) * Pop (10km) & -10.04 & 12.04^{***} \\ 
+   & Great Recession (2008/09) & -2.23 & 4.23^{*} \\ 
+   & Covid Pandemic (2020/21) & 0.07 & 1.93 \\ 
+   \hline 
+ \multicolumn{2}{l}{\footnotesize{\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
+\end{tabular}
+\caption{Model Fit Improvement by Single Term Deletions} 
+\label{tbl:t_drop1}
+\end{table}
+
+Table \ref{tbl:t_drop1} shows model fit improvement by adding each variable to the model with the other main variables but without the variable in question.
+For the most part, variables that are significant in the main model (self-identification and the main effects and interaction of population and private museums in the local environment) significantly improve the model when added.
+The one variable deviating from this pattern is the dummy variable for the years of the Great Recession, which despite an insignificant model coefficient significantly improves model fit; however model improvement is relatively small compared to the other variables.
 \end{document}

### 2024-09-30 scripts/cfg.R
add model of founder name - death interaction

@@ -53,7 +53,8 @@ gc_tbls <- function(c_tblargs) {
         "_env",      "env",          "Alternative specification of environment",                        
         "_af",       "af",           "Alternative specification: include Exhibition",                   
         "_timecfg",  "timecfg",      "Cox PH regression results with different time configurations",    
-        "_dimred",   "dimred",       "Cox PH regression models with PCA factors of museum facilities",  
+        "_dimred",   "dimred",       "Cox PH regression models with PCA factors of museum facilities",
+        "_addgns",   "addgns",       "Cox PH regression models with additional specifications",
         "_reg",      "reg",          "Cox PH regression results with different region dummies included")
 
     l_tblcfgs_coxph <- split(dt_cfg_prep, 1:nrow(dt_cfg_prep)) %>%
@@ -279,7 +280,7 @@ gc_vvs <- function() {
         "popm_circle10:proxcnt10_log"     = "Nbr PM (10km, log) * Pop (10km)",
         "proxcnt10:popm_circle10_log"     = "Nbr PM (10km) * Pop (10km, log)",
         
-                
+        "founder_dead_binary:muem_fndr_name" = "Founder name in Museum name * Founder died",
         
         audience10                = "Local Audience per PM",
         "I(audience10^2)"         = "Local Audience per PM^2",
@@ -313,7 +314,8 @@ gc_vvs <- function() {
     
     l_vrblgrps <- list(# variable groups
         founder  = .c(gender, founder_dead1, founder_dead_binary),
-        museum   = .c(slfidfcn, muem_fndr_name, mow, an_inclusion, PC1, PC2,
+        museum   = .c(slfidfcn, muem_fndr_name, "founder_dead_binary:muem_fndr_name",
+                      mow, an_inclusion, PC1, PC2,
                       exhbany, exhbrollany,
                       year_opened,
                       exhbqntl_cy, exhbcnt, exhbrollsum_avg,
@@ -337,7 +339,7 @@ gc_vvs <- function() {
                    founder_dead1, founder_dead_binary, 
                    an_inclusion, pmdens_circle10, "I(pmdens_circle10^2)", "proxcnt10:popm_circle10",
                    year, "I(year^2)", time_period, "popm_circle10:I(proxcnt10^2)",
-                   exhbany, exhbrollany, 
[…]

### 2024-09-30 scripts/closing_main.R

@@ -380,6 +380,7 @@ l_mdlnames_reg <- c("r_pop4", "r_reg6", "r_regsub2", "r_regsub2_samplecprn",
 
 l_mdlnames_dimred <- c("r_pop4", "r_pc1", "r_pc2", "r_pcboth") # dimred for supplementary materials
 
+l_mdlnames_addgns <- c("r_pop4", "r_founder_name_death_int")
 
 
 ## improvement by adding variables

### 2024-09-30 scripts/regression.R

@@ -1556,10 +1556,13 @@ gl_mdls <- function(dt_pmyear, dt_pmcpct) {
         ## include PC
         r_pc1 = coxph(gf_coxph_close(vrbls_to_add = "PC1"), dt_pmyear),
         r_pc2 = coxph(gf_coxph_close(vrbls_to_add = "PC2"), dt_pmyear),
-        r_pcboth = coxph(gf_coxph_close(vrbls_to_add = c("PC1", "PC2")), dt_pmyear)
+        r_pcboth = coxph(gf_coxph_close(vrbls_to_add = c("PC1", "PC2")), dt_pmyear),
 
 
-
+        ## interaction of death and founder name
+        r_founder_name_death_int = coxph(gf_coxph_close(vrbls_to_add = "muem_fndr_name*founder_dead_binary"),
+                                         dt_pmyear)
+                                         
         
         
 
@@ -2444,6 +2447,7 @@ gt_reg_coxph_dens <- gt_reg_coxph
 gt_reg_coxph_env <- gt_reg_coxph
 gt_reg_coxph_af <- gt_reg_coxph
 gt_reg_coxph_dimred <- gt_reg_coxph
+gt_reg_coxph_addgns <- gt_reg_coxph
 
 
 gt_reg_coxph_reg <- function(l_mdls, l_mdlnames) {

### 2024-10-01 texts/paper_closing.tex
new latex version

@@
-% Created 2024-09-27 vr 16:13
+% Created 2024-09-30 ma 14:05
 % Intended LaTeX compiler: pdflatex
@@
 
-While a recent study by \textcite{Velthuis_Gera_2024_fragility} has investigated closing reasons of private museums, I extend/complement this study by using a more elaborate statistical model and additional data sources.
+While a recent study by \textcite{Velthuis_Gera_2024_fragility} has systematically investigated closing reasons of private museums, I extend/complement this research by using a more elaborate statistical model and additional data sources.
 In particular, I compare private museum closing rates to those of other museum populations, and analyze the risk associated with variables on the level of the founder, museum and environment. 
@@
 Due to the founders central role, private museums have been argued to be highly dependent on their founder for their continuing existence, as museums generally cannot cover expenses via revenues from ticket prices, museum shops and cafes:
-The \textcite{IMLS_2008_funding} found that for non-profit American art museums, less than half (48.1\%) the revenues come from earned income, leaving substantial gaps in the budgets that are filled by a mix of private donations (23.0\%), investment (18.5\%) and government support (10.4\%) (p.27).
+The \textcite{IMLS_2008_funding} found that American non-profit art museums receive less than half (48.1\%) of their revenues from earned income, leaving substantial gaps in the budgets that are filled by a mix of private donations (23.0\%), investment (18.5\%) and government support (10.4\%) (p.27).
 Outside of the United States, the reliance on revenue streams beyond operations is even larger:
 German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table p.233}, with private museums however requiring less support as operations provide around 47\% of their budget (ibid.).
-In the Germany cultural sector, non-profit organizations more widely  draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
-On a European level, only 12\% of museum incomes are generated by entry fees, whereas 69\% originate from subsidies \parencite{EGMUS_2024_complete}.\footnote{Own calculations from on EGMUS data, based on all countries with income data from 2015 onwards.}
+In the German cultural sector, non-profit organizations more widely  draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
+On a European level, only 12\% of museum incomes are generated by entry fees, whereas 69\% originate from subsidies \parencite{EGMUS_2024_complete}.\footnote{Own calculations from EGMUS data, based on all countries with income data from 2015 onwards.}
 
@@
 Other studies have measured diversification as the Herfindahl Index (a measure of concentration) of income sources such as public support, program service revenues, dues and assessments, net fundraising income and profits from sale of inventory \parencite[p.381]{Hager_2001_vulnerability} or contributions, program service revenue, investment income, other revenues \parencite[p.37]{Lu_Shon_Zhang_2019_dissolution}, with both studies finding a positive association between diversification and survival; in the case of \cite{Hager_2001_vulnerability} also specifically for art museums.
-Next to diversification, volatility, i.e. fluctuation in revenue streams has been associated with mortality as well \parencite{Mayer_2022_simmer}.
+Next to diversification, volatility, i.e. fluctuation in revenue streams, has been associated with mortality as well \parencite{Mayer_2022_simmer}.
 Despite limited reception of this research stream in the private museum literature, identifying the high reliance on the founder as a source of risk thus corresponds to management insights.
@@
 Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations possibly constitute factors that contribute to its viability and hence longevity.
-While some of these aspects can be influenced by the founder (in particular the museum's location and strategies) , other are less so.
-In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship and funding choices, the influence of the individual founder is severely limited.
+While some of these aspects can be influenced by the founder (in particular the museum's location and strategies), other are less so.
+In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
+Other environmental factors beyond the recognitition of the founder might influence the life chances of a private museum.
 \paragraph*{Competition}
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Sep 17 14:48:46 2024
+% Fri Sep 27 17:51:18 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Sep 17 14:48:45 2024
+% Fri Sep 27 17:51:17 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 294 & 0.584 &    0.604 &  0.49 & 0 & 1 \\ 
-   & Gender - Female & 79 & 0.157 &    0.166 &  0.37 & 0 & 1 \\ 
-   & Gender - Couple & 130 & 0.258 &    0.231 &  0.42 & 0 & 1 \\ 
-   & Founder - alive &  &  &    0.903 &  0.30 & 0 & 1 \\ 
-   & Founder - died recently &  &  &    0.013 &  0.11 & 0 & 1 \\ 
-   & Founder - died 2+ years ago &  &  &    0.084 &  0.28 & 0 & 1 \\ 
-   & Founder died &  &  &    0.097 &  0.30 & 0 & 1 \\ 
+ & Gender - Male & 294 & 0.584 &  6.0e-01 &  0.489 & 0 & 1 \\ 
+   & Gender - Female & 79 & 0.157 &  1.7e-01 &  0.372 & 0 & 1 \\ 
+   & Gender - Couple & 130 & 0.258 &  2.3e-01 &  0.421 & 0 & 1 \\ 
+   & Founder - alive &  &  &  9.0e-01 &  0.296 & 0 & 1 \\ 
+   & Founder - died recently &  &  &  1.3e-02 &  0.115 & 0 & 1 \\ 
+   & Founder - died 2+ years ago &  &  &  8.4e-02 &  0.277 & 0 & 1 \\ 
+   & Founder died &  &  &  9.7e-02 &  0.296 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 190 & 0.378 &    0.408 &  0.49 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 104 & 0.207 &    0.189 &  0.39 & 0 & 1 \\ 
-   & Self-Identification - Collection & 69 & 0.137 &    0.130 &  0.34 & 0 & 1 \\ 
-   & Self-Identification - Other & 140 & 0.278 &    0.274 &  0.45 & 0 & 1 \\ 
-   & Founder name in Museum name & 240 & 0.477 &    0.477 &  0.50 & 0 & 1 \\ 
-   & AN Ranking - Not Included &  &  &    0.802 &  0.40 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  &    0.144 &  0.35 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  &    0.053 &  0.23 & 0 & 1 \\ 
-   & Exhibition any &  &  &    0.630 &  0.48 & 0 & 1 \\ 
-   & Opening year &  &  & 2001.493 & 11.10 & 1960 & 2020 \\ 
+ & Self-Identification - Museum & 190 & 0.378 &  4.1e-01 &  0.491 & 0 & 1 \\ 
+   & Self-Identification - Foundation & 104 & 0.207 &  1.9e-01 &  0.391 & 0 & 1 \\ 
+   & Self-Identification - Collection & 69 & 0.137 &  1.3e-01 &  0.336 & 0 & 1 \\ 
+   & Self-Identification - Other & 140 & 0.278 &  2.7e-01 &  0.446 & 0 & 1 \\ 
+   & Founder name in Museum name & 240 & 0.477 &  4.8e-01 &  0.500 & 0 & 1 \\ 
+   & AN Ranking - Not Included &  &  &  8.0e-01 &  0.398 & 0 & 1 \\ 
+   & AN Ranking - Included &  &  &  1.4e-01 &  0.351 & 0 & 1 \\ 
+   & AN Ranking - Dropped &  &  &  5.3e-02 &  0.225 & 0 & 1 \\ 
+   & Exhibition any &  &  &  6.3e-01 &  0.483 & 0 & 1 \\ 
+   & Opening year &  &  &  2.0e+03 & 11.104 & 1960 & 2020 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density (country) &  &  &    0.450 &  1.26 & 0.00077 & 27.26 \\ 
-   & Pop. (millions) within 10km &  &  &    1.337 &  1.68 & 0.000087 & 10.81 \\ 
-   & Nbr PM within 10km &  &  &    1.778 &  3.14 & 0 & 16 \\ 
-   & PM density (10km, log) &  &  &    0.527 &  0.79 & 0 & 4.35 \\ 
-   & Nbr PM within 10km (log) &  &  &    0.613 &  0.82 & 0 & 2.83 \\ 
-   & Pop. (millions) within 10km (log) &  &  &   -0.893 &  1.97 & -9.3 & 2.38 \\ 
-   & Local Audience per PM &  &  &    0.567 &  0.86 & 0.000087 & 8.16 \\ 
-   & Local Audience per PM (log) &  &  &   -1.505 &  1.64 & -9.3 & 2.10 \\ 
-   & Region - Africa & 8 & 0.016 &    0.012 &  0.11 & 0 & 1 \\ 
-   & Region - Asia & 142 & 0.282 &    0.292 &  0.45 & 0 & 1 \\ 
-   & Region - Europe & 248 & 0.493 &    0.497 &  0.50 & 0 & 1 \\ 
-   & Region - Latin America & 23 & 0.046 &    0.042 &  0.20 & 0 & 1 \\ 
-   & Region - North America & 72 & 0.143 &    0.138 &  0.34 & 0 & 1 \\ 
-   & Region - Oceania & 10 & 0.020 &    0.019 &  0.13 & 0 & 1 \\ 
-   & Time Period 2000-2004 &  &  &    0.101 &  0.30 & 0 & 1 \\ 
-   & Time Period 2005-2009 &  &  &    0.166 &  0.37 & 0 & 1 \\ 
-   & Time Period 2010-2014 &  &  &    0.258 &  0.44 & 0 & 1 \\ 
-   & Time Period 2015-2019 &  &  &    0.331 &  0.47 & 0 & 1 \\ 
-   & Time Period 2020-2024 &  &  &    0.145 &  0.35 & 0 & 1 \\ 
-   & Great Recession (2008/09) &  &  &    0.076 &  0.27 & 0 & 1 \\ 
-   & Covid Pandemic (2020/21) &  &  &    0.145 &  0.35 & 0 & 1 \\ 
+ & PM density (country) &  &  &  4.5e-01 &  1.261 & 0.00077 & 27.26 \\ 
+   & Pop. (millions) within 10km &  &  &  1.3e+00 &  1.682 & 0.000087 & 10.81 \\ 
+   & Nbr PM within 10km &  &  &  1.8e+00 &  3.143 & 0 & 16 \\ 
+   & PM density (10km, log) &  &  &  5.3e-01 &  0.786 & 0 & 4.35 \\ 
+   & Nbr PM within 10km (log) &  &  &  6.1e-01 &  0.816 & 0 & 2.83 \\ 
+   & Pop. (millions) within 10km (log) &  &  & -8.9e-01 &  1.966 & -9.3 & 2.38 \\ 
+   & Local Audience per PM &  &  &  5.7e-01 &  0.865 & 0.000087 & 8.16 \\ 
+   & Local Audience per PM (log) &  &  & -1.5e+00 &  1.638 & -9.3 & 2.10 \\ 
+   & Region - Africa & 8 & 0.016 &  1.2e-02 &  0.110 & 0 & 1 \\ 
+   & Region - Asia & 142 & 0.282 &  2.9e-01 &  0.455 & 0 & 1 \\ 
+   & Region - Europe & 248 & 0.493 &  5.0e-01 &  0.500 & 0 & 1 \\ 
+   & Region - Latin America & 23 & 0.046 &  4.2e-02 &  0.201 & 0 & 1 \\ 
+   & Region - North America & 72 & 0.143 &  1.4e-01 &  0.345 & 0 & 1 \\ 
+   & Region - Oceania & 10 & 0.020 &  1.9e-02 &  0.135 & 0 & 1 \\ 
+   & UN Subregion - Northern Africa & 1 & 0.002 &  8.2e-04 &  0.029 & 0 & 1 \\ 
+   & UN Subregion - Northern America & 72 & 0.143 &  1.4e-01 &  0.345 & 0 & 1 \\ 
+   & UN Subregion - Eastern Asia & 96 & 0.191 &  2.2e-01 &  0.411 & 0 & 1 \\ 
+   & UN Subregion - Southern Asia & 9 & 0.018 &  1.5e-02 &  0.120 & 0 & 1 \\ 
+   & UN Subregion - South-eastern Asia & 12 & 0.024 &  2.5e-02 &  0.155 & 0 & 1 \\ 
+   & UN Subregion - Southern Europe & 70 & 0.139 &  1.5e-01 &  0.361 & 0 & 1 \\ 
+   & UN Subregion - Australia and New Zealand & 10 & 0.020 &  1.9e-02 &  0.135 & 0 & 1 \\ 
+   & UN Subregion - Western Asia & 25 & 0.050 &  3.7e-02 &  0.189 & 0 & 1 \\ 
+   & UN Subregion - Eastern Europe & 22 & 0.044 &  5.0e-02 &  0.218 & 0 & 1 \\ 
+   & UN Subregion - Northern Europe & 27 & 0.054 &  5.7e-02 &  0.231 & 0 & 1 \\ 
+   & UN Subregion - Western Europe & 129 & 0.256 &  2.4e-01 &  0.425 & 0 & 1 \\ 
+   & UN Subregion - Sub-Saharan Africa & 7 & 0.014 &  1.1e-02 &  0.107 & 0 & 1 \\ 
+   & UN Subregion - Latin America and the Caribbean & 23 & 0.046 &  4.2e-02 &  0.201 & 0 & 1 \\ 
+   & Time Period 2000-2004 &  &  &  1.0e-01 &  0.301 & 0 & 1 \\ 
+   & Time Period 2005-2009 &  &  &  1.7e-01 &  0.372 & 0 & 1 \\ 
+   & Time Period 2010-2014 &  &  &  2.6e-01 &  0.438 & 0 & 1 \\ 
+   & Time Period 2015-2019 &  &  &  3.3e-01 &  0.471 & 0 & 1 \\ 
+   & Time Period 2020-2024 &  &  &  1.4e-01 &  0.352 & 0 & 1 \\ 
+   & Great Recession (2008/09) &  &  &  7.6e-02 &  0.265 & 0 & 1 \\ 
+   & Covid Pandemic (2020/21) &  &  &  1.4e-01 &  0.352 & 0 & 1 \\ 
    \hline
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Thu Sep 26 17:44:59 2024
+% Fri Sep 27 17:51:41 2024
 \begin{table}[ht]
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Tue Sep 17 14:48:50 2024
+% Fri Sep 27 17:51:20 2024
 \begin{table}[ht]
@@
 \end{tabular}
-\caption{Cox PH regression results wiht different death configurations} 
+\caption{Cox PH regression results with different death configurations} 
 \label{tbl:t_reg_coxph_deathcfg}

### 2024-10-02 texts/paper_closing.tex
minor writing for better flow

@@
-% Created 2024-09-30 ma 14:05
+% Created 2024-10-02 wo 15:08
 % Intended LaTeX compiler: pdflatex
@@
 from foundations, individuals, federated funders, corporations, trusts, government at federal, state, county and municipal level as well as self-generated sources such as dues, interests, and service revenue, p.31) are more likely to survive.
-Other studies have measured diversification as the Herfindahl Index (a measure of concentration) of income sources such as public support, program service revenues, dues and assessments, net fundraising income and profits from sale of inventory \parencite[p.381]{Hager_2001_vulnerability} or contributions, program service revenue, investment income, other revenues \parencite[p.37]{Lu_Shon_Zhang_2019_dissolution}, with both studies finding a positive association between diversification and survival; in the case of \cite{Hager_2001_vulnerability} also specifically for art museums.
+Other studies have measured diversification as the Herfindahl Index (a measure of concentration) of income sources such as public support, program service revenues, dues and assessments, net fundraising income and profits from sale of inventory \parencite[p.381]{Hager_2001_vulnerability} or contributions, program service revenue, investment income, other revenues \parencite[p.37]{Lu_Shon_Zhang_2019_dissolution}, with both studies finding a positive association between diversification and survival; in the case of \textcite{Hager_2001_vulnerability} also specifically for art museums.
 Next to diversification, volatility, i.e. fluctuation in revenue streams, has been associated with mortality as well \parencite{Mayer_2022_simmer}.
 Despite limited reception of this research stream in the private museum literature, identifying the high reliance on the founder as a source of risk thus corresponds to management insights. 
+Resulting from the dependence of the museum on the founder, it is plausible that interruptions to this key revenue source would endanger the viability of the museum, which can be formulated as: 
+\textbf{Hypothesis 1}: Events which disrupt the founder's ability to provide resources to their private museums increase the risk of closing.
 
-Lack of diversification is then argued to pose a problem in particular in the case of the founder's death:
+The most direct interruption a founder and their museum can experience is the death of the founder; this event has in fact already been extensively argued to result in museum closure:
 \textcite{Walker_2019_collector} argues that "the death of the original founder and creator can [\ldots{}] place the future of private museums and collections in jeopardy" as "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museums indefinitely" (p.234).
@@
 \textcite{StylianouLambert_etal_2014_museums}, after discussing a case of a private museum whose owner "does not believe that anyone else could love the museum as much as she does", argue that this "generates questions regarding the cultural sustainability of small private museums in cases where their initiators are not able to care for them any longer" (p.580).
-
-Private museums heavily rely on their founders for survival; events that interrupt the founders ability to provide resources are therefore associated with a highler likelihood of closing.
-
-\textbf{Hypothesis 1}: Events which disrupt the founder's ability to provide resources to their private museums increase the risk of closing, in particular:
-
-The death of the founder is a clearly financial and organizational disruption for the museum, and as previous research has seen it as a precursor of museum closure, a hypothesis can be formulated as: 
+The death of the founder thus constitutes a clear financial and organizational disruption for the museum, and as previous research has seen it as a precursor of museum closure, a hypothesis can be formulated as:
 \textbf{Hypothesis 1a}: Private museums are more likely to close after the death of the founder.
@@
 A less obvious yet possibly impactful event that can jeopardize a founder's ability to sustain their museum and potentially shorten its lifespan is a decline of status of the collector within the art world.
-Recognition bestowed by prominent art world authorities confers the acknowledgment of "cultural expertise" \parencite[p.1486]{Braden_2016_recognition}, thus validating the collector-founder's refined taste, which constitutes a form symbolic capital that might yield tangible benefits \parencite{Bourdieu_1993_production}.
+Recognition bestowed by prominent art world authorities confers the acknowledgment of "cultural expertise" \parencite[p.1486]{Braden_2016_recognition}, thus validating the collector-founder's refined taste, which constitutes a form symbolic capital \parencite{Bourdieu_1993_production}.
 This symbolic capital might provide opportunities to acquire material advantages such as collaborations with other institutions and access to broader audiences, ultimately bolstering the museum's longevity.
 
-In the face of a loss of recognition, the consequences can extend beyond the personal demotivation it may cause the founder.
+While limited research exists that investigates reputation effects for (art) museums, its effects have been investigated for non-profits more widely.
+Here reputation is often referred to as an organization's resource or asset \parencite{Kong_Farrell_2010_image,Goldfarb_Zavyalova_Pillai_2018_Rao,Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}.
+Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survial \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability} \footnote{Furthermore, the term "survival" is sometimes used more loosely to refer to a non-profit's effective operation and financial condition rather than the more narrowly defined dissolution (e.g.
+\cite[p.58]{Santos_Laureano_Moro_2019_reputation}, \cite[p.15]{Heller_2008_alliances}, \cite[p.111]{Schloderer_Sarstedt_Ringle_2014_reputation})}, with most studies finding support for a positive effect of reputation.
+Next to the reputation of the general public, studies have also found reputation effects among more narrowly defined groups, in particular peers \parencite{Padanyi_Gainer_2003_peerreputation} and networks of similar organizations on regional and national scale \parencite{Walker_McCarthy_2010_survival}.
+In particular this reputation among more narrowly defined groups makes it likely that the reputation of the  \emph{founder} matters (beyond the reputation of the \emph{organization}, the focus on most prior research) given the highly personal character of the private museum initiative and the central role of the founder in negotiations with decision makers from other organizations or the public sector.
+
+In the case of the founder losing his reputation, the consequences then might extend beyond personal demotivation.
 Such a decline could also curtail potential opportunities for cooperation with other institutions and limit the museum's reach to larger audiences, thus posing a risk to the museum's continued operation and survival in the long term.
-\textbf{Hypothesis 1b}: Private museums are more likely to close after a decline of their founder's status, measured by exclusion from a prestigious ranking.
+\textbf{Hypothesis 1b}: Private museums are more likely to close after a decline of their founder's status.
 
@@
 In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
-Other environmental factors beyond the recognitition of the founder might influence the life chances of a private museum.
 \paragraph*{Competition}
@@
 The mere availability of audiences and other potential donors might however not be sufficient if a museum is not perceived as deserving support; i.e. if its identity is perceived as inappropriate. 
-An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
+An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns  \parencite{Lange_Lee_Dai_2010_reputation}.
 As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
@@
 Nonetheless, other studies find little to no effect of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
+\textcite{Walker_McCarthy_2010_survival} find support for some, but not all legitimacy indicators.
 

### 2024-10-03 texts/paper_closing.tex
more re-writing/re-ordering of hypotheses

@@
-% Created 2024-10-02 wo 15:08
+% Created 2024-10-03 do 13:26
 % Intended LaTeX compiler: pdflatex
@@
 In this paper, I address this gap by investigating the closure event of members of this new organizational form.
-Analysis which factors are associated with museum closures provides insight not only into the event of closing, but also into the ongoing processes of a private museums, such as dependency relationships.
+Analyzing which factors are associated with museum closures provides insight not only into the event of closing, but also into the ongoing processes of a private museums, such as dependency relationships.
 Furthermore, analyzing which museums survive allows to make informed speculations on the future of this recently emerged organizational form.
@@
 The \textcite{IMLS_2008_funding} found that American non-profit art museums receive less than half (48.1\%) of their revenues from earned income, leaving substantial gaps in the budgets that are filled by a mix of private donations (23.0\%), investment (18.5\%) and government support (10.4\%) (p.27).
-Outside of the United States, the reliance on revenue streams beyond operations is even larger:
-German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table p.233}, with private museums however requiring less support as operations provide around 47\% of their budget (ibid.).
+Outside of the United States, the reliance on revenue streams beyond operations appears even larger:
+German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table b), p.233}, with private museums however requiring less support as operations provide around 47\% of their budget (ibid.).
 In the German cultural sector, non-profit organizations more widely draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
@@
 \textcite{Adam_2021_rise} argues that "most of the cases of defunct private museums come back to the issue of cost" (p.79); a sentiment shared by \textcite{Walker_2019_collector} who notes that "private institutions struggle to contain escalating costs that are associated with running a museum" (p.234).
-In other studies, "insufficient funding, high maintenance costs and lack of strong government support" \parencite[p.7]{Zennaro_2017_shanghai}, a "shortage of fundings and interruptions in cash" \parencite[p.45]{Song_2008_private}, bankruptcies \parencite{Velthuis_Gera_2024_fragility,Liu_2019_identities,DeNigris_2018_museums}, costly legal battles \parencite{Velthuis_Gera_2024_fragility}, stock devaluations \parencite{Walker_2019_collector} or failing auction sales \parencite{Bechtler_Imhof_2018_future} were central reasons that forced private museums to close.
+In other studies, "insufficient funding, high maintenance costs and lack of strong government support" \parencite[p.7]{Zennaro_2017_shanghai}, a "shortage of fundings and interruptions in cash" \parencite[p.45]{Song_2008_private}, bankruptcies \parencite{Velthuis_Gera_2024_fragility,Liu_2019_identities,DeNigris_2018_museums}, costly legal battles \parencite{Velthuis_Gera_2024_fragility}, stock devaluations \parencite{Walker_2019_collector} or failing auction sales \parencite{Bechtler_Imhof_2018_future} have been found as central reasons that forced private museums to close.
 In a systematic review of closing reasons given in newspapers, magazines, social media accounts and personal exchanges, \textcite{Velthuis_Gera_2024_fragility} find financial issues as the most commonly mentioned reasons for private museum closing.
@@
 Nethertheless, the identification of the centrality of the founder as a critical source of vulnerability corresponds strongly to the finding in non-profit management of a relation between diversification and mortality \parencite{Tuckman_Chang_1991_vulnerability}.
-For example, \cite{Bielefeld_1994_survival} finds that nonprofits with a larger number of funding sources (e.g.
+For example, \textcite{Bielefeld_1994_survival} finds that nonprofits with a larger number of funding sources (e.g.
 from foundations, individuals, federated funders, corporations, trusts, government at federal, state, county and municipal level as well as self-generated sources such as dues, interests, and service revenue, p.31) are more likely to survive.
@@
 Resulting from the dependence of the museum on the founder, it is plausible that interruptions to this key revenue source would endanger the viability of the museum, which can be formulated as: 
+\bigbreak
+\noindent
 \textbf{Hypothesis 1}: Events which disrupt the founder's ability to provide resources to their private museums increase the risk of closing.
@@
 The death of the founder thus constitutes a clear financial and organizational disruption for the museum, and as previous research has seen it as a precursor of museum closure, a hypothesis can be formulated as:
+\bigbreak
+\noindent
 \textbf{Hypothesis 1a}: Private museums are more likely to close after the death of the founder.
 
-A less obvious yet possibly impactful event that can jeopardize a founder's ability to sustain their museum and potentially shorten its lifespan is a decline of status of the collector within the art world.
+A less obvious yet possibly impactful event that might jeopardize a founder's ability to sustain their museum and shorten its lifespan is a decline of status of the collector within the art world.
 Recognition bestowed by prominent art world authorities confers the acknowledgment of "cultural expertise" \parencite[p.1486]{Braden_2016_recognition}, thus validating the collector-founder's refined taste, which constitutes a form symbolic capital \parencite{Bourdieu_1993_production}.
@@
 Here reputation is often referred to as an organization's resource or asset \parencite{Kong_Farrell_2010_image,Goldfarb_Zavyalova_Pillai_2018_Rao,Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}.
-Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survial \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability} \footnote{Furthermore, the term "survival" is sometimes used more loosely to refer to a non-profit's effective operation and financial condition rather than the more narrowly defined dissolution (e.g.
+Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survial \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}\footnote{Furthermore, the term "survival" is sometimes used more loosely to refer to a non-profit's effective operation and financial condition rather than the more narrowly defined dissolution (e.g.
 \cite[p.58]{Santos_Laureano_Moro_2019_reputation}, \cite[p.15]{Heller_2008_alliances}, \cite[p.111]{Schloderer_Sarstedt_Ringle_2014_reputation})}, with most studies finding support for a positive effect of reputation.
@@
 Such a decline could also curtail potential opportunities for cooperation with other institutions and limit the museum's reach to larger audiences, thus posing a risk to the museum's continued operation and survival in the long term.
+\bigbreak
+\noindent
 \textbf{Hypothesis 1b}: Private museums are more likely to close after a decline of their founder's status.
 
-While the low diversification, i.e.
-the centrality of the founder for museum finances, has been argued to constitute the key feature of private museum vulnerability, it is also important to consider the other ways in which private museums, as (non-profit) organizations, are entangled with their environments.
-Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations possibly constitute factors that contribute to its viability and hence longevity.
-While some of these aspects can be influenced by the founder (in particular the museum's location and strategies), other are less so.
-In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
+\paragraph*{Identity}
+
+The perception of the museum itself, beyond the reputation of the founder, might also affect survival prospects.
+An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns  \parencite{Lange_Lee_Dai_2010_reputation}, which in turn can facilitate survival prospects \parencite{Rao_1994_reputation}.
+In the context of private museums, a more positive identity could lead to higher visitor numbers, discounts from art dealers, government grants or collaborations with other museums or corporations, resulting in higher revenues and lower acquisition costs.
+
+Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
+Next to material organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate.
+However, the category of museums could be relatively flexible (for example, the term "museum" is generally not subject to state regulation in the US or Germany \parencite{Museumsbund_ICOMDE_2006_standards,Lister_2023_marketing}), which might result in a relatively high tolerance of diversity and hence limited devaluation of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.
+
+\bigbreak
+\noindent
+\textbf{Hypothesis 4}: Private museums with more understandable identities, indicated by adherence to naming conventions, are less likely to close.
+
+It is however necessary to consider that in particular the name of a museum might be associated with a museum's survival via identity, but also reflect founder intentions regarding the institutions longevity; this possibility is discussed in more detail in the results section.
 \paragraph*{Competition}
 
-Private museums have been characterized as highly competitive.
-While some self-descriptions focus on collaborative aspect, previous studies have highlighted how private museums compete with public museums over art works, audiences, sponsoring and donors \parencite[p.4]{Kolbe_etal_2022_privatemuseum}.
+Just as the environment can be supportive of museums recognized perceived as renowned, it can also be a source of risk if it such support is absent.
+In particular this might be the case under conditions of harsh competition, which private museums have been characterized to engage in.
+While some self-descriptions by founders focus on collaborative aspects \parencite{Duron_2020_rebaudengo,BMW_2016_salsali}, previous studies have highlighted how private museums compete with public museums over art works, audiences, sponsoring and donors \parencite[p.4]{Kolbe_etal_2022_privatemuseum}.
 So far the primary interest of investigating competition has been to evaluate whether private museums pose a threat to art provision by public institutions.
 However, less focus has been given to the fact that operating in a competitive environment may also have consequences for the private museums themselves, in particular their survival aspects.
+
 While private museums presumably depend on their founder to a large extent, income from tickets and facilities, as well sponsorships and public support possibly also constitute other non-negligible revenue streams.
-While competition directly has not yet been investigated as a cause for private museum closing, a possible mechanism of competition, "insufficient interest from the public", has been identified as the second most mentioned closure reason by \textcite[p.6]{Velthuis_Gera_2024_fragility}.
-Lack of interest by the public can be a consequence of multiple processes.
+Competition directly has not yet been investigated as a cause for private museum closing, but a possible mechanism of competition, "insufficient interest from the public", has been identified as the second most reported closure reason by \textcite[p.6]{Velthuis_Gera_2024_fragility}.
+Lack of interest by the public can result from multiple processes.
 While competition is one such processes, and applies if nearby competing institutions capture large portions of the audience, lack of interest can also result from a lack of audience (in the absence of competing institutions), which may be the case for private museums located in sparsely populated areas.
@@
 \textbf{Hypothesis 3}: A private museum is more likely to close in a more competitive environment.
-\paragraph*{Identity}
-
-The mere availability of audiences and other potential donors might however not be sufficient if a museum is not perceived as deserving support; i.e. if its identity is perceived as inappropriate. 
-An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns  \parencite{Lange_Lee_Dai_2010_reputation}.
-As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
-Even for non-profit organizations such as museums, which do not produce tangible goods (a domain where identity-related effects are especially prevalent, e.g.
-\cite{Hsu_2015_granted,Bogaert_etal_2014_ecological}), a clear and positive identity might be helpful in a number of ways:
-In the context of private museums, a negative identity could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.
-
-The empirical record of the link between identity and survival for non-profit organizations however is mixed: 
-For example \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close, and \textcite{HernandezOrtiz_2022_discontinuity} observes a declining image or reputation as a cause of closure in a number of non-profits (p.115).
-Nonetheless, other studies find little to no effect of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
-\textcite{Walker_McCarthy_2010_survival} find support for some, but not all legitimacy indicators.
-
-Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
-Next to material organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate.
-However, the category of museums could be relatively flexible (for example, the term "museum" is generally not subject to state regulation in the US or Germany \parencite{Museumsbund_ICOMDE_2006_standards,Lister_2023_marketing}), which might result in a relatively high tolerance of diversity and hence limited devaluation of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.
-
-\bigbreak
-\noindent
-\textbf{Hypothesis 4}: Private museums with more understandable identities, indicated by adherence to naming conventions, are less likely to close.
-
-It is however necessary to consider that in particular the name of a museum might be associated with a museum's survival via identity, but also reflect founder intentions regarding the institutions longevity; this possibility is discussed in more detail in the results section.
 \subsection*{Methods and Data}
@@
 Currently, the database includes 550 museums, of which 453 are currently open, 72 have closed and 25 have transformed into other organizational forms.\footnote{The 25 institutions which were private museums at some point and have since been transformed into other organizational forms are not included in this analysis and discussed in the limitations.}
-Using this database, in particular year of opening and, if available, closing, it is possible to reconstruct the life course of the each institution with museum-year as the unit of analysis.
+Using this database, in particular year of opening and, if available, closing, it is possible to reconstruct the life course of each institution with museum-year as the unit of analysis.
 While the database is not limited to private museums of a particular time period, due to the recency of the private museum boom in the last two decades 80\% of the museums included in it have opened after 2000.
-As the databse was constructed retrospectively from 2020 to 2022, I focus here on closing events from 2000 to 2021 to limit the possibility that some institutions were missed, as such risks are likely higher for earlier time periods.
+As the database was constructed retrospectively from 2020 to 2022, I focus here on closing events from 2000 to 2021 to limit the possibility that some institutions were missed, as such risks are likely higher for earlier time periods.
 Furthermore, a small number of museums are excluded, in particular 2 museums for which the closing date could not be found, 17 museums which opened in 2021 and later (as survival analyses requires positive survival times), 1 museum the opening year of which could not be determined, as well as 2 museums which closed before 2000 and thereby fall outside the period under investigation.

### 2024-10-04 scripts/cfg.R
add some numbers, update sumstat tables

@@ -262,7 +262,7 @@ gc_vvs <- function() {
         pmdens_cry                = "PM density (country)",
         "I(pmdens_cry^2)"         = "PM density^2 (country)",
         popm_circle10             = "Pop. (millions) within 10km",
-        popm_country              = "Pop. (millions) country",        
+        popm_country              = "Pop. (millions) country",
         proxcnt10                 = "Nbr PM within 10km",
         "I(proxcnt10^2)"          = "Nbr PM^2 within 10km",
         pmdens_circle10           = "PM density (10km)",
@@ -270,8 +270,8 @@ gc_vvs <- function() {
         pmdens_circle10_log       = "PM density (10km, log)",
         "I(pmdens_circle10_log^2)"= "PM density (10km, log^2)",
         "proxcnt10:popm_circle10" = "Nbr PM (10km) * Pop (10km)",
-        
         proxcnt10_log             = "Nbr PM within 10km (log)",
+
         popm_circle10_log         = "Pop. (millions) within 10km (log)",
         
         
@@ -286,6 +286,8 @@ gc_vvs <- function() {
         "I(audience10^2)"         = "Local Audience per PM^2",
         audience10_log            = "Local Audience per PM (log)",
         "I(audience10_log^2)"     = "Local Audience per PM (log)^2",
+        recession                 = "Great Recession (2008/09)",
+        covid                     = "Covid Pandemic (2020/21)",
         iso3c                     = "Country",
         west                      = "Europe and North America",
         reg6                      = "Region",
@@ -293,6 +295,7 @@ gc_vvs <- function() {
         an_inclusion              = "ArtNews Ranking inclusion",
         exhbany                   = "Exhibition any",
         exhbrollany               = "Exhibition any last 5 years",
+
         exhbqntl_roll             = "Exhibition Quantile (year, rolled)",
         "I(exhbqntl_year^2)"      = "Exhibition Quantile (year)^2",
         exhbqntl_cy               = "Exhibition Quantile (CY)",
@@ -301,6 +304,7 @@ gc_vvs <- function() {
         exhbqntl_year             = "Exhibition Quantile (year)",
         exhbprop_top10_log        = "Exh. top 10% (log)",
         exhbprop_top10_utf        = "Exh. top 10%",
+
         "I(exhbqntl_roll^2)"      = "Exhibition Quantile^2 (year, rolled)",
         PC1                       = "PC1 (Size)",
         PC2                       = "PC2 (Support)",
[…]

### 2024-10-04 scripts/closing_main.R

@@ -72,6 +72,9 @@ gd_nbrs <- function() {
         list(nbr_name = "pm_n_used",     nbr_fmt = dt_pmyear[, fnunique(ID)]),
         list(nbr_name = "n_pm_close_after_recent_death",
              nbr_fmt = dt_pmyear[founder_dead5 == "recently_dead" & closing == 1, .N]),
+        list(nbr_name = "pmyear_proxcnt10_geq0",
+             nbr_fmt = dt_pmyear[, .(proxcnt10 = sum(proxcnt10 > 0), .N), year] %>%
+                 .[, perc := 100*(proxcnt10/N)] %>% .[, mean(perc)] %>% format(digits = 2)),
         list(nbr_name = "pm_open_from2021",
              nbr_fmt=dt_pmdb[year_opened>= 2021 & museum_status %in% c("private museum", "closed"),.N])) %>%        
         rbindlist

### 2024-10-04 scripts/descriptives.R

@@ -100,7 +100,8 @@ gt_sumstats <- function(dt_pmyear, dt_pmcpct) {
         Reduce(cbind, .) %>% adt %>%
         melt(measure.vars = names(.), variable.name = "term") %>%
         .[, .(pm_mean = mean(value), pm_sum = sum(value)), term]
-    
+
+        
     ## combine pm-year-level and pm-level data, reorder
     dt_cbn2 <- copy(dt_cbn)[dt_sumry_pm, `:=`("pm_mean" = i.pm_mean, "pm_sum" =  i.pm_sum), on = "term"] %>%
         .[, vrbl := factor(vrbl, levels = levels(c_vvs$dt_vrblinfo$vrbl))] %>% # somehow necessary to relevel? 
@@ -109,10 +110,14 @@ gt_sumstats <- function(dt_pmyear, dt_pmcpct) {
     ## create summary column names
     sumstats_cols <- c("grp_filler" = "", "term_lbl" = "Variable", "pm_sum" = "Count", "pm_mean" = "Mean",
                        "mean" = "Mean", "sd" = "SD", min = "Min.", max = "Max.")
+
     
     ## variables to yeet from table
     vrbls_toyeet <- c("mow", "year", "exhbrollany", "PC1", "PC2", "popm_country", "west", "year",
-                      "pmdens_circle10")
+                      "pmdens_circle10", "regsub", "time_period", "year_opened", "founder_dead1",
+                      "pmdens_circle10", "pmdens_circle10_log", "proxcnt10_log", "audience10", "audience10_log",
+                      "popm_circle10_log", "exhbany")
+    
 
     ## format the columns
     dt_cbn_viz <- copy(dt_cbn2) %>%

### 2024-10-04 texts/paper_closing.tex
minor rewriting/relabellign, move museum regulation to measurement

@@
-% Created 2024-10-03 do 13:26
+% Created 2024-10-04 vr 15:42
 % Intended LaTeX compiler: pdflatex
@@
 
-\subsubsection*{definition}
-
 While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{diMaggio_1982_boston,Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than e.g.
@@
 Existing research on private museum is conducted primarily by scholars of the art field or market as well as art historians.
-Nethertheless, the identification of the centrality of the founder as a critical source of vulnerability corresponds strongly to the finding in non-profit management of a relation between diversification and mortality \parencite{Tuckman_Chang_1991_vulnerability}.
+Nethertheless, the identification of the centrality of the founder as a critical source of vulnerability corresponds strongly to the finding in non-profit management of a relation between diversification and mortality \parencite{Tuckman_Chang_1991_vulnerability,Hung_Hager_2018_diversification}.
 For example, \textcite{Bielefeld_1994_survival} finds that nonprofits with a larger number of funding sources (e.g.
@@
 While limited research exists that investigates reputation effects for (art) museums, its effects have been investigated for non-profits more widely.
-Here reputation is often referred to as an organization's resource or asset \parencite{Kong_Farrell_2010_image,Goldfarb_Zavyalova_Pillai_2018_Rao,Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}.
-Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survial \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}\footnote{Furthermore, the term "survival" is sometimes used more loosely to refer to a non-profit's effective operation and financial condition rather than the more narrowly defined dissolution (e.g.
+Here reputation is often referred to as an organization's resource or asset \parencite{Kong_Farrell_2010_image,Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}. 
+Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survial \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}\footnote{Furthermore, the term "survival" is sometimes used more loosely to refer to a non-profit's effective operation and financial health rather than the more narrowly defined dissolution (e.g.
 \cite[p.58]{Santos_Laureano_Moro_2019_reputation}, \cite[p.15]{Heller_2008_alliances}, \cite[p.111]{Schloderer_Sarstedt_Ringle_2014_reputation})}, with most studies finding support for a positive effect of reputation.
@@
 
-In the case of the founder losing his reputation, the consequences then might extend beyond personal demotivation.
+In the case of the founder losing their reputation, the consequences then might extend beyond personal demotivation.
 Such a decline could also curtail potential opportunities for cooperation with other institutions and limit the museum's reach to larger audiences, thus posing a risk to the museum's continued operation and survival in the long term.
@@
 The perception of the museum itself, beyond the reputation of the founder, might also affect survival prospects.
-An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns  \parencite{Lange_Lee_Dai_2010_reputation}, which in turn can facilitate survival prospects \parencite{Rao_1994_reputation}.
+As has also been summarized in the previous section, an identity that is legitimate (understandable) and favorable (positive) has been argued to have a large number of positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns \parencite{Lange_Lee_Dai_2010_reputation}, which in turn can facilitate survival prospects \parencite{Rao_1994_reputation}.
 In the context of private museums, a more positive identity could lead to higher visitor numbers, discounts from art dealers, government grants or collaborations with other museums or corporations, resulting in higher revenues and lower acquisition costs.
 
-Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
-Next to material organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate.
-However, the category of museums could be relatively flexible (for example, the term "museum" is generally not subject to state regulation in the US or Germany \parencite{Museumsbund_ICOMDE_2006_standards,Lister_2023_marketing}), which might result in a relatively high tolerance of diversity and hence limited devaluation of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.
+A favorable identity might be obtained by isomorphism, i.e. adopting features from established organizational  blueprints \parencite{diMaggio_1983_iron}.
+Next to material organizational features, adherence to symbolic features such as naming conventions has been found to enhance perceptions of legitimacy; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate \parencite{Glynn_Abzug_2002_names}.
+Assuming that such a legitimacy effect translates into better survival prospect, a hypothesis can be formulated as:
 
@@
 \noindent
-\textbf{Hypothesis 4}: Private museums with more understandable identities, indicated by adherence to naming conventions, are less likely to close.
+\textbf{Hypothesis 2}: Private museums with more understandable identities, indicated by adherence to naming conventions, are less likely to close.
 
-It is however necessary to consider that in particular the name of a museum might be associated with a museum's survival via identity, but also reflect founder intentions regarding the institutions longevity; this possibility is discussed in more detail in the results section.
+It is however necessary to consider that the name of a museum might be associated with a museum's survival not only via its perception by other parties, but also via reflection of the founder's intentions regarding the institutions longevity; this possibility is discussed in more detail in the results section.
 \paragraph*{Competition}
@@
 Partial maximum likelihood estimation allows calculating \(\beta\) without defining the baseline hazard rate, which therefore is not constrained to a parametric form \parencite{Moore_2015_survival}.
-\subsubsection*{Main Predictors (Cox Proportional Hazards Model)}
+\subsubsection*{Main Predictors}
 
@@
 A measure of founder death is constructed as a time-varying covariate, which takes the value of 1 from the year of the founder's death onwards.
-\paragraph*{Legitimacy}
+\paragraph*{Founder reputaton}
+
+Founder reputation is measured via inclusion of the founder in the Artnews top 200 collector ranking \parencite{Artnews_ranking}.
+This ranking, established in 1990, lists each year the 200 collectors the editors of the magazine consider most relevant.
+For each year, a museums can have one of three values: "Not included"; in which case the founder is not included in the year in question and has not been so in the past, "Included"; when the founder is included, or "Dropped", for cases where the founder was included at some point in the past but is no longer included in the current year.
+Cases where multiple individuals are involved in the founding of a private museum are resolved by aggregating the Artnews ranking inclusion history to the founder level (i.e., if only one of two founders is dropped from the Artnews ranking but the other remains included, the founder couple as a whole is considered included).
+The variable is lagged by one year to avoid reverse causality, i.e.
+to exclude the possibility that an association is observed which is present due to founders being dropped from the ranking as a consequence of the closure of their museum.
+\paragraph*{Museum Identity}
 
@@
 
-Two measures are constructed that aim to capture an effect of legitimacy on closing.
-First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
+Self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
 Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might shape expectations and influence forms of engagement.
-In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums.
+In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums, leading to higher survival prospects.
 
@@
 In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum.}
-\paragraph*{Reputation}
-
-Reputation is measured via inclusion of the founder in the Artnews top 200 collector ranking \parencite{Artnews_ranking}.
-This ranking, established in 1990, lists each year the 200 collectors the editors of the magazine consider most relevant.
-For each year, a museums can have one of three values: "Not included"; in which case the founder is not included in the year in question and has not been so in the past, "Included"; when the founder is included, or "Dropped", for cases where the founder was included at some point in the past but is no longer included in the current year.
-Cases where multiple individuals are involved in the founding of a private museum are resolved by aggregating the Artnews ranking inclusion history to the founder level (i.e., if only one of two founders is dropped from the Artnews ranking but the other remains included, the founder couple as a whole is considered included).
-The variable is lagged by one year to avoid reverse causality, i.e.
-to exclude the possibility that an association is observed which is present due to founders being dropped from the ranking as a consequence of the closure of their museum.
+At the same time, for an association between name and survival to be attributed to the name, the name and other organizational characteristics cannot be linked too closely.
+This seems to be the case for museums, where membership is not subject to strong regulations: 
+The term "museum" is not a protected term in the US \parencite[p.205]{Moore_2022_best} or European countries such as Germany \parencite[p.4]{Museumsbund_ICOMDE_2006_standards}, Denmark, Austria, Croatia or Finland \parencite{EGMUS_2024_reports}\footnote{While I was not able to find concrete information on the naming regulations of museums for every country, I did not find any country where such naming regulation is present.}.
+Neither is membership in national or international museum associations necessary for an institution to be recognized as a museum: 
+ICOM has around 3,000 institutional members \parencite{ICOM_2020_report19}, a relatively small fraction of the over 104,000 museums estimated to exist globally \parencite{UNESCO_2021_covid}, and while national associations fare somewhat better, with e.g.
+the American Association of Museums representing over 4,000 of the country's 35,000 museums \parencite{LOC_2019_AAM}, and the German Museumsbund representing over 1,300 \parencite{Museumsbund_2024_mitgliedmuseen} of Germany's 7,120 museums \parencite{IMF_2024_museumsstatistik}, the ability of these associations to impose standards is still limited.
+In such an unregulated field, names do not clearly reflect institutional characteristics, which leaves evaluation of a musem to less institutionalized practical classification systems \parencite{van_Venrooij_2018_fuzziness}.
 \paragraph*{Competition}
@@
 I then use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
-To be able to estimate both competition and demand/audience/population separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two.
+To be able to estimate both competition and population effects separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two (alternative specifications are presented in the supplementary materials).
+While this operationalization is limited to private museum in the neighborhood, rather than the more complete set of all museums private museums may compete with, it is by no means a rarity to find private museums within a 10 km radius, as in 41\% museum-years one or more private museums in the surroundings are observed.
 \subsubsection*{Control variables}
@@
 
+On the level of museum, I control for whether a museum includes the name of the founder (e.g. "Liam's Gallery" includes the name of the founder).
+As another property of the name, it might be indicative of the commitment founder, but it might also might support by third parties less attractive.
+
 External shocks might interrupt operations, which reduces income from tickets, as well as make other donors more hesitant to commit money in uncertain times.
@@
 % latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep 27 17:51:17 2024
+% Fri Oct  4 15:36:13 2024
 \begin{table}[ht]
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 294 & 0.584 &  6.0e-01 &  0.489 & 0 & 1 \\ 
-   & Gender - Female & 79 & 0.157 &  1.7e-01 &  0.372 & 0 & 1 \\ 
-   & Gender - Couple & 130 & 0.258 &  2.3e-01 &  0.421 & 0 & 1 \\ 
-   & Founder - alive &  &  &  9.0e-01 &  0.296 & 0 & 1 \\ 
-   & Founder - died recently &  &  &  1.3e-02 &  0.115 & 0 & 1 \\ 
-   & Founder - died 2+ years ago &  &  &  8.4e-02 &  0.277 & 0 & 1 \\ 
-   & Founder died &  &  &  9.7e-02 &  0.296 & 0 & 1 \\ 
+ & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
+   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
+   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
+   & Founder died &  &  & 0.097 & 0.30 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 190 & 0.378 &  4.1e-01 &  0.491 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 104 & 0.207 &  1.9e-01 &  0.391 & 0 & 1 \\ 
-   & Self-Identification - Collection & 69 & 0.137 &  1.3e-01 &  0.336 & 0 & 1 \\ 
-   & Self-Identification - Other & 140 & 0.278 &  2.7e-01 &  0.446 & 0 & 1 \\ 
-   & Founder name in Museum name & 240 & 0.477 &  4.8e-01 &  0.500 & 0 & 1 \\ 
-   & AN Ranking - Not Included &  &  &  8.0e-01 &  0.398 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  &  1.4e-01 &  0.351 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  &  5.3e-02 &  0.225 & 0 & 1 \\ 
-   & Exhibition any &  &  &  6.3e-01 &  0.483 & 0 & 1 \\ 
-   & Opening year &  &  &  2.0e+03 & 11.104 & 1960 & 2020 \\ 
+ & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
+   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
+   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
+   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
+   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
+   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
+   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
+   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density (country) &  &  &  4.5e-01 &  1.261 & 0.00077 & 27.26 \\ 
-   & Pop. (millions) within 10km &  &  &  1.3e+00 &  1.682 & 0.000087 & 10.81 \\ 
-   & Nbr PM within 10km &  &  &  1.8e+00 &  3.143 & 0 & 16 \\ 
-   & PM density (10km, log) &  &  &  5.3e-01 &  0.786 & 0 & 4.35 \\ 
-   & Nbr PM within 10km (log) &  &  &  6.1e-01 &  0.816 & 0 & 2.83 \\ 
-   & Pop. (millions) within 10km (log) &  &  & -8.9e-01 &  1.966 & -9.3 & 2.38 \\ 
-   & Local Audience per PM &  &  &  5.7e-01 &  0.865 & 0.000087 & 8.16 \\ 
-   & Local Audience per PM (log) &  &  & -1.5e+00 &  1.638 & -9.3 & 2.10 \\ 
-   & Region - Africa & 8 & 0.016 &  1.2e-02 &  0.110 & 0 & 1 \\ 
-   & Region - Asia & 142 & 0.282 &  2.9e-01 &  0.455 & 0 & 1 \\ 
-   & Region - Europe & 248 & 0.493 &  5.0e-01 &  0.500 & 0 & 1 \\ 
-   & Region - Latin America & 23 & 0.046 &  4.2e-02 &  0.201 & 0 & 1 \\ 
-   & Region - North America & 72 & 0.143 &  1.4e-01 &  0.345 & 0 & 1 \\ 
-   & Region - Oceania & 10 & 0.020 &  1.9e-02 &  0.135 & 0 & 1 \\ 
-   & UN Subregion - Northern Africa & 1 & 0.002 &  8.2e-04 &  0.029 & 0 & 1 \\ 
-   & UN Subregion - Northern America & 72 & 0.143 &  1.4e-01 &  0.345 & 0 & 1 \\ 
-   & UN Subregion - Eastern Asia & 96 & 0.191 &  2.2e-01 &  0.411 & 0 & 1 \\ 
-   & UN Subregion - Southern Asia & 9 & 0.018 &  1.5e-02 &  0.120 & 0 & 1 \\ 
-   & UN Subregion - South-eastern Asia & 12 & 0.024 &  2.5e-02 &  0.155 & 0 & 1 \\ 
-   & UN Subregion - Southern Europe & 70 & 0.139 &  1.5e-01 &  0.361 & 0 & 1 \\ 
-   & UN Subregion - Australia and New Zealand & 10 & 0.020 &  1.9e-02 &  0.135 & 0 & 1 \\ 
-   & UN Subregion - Western Asia & 25 & 0.050 &  3.7e-02 &  0.189 & 0 & 1 \\ 
-   & UN Subregion - Eastern Europe & 22 & 0.044 &  5.0e-02 &  0.218 & 0 & 1 \\ 
-   & UN Subregion - Northern Europe & 27 & 0.054 &  5.7e-02 &  0.231 & 0 & 1 \\ 
-   & UN Subregion - Western Europe & 129 & 0.256 &  2.4e-01 &  0.425 & 0 & 1 \\ 
-   & UN Subregion - Sub-Saharan Africa & 7 & 0.014 &  1.1e-02 &  0.107 & 0 & 1 \\ 
-   & UN Subregion - Latin America and the Caribbean & 23 & 0.046 &  4.2e-02 &  0.201 & 0 & 1 \\ 
-   & Time Period 2000-2004 &  &  &  1.0e-01 &  0.301 & 0 & 1 \\ 
-   & Time Period 2005-2009 &  &  &  1.7e-01 &  0.372 & 0 & 1 \\ 
-   & Time Period 2010-2014 &  &  &  2.6e-01 &  0.438 & 0 & 1 \\ 
-   & Time Period 2015-2019 &  &  &  3.3e-01 &  0.471 & 0 & 1 \\ 
-   & Time Period 2020-2024 &  &  &  1.4e-01 &  0.352 & 0 & 1 \\ 
-   & Great Recession (2008/09) &  &  &  7.6e-02 &  0.265 & 0 & 1 \\ 
-   & Covid Pandemic (2020/21) &  &  &  1.4e-01 &  0.352 & 0 & 1 \\ 
+ & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
+   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
+   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
+   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
+   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
+   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
+   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
+   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
+   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
+   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
+   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
    \hline
@@
 Before discussing the regression models, I provide a descriptive account on private museum closure using the hazard and survival functions which describe variation the closing risk over the museum life-course.
-The hazard rate is a non-parametric function which describes the probability of exiting at age \(t_i\) (conditional on being alive), in the context of museum-years as units of analysis it can be formulated as \(h(t_i) = \frac{d_i}{n_i}\), with \(n_i\) as the number of units at risk at age \(t_i\) and \(d_i\) as the number of exits at age \(t_i\).
+The hazard rate is a non-parametric function which describes the probability of exiting at age \(t_i\) conditional on being alive, in the context of museum-years as units of analysis it can be formulated as \(h(t_i) = \frac{d_i}{n_i}\), with \(n_i\) as the number of units at risk at age \(t_i\) and \(d_i\) as the number of exits at age \(t_i\).
 The survival function is the product of these conditional probabilities (\(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\)) and describes the chance of surviving up to age \(t_i\).
@@
 So far only a small number of studies has investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
-Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form data is publicly available \parencite{Lecy_2023_core,Lecy_2023_core}.
+Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form 990 data is publicly available \parencite{Lecy_2023_core}.
 This data has been used in many studies of non-profit populations, and constitutes an effective comparison group for private museums as both share the same organizational form (non-profit) and unprofitable cultural sector environment.
-So far three studies have used this data to investigate museum closure by calculating hazard rates not as a function of age age but of calendar year:
+So far three studies have used this data to investigate museum closure by calculating hazard rates not as a function of age but of calendar year:
 \begin{itemize}
 \item \textcite{Bowen_etal_1994_charitable} investigate the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
-\item \textcite{Gordon_etal_2013_insolvency} observe 35 closures over the years of 2000-2003 with 5,167 museum-years (p.368), resulting in an average annual closing rate of 0.68\% (p.377).
+\item \textcite{Gordon_etal_2013_insolvency} observe 35 closures based on 5,167 museum-years between 2000 and 2003 (p.368), resulting in an average annual closing rate of 0.68\% (p.377)\footnote{The difference to \cite{Bowen_etal_1994_charitable} is likely due to exclusion of organizations with revenues below 150,000 USD.}.
 \item \textcite{Hager_2001_vulnerability} has conducted the only study specifically on art museums (NTEE code A51); he observes 42 closures over a period of four years (1994-1997) from a starting populaton of 448 (p.383), corresponding to an average yearly closing rate of 2.4\%, or around 1.9\% under the more realistic assumption of effectively using a five-year time period.
@@
 First, this measure of overall museum closing rates cannot take museum-level variables into account, thus direct comparability hinges on the assumption that on private museums display a similar distribution of survival-relevant attributes to US non-profit museums.
-More specifically, private museums might have such disproportionately high assets and/or revenues that the appropriate comparison group would not be the entire (art) museum population, but rather only its in wealthiest half, third or quarter, which in turn could be characterized by substantially higher survival rates (such a size difference likely explains the difference between the hazard rates of \textcite{Gordon_etal_2013_insolvency} and \textcite{Bowen_etal_1994_charitable}, as the former only includes museums with operational revenues above 150,000 USD).
 Secondly, as previous studies have focused exclusively on the US, survival rates for non-profits in other countries might differ, for example in particular in Europe one possible reason might be more public support for non-profits.
 While additional analyses, reported in the supplementary materials, do not indicate a substantial influence of time-invariant country (or region) factors on private museum closing, mortality of non-private museums might be stronger influenced by these country-level factors.
-Thirdly, a number of limitations of form 990 data might lead to inaccurate mortality estimates in the first place.
-As closure is generally estimated from non-filing for a number of years, incorect closing assessments and mortality estimates can arise as organizations continue operations without filing, file but continue to exist only on paper, or transform thus producing records of several organizations while effectively only a single organization exists \parencite{Bielefeld_1994_survival}.
-Taken together, these factors substantially limit the extent to which a lack of difference in closing rates between private museum and American non-profit museums in general is indicative of similar sustainability of these different organizational populations.
+While thus a comparison of closing rates of different museum populations provides initial insights, a more extensive comparative investigation would be necessary to further assess how closing rates of private museums correspond to those of other museum populations.
 \subsubsection*{Regression Results}
@@
 
-Neither gender of the founder nor external shocks (the Great Recession and the Covid-19 Pandemic) are associated with significantly higher closing rates.
-Given the non-significant gender difference, it can be expected that the population of private museums will continue to remain a man-dominated affair, unless a strong increase in museum founding by women takes place.
+Neither gender of the founder, inclusion of the founder name in the museum name nor external shocks (the Great Recession and the Covid-19 Pandemic) are associated with significantly higher closing rates.
+Given the non-significant gender difference, it can be expected that the population of private museums founders will continue to remain predominantly male, unless a strong increase in museum founding by women takes place.
 At the same time, this finding also provides no evidence that female founders face gender-specific challenges, at least not to an extent that these decrease the survival prospects of their private museums.
+Museums whose name contain the name of the founder face a non-significantly 4.9\% elevated risk of closure, which indicates that there is little evidence that founders face greater difficulties to secure a long-term future for their museums by choosing to emphasize their personal contribution.
+A possible explanation might be that even when other parties do indeed feel less inclined to contribute, these gaps are filled by a stronger commitment of the founder, who having committed her name to the initiative, wants to keep the museum open event at great costs.
 The insignificance of the coefficients of the external shocks indicate that museums are overall relatively resilient; possibly unlike other types of art organizations with lower assets and higher reliance on earned incomes \parencite[p.102]{Bowen_etal_1994_charitable}.
-\paragraph*{Founder dependence (H2)}
+\paragraph*{Founder dependence (H1)}
 
@@
 The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e.
-museums are not significantly more likely to close after their founder has died, which provides little support to H2a.
-While the point estimate is positive (0.280, corresponding to a  32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that despite the cumulative character even decade-long survival times do not differ substantially (figure \ref{fig:p_surv_death}).
+museums are not significantly more likely to close after their founder has died, which provides little support to H1a.
+While the point estimate is positive (0.280, corresponding to a 32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that even decade-long survival prospects do not differ substantially despite the cumulative character of risk (figure \ref{fig:p_surv_death}).
 
@@
 
-Museums whose name contain the name of the founder face a non-significantly 4.9\% elevated risk of closure, which indicates that there is little evidence that founders face greater difficulties to secure a long-term future for their museums by choosing to emphasize their personal contribution; thus providing no support for hypothesis 2c.
-A possible explanation might be that even when other parties do indeed feel less inclined to contribute, these gaps are filled by a stronger commitment of the founder, who having committed her name to the initiative, wants to keep the museum open event at great costs.
+Taken together, the inability to explain private museum closing with the death of founder and her exclusion from a prestitious ranking question the hypothesized central role of the founder (Hypothesis 1).
+In other words, so far little evidence points to low diversification, i.e. reliance on founders, as a substantial source of involuntary closing risk for private museums.
+\paragraph*{Museum Identity (H2)}
 
-Taken together, the inability to explain private museum closing with the death of founder, her exclusion from a prestitious ranking and the presence of her name in the museum's name question the hypothesized central role of the founder (Hypothesis 2).
-In other words, so far little evidence points to low diversification, i.e. reliance on founders, as a substantial source of involuntary closing risk for private museums.
+Museums which include the term "collections" in their name are the least likely to close (0.63 times the rate of museums with the name "museum", while those with the term "foundation" experience a closing rate elevated by 23\%; yet both of these differences are statistically significant.
+However, institutions which include neither of these are the most likely to close, and have mortality rates almost three times as high (198\%) than institutions including the term "museum".
+The usage of unconventional names might reflect adherence to museum standards which makes museums more understandable and familiar to third parties (e.g.
+audiences, other museums, companies or the government) and thereby facilitates interactions which are beneficial for long-term survival (e.g.
+attracting visitors, cooperations, sponsorships or subsidies).
+However, as founders can choose the name of their museum arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.
+Some support for the latter interpretaton is given by the fact that two of the three museums for which \textcite{Velthuis_Gera_2024_fragility} identify a temporal intention as the closing reason do not self-identify as museum, collection or foundation.
+A temporal intentions are however the exceptions among closing reasons identified by \textcite{Velthuis_Gera_2024_fragility} (p.6), and as similarly only a fraction of private museum chooses such a name (140 museums, or 28\%), the overall proportion of these types of voluntary closures compared to all closures is presumably limited.
 \paragraph*{Competition (H3)}
@@
 While not all associations correspond to predictions made by resource dependence, the most direct measurement of increased competition, number of private museums in the local surrounding, is associated with higher closing chances for a large part of the sample, which in turn supports the substantial role of competition (H3).
-\paragraph*{Identity (H4)}
-
-Museums which include the term "collections" in their name are the least likely to close (0.63 times the rate of museums with the name "museum", while those with the term foundation experience 23\% elevated closure rates (but not significantly higher).
-However, institutions which include neither of these are the most likely to close, and have mortality rates almost three times as high (198\%) than institutions including the term "museum".
-The usage of unconventional names might reflect adherence to museum standards which makes museums more understandable and familiar to third parties (e.g.
-audiences, other museums, companies or the government) and thereby facilitates interactions which are beneficial for long-term survival (e.g.
-attracting visitors, cooperations, sponsorships or subsidies).
-However, as founders can choose the name of their museum arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.
-Some support for the latter interpretaton is given by the fact that two of the three museums for which \textcite{Velthuis_Gera_2024_fragility} identify a temporal intention as the closing reason do not self-identify as museum, collection or foundation.
-A temporal intentions are however the exceptions among closing reasons identified by \textcite{Velthuis_Gera_2024_fragility} (p.6), and as similarly only a small fraction of private museum chooses such a name (140 museums, or 28\%), the overall proportion of these types of voluntary closures compared to all closures is presumably limited.
 \subsection*{Discussion and Conclusion}
@@
 So far only a small fraction (47 museums, 9.3\%) of museums has experienced the death of their founder, one of the primary reasons hypothesized to lead to the private museum closure. 
-While so far these museums have not seen substantially elevated closing risks, these estimates will become more precise as more founders pass away.
+While so far these museums have not seen significantly elevated closing risks, these estimates will become more precise as more founders pass away.
 As the currently large confidence interval (figure \ref{fig:p_surv_death}) for museums whose founders have died allows a wide range of survival chances, it is entirely possible that previous scholars have indeed correctly identified a key dependency (the current absence of evidence of it should not be taken as evidence of absence) and that therefore later analyses will a significantly association between founder death and closing risk as well as a higher average closing risk for private museums.\footnote{Similarly, as 80\% of private museums have been founded in the new millenium, only a few museums have so far reached an age above 30 years, which makes the estimation of the age-dependent hazard for this age range highly speculative.}
@@
 
-While overall private museum closing rates are generally not diverging from museums in general, it has to be kept in mind that this comparison is based on American non-profit museums.
-To my knowledge, currently no data sources exist that allow estimation of closing rates of (European) public, state-funded museums.
-Although I argue that the American non-profit museums serve as a better comparison to evaluate private museum surival rates than state-funded museums because the comparison allows to focus on the centrality of the founder, the contrast to public museums would still provide additional insights into the relationship between ownership and survival rates.
-While public museums have been characterized to some extent as very stable due to government picking up deficits \parencite{Meier_Frey_2003_faces,Bechtler_Imhof_2018_future}, \textcite{Walker_2019_collector} argues that due to declining cultural spending even public museums might face hard times.
-Most national public flagship institutions might remain sufficiently funded to survive, however this may not be the case for the much larger of smaller museums in less touristic regions who rely on more limited municipal funding (49\% of the European museum population, \cite{EGMUS_2024_complete}), as \textcite{StylianouLambert_etal_2014_museums} explore for a number of smaller publicly funded ethnography museums in Cyprus.
-Yet without access to museum registers comparable to the IRS/NCCS datasets, such questions of the relation between a wider range of organizational form and survival remain speculative.
-
-The primary mechanism that has been argued to lead to museum closure is costs, and while this study measures it indirectly, primarily through indicators on the level of the founder, museum and environment, the financial situation of a museum is not used directly.
+The primary mechanism that has been argued to lead to museum closure is costs, and while this study measures it indirectly, primarily through indicators on the level of the founder, museum and environment, the effect of the financial situation of a museum is not investigated directly.
 The primary reason for this is data availability.
@@
 Similarly, other museum characteristics which were not considered here, such as as museum size, facilities, as well as marketing and outreach activities, might be related to long-term survival prospects.\footnote{While the original data collection included the assessment of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear during data analysis that the data collected was unsuitable to construct accurate indicators from these findings due to difficulty in assessing them in many cases.
-Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Wayback machine, less central pages (such as those with information about facilities and activities), were archived much less frequently, and sometimes inaccessible despite being archived due to changes in webtechnology (such as the retirement of Adobe flash).}
+Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Wayback machine, less central pages (such as those with information about facilities and activities), were archived much less frequently, and sometimes inaccessible despite being archived due to changes in webtechnology (such as the retirement of Adobe flash).
+Analysis based on this data are reported in the supplementary materials.}
 As such, private museums remain relatively intransparent, which does not prevent, but to some extent limits the identification of risk factors.

### 2024-10-04 texts/paper_closing.tex
cleanup, grammar/spellcheck

@@
-% Created 2024-10-04 vr 15:42
+% Created 2024-10-04 vr 17:56
 % Intended LaTeX compiler: pdflatex
@@
 
-In recent years, private collector-run museums have seen an unprecedented proliferation, with hundreds of organizations founded since the beginning of the millenium \parencite{Velthuis_etal_2023_boom,LarrysList_2015_report}.
+In recent years, private collector-run museums have seen an unprecedented proliferation, with hundreds of organizations founded since the beginning of the millennium \parencite{Velthuis_etal_2023_boom,LarrysList_2015_report}.
 These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums operated and financed by the state, foundations or associations.
@@
 In particular, I compare private museum closing rates to those of other museum populations, and analyze the risk associated with variables on the level of the founder, museum and environment. 
-Taken together, the results show that (at least so far) little evidence exists neither for private museums being overly dependend on their founder, nor having overall higher mortality rates than other non-profit museums.
-While little evidence points toward private museums being unvoluntarily at risk due to their low diversification, private museums may close due to environmental pressures, which exhibit a complex relationship which for most museums consists of competition from other private museums as well as, unexpectedly, large audiences.
+Taken together, the results show that (at least so far) little evidence exists neither for private museums being overly dependent on their founder, nor having overall higher mortality rates than other non-profit museums.
+While little evidence points toward private museums being involuntarily at risk due to their low diversification, private museums may close due to environmental pressures, which exhibit a complex relationship which for most museums consists of competition from other private museums as well as, unexpectedly, large audiences.
 Finally, private museums with unconventional names (in particular, without the term "museum" in the name) face a higher closing risk, which may indicate either a temporary intention by their founders from the very beginning and/or limited recognition by third parties as potential closing reasons.
@@
 The central role of the founder delimits a private museum from other organizational forms such as public museums supported by local or state governments, corporate museums run by companies or other non-profit museums operated by associations or foundations with more dispersed ownership and control.\footnote{Which is not to say that for an institution to be considered a private museum, it has to be legal personal ownership of the founder.
-Insted the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms; generally this has to be assessed on a case-by-case basis.}
+Instead the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms; generally this has to be assessed on a case-by-case basis.}
 
-Due to the founders central role, private museums have been argued to be highly dependent on their founder for their continuing existence, as museums generally cannot cover expenses via revenues from ticket prices, museum shops and cafes:
+Private museums have been argued to be highly dependent on their founder for their continuing existence, as museums generally cannot cover expenses via revenues from ticket prices, museum shops and cafes:
 The \textcite{IMLS_2008_funding} found that American non-profit art museums receive less than half (48.1\%) of their revenues from earned income, leaving substantial gaps in the budgets that are filled by a mix of private donations (23.0\%), investment (18.5\%) and government support (10.4\%) (p.27).
-Outside of the United States, the reliance on revenue streams beyond operations appears even larger:
+Outside the United States, the reliance on revenue streams beyond operations appears even larger:
 German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table b), p.233}, with private museums however requiring less support as operations provide around 47\% of their budget (ibid.).
@@
 
-Given that operating at "the margin of financial sustainability" is the "ordinary condition" for cultural NPOs, \parencite[p.2]{Licci_BaraldiBonini_2024_sustainability}, it is not surprising that costs have been listed as a primary reason for private museum closure:
+Given that operating at "the margin of financial sustainability" is the "ordinary condition" for Non-profit organizations (NPO) in the cultural sector, \parencite[p.2]{Licci_BaraldiBonini_2024_sustainability}, it is not surprising that costs have been listed as a primary reason for private museum closure:
 \textcite{Adam_2021_rise} argues that "most of the cases of defunct private museums come back to the issue of cost" (p.79); a sentiment shared by \textcite{Walker_2019_collector} who notes that "private institutions struggle to contain escalating costs that are associated with running a museum" (p.234).
@@
 
-A central reason for financial vulnerability has been argued to be the crucial reliance on the single founder, who, as the iniators of their private museums, likely have to contribute a large part of their institution's non-operating income \parencite{Frey_Meier_2002_beyeler}:
+A central reason for financial vulnerability has been argued to be the crucial reliance on the single founder, who, as the initiators of their private museums, likely have to contribute a large part of their institution's non-operating income \parencite{Frey_Meier_2002_beyeler}:
 \textcite{Adam_2021_rise} argues that "ultimately, many of these failures demonstrate the fragility of spaces that rely on a single founder, whose motivations and financial stability may change, or who may not have realised the difficulties inherent in establishing their own art space" (p.82).
@@
 Existing research on private museum is conducted primarily by scholars of the art field or market as well as art historians.
-Nethertheless, the identification of the centrality of the founder as a critical source of vulnerability corresponds strongly to the finding in non-profit management of a relation between diversification and mortality \parencite{Tuckman_Chang_1991_vulnerability,Hung_Hager_2018_diversification}.
+Nevertheless, the identification of the centrality of the founder as a critical source of vulnerability corresponds strongly to the finding in non-profit management of a relation between diversification and mortality \parencite{Tuckman_Chang_1991_vulnerability,Hung_Hager_2018_diversification}.
 For example, \textcite{Bielefeld_1994_survival} finds that nonprofits with a larger number of funding sources (e.g.
@@
 Here reputation is often referred to as an organization's resource or asset \parencite{Kong_Farrell_2010_image,Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}. 
-Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survial \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}\footnote{Furthermore, the term "survival" is sometimes used more loosely to refer to a non-profit's effective operation and financial health rather than the more narrowly defined dissolution (e.g.
-\cite[p.58]{Santos_Laureano_Moro_2019_reputation}, \cite[p.15]{Heller_2008_alliances}, \cite[p.111]{Schloderer_Sarstedt_Ringle_2014_reputation})}, with most studies finding support for a positive effect of reputation.
+Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survival \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}, with most studies finding support for a positive effect of reputation.
 Next to the reputation of the general public, studies have also found reputation effects among more narrowly defined groups, in particular peers \parencite{Padanyi_Gainer_2003_peerreputation} and networks of similar organizations on regional and national scale \parencite{Walker_McCarthy_2010_survival}.
@@
 The perception of the museum itself, beyond the reputation of the founder, might also affect survival prospects.
-As has also been summarized in the previous section, an identity that is legitimate (understandable) and favorable (positive) has been argued to have a large number of positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns \parencite{Lange_Lee_Dai_2010_reputation}, which in turn can facilitate survival prospects \parencite{Rao_1994_reputation}.
+As has also been summarized in the previous section, an identity that is legitimate (understandable) and favorable (positive) has been argued to have numerous positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns \parencite{Lange_Lee_Dai_2010_reputation}, which in turn can facilitate survival prospects \parencite{Rao_1994_reputation}.
 In the context of private museums, a more positive identity could lead to higher visitor numbers, discounts from art dealers, government grants or collaborations with other museums or corporations, resulting in higher revenues and lower acquisition costs.
@@
 
-It is however necessary to consider that the name of a museum might be associated with a museum's survival not only via its perception by other parties, but also via reflection of the founder's intentions regarding the institutions longevity; this possibility is discussed in more detail in the results section.
+It is however necessary to consider that the name of a museum might be associated with a museum's survival not only via its perception by other parties, but also via reflection of the founder's intentions regarding the institution's longevity; this possibility is discussed in more detail in the results section.
 \paragraph*{Competition}
@@
 Competition directly has not yet been investigated as a cause for private museum closing, but a possible mechanism of competition, "insufficient interest from the public", has been identified as the second most reported closure reason by \textcite[p.6]{Velthuis_Gera_2024_fragility}.
-Lack of interest by the public can result from multiple processes.
+Lack of interest from the public can result from multiple processes.
 While competition is one such processes, and applies if nearby competing institutions capture large portions of the audience, lack of interest can also result from a lack of audience (in the absence of competing institutions), which may be the case for private museums located in sparsely populated areas.
@@
 As the database was constructed retrospectively from 2020 to 2022, I focus here on closing events from 2000 to 2021 to limit the possibility that some institutions were missed, as such risks are likely higher for earlier time periods.
-Furthermore, a small number of museums are excluded, in particular 2 museums for which the closing date could not be found, 17 museums which opened in 2021 and later (as survival analyses requires positive survival times), 1 museum the opening year of which could not be determined, as well as 2 museums which closed before 2000 and thereby fall outside the period under investigation.
+Furthermore, a small number of museums are excluded, in particular 2 museums for which the closing date could not be found, 17 museums which opened in 2021 and later (as survival analysis requires positive survival times), 1 museum the opening year of which could not be determined, as well as 2 museums which closed before 2000 and thereby fall outside the period under investigation.
 This leaves 503 private museums at risk which have accumulated 6096 museum-years and 68 closures.
-This data allows to conduct survival analysis (also known as event history analysis), the most common statistical technique to investigate hazard rates and identify mortality-assocated covariates \parencite{Moore_2015_survival,Allison_2014_event}.
+This data is well-suited for survival analysis (also known as event history analysis), the most common statistical technique to investigate hazard rates and identify mortality-associated covariates \parencite{Moore_2015_survival,Allison_2014_event}.
 
-In particular, Cox proportional hazard models allows to identify the risk that a number of variables pose for a museum's chance of closing. 
+In particular, I use the Cox proportional hazard model to identify the risk that a number of variables pose for a museum's chance of closing. 
 The dependent variable is an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
@@
 The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
-Partial maximum likelihood estimation allows calculating \(\beta\) without defining the baseline hazard rate, which therefore is not constrained to a parametric form \parencite{Moore_2015_survival}.
 \subsubsection*{Main Predictors}
@@
 
-A measure of founder death is constructed as a time-varying covariate, which takes the value of 1 from the year of the founder's death onwards.
+A measure of founder death is constructed as a time-varying covariate with values of 1 from the year of the founder's death onwards and 0 otherwise.
 \paragraph*{Founder reputaton}
@@
 This ranking, established in 1990, lists each year the 200 collectors the editors of the magazine consider most relevant.
-For each year, a museums can have one of three values: "Not included"; in which case the founder is not included in the year in question and has not been so in the past, "Included"; when the founder is included, or "Dropped", for cases where the founder was included at some point in the past but is no longer included in the current year.
-Cases where multiple individuals are involved in the founding of a private museum are resolved by aggregating the Artnews ranking inclusion history to the founder level (i.e., if only one of two founders is dropped from the Artnews ranking but the other remains included, the founder couple as a whole is considered included).
+For each year, a museum can have one of three values: "Not included"; in which case the founder is not included in the year in question and has not been so in the past, "Included"; when the founder is included, or "Dropped", for cases where the founder was included at some point in the past but is no longer included in the current year.
+Cases where multiple individuals are involved in the founding of a private museum are resolved by aggregating the Artnews ranking inclusion history to the founder level (i.e., if only one of two founders is dropped from the Artnews ranking, but the other remains included, the founder couple as a whole is considered included).
 The variable is lagged by one year to avoid reverse causality, i.e.
@@
 
-Self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
+Self-identification measures whether the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
 Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might shape expectations and influence forms of engagement.
@@
 Neither is membership in national or international museum associations necessary for an institution to be recognized as a museum: 
-ICOM has around 3,000 institutional members \parencite{ICOM_2020_report19}, a relatively small fraction of the over 104,000 museums estimated to exist globally \parencite{UNESCO_2021_covid}, and while national associations fare somewhat better, with e.g.
+The International Council of Museums (ICOM) has around 3,000 institutional members \parencite{ICOM_2020_report19}, a relatively small fraction of the over 104,000 museums estimated to exist globally \parencite{UNESCO_2021_covid}, and while national associations fare somewhat better, with e.g.
 the American Association of Museums representing over 4,000 of the country's 35,000 museums \parencite{LOC_2019_AAM}, and the German Museumsbund representing over 1,300 \parencite{Museumsbund_2024_mitgliedmuseen} of Germany's 7,120 museums \parencite{IMF_2024_museumsstatistik}, the ability of these associations to impose standards is still limited.
-In such an unregulated field, names do not clearly reflect institutional characteristics, which leaves evaluation of a musem to less institutionalized practical classification systems \parencite{van_Venrooij_2018_fuzziness}.
+In such an unregulated field, names do not clearly reflect institutional characteristics, which leaves evaluation of a museum to less institutionalized practical classification systems \parencite{van_Venrooij_2018_fuzziness}.
 \paragraph*{Competition}
@@
 On a national level, density of private museum is calculated as the number of private museums per million population.
-To measure competition on a local level, I first determine the coordinates of museum using the Google Maps API; the coordindates of museums which are not found that way (particularly those located in countries with limited Google presence such as South Korea, China and Russia) are searched manually (often using other map services such as Kakao Maps, Baidu Maps and Yandex Maps).
+To measure competition on a local level, I first determine the coordinates of museum using the Google Maps API; the coordinates of museums which are not found that way (particularly those located in countries with limited Google presence such as South Korea, China and Russia) are searched manually (often using other map services such as Kakao Maps, Baidu Maps and Yandex Maps).
 For closed museums, which often are not included in the current map databases, coordinates are also determined via addresses mentioned on snapshots in the Wayback Machine.
@@
 On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
-Women constitute a minority of the private museums founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would have a greater difficulties in securing resources third parties, presumably primarily governments and corporate sponsors.
+Women constitute a minority of the private museums founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would face greater difficulties in securing resources from third parties, primarily governments and corporate sponsors.
 However, women may also be particularly associated with philanthropic initiatives - in contrast to corporate activities \parencite{Milam_2013_artgirls} - to such an extent that devaluation of female initiatives may not necessarily be present.
@@
 Such analysis can be used to estimate the average life expectancy of a private museum.
-While only a fraction of all opened museums has closed (68 out of 503), and even the complete survival function has not reached 0.5, under the assumption of average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, it is possible to predict the median life expectancy as approximately 52 years (yet as only around half of this range is observed for a large number of museums, the certainty of such measurement is clearly limited).
+While only a fraction of all opened museums has closed (68 out of 503), and even the complete survival function has not reached 0.5, under the assumption of average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, it is possible to predict the median life expectancy as approximately 52 years (yet as only around half of this range is observed for most museums, the certainty of such measurement is clearly limited).
 
 Calculating such survival statistics allows (to a degree) to assess whether private museums differ in their longevity from comparable institutions.
-So far only a small number of studies has investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
+So far only a few studies has investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
 Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form 990 data is publicly available \parencite{Lecy_2023_core}.
@@
 \item \textcite{Gordon_etal_2013_insolvency} observe 35 closures based on 5,167 museum-years between 2000 and 2003 (p.368), resulting in an average annual closing rate of 0.68\% (p.377)\footnote{The difference to \cite{Bowen_etal_1994_charitable} is likely due to exclusion of organizations with revenues below 150,000 USD.}.
-\item \textcite{Hager_2001_vulnerability} has conducted the only study specifically on art museums (NTEE code A51); he observes 42 closures over a period of four years (1994-1997) from a starting populaton of 448 (p.383), corresponding to an average yearly closing rate of 2.4\%, or around 1.9\% under the more realistic assumption of effectively using a five-year time period.
+\item \textcite{Hager_2001_vulnerability} has conducted the only study specifically on art museums (NTEE code A51); he observes 42 closures over a period of four years (1994-1997) from a starting population of 448 (p.383), corresponding to an average yearly closing rate of 2.4\%, or around 1.9\% under the more realistic assumption of effectively using a five-year time period.
 \end{itemize}
 
-Construcing private museum closing rates in a similar manner (as average of proportion closed each calendar year, rather than at each age) results in average closing rates of 0.84\% overall, 1.36\% for the period 2010-2011 and 1.12\% when weighing yearly closing proportions by the number of museums at risk.
+Constructing private museum closing rates in the same manner (as average of proportion closed each calendar year, rather than at each age) results in average closing rates of 0.84\% overall, 1.36\% for the period 2010-2011 and 1.12\% when weighing yearly closing proportions by the number of museums at risk.
 Private museum closing rates thus do not appear substantially higher than the range of possible values established by previous studies, and in particular not higher than the closing rate of the most direct comparison group of non-profit art museums by \textcite{Hager_2001_vulnerability}.
@@
 To investigate which covariates are associated with increased risk of closing, table \ref{tbl:t_reg_coxph} shows the results of Cox proportional hazard regression model.
-Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.
+Coefficients are interpreted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.
 \paragraph*{Control Variables}
@@
 Neither gender of the founder, inclusion of the founder name in the museum name nor external shocks (the Great Recession and the Covid-19 Pandemic) are associated with significantly higher closing rates.
-Given the non-significant gender difference, it can be expected that the population of private museums founders will continue to remain predominantly male, unless a strong increase in museum founding by women takes place.
+Given the non-significant gender difference, it can be expected that the population of private museums founders will remain predominantly male, unless a strong increase in museum founding by women takes place.
 At the same time, this finding also provides no evidence that female founders face gender-specific challenges, at least not to an extent that these decrease the survival prospects of their private museums.
@@
 
-It is in principle possible to construct an alternative measure of founder death by partioning the time after the death in a short-term and long-term period; the short-term period might then capture the disruption by the founder, whereas the long-term period would only be reached by museums who have successfully acquired alternative funding models and are hence relatively viable.
+It is in principle possible to construct an alternative measure of founder death by partitioning the time after the death in a short-term and long-term period; the short-term period might then capture the disruption by the founder, whereas the long-term period would only be reached by museums who have successfully acquired alternative funding models and are hence relatively viable.
 However, the choice of choosing a cut-off point between the short- and long-term periods is relatively arbitrary.
@@
 While the coefficient in the short-term period is consistently higher than both the overall death coefficient and the long-term period coefficients, so far the evidence is inconclusive as only few cases are statistically significant\footnote{P-values are also not adjusted for multiple tests}.
-Furthermore, such a shock passes quickly relative to the predicted median life time of museums of 52 years, thus "giving" the founder death little time to lead to many museum closures. 
-Considering the numbers underlying the death effect estimates illustrates the uncertainty of the determning the effect of the death of the founder on aclosing: 
+Furthermore, such a shock passes quickly relative to the predicted median lifetime of museums of 52 years, thus "giving" the founder death little time to lead to many museum closures. 
+Considering the raw numbers underlying the death effect estimates illustrates the uncertainty involved in determining the effect of the death of the founder on closing: 
 While 47 private museums have seen the death of their founders, only 3 of these have closed in the following 5 years; given such low numbers it cannot be ruled out that the statistical significance in a few configurations of founder death time results from random fluctuations rather than an underlying pattern.
@@
 
-Taken together, the inability to explain private museum closing with the death of founder and her exclusion from a prestitious ranking question the hypothesized central role of the founder (Hypothesis 1).
+Taken together, the inability to explain private museum closing with the death of founder and their exclusion from a prestigious ranking question the hypothesized central role of the founder (Hypothesis 1).
 In other words, so far little evidence points to low diversification, i.e. reliance on founders, as a substantial source of involuntary closing risk for private museums.
@@
 However, as founders can choose the name of their museum arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.
-Some support for the latter interpretaton is given by the fact that two of the three museums for which \textcite{Velthuis_Gera_2024_fragility} identify a temporal intention as the closing reason do not self-identify as museum, collection or foundation.
-A temporal intentions are however the exceptions among closing reasons identified by \textcite{Velthuis_Gera_2024_fragility} (p.6), and as similarly only a fraction of private museum chooses such a name (140 museums, or 28\%), the overall proportion of these types of voluntary closures compared to all closures is presumably limited.
+Some support for the latter interpretation is given by the fact that two of the three museums for which \textcite{Velthuis_Gera_2024_fragility} identify a temporal intention as the closing reason do not self-identify as museum, collection or foundation.
+Temporal intentions are however the exceptions among closing reasons identified by \textcite{Velthuis_Gera_2024_fragility} (p.6), and as similarly only a fraction of private museum chooses such a name (140 museums, or 28\%), the overall proportion of these types of voluntary closures compared to all closures is presumably limited.
 \paragraph*{Competition (H3)}
@@
 Country-level measures of the private museum population show a marginally significant association with mortality (b=0.648, p=0.058).
-While these results provide a support for evidence of competition on the country level leading to closure, it is worth noting that the observed relationship does not correspond to the generally accepted non-monotonic relationship between density and closures (as the linear term is positive, and the squared term not significant at p = 0.22), which postulates that density increases at low densities reduce closing risk (corresponding to a negative linear coefficient), and increases at high numbers increase risk (corresponding to a positive squard term).
+While these results provide a support for evidence of competition on the country level leading to closure, it is worth noting that the observed relationship does not correspond to the generally accepted non-monotonic relationship between density and closures (as the linear term is positive, and the squared term not significant at p = 0.22), which postulates that density increases at low densities reduce closing risk (corresponding to a negative linear coefficient), and increases at high numbers increase risk (corresponding to a positive squared term).
 
@@
 
-Previously the dozens of closures have been seen as indicator of their vulnerability and short-livedness \parencite{Adam_2020_close}, however this analysis shows the importance studying closing not in isolaton but in comparison to both non-closures and closures of comparable institutions.
-While the booming numbers of private museums themselves have received substantial attention, less consideration has been given to the fact that large populations can generate dozens of closures without requiring high closing rates, especially when cloures are considered over a span of several years or decades.
+Previously the dozens of closures have been seen as indicator of their vulnerability and short-livedness \parencite{Adam_2020_close}, however this analysis shows the importance studying closing not in isolation but in comparison to both non-closures and closures of comparable institutions.
+While the booming numbers of private museums themselves have received substantial attention, less consideration has been given to the fact that large populations can generate dozens of closures without requiring high closing rates, especially when closures are considered over a span of several years or decades.
 In other words, the sheer size to which the private museum population has grown over the last decades has made it all but inevitable that some of them would close, and do so after only a few years.
@@
 Furthermore, the centrality of the founder might leave little room to question who is responsible to provide additional funds in times of financial difficulties, whereas in organizations without a central figure each member may feel less responsible.
-It might also be such commitment that leads founder to plan the future of their museum to such an extent that their death is not significantly associated with unvoluntary closing.
+It might also be such commitment that leads founder to plan the future of their museum to such an extent that their death is not significantly associated with involuntary closing.
 
 While so far little evidence points toward low diversification, i.e.
-reliance on the founder, as a key vulnerability of private museums to unvoluntary closures, the centrality of the founder may be more pronounced in voluntary closures.
+reliance on the founder, as a key vulnerability of private museums to involuntary closures, the centrality of the founder may be more pronounced in voluntary closures.
 Indicated by unconventional naming choice, a subset of founders might from the very beginning envision the museum as temporary.
@@
 While so far these museums have not seen significantly elevated closing risks, these estimates will become more precise as more founders pass away.
-As the currently large confidence interval (figure \ref{fig:p_surv_death}) for museums whose founders have died allows a wide range of survival chances, it is entirely possible that previous scholars have indeed correctly identified a key dependency (the current absence of evidence of it should not be taken as evidence of absence) and that therefore later analyses will a significantly association between founder death and closing risk as well as a higher average closing risk for private museums.\footnote{Similarly, as 80\% of private museums have been founded in the new millenium, only a few museums have so far reached an age above 30 years, which makes the estimation of the age-dependent hazard for this age range highly speculative.}
+As the currently large confidence interval (figure \ref{fig:p_surv_death}) for museums whose founders have died allows a wide range of survival chances, it is entirely possible that previous scholars have indeed correctly identified a key dependency (the current absence of evidence of it should not be taken as evidence of absence) and that therefore later analyses will find a significant association between founder death and closing risk as well as a higher average closing risk for private museums.\footnote{Similarly, as 80\% of private museums have been founded in the new millennium, only a few museums have so far reached an age above 30 years, which makes the estimation of the age-dependent hazard for this age range highly speculative.}
 At the same time, it is also possible that private museums are generally less dependent on a single person (or couple) than has been assumed, and have in fact become institutionalized to an extent that most heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
@@
 The effort to compile such information on a global scale ranges from extremely challenging (harmonizing different reporting standards, language barriers) to outright impossible for institutions who do not even (have to) report public financial information.
-Similarly, other museum characteristics which were not considered here, such as as museum size, facilities, as well as marketing and outreach activities, might be related to long-term survival prospects.\footnote{While the original data collection included the assessment of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear during data analysis that the data collected was unsuitable to construct accurate indicators from these findings due to difficulty in assessing them in many cases.
-Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Wayback machine, less central pages (such as those with information about facilities and activities), were archived much less frequently, and sometimes inaccessible despite being archived due to changes in webtechnology (such as the retirement of Adobe flash).
-Analysis based on this data are reported in the supplementary materials.}
-As such, private museums remain relatively intransparent, which does not prevent, but to some extent limits the identification of risk factors.
+Similarly, other museum characteristics which were not considered here, such as museum size, facilities, as well as marketing and outreach activities, might be related to long-term survival prospects.\footnote{While the original data collection included the assessment of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear during data analysis that the data collected was unsuitable to construct accurate indicators from these findings due to difficulty in assessing them in many cases.
+Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Wayback machine, less central pages (such as those with information about facilities and activities), were archived much less frequently, and sometimes inaccessible despite being archived due to changes in web technology (such as the retirement of Adobe flash).
+Analyses based on this data are reported in the supplementary materials.}
+As such, private museums remain relatively untransparent, which does not prevent, but to some extent limits the identification of risk factors.
 
-For this study, I only investigated the occurence of closure events.
+For this study, I only investigated the occurrence of closure events.
 However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms.
@@
 Sometimes this involves changes in the composition of the board of directors (or equivalent), with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum to an extent that it no longer fits the working definition.
-Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to consistently determine the date of such transitions.\footnote{Consequently they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing for at least some time.
+Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to consistently determine the date of such transitions.\footnote{Consequently they are excluded from the analysis all together, and thus also not contributing to the hazard rate for closing, despite being entities at risk for closing for at least some time.
 However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
-The main issues that made the determination of the date impossible was the intransparency of these organizations, the gradual process of the transition, as well as that these events life often years or decades in the past.
-The possibility of other outcomes than surival and closures has been investigated for NPOs more generally
+The main issues that made the determination of the date impossible was the intransparency of these organizations, the gradual process of the transition, and the substantial amount of time that had passed since.
+The possibility of other outcomes than survival and closures has been investigated for NPOs more generally
 \parencite{Searing_2020_zombies,HernandezOrtiz_2022_discontinuity,Helmig_Ingerfurth_Pinz_2013_nonprofit}, and for private museums specifically on a case study basis: 
@@
 
-While this study has already included measures of both the national and local environment, the ability to clearly observe spatial museum location allows to measure environmental influences in greater detail.
-For once, so far competition has been limited to other private museums, but geocoding of a wider range of institutions would lead to a more encompassing assessment of competitive and dynamics.
+While this study has already included measures of both the national and local environment, the ability to clearly observe spatial museum location allows measuring environmental influences in greater detail.
+For once, so far competition has been limited to other private museums, but geocoding of a wider range of institutions would lead to a more encompassing assessment of competitive dynamics.
 Furthermore, including wider institutional changes such as tax incentives, government subsidies, but also political changes and censorship would lead to a more complete description of risk factors, and in more detail identify niches which are particularly suited for private museums.

### 2024-10-04 texts/paper_closing.tex
more cleaning, word cutting, moving text around

@@
-% Created 2024-10-04 vr 17:56
+% Created 2024-10-04 vr 19:22
 % Intended LaTeX compiler: pdflatex
@@
 These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums operated and financed by the state, foundations or associations.
-While many aspects of this new organizational form has attracted attention, such as their emergence, relations to other institutions or impact on artist consecration (cf.
-\cite{Kolbe_etal_2022_privatemuseum} for a literature review), the process of closure has received considerably less attention.
-Furthermore, the focus that has been given to questions of sustainability has been primarily conducted through case studies; quantitative studies have been mostly absent.
-In this paper, I address this gap by investigating the closure event of members of this new organizational form.
+Many aspects of this new organizational form has attracted attention, such as their emergence, relations to other institutions or impact on artist consecration (cf.
+\cite{Kolbe_etal_2022_privatemuseum} for a literature review).
+Long-term sustainability or private museum closure has also been investigated, however primarily through case studies; quantitative studies have been mostly absent.
+In this paper, I address this gap by quantitatively investigating the closure event of members of this new organizational form.
 Analyzing which factors are associated with museum closures provides insight not only into the event of closing, but also into the ongoing processes of a private museums, such as dependency relationships.
-Furthermore, analyzing which museums survive allows to make informed speculations on the future of this recently emerged organizational form.
+Furthermore, analyzing how long museums survive allows to make informed speculations on the future of this recently emerged organizational form.
 
-While a recent study by \textcite{Velthuis_Gera_2024_fragility} has systematically investigated closing reasons of private museums, I extend/complement this research by using a more elaborate statistical model and additional data sources.
+A recent study by \textcite{Velthuis_Gera_2024_fragility} has systematically investigated closing reasons of private museums, and I built on this research by using a more elaborate statistical model and additional data sources.
 In particular, I compare private museum closing rates to those of other museum populations, and analyze the risk associated with variables on the level of the founder, museum and environment. 
-Taken together, the results show that (at least so far) little evidence exists neither for private museums being overly dependent on their founder, nor having overall higher mortality rates than other non-profit museums.
-While little evidence points toward private museums being involuntarily at risk due to their low diversification, private museums may close due to environmental pressures, which exhibit a complex relationship which for most museums consists of competition from other private museums as well as, unexpectedly, large audiences.
-Finally, private museums with unconventional names (in particular, without the term "museum" in the name) face a higher closing risk, which may indicate either a temporary intention by their founders from the very beginning and/or limited recognition by third parties as potential closing reasons.
-
-This study furthermore combines museum research with quantitative non-profit management literature, a link which has so far been weak. 
+Whereas previous research had identified the reliance on the founder as a key vulnerability, quantitative analyses show no significant increase in closing risk for museums the founders of which have died or lost their art-world status.
+Secondly, private museums with unconventional names (in particular, without the term "museum", "foundation" or "collection" in the name) face a higher closing risk, which may indicate either limited recognition by third parties as potential closing reasons and/or a temporary intention by their founders from the very beginning.
+Finally, private museums face higher closing risks under certain environmental conditions, such as high competition from other private museums and, unexpectedly, the presence of large audiences.
 \subsection*{Private museums definition and dependency relations}
 
-While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{diMaggio_1982_boston,Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than e.g.
+While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than e.g.
 loaning or donating their collection or opening museums as a group.
 This phenomenon of private collectors taking the initiative in setting up a museum of their own has become increasingly widespread, with around 80\% of currently open private museums having opened since 2000 \parencite{Velthuis_etal_2023_boom}.
-To be considered as a private museum for this study, a collector needs to have amassed a substantial art collection, which he exhibits in a building in a way that is accessible to the public, all while receiving limited public and corporate funding.
+To be considered as a private museum for this study, a collector needs to have amassed a substantial art collection, which he or she exhibits in a building in a way that is accessible to the public while receiving limited public and corporate funding.
 The central role of the founder delimits a private museum from other organizational forms such as public museums supported by local or state governments, corporate museums run by companies or other non-profit museums operated by associations or foundations with more dispersed ownership and control.\footnote{Which is not to say that for an institution to be considered a private museum, it has to be legal personal ownership of the founder.
@@
 The \textcite{IMLS_2008_funding} found that American non-profit art museums receive less than half (48.1\%) of their revenues from earned income, leaving substantial gaps in the budgets that are filled by a mix of private donations (23.0\%), investment (18.5\%) and government support (10.4\%) (p.27).
-Outside the United States, the reliance on revenue streams beyond operations appears even larger:
+Outside the United States, the reliance on revenue streams beyond operations appears to be even larger:
 German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table b), p.233}, with private museums however requiring less support as operations provide around 47\% of their budget (ibid.).
@@
 
-Given that operating at "the margin of financial sustainability" is the "ordinary condition" for Non-profit organizations (NPO) in the cultural sector, \parencite[p.2]{Licci_BaraldiBonini_2024_sustainability}, it is not surprising that costs have been listed as a primary reason for private museum closure:
+Given that operating at "the margin of financial sustainability" is the "ordinary condition" for non-profit organizations (NPO) in the cultural sector, \parencite[p.2]{Licci_BaraldiBonini_2024_sustainability}, it is not surprising that costs have been listed as a primary reason for private museum closure:
 \textcite{Adam_2021_rise} argues that "most of the cases of defunct private museums come back to the issue of cost" (p.79); a sentiment shared by \textcite{Walker_2019_collector} who notes that "private institutions struggle to contain escalating costs that are associated with running a museum" (p.234).
@@
 Other studies have measured diversification as the Herfindahl Index (a measure of concentration) of income sources such as public support, program service revenues, dues and assessments, net fundraising income and profits from sale of inventory \parencite[p.381]{Hager_2001_vulnerability} or contributions, program service revenue, investment income, other revenues \parencite[p.37]{Lu_Shon_Zhang_2019_dissolution}, with both studies finding a positive association between diversification and survival; in the case of \textcite{Hager_2001_vulnerability} also specifically for art museums.
-Next to diversification, volatility, i.e. fluctuation in revenue streams, has been associated with mortality as well \parencite{Mayer_2022_simmer}.
 Despite limited reception of this research stream in the private museum literature, identifying the high reliance on the founder as a source of risk thus corresponds to management insights. 
@@
 
-The most direct interruption a founder and their museum can experience is the death of the founder; this event has in fact already been extensively argued to result in museum closure:
+The most direct interruption a founder and their museum can experience is the death of the founder; this event has in fact already been repeatedly argued to result in museum closure:
 \textcite{Walker_2019_collector} argues that "the death of the original founder and creator can [\ldots{}] place the future of private museums and collections in jeopardy" as "seldom do heirs share a similar passion or wish to take on the financial burden of maintaining private museums indefinitely" (p.234).
 \textcite{Bechtler_Imhof_2018_future} argue that in order to ensure private museum longevity, "flexible, easily adapted designs for private museums" are necessary "to reduce the financial burden on their heirs" (p.188).
-\textcite{Adam_2021_rise} argues that succession introduces financial strains as "collectors’ successors may not look kindly on what may well be a money pit when [\ldots{}] they will have to pick up the bills" (p.77), and also highlights the aesthetic dimension as "the nature of contemporary art is to be fresh and new, but what is ‘fresh and new’ for the founder might seem ‘old hat’ to their heirs".
+\textcite{Adam_2021_rise} argues that succession introduces financial strains as "collectors’ successors may not look kindly on what may well be a money pit when [\ldots{}] they will have to pick up the bills" (p.77), and also highlights the aesthetic dimension: "The nature of contemporary art is to be fresh and new, but what is ‘fresh and new’ for the founder might seem ‘old hat’ to their heirs".
 (p.76).
@@
 
-It is however necessary to consider that the name of a museum might be associated with a museum's survival not only via its perception by other parties, but also via reflection of the founder's intentions regarding the institution's longevity; this possibility is discussed in more detail in the results section.
+It is however necessary to consider that the name of a museum might be associated with a museum's survival not only via its perception by other parties, but also via reflection of the founder's intentions regarding the institution's longevity; this possibility is discussed in more detail in the results.
 \paragraph*{Competition}
@@
 
-While private museums presumably depend on their founder to a large extent, income from tickets and facilities, as well sponsorships and public support possibly also constitute other non-negligible revenue streams.
+While private museums presumably depend on their founder to a large extent, income from tickets and facilities, as well sponsorships and public support possibly also constitute other non-negligible revenue streams, in particular as they have been characterized as having strong incentives to develop these income sources \parencite{Frey_Meier_2002_beyeler}.
 Competition directly has not yet been investigated as a cause for private museum closing, but a possible mechanism of competition, "insufficient interest from the public", has been identified as the second most reported closure reason by \textcite[p.6]{Velthuis_Gera_2024_fragility}.
@@
 At the same time, for an association between name and survival to be attributed to the name, the name and other organizational characteristics cannot be linked too closely.
-This seems to be the case for museums, where membership is not subject to strong regulations: 
+This seems to be the case for museums, as organizations are not subject to strong regulations to be considered a museums: 
 The term "museum" is not a protected term in the US \parencite[p.205]{Moore_2022_best} or European countries such as Germany \parencite[p.4]{Museumsbund_ICOMDE_2006_standards}, Denmark, Austria, Croatia or Finland \parencite{EGMUS_2024_reports}\footnote{While I was not able to find concrete information on the naming regulations of museums for every country, I did not find any country where such naming regulation is present.}.
@@
 the American Association of Museums representing over 4,000 of the country's 35,000 museums \parencite{LOC_2019_AAM}, and the German Museumsbund representing over 1,300 \parencite{Museumsbund_2024_mitgliedmuseen} of Germany's 7,120 museums \parencite{IMF_2024_museumsstatistik}, the ability of these associations to impose standards is still limited.
-In such an unregulated field, names do not clearly reflect institutional characteristics, which leaves evaluation of a museum to less institutionalized practical classification systems \parencite{van_Venrooij_2018_fuzziness}.
+In such a largely unregulated field, names do not clearly reflect institutional characteristics, which leaves evaluation of a museum to less institutionalized practical classification systems \parencite{van_Venrooij_2018_fuzziness}.
 \paragraph*{Competition}
@@
 On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
-Women constitute a minority of the private museums founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would face greater difficulties in securing resources from third parties, primarily governments and corporate sponsors.
+Women are a minority among private museums founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would face greater difficulties in securing resources from third parties, primarily governments and corporate sponsors.
 However, women may also be particularly associated with philanthropic initiatives - in contrast to corporate activities \parencite{Milam_2013_artgirls} - to such an extent that devaluation of female initiatives may not necessarily be present.
@@
 
-However, a number of limitations complicate such a comparison.
+However, two limitations complicate such a comparison.
 First, this measure of overall museum closing rates cannot take museum-level variables into account, thus direct comparability hinges on the assumption that on private museums display a similar distribution of survival-relevant attributes to US non-profit museums.
 Secondly, as previous studies have focused exclusively on the US, survival rates for non-profits in other countries might differ, for example in particular in Europe one possible reason might be more public support for non-profits.
-While additional analyses, reported in the supplementary materials, do not indicate a substantial influence of time-invariant country (or region) factors on private museum closing, mortality of non-private museums might be stronger influenced by these country-level factors.
+Additional analyses, reported in the supplementary materials, do not indicate a substantial influence of time-invariant country (or region) factors on private museum closing, however mortality of non-private museums might be stronger influenced by these country-level factors.
 While thus a comparison of closing rates of different museum populations provides initial insights, a more extensive comparative investigation would be necessary to further assess how closing rates of private museums correspond to those of other museum populations.
@@
 At the same time, this finding also provides no evidence that female founders face gender-specific challenges, at least not to an extent that these decrease the survival prospects of their private museums.
-Museums whose name contain the name of the founder face a non-significantly 4.9\% elevated risk of closure, which indicates that there is little evidence that founders face greater difficulties to secure a long-term future for their museums by choosing to emphasize their personal contribution.
+Museums whose name contain the name of the founder face no significantly elevated risk of closure, which provides little evidence that founders face greater difficulties to secure a long-term future for their museums by choosing to emphasize their personal contribution.
 A possible explanation might be that even when other parties do indeed feel less inclined to contribute, these gaps are filled by a stronger commitment of the founder, who having committed her name to the initiative, wants to keep the museum open event at great costs.
@@
 \paragraph*{Founder dependence (H1)}
-
-% latex table generated in R 4.3.3 by xtable 1.8-4 package
-% Fri Sep 27 17:51:20 2024
-\begin{table}[ht]
-\centering
-\begin{tabular}{rD{)}{)}{8)3}D{)}{)}{8)3}}
-  \hline 
- \multicolumn{1}{l}{Recent death length} & \multicolumn{1}{l}{Recently dead} & \multicolumn{1}{l}{Long dead}\\ 
- \hline
-   1 & .97 \; (1.02) & .19 \; (0.46) \\ 
-    2 & 1.37 \; (0.61)^{*} & -.16 \; (0.55) \\ 
-    3 & 1.06 \; (0.61) & -.09 \; (0.55) \\ 
-    4 & .83 \; (0.61) & -.02 \; (0.55) \\ 
-    5 & .62 \; (0.61) & .07 \; (0.55) \\ 
-    6 & .50 \; (0.61) & .13 \; (0.55) \\ 
-    7 & .87 \; (0.49) & -.51 \; (0.75) \\ 
-    8 & .80 \; (0.49) & -.45 \; (0.75) \\ 
-    9 & .91 \; (0.46)^{*} & -1.11 \; (1.03) \\ 
-   10 & .83 \; (0.46) & -1.03 \; (1.03) \\ 
-   11 & .78 \; (0.46) & -.98 \; (1.03) \\ 
-   12 & .71 \; (0.46) & -.90 \; (1.03) \\ 
-   \hline
-\end{tabular}
-\caption{Cox PH regression results with different death configurations} 
-\label{tbl:t_reg_coxph_deathcfg}
-\end{table}
 
@@
 The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e.
-museums are not significantly more likely to close after their founder has died, which provides little support to H1a.
+museums are not significantly more likely to close after their founder has died, which provides little support to H1a.\footnote{An alternative specification of founder death which partitions the time after the death into a short-term and long-term period is reported in the supplementary materials; this specification also provides little evidence for a significant effect of the death of the founder}
 While the point estimate is positive (0.280, corresponding to a 32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that even decade-long survival prospects do not differ substantially despite the cumulative character of risk (figure \ref{fig:p_surv_death}).
 
-It is in principle possible to construct an alternative measure of founder death by partitioning the time after the death in a short-term and long-term period; the short-term period might then capture the disruption by the founder, whereas the long-term period would only be reached by museums who have successfully acquired alternative funding models and are hence relatively viable.
-However, the choice of choosing a cut-off point between the short- and long-term periods is relatively arbitrary.
-
-Table \ref{tbl:t_reg_coxph_deathcfg} shows coefficients of both periods with different cut-off points.
-While the coefficient in the short-term period is consistently higher than both the overall death coefficient and the long-term period coefficients, so far the evidence is inconclusive as only few cases are statistically significant\footnote{P-values are also not adjusted for multiple tests}.
-Furthermore, such a shock passes quickly relative to the predicted median lifetime of museums of 52 years, thus "giving" the founder death little time to lead to many museum closures. 
-Considering the raw numbers underlying the death effect estimates illustrates the uncertainty involved in determining the effect of the death of the founder on closing: 
-While 47 private museums have seen the death of their founders, only 3 of these have closed in the following 5 years; given such low numbers it cannot be ruled out that the statistical significance in a few configurations of founder death time results from random fluctuations rather than an underlying pattern.
-
-Other founder-level characteristics also do not indicate that founder-related variables are strongly associated to museum closure, as the coefficients of ARTnews ranking inclusion (measuring reputation) and inclusion of founder's name in the museum name are not statistically significant.
+Coefficients for founder reputation, measured via inclusion in the ARTnews ranking, are not statistically significant.
 Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (21\% elevated closing risk) and by founders who were included at some point but are no longer included (58\% elevated closing risk).
-However as none of the differences are statistically significant, they provide little support for hypothesis 2b.
-It is also worth to point out that the order of the categories does not fully correspond to the expected order, according to which museums whose collectors are not included would be more likely to close than collectors who are.
-However, as all differences are not statistically significant, there is no strong evidence that this reflects unexpected status mechanisms rather than randomness.
+However as none of the differences are statistically significant, they provide little support for hypothesis 1b.
 
@@
 Country-level measures of the private museum population show a marginally significant association with mortality (b=0.648, p=0.058).
-While these results provide a support for evidence of competition on the country level leading to closure, it is worth noting that the observed relationship does not correspond to the generally accepted non-monotonic relationship between density and closures (as the linear term is positive, and the squared term not significant at p = 0.22), which postulates that density increases at low densities reduce closing risk (corresponding to a negative linear coefficient), and increases at high numbers increase risk (corresponding to a positive squared term).
-
 \begin{figure}[htbp]

### 2024-10-07 texts/paper_closing.tex
bunch of grammar fixes

@@
-% Created 2024-10-04 vr 19:22
+% Created 2024-10-07 ma 14:02
 % Intended LaTeX compiler: pdflatex
@@
 These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums operated and financed by the state, foundations or associations.
-Many aspects of this new organizational form has attracted attention, such as their emergence, relations to other institutions or impact on artist consecration (cf.
-\cite{Kolbe_etal_2022_privatemuseum} for a literature review).
-Long-term sustainability or private museum closure has also been investigated, however primarily through case studies; quantitative studies have been mostly absent.
+Many aspects of this new organizational form have attracted attention, such as their emergence, relations to other institutions or impact on artist consecration (cf.
+\textcite{Kolbe_etal_2022_privatemuseum} for a literature review).
+Long-term survival or private museum closure has also been investigated, however primarily through case studies; quantitative studies have been mostly absent.
 In this paper, I address this gap by quantitatively investigating the closure event of members of this new organizational form.
-Analyzing which factors are associated with museum closures provides insight not only into the event of closing, but also into the ongoing processes of a private museums, such as dependency relationships.
-Furthermore, analyzing how long museums survive allows to make informed speculations on the future of this recently emerged organizational form.
+Analyzing which factors are associated with museum closures provides insight into not only the event of closing, but also the ongoing internal processes and dependency relationships of private museums.
+Furthermore, analyzing how long museums survive provides a basis for informed speculations on the future of this recently emerged organizational form.
 
-A recent study by \textcite{Velthuis_Gera_2024_fragility} has systematically investigated closing reasons of private museums, and I built on this research by using a more elaborate statistical model and additional data sources.
-In particular, I compare private museum closing rates to those of other museum populations, and analyze the risk associated with variables on the level of the founder, museum and environment. 
-Whereas previous research had identified the reliance on the founder as a key vulnerability, quantitative analyses show no significant increase in closing risk for museums the founders of which have died or lost their art-world status.
+A recent study by \textcite{Velthuis_Gera_2024_fragility} has systematically investigated closing reasons of private museums, and I build on this research by using a more elaborate statistical model and additional data sources.
+In particular, I analyze the risk associated with variables on the level of the founder, museum and environment, obtaining three main findings. 
+Firstly, whereas previous research had identified the reliance on the founder as a key vulnerability, quantitative analyses show no significant increase in closing risk for museums whose founders have died or lost status in the art world.
+A descriptive comparison of closing rates to other museum populations also shows no elevated closing risk for private museums.
 Secondly, private museums with unconventional names (in particular, without the term "museum", "foundation" or "collection" in the name) face a higher closing risk, which may indicate either limited recognition by third parties as potential closing reasons and/or a temporary intention by their founders from the very beginning.
@@
 
-While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than e.g.
-loaning or donating their collection or opening museums as a group.
+While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than loaning or donating their collection or opening museums as a group.
 This phenomenon of private collectors taking the initiative in setting up a museum of their own has become increasingly widespread, with around 80\% of currently open private museums having opened since 2000 \parencite{Velthuis_etal_2023_boom}.
@@
 The central role of the founder delimits a private museum from other organizational forms such as public museums supported by local or state governments, corporate museums run by companies or other non-profit museums operated by associations or foundations with more dispersed ownership and control.\footnote{Which is not to say that for an institution to be considered a private museum, it has to be legal personal ownership of the founder.
-Instead the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms; generally this has to be assessed on a case-by-case basis.}
+Instead, the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms; generally, this has to be assessed on a case-by-case basis.}
 
@@
 A central reason for financial vulnerability has been argued to be the crucial reliance on the single founder, who, as the initiators of their private museums, likely have to contribute a large part of their institution's non-operating income \parencite{Frey_Meier_2002_beyeler}:
-\textcite{Adam_2021_rise} argues that "ultimately, many of these failures demonstrate the fragility of spaces that rely on a single founder, whose motivations and financial stability may change, or who may not have realised the difficulties inherent in establishing their own art space" (p.82).
+\textcite{Adam_2021_rise} argues that "ultimately, many of these failures demonstrate the fragility of spaces that rely on a single founder, whose motivations and financial stability may change, or who may not have realized the difficulties inherent in establishing their own art space" (p.82).
 \textcite{Velthuis_Gera_2024_fragility} similarly argue that "because of their funding models and reliance on a sole founder, [private museums] are inherently fragile organizations" (p.1).
-\textcite{Bechtler_Imhof_2018_future} also characterize "the dependency on single individuals only" as one of main reasons that "make these private museums fragile" (p.53).
+\textcite{Bechtler_Imhof_2018_future} also characterize "the dependency on single individuals only" as one of the main reasons that "make these private museums fragile" (p.53).
 \textcite{StylianouLambert_etal_2014_museums} similarly describe many private institutions as "small individual museums that depend too much on their creators to guarantee their sustainability" (p.582).
-Beyond a direct financial component, private museums have been also been characterized as fragile since they can only rely on their founder for "taste", "vision and drive" \parencite[p.77]{Adam_2021_rise}, "passion" \parencite[p.234]{Walker_2019_collector} or "skills and knowledge" \parencite[p.580]{StylianouLambert_etal_2014_museums}.
+Beyond a direct financial component, private museums have also been characterized as fragile since they can only rely on their founder for "taste", "vision and drive" \parencite[p.77]{Adam_2021_rise}, "passion" \parencite[p.234]{Walker_2019_collector} or "skills and knowledge" \parencite[p.580]{StylianouLambert_etal_2014_museums}.
 
-Existing research on private museum is conducted primarily by scholars of the art field or market as well as art historians.
+Existing research on private museums has been conducted primarily by scholars of the art field or market as well as art historians.
 Nevertheless, the identification of the centrality of the founder as a critical source of vulnerability corresponds strongly to the finding in non-profit management of a relation between diversification and mortality \parencite{Tuckman_Chang_1991_vulnerability,Hung_Hager_2018_diversification}.
 For example, \textcite{Bielefeld_1994_survival} finds that nonprofits with a larger number of funding sources (e.g.
-from foundations, individuals, federated funders, corporations, trusts, government at federal, state, county and municipal level as well as self-generated sources such as dues, interests, and service revenue, p.31) are more likely to survive.
+foundations, individuals, federated funders, corporations, trusts, government at federal, state, county and municipal levels as well as self-generated sources such as dues, interests, and service revenue, p.31) are more likely to survive.
 Other studies have measured diversification as the Herfindahl Index (a measure of concentration) of income sources such as public support, program service revenues, dues and assessments, net fundraising income and profits from sale of inventory \parencite[p.381]{Hager_2001_vulnerability} or contributions, program service revenue, investment income, other revenues \parencite[p.37]{Lu_Shon_Zhang_2019_dissolution}, with both studies finding a positive association between diversification and survival; in the case of \textcite{Hager_2001_vulnerability} also specifically for art museums.
@@
 
-A less obvious yet possibly impactful event that might jeopardize a founder's ability to sustain their museum and shorten its lifespan is a decline of status of the collector within the art world.
+A less obvious yet possibly impactful event that might jeopardize a founder's ability to sustain their museum and shorten its lifespan is status decline of the collector within the art world.
 Recognition bestowed by prominent art world authorities confers the acknowledgment of "cultural expertise" \parencite[p.1486]{Braden_2016_recognition}, thus validating the collector-founder's refined taste, which constitutes a form symbolic capital \parencite{Bourdieu_1993_production}.
@@
 Next to the reputation of the general public, studies have also found reputation effects among more narrowly defined groups, in particular peers \parencite{Padanyi_Gainer_2003_peerreputation} and networks of similar organizations on regional and national scale \parencite{Walker_McCarthy_2010_survival}.
-In particular this reputation among more narrowly defined groups makes it likely that the reputation of the \emph{founder} matters (beyond the reputation of the \emph{organization}, the focus on most prior research) given the highly personal character of the private museum initiative and the central role of the founder in negotiations with decision makers from other organizations or the public sector.
+In particular, this reputation among more narrowly defined groups makes it likely that the reputation of the \emph{founder} matters (beyond the reputation of the \emph{organization}, the focus on most prior research) given the highly personal character of the private museum initiative and the central role of the founder in negotiations with decision makers from other organizations or the public sector.
 
@@
 The perception of the museum itself, beyond the reputation of the founder, might also affect survival prospects.
-As has also been summarized in the previous section, an identity that is legitimate (understandable) and favorable (positive) has been argued to have numerous positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns \parencite{Lange_Lee_Dai_2010_reputation}, which in turn can facilitate survival prospects \parencite{Rao_1994_reputation}.
+As has also been summarized in the previous section, an identity that is legitimate (understandable) and favorable (positive) has been argued to have numerous positive outcomes for organizations such as higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns \parencite{Lange_Lee_Dai_2010_reputation}, which in turn can facilitate survival prospects \parencite{Rao_1994_reputation}.
 In the context of private museums, a more positive identity could lead to higher visitor numbers, discounts from art dealers, government grants or collaborations with other museums or corporations, resulting in higher revenues and lower acquisition costs.
@@
 Next to material organizational features, adherence to symbolic features such as naming conventions has been found to enhance perceptions of legitimacy; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate \parencite{Glynn_Abzug_2002_names}.
-Assuming that such a legitimacy effect translates into better survival prospect, a hypothesis can be formulated as:
+Assuming that such a legitimacy effect translates into better survival prospects, a hypothesis can be formulated as:
 
@@
 
-It is however necessary to consider that the name of a museum might be associated with a museum's survival not only via its perception by other parties, but also via reflection of the founder's intentions regarding the institution's longevity; this possibility is discussed in more detail in the results.
+It is however necessary to consider that the name of a museum might be associated with a museum's survival not only via its perception by other parties but also via reflection of the founder's intentions regarding the institution's longevity; this possibility is discussed in more detail in the results.
 \paragraph*{Competition}
 
-Just as the environment can be supportive of museums recognized perceived as renowned, it can also be a source of risk if it such support is absent.
+Just as the environment can be supportive of museums recognized as renowned, it can also be a source of risk if such support is absent.
 In particular this might be the case under conditions of harsh competition, which private museums have been characterized to engage in.
@@
 Qualitative studies which trace the history and/or closing reasons for each organization individually have highlighted competition over funding.
-\textcite{Hager_1999_demise} reports that "both individual donations/subscriptions and community and corporate grants tended to go to the singular, most reputable arts organizations of their types", resulting in "strong competitive pressures" for the vast majority of organizations (ibid.).
+\textcite{Hager_1999_demise} reports that "both individual donations/subscriptions and community and corporate grants tended to go to the singular, most reputable arts organizations of their types" (p.173), resulting in "strong competitive pressures" for the vast majority of organizations (ibid.).
 Similarly, \textcite{HernandezOrtiz_2022_discontinuity} found that an "[increasingly] crowded niche increased the competition and limited [NPOs'] access to resources and clients" (p.116) with an informant stating that "there was less money to go around and more organizations seeking the money [\ldots{}] we had a full-time grant writer, we were always applying for grants.
@@
 Currently, the database includes 550 museums, of which 453 are currently open, 72 have closed and 25 have transformed into other organizational forms.\footnote{The 25 institutions which were private museums at some point and have since been transformed into other organizational forms are not included in this analysis and discussed in the limitations.}
-Using this database, in particular year of opening and, if available, closing, it is possible to reconstruct the life course of each institution with museum-year as the unit of analysis.
+Using this database, in particular year of opening and closing, it is possible to reconstruct the life course of each institution with museum-year as the unit of analysis.
 While the database is not limited to private museums of a particular time period, due to the recency of the private museum boom in the last two decades 80\% of the museums included in it have opened after 2000.
@@
 The variable is lagged by one year to avoid reverse causality, i.e.
-to exclude the possibility that an association is observed which is present due to founders being dropped from the ranking as a consequence of the closure of their museum.
+to exclude the possibility that an association is observed due to founders being dropped from the ranking as a consequence of the closure of their museum.
 \paragraph*{Museum Identity}
@@
 To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55,000 museums, are analyzed.
-In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum.}
+In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts, preliminary investigations of the database indicated that it has been updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of an institutions' recognition as a museum.}
 At the same time, for an association between name and survival to be attributed to the name, the name and other organizational characteristics cannot be linked too closely.
-This seems to be the case for museums, as organizations are not subject to strong regulations to be considered a museums: 
+This seems to be the case for museums, as organizations are not subject to strong regulations to be considered a museum: 
 The term "museum" is not a protected term in the US \parencite[p.205]{Moore_2022_best} or European countries such as Germany \parencite[p.4]{Museumsbund_ICOMDE_2006_standards}, Denmark, Austria, Croatia or Finland \parencite{EGMUS_2024_reports}\footnote{While I was not able to find concrete information on the naming regulations of museums for every country, I did not find any country where such naming regulation is present.}.
@@
 
-On a national level, density of private museum is calculated as the number of private museums per million population.
-To measure competition on a local level, I first determine the coordinates of museum using the Google Maps API; the coordinates of museums which are not found that way (particularly those located in countries with limited Google presence such as South Korea, China and Russia) are searched manually (often using other map services such as Kakao Maps, Baidu Maps and Yandex Maps).
+On a national level, density of private museums is calculated as the number of private museums per million population.
+To measure competition on a local level, I first determine the coordinates of museums using the Google Maps API; the coordinates of museums which are not found that way (particularly those located in countries with limited Google presence such as South Korea, China and Russia) are searched manually (often using other map services such as Kakao Maps, Baidu Maps and Yandex Maps).
 For closed museums, which often are not included in the current map databases, coordinates are also determined via addresses mentioned on snapshots in the Wayback Machine.
-I then use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
+These coordinates are then used to calculate two measures that describe the local environment within a ten-kilometer radius around each museum for each year:
+First, the number of other private museums and second the population counts using the Global Human Settlement Layer \parencite{EC_2023_GHSL}. 
 To be able to estimate both competition and population effects separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two (alternative specifications are presented in the supplementary materials).
-While this operationalization is limited to private museum in the neighborhood, rather than the more complete set of all museums private museums may compete with, it is by no means a rarity to find private museums within a 10 km radius, as in 41\% museum-years one or more private museums in the surroundings are observed.
+While this operationalization is limited to private museums in the neighborhood, rather than the more complete set of all museums private museums may compete with, it is by no means a rarity to find private museums within a 10 km radius, as in 41\% museum-years one or more private museums in the surroundings are observed.
 \subsubsection*{Control variables}
@@
 On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
-Women are a minority among private museums founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would face greater difficulties in securing resources from third parties, primarily governments and corporate sponsors.
+Women are a minority among private museum founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would face greater difficulties in securing resources from third parties, primarily governments and corporate sponsors.
 However, women may also be particularly associated with philanthropic initiatives - in contrast to corporate activities \parencite{Milam_2013_artgirls} - to such an extent that devaluation of female initiatives may not necessarily be present.
 
-On the level of museum, I control for whether a museum includes the name of the founder (e.g. "Liam's Gallery" includes the name of the founder).
-As another property of the name, it might be indicative of the commitment founder, but it might also might support by third parties less attractive.
+On the level of the museum, I control for whether a museum includes the name of the founder (e.g. "Liam's Gallery" includes the name of the founder).
+As another property of the name, it might be indicative of the commitment founder, but it also might make support by third parties less attractive.
 
 External shocks might interrupt operations, which reduces income from tickets, as well as make other donors more hesitant to commit money in uncertain times.
-However, museums, including private museums, might also be relatively resilient as they can adopt measures such as tightening their belt, additional fundraising, and expanding their marketing efforts \parencite{Geller_Salamon_2010_resilience}, which might bolster their resilience.
-To account for two prevalent shocks in the recent decades, the Great Recession and the Covid-19 pandemic, I thus include two dummy variables for 2008/2009 and 2020/2021; respectively.
+However, museums might also be relatively resilient as they can adopt measures such as tightening their belt, additional fundraising, and expanding their marketing efforts \parencite{Geller_Salamon_2010_resilience}, which might bolster their resilience.
+To account for two prevalent shocks in the recent decades, the Great Recession and the Covid-19 pandemic, I thus include two dummy variables for 2008/2009 and 2020/2021.
 \subsection*{Results}
@@
 
-Before discussing the regression models, I provide a descriptive account on private museum closure using the hazard and survival functions which describe variation the closing risk over the museum life-course.
+Before discussing the regression models, I provide a descriptive account of private museum closure using the hazard and survival functions which describe (variation in) the closing risk over the museum life course.
 The hazard rate is a non-parametric function which describes the probability of exiting at age \(t_i\) conditional on being alive, in the context of museum-years as units of analysis it can be formulated as \(h(t_i) = \frac{d_i}{n_i}\), with \(n_i\) as the number of units at risk at age \(t_i\) and \(d_i\) as the number of exits at age \(t_i\).
@@
 the overall average hazard rate is 0.90\%), for ages above 30 only few observations are available, which make these predictions rather uncertain.}.
-The increase in the first years is likely explained by the fact that as the establishment of a museum requires considerable resources, their founders have allocated enough resources to keep the risk of closure minimal in the first years after opening.
+The increase in the first years is likely explained by the fact that as the establishment of a museum requires considerable resources, founders have allocated enough resources to keep the risk of closure minimal in the first years after opening.
 
 Such analysis can be used to estimate the average life expectancy of a private museum.
-While only a fraction of all opened museums has closed (68 out of 503), and even the complete survival function has not reached 0.5, under the assumption of average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, it is possible to predict the median life expectancy as approximately 52 years (yet as only around half of this range is observed for most museums, the certainty of such measurement is clearly limited).
+While only a fraction of all opened museums has closed (68 out of 503), and even the complete survival function has not reached 0.5, under the assumption of an average closing risk of 0.73\% in the first 8 years and 1.20\% onwards, it is possible to predict the median life expectancy as approximately 52 years (yet as only around half of this range is observed for most museums, the certainty of such measurement is clearly limited).
 
 Calculating such survival statistics allows (to a degree) to assess whether private museums differ in their longevity from comparable institutions.
-So far only a few studies has investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
+So far only a few studies have investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
 Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form 990 data is publicly available \parencite{Lecy_2023_core}.
-This data has been used in many studies of non-profit populations, and constitutes an effective comparison group for private museums as both share the same organizational form (non-profit) and unprofitable cultural sector environment.
+This data has been used in many studies of non-profit populations and constitutes an effective comparison group for private museums as both share the same organizational form (non-profit) and unprofitable cultural sector environment.
 So far three studies have used this data to investigate museum closure by calculating hazard rates not as a function of age but of calendar year:
@@
 
-Constructing private museum closing rates in the same manner (as average of proportion closed each calendar year, rather than at each age) results in average closing rates of 0.84\% overall, 1.36\% for the period 2010-2011 and 1.12\% when weighing yearly closing proportions by the number of museums at risk.
+Constructing private museum closing rates in the same manner (as the average of proportion closed each calendar year, rather than at each age) results in average closing rates of 0.84\% overall, 1.36\% for the period 2010-2011 and 1.12\% when weighing yearly closing proportions by the number of museums at risk.
 Private museum closing rates thus do not appear substantially higher than the range of possible values established by previous studies, and in particular not higher than the closing rate of the most direct comparison group of non-profit art museums by \textcite{Hager_2001_vulnerability}.
@@
 However, two limitations complicate such a comparison.
-First, this measure of overall museum closing rates cannot take museum-level variables into account, thus direct comparability hinges on the assumption that on private museums display a similar distribution of survival-relevant attributes to US non-profit museums.
+First, this measure of overall museum closing rates cannot take museum-level variables into account, thus direct comparability hinges on the assumption that private museums display a similar distribution of survival-relevant attributes to US non-profit museums.
 Secondly, as previous studies have focused exclusively on the US, survival rates for non-profits in other countries might differ, for example in particular in Europe one possible reason might be more public support for non-profits.
-Additional analyses, reported in the supplementary materials, do not indicate a substantial influence of time-invariant country (or region) factors on private museum closing, however mortality of non-private museums might be stronger influenced by these country-level factors.
+Additional analyses, reported in the supplementary materials, do not indicate a substantial influence of time-invariant country (or region) factors on private museum closing, however mortality of non-private museums might be more strongly influenced by these country-level factors.
 While thus a comparison of closing rates of different museum populations provides initial insights, a more extensive comparative investigation would be necessary to further assess how closing rates of private museums correspond to those of other museum populations.
@@
 
-Neither gender of the founder, inclusion of the founder name in the museum name nor external shocks (the Great Recession and the Covid-19 Pandemic) are associated with significantly higher closing rates.
-Given the non-significant gender difference, it can be expected that the population of private museums founders will remain predominantly male, unless a strong increase in museum founding by women takes place.
+Neither gender of the founder, inclusion of the founder's name in the museum name nor external shocks (the Great Recession and the Covid-19 Pandemic) are associated with significantly higher closing rates.
+Given the non-significant gender difference, it can be expected that the population of private museum founders will remain predominantly male, unless a strong increase in museum founding by women takes place.
 At the same time, this finding also provides no evidence that female founders face gender-specific challenges, at least not to an extent that these decrease the survival prospects of their private museums.
-Museums whose name contain the name of the founder face no significantly elevated risk of closure, which provides little evidence that founders face greater difficulties to secure a long-term future for their museums by choosing to emphasize their personal contribution.
+Museums whose names contain the name of the founder face no significantly elevated risk of closure, which provides little evidence that founders face greater difficulties in securing a long-term future for their museums by choosing to emphasize their personal contribution.
 A possible explanation might be that even when other parties do indeed feel less inclined to contribute, these gaps are filled by a stronger commitment of the founder, who having committed her name to the initiative, wants to keep the museum open event at great costs.
-The insignificance of the coefficients of the external shocks indicate that museums are overall relatively resilient; possibly unlike other types of art organizations with lower assets and higher reliance on earned incomes \parencite[p.102]{Bowen_etal_1994_charitable}.
+The insignificance of the coefficients of the external shocks indicates that museums are overall relatively resilient; possibly unlike other types of art organizations with lower assets and higher reliance on earned incomes \parencite[p.102]{Bowen_etal_1994_charitable}.
 \paragraph*{Founder dependence (H1)}
@@
 
-Coefficients for founder reputation, measured via inclusion in the ARTnews ranking, are not statistically significant.
+Coefficients for founder reputation, measured via inclusion in the ARTnews ranking, are also not statistically significant.
 Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (21\% elevated closing risk) and by founders who were included at some point but are no longer included (58\% elevated closing risk).
-However as none of the differences are statistically significant, they provide little support for hypothesis 1b.
+However as none of the differences are statistically significant, they provide little support for H1b.
 
-Taken together, the inability to explain private museum closing with the death of founder and their exclusion from a prestigious ranking question the hypothesized central role of the founder (Hypothesis 1).
+Taken together, the inability to explain private museum closing with the death of the founder and their exclusion from a prestigious ranking question the hypothesized central role of the founder (Hypothesis 1).
 In other words, so far little evidence points to low diversification, i.e. reliance on founders, as a substantial source of involuntary closing risk for private museums.
@@
 
-Museums which include the term "collections" in their name are the least likely to close (0.63 times the rate of museums with the name "museum", while those with the term "foundation" experience a closing rate elevated by 23\%; yet both of these differences are statistically significant.
+Museums which include the term "collection" in their name are the least likely to close (0.63 times the rate of museums with the name "museum", while those with the term "foundation" experience a closing rate elevated by 23\%; yet both of these differences are statistically significant.
 However, institutions which include neither of these are the most likely to close, and have mortality rates almost three times as high (198\%) than institutions including the term "museum".
@@
 attracting visitors, cooperations, sponsorships or subsidies).
-However, as founders can choose the name of their museum arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an institution enduring in perpetuity but rather a more temporally bounded project.
+However, as founders can choose the name of their museum arbitrarily, they might choose a name without reference to organizational forms associated with perpetuity precisely because their intention is not an enduring institution but rather a more temporally bounded project.
 Some support for the latter interpretation is given by the fact that two of the three museums for which \textcite{Velthuis_Gera_2024_fragility} identify a temporal intention as the closing reason do not self-identify as museum, collection or foundation.
-Temporal intentions are however the exceptions among closing reasons identified by \textcite{Velthuis_Gera_2024_fragility} (p.6), and as similarly only a fraction of private museum chooses such a name (140 museums, or 28\%), the overall proportion of these types of voluntary closures compared to all closures is presumably limited.
 \paragraph*{Competition (H3)}
@@
 
-At the local level, the number of private museum and population numbers predict survival chances as the main effects of population and number of private museums as well as its interaction are significant.
+At the local level, private museums and population numbers predict survival chances as the main effects of population and number of private museums, as well as its interaction are significant.
 The particular pattern however is complex:
@@
 Thus, for population values of 0 to 2.97 million people, an increase in the number of private museums corresponds to an increase in mortality (bottom half of figure \ref{fig:p_pred_heatmap}), which provides support for hypothesis 3 according to which competition leads to museum closure, in particular as this range includes 5056 museums years, or 83\% of the dataset.
-Yet at the same time, at low private museums numbers (0 to 3 private museums, left half of figure \ref{fig:p_pred_heatmap}), increases in population also increase mortality; this range also includes a large number of museum-years (4960 museum years; 81\% of the data).
+Yet at the same time, at low private museum numbers (0 to 3 private museums, left half of figure \ref{fig:p_pred_heatmap}), increases in population also increase mortality; this range also includes a large number of museum-years (4960 museum years; 81\% of the data).
 Such a relationship is unexpected insofar as it is unclear why a larger potential audience would be associated with a higher risk of closure.\footnote{Alternative approaches of modeling competition are discussed in the supplementary materials, but cannot answer this question.}
@@
 Alternatively, areas with high population and low private museum numbers might more generally lack cultural infrastructure; which one could see supported by closures in Jakarta, Istanbul and Mexico City, but less so by closings in Paris, Tokyo or Madrid.
-However, low private museums numbers indicating lack of cultural infrastructure might also explain the decrease in mortality associated with increases in private museum numbers at high population values (figure \ref{fig:p_pred_heatmap}, upper half), as such pattern does not correspond to that predicted by competition.
-More in line with expectation is however the association between increases of population numbers and lower mortality at higher numbers of private museums (right half), as it indicates that audiences can facilitate museum survival.
+However, low private museums numbers indicating a lack of cultural infrastructure might also explain the decrease in mortality associated with increases in private museum numbers at high population values (figure \ref{fig:p_pred_heatmap}, upper half), as such pattern does not correspond to that predicted by competition.
+More in line with expectations is however the association between increases in population numbers and lower mortality at higher numbers of private museums (right half), as it indicates that audiences can facilitate museum survival.
 
-Taken together, figure \ref{fig:p_pred_heatmap} indicates two niches as particular supportive of private museum survival, on the one hand remote areas with low population and no competing private museums, and on the other densely populated areas with at least some other private museums.
+Taken together, figure \ref{fig:p_pred_heatmap} indicates two niches as particularly supportive of private museum survival, on the one hand, remote areas with low population and no competing private museums, and on the other densely populated areas with at least some other private museums.
 
-While not all associations correspond to predictions made by resource dependence, the most direct measurement of increased competition, number of private museums in the local surrounding, is associated with higher closing chances for a large part of the sample, which in turn supports the substantial role of competition (H3).
+While not all associations correspond to predictions made by resource dependence, the most direct measurement of increased competition, the number of private museums in the local environment, is associated with higher closing chances for a large part of the sample, which in turn supports the substantial role of competition (H3).
 \subsection*{Discussion and Conclusion}
 
-Previously the dozens of closures have been seen as indicator of their vulnerability and short-livedness \parencite{Adam_2020_close}, however this analysis shows the importance studying closing not in isolation but in comparison to both non-closures and closures of comparable institutions.
-While the booming numbers of private museums themselves have received substantial attention, less consideration has been given to the fact that large populations can generate dozens of closures without requiring high closing rates, especially when closures are considered over a span of several years or decades.
-In other words, the sheer size to which the private museum population has grown over the last decades has made it all but inevitable that some of them would close, and do so after only a few years.
-Based on the current analysis, private museums will continue to close in the years to come; at hazard rates of around 1\% on average a handful of closures every year are to be expected.
+Whereas previous research has identified the reliance on the founder as a key vulnerability, this study found little support for such a dependency.
+Multiple reasons might be at play that mitigate this risk of low diversification.
+First, it might require more commitment from collectors to open a museum compared to less involved art patronage of being a board member in existing institutions or donating works, which would result in private museum founders being more motivated to secure the continued existence of their institutions.
+Furthermore, the centrality of the founder might leave little uncertainty as to who is responsible for providing additional funds in times of financial difficulties, whereas in organizations without a central figure each member may feel less responsible.
+It might also be such commitment that leads founders to plan the future of their museum e.g.
+via an endowment to such an extent that their death is not significantly associated with involuntary closing.
 
-Comparing private museums closures to closures of other organizational form advances our understanding of the sustainability of this new organizational form.
-While private museums do close, the comparison to previous studies of museum closing rates provides no evidence that dependence on single founders constitutes a less stable organizational form than reliance on less centralized foundations, associations or corporate sponsorship.
-Multiple reasons might be the at play that mitigate this risk of low diversification.
-First, it might take more commitment to open a museum as an individual or couple compared to less involved art patronage of being a board member in existing institutions or donating works, which would result in private museums founders being more motivated to secure the continued existence of their institutions.
-Furthermore, the centrality of the founder might leave little room to question who is responsible to provide additional funds in times of financial difficulties, whereas in organizations without a central figure each member may feel less responsible.
-It might also be such commitment that leads founder to plan the future of their museum to such an extent that their death is not significantly associated with involuntary closing.
+Similarly, characterizations of private museums as generally fragile \cite{Adam_2020_close,Bechtler_Imhof_2018_future} are not supported here either.
+While the descriptive comparison to other studies allows only preliminary conclusions, it still shows the importance of considering closings not in isolation, but in comparison to both non-closures and closures of comparable institutions.
+In particular, the context of the growing private museum population deserves consideration, as large populations can generate dozens of closures without requiring high closing rates, especially when closures are considered over a span of several years or decades.
 
-While so far little evidence points toward low diversification, i.e.
-reliance on the founder, as a key vulnerability of private museums to involuntary closures, the centrality of the founder may be more pronounced in voluntary closures.
-Indicated by unconventional naming choice, a subset of founders might from the very beginning envision the museum as temporary.
+While so far little evidence points toward reliance on the founder as a key vulnerability of private museums to involuntary closures, the centrality of the founder may be more pronounced in voluntary closures.
+Indicated by unconventional naming choices, a subset of founders might from the very beginning envision the museum as temporary.
 On the other hand, higher closing rates for unconventionally named museums might reflect absence of recognition and support by third parties in the environment.
@@
 While the overall relationship is complex, for the majority of private museums increases in both variables are associated with higher closing rates.
-Whereas it is plausible that the association between higher institution counts and closing rates reflects competitive pressures, it is less obvious what may lay behind observing a positive association behind larger population and closing risk.
-\subsubsection*{Limitations}
+Whereas it is plausible that the association between higher institution counts and closing rates reflects competitive pressures, it is less obvious what may lay behind observing a positive association between larger population and closing risk.
+\subsubsection*{Limitations and Future Research}
 
 A number of limitations are worth considering:
-So far only a small fraction (47 museums, 9.3\%) of museums has experienced the death of their founder, one of the primary reasons hypothesized to lead to the private museum closure. 
+So far only few museums have experienced the death of their founder (47 museums, 9.3\%), one of the primary reasons hypothesized to lead to the private museum closure. 
 While so far these museums have not seen significantly elevated closing risks, these estimates will become more precise as more founders pass away.
 As the currently large confidence interval (figure \ref{fig:p_surv_death}) for museums whose founders have died allows a wide range of survival chances, it is entirely possible that previous scholars have indeed correctly identified a key dependency (the current absence of evidence of it should not be taken as evidence of absence) and that therefore later analyses will find a significant association between founder death and closing risk as well as a higher average closing risk for private museums.\footnote{Similarly, as 80\% of private museums have been founded in the new millennium, only a few museums have so far reached an age above 30 years, which makes the estimation of the age-dependent hazard for this age range highly speculative.}
-At the same time, it is also possible that private museums are generally less dependent on a single person (or couple) than has been assumed, and have in fact become institutionalized to an extent that most heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
+At the same time, it is also possible that private museums are generally less dependent on a single founder than has been assumed, and have in fact become institutionalized to an extent that most heirs feel motivated to continue the original founders' efforts.
 
@@
 While centralized non-profit financial information is available for American non-profits through the IRS/NCCS files, the much larger private museum population in the rest of the world is not subject to similar reporting requirements.
-The effort to compile such information on a global scale ranges from extremely challenging (harmonizing different reporting standards, language barriers) to outright impossible for institutions who do not even (have to) report public financial information.
+The effort to compile such information on a global scale ranges from extremely challenging (harmonizing different reporting standards and language barriers) to outright impossible for institutions that do not even (have to) report public financial information.
 Similarly, other museum characteristics which were not considered here, such as museum size, facilities, as well as marketing and outreach activities, might be related to long-term survival prospects.\footnote{While the original data collection included the assessment of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear during data analysis that the data collected was unsuitable to construct accurate indicators from these findings due to difficulty in assessing them in many cases.
@@
 Analyses based on this data are reported in the supplementary materials.}
-As such, private museums remain relatively untransparent, which does not prevent, but to some extent limits the identification of risk factors.
+As such, private museums remain relatively intransparent which to some extent limits the identification of risk factors.
 
 For this study, I only investigated the occurrence of closure events.
-However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms.
-One way in which this can happen is when other parties, such as local governments, other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
+However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms as a consequence of involvement of local governments, other philanthropists, foundations, or corporations in the ownership, governance or funding of the museum.
 Sometimes this involves changes in the composition of the board of directors (or equivalent), with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum to an extent that it no longer fits the working definition.
-Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to consistently determine the date of such transitions.\footnote{Consequently they are excluded from the analysis all together, and thus also not contributing to the hazard rate for closing, despite being entities at risk for closing for at least some time.
+Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to consistently determine the date of such transitions.\footnote{Consequently they are excluded from the analysis altogether, and thus also not contributing to the hazard rate for closing, despite being entities at risk for closing for at least some time.
 However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
@@
 \textcite{Walker_2019_collector} argues that in the case of Germany, private museum founders turn to the state to ensure the survival of their projects in the form of public-private partnerships.
-Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research.
+Investigating this process of transformation into a different organizational form thus provides fruitful avenues for further research.
 
-While this study has already included measures of both the national and local environment, the ability to clearly observe spatial museum location allows measuring environmental influences in greater detail.
+Finally, while this study has already included measures of both the national and local environment, the ability to clearly observe spatial museum location allows measuring environmental influences in greater detail.
 For once, so far competition has been limited to other private museums, but geocoding of a wider range of institutions would lead to a more encompassing assessment of competitive dynamics.

### 2024-10-08 texts/sup_materials.tex
newer version of sup_materials

@@
-% Created 2024-09-30 ma 14:08
+% Created 2024-10-07 ma 14:12
 % Intended LaTeX compiler: pdflatex
@@
 
+\subsection*{Alternative founder death specification}
+
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Fri Sep 27 17:51:20 2024
+\begin{table}[ht]
+\centering
+\begin{tabular}{rD{)}{)}{8)3}D{)}{)}{8)3}}
+  \hline 
+ \multicolumn{1}{l}{Recent death length} & \multicolumn{1}{l}{Recently dead} & \multicolumn{1}{l}{Long dead}\\ 
+ \hline
+   1 & .97 \; (1.02) & .19 \; (0.46) \\ 
+    2 & 1.37 \; (0.61)^{*} & -.16 \; (0.55) \\ 
+    3 & 1.06 \; (0.61) & -.09 \; (0.55) \\ 
+    4 & .83 \; (0.61) & -.02 \; (0.55) \\ 
+    5 & .62 \; (0.61) & .07 \; (0.55) \\ 
+    6 & .50 \; (0.61) & .13 \; (0.55) \\ 
+    7 & .87 \; (0.49) & -.51 \; (0.75) \\ 
+    8 & .80 \; (0.49) & -.45 \; (0.75) \\ 
+    9 & .91 \; (0.46)^{*} & -1.11 \; (1.03) \\ 
+   10 & .83 \; (0.46) & -1.03 \; (1.03) \\ 
+   11 & .78 \; (0.46) & -.98 \; (1.03) \\ 
+   12 & .71 \; (0.46) & -.90 \; (1.03) \\ 
+   \hline
+\end{tabular}
+\caption{Cox PH regression results with different death configurations} 
+\label{tbl:t_reg_coxph_deathcfg}
+\end{table}
+
+It is possible to construct an alternative measure of founder death by partitioning the time after the death in a short-term and long-term period; the short-term period might then capture the disruption by the founder, whereas the long-term period would only be reached by museums who have successfully acquired alternative funding models and are hence relatively viable.
+
+However, the choice of choosing a cut-off point between the short- and long-term periods is relatively arbitrary.
+
+Table \ref{tbl:t_reg_coxph_deathcfg} shows coefficients of both periods with different cut-off points.
+
+While the coefficient in the short-term period is consistently higher than both the overall death coefficient and the long-term period coefficients, so far the evidence is inconclusive as only few cases are statistically significant\footnote{P-values are also not adjusted for multiple tests}.
+
+Furthermore, such a shock passes quickly relative to the predicted median lifetime of museums of 52 years, thus "giving" the founder death little time to lead to many museum closures.
+
+Considering the raw numbers underlying the death effect estimates illustrates the uncertainty involved in determining the effect of the death of the founder on closing:
+
+While 47 private museums have seen the death of their founders, only 3 of these have closed in the following 5 years; given such low numbers it cannot be ruled out that the statistical significance in a few configurations of founder death time results from random fluctuations rather than an underlying pattern.
 \subsection*{Alternative competition specifications}
@@
 Alternative Specifications of competition exist.
+
 First, it is possible to argue that the primary mechanism through which private museums compete with each other is by limiting each other's audience.
+
 This specification leads to the construction of the Audience variable, which describes the number of people in the 10 km surrounding by the number of private museums present.
+
 Under this assumption, the situation of a private museum which is alone in an environment of 1 million people is equivalent to one in an environment of 3 million people with 2 other private museums, as each museums is "assigned" a pool of 1 million people.
+
 Secondly, one might argue that the competition between private museums is scaled by the amount of people, which corresponds to specifying competition as the number of other private museums per (million) population.
+
 In this case, the absence of other private museums assumes absence of competition, regardless of the audience size.
@@
 These while it would be possible for these different specifications to lead to similar interpretations, in practice they diverge substantially (table \ref{tbl:t_reg_coxph_env}).
+
 Using Private museum density (model 2 and 3 for linear and log-transformed audience, figure \ref{fig:p_pred_heatmap_alt} bottom left), the general conclusion would be that (logged) competition increases mortality as predicted closing chance is highest in areas of low population and large private museum populations.
+
 However, using audience (models 4 and 5, figure \ref{fig:p_pred_heatmap_alt} bottom right) leads to the opposite conclusion, as higher audience is associated with higher mortality; predicted closing chance is highest for areas of low numbers of private museums and large populations.
+
 While it is beyond the scope of the paper to explore the origin of these diverging perspectives in detail, it is worth pointing out that the main specification of private interacted private museum and population counts captures both of these relationships, which arguably makes it preferable for its encompassingness.
@@
 To investigate the robustness of the coefficients across different values, table \ref{tbl:t_reg_coxph_density} shows how coefficients according to sample restrictions.
+
 In model 1, only museums are included which are located in areas with the highest value combination of number and private museums and population, i.e.
 museums located in an environment of less than 2 million people and 0 or 1 other private museums (the "countryside").
+
 In model 2, the "countryside" is excluded.
+
 However, both these models are not reliable, as they do not properly converge (indicated by extremely large coefficients in both models).
@@
 Table \ref{tbl:t_reg_coxph_timeslice} investigates whether relationships have substantially changed over time.
+
 However, subsetting the dataset to different year ranges shows general consistency of the main findings, in particular insignificant coefficients for the founder's death, gender, Artnews ranking variables, inclusion of founder name in museum name, positive and significant coefficients for self-identification as other, population and private museum numbers, and a significant negative interaction between private museum numbers and population.
@@
 It is also possible to include an indicator whether museums have had exhibitions of contemporary art.
+
 For this the database of Artfacts is used.
+
 It is not included in the main model as it might reflect resources (with larger museums being more likely to organize exhibitions), which would then influence the coefficients of other variables.
+
 Controlling for the mechanism (or a proxy of it) would then lead to coefficients corresponding to comparisons where resources are equal.
+
 Alternatively, exhibitions could enhance the reputation of museums, as it might lead to higher recognition among third parties such as sponsors and governments of the public good the museum provides.
+
 Temporary exhibitions might also be a way to attract larger audiences, but as museum operations are unprofitable, the ticket revenues likely do not lead to a better financial situation.
+
 To investigate the role of exhibitions anyways, table \ref{tbl:t_reg_coxph_af} includes next to the main model two models with different exhibition specifications.
+
 "Exhibition any" is a time-invariant indicator measuring whether Artfacts has ever recorded this museum as organizating an exhibition, "Exhibition any last 5 years" is a time-varying variable indicating whether an exhibition has been taken place in the previous 5 years.
+
 Both coefficients are not significant, and do not substantially change the coefficients of other variables. 
@@
 As private museum closing might depend on particular country- or region-level factors, table \ref{tbl:t_reg_coxph_reg} shows a number of Cox Proportional Hazard regression models results with different sets of dummy variables.
+
 In particular, dummy variables are added for UN region code (with a minor modification of splitting the Americas into North and Latin America according to the UN subregion codes and reference category of Africa), the UN subregion code itself (with reference category of Northern America), as well as country level (with reference category of United States).
+
 For models with country-dummies, country-level private museum density variables are removed as the high collinearity led to unreasonably high country-dummy estimates.
+
 As many countries and some UN subregions have too few private museums for the model to converge correctly, the dataset is reduced to include only regions or countries with 10 or more private museums (in the case of country2, 15 private museums).
+
 To identify whether any change in coefficients is due to addition of variables or exclusion of cases, a separate model with the same restricted sample but without region/country dummies is included.
@@
 None of the models show a significant region or country dummy variables, nor substantial changes of the coefficients of the main predictors (a minor change is that the addition of country dummies results in a significant coefficient for the Covid-19 pandemic).
+
 While log-likelihood decreases by definition, model fit indices (AIC and BIC) that penalize inclusion of additional variables indicate worse fit for models with region/country dummies, except in the case of the AIC for the inclusion of UN subregion dummies, where a small improvement is observed.
+
 Taken together, these results indicate little support for an importance of time-invariant contextual factors on the level of the region or country on private museum survival. 
@@
 \centering
-\includegraphics[width=18cm]{../figures/p_vrblcvrg_ratio.pdf}
+\includegraphics[width=18cm]{../figures/p_vrblcvrg_ratio.png}
 \caption{\label{fig:p_vrblcvrg_ratio}PMDB variable coverage (abs/rel prop) by museum status and variable group}
@@
 Figure \ref{fig:p_vrblcvrg_ratio} shows the variable coverage by whether a museum is open or closed at the status of data collection (2020-2022).
+
 Not only is coverage on most variables far from complete, which would already make it difficult to construct indicators of them, but variable coverage is substantially worse for closed museums than for open museums, especially variables related to the collection, operation, relations to other actors and social media.
+
 In principle it is possible to treat absence of evidence as evidence of absence, and assume that not measuring the presence of e.g.
@@
 \centering
-\includegraphics[width=18cm]{../figures/p_vrblcvrg_pca.pdf}
+\includegraphics[width=18cm]{../figures/p_vrblcvrg_pca.png}
 \caption{\label{fig:p_vrblcvrg_pca}coverage of variables used in PCA}
@@
 \centering
-\includegraphics[width=14cm]{../figures/p_pca_loadings.pdf}
+\includegraphics[width=14cm]{../figures/p_pca_loadings.png}
 \caption{\label{fig:p_pca_loadings}loadings of first 2 PCs}
@@
 \centering
-\includegraphics[width=16cm]{../figures/p_pca_scores.pdf}
+\includegraphics[width=16cm]{../figures/p_pca_scores.png}
 \caption{\label{fig:p_pca_scores}scores on first PCs}
@@
 not including variables such as floor size, collection size or opening times; figure \ref{fig:p_vrblcvrg_pca}) a principal component analysis was performed of which the first two factors are extracted with varimax rotation (figure \ref{fig:p_pca_loadings}).
+
 The first component appears to differentiate museums based on facilities (museumshop, restaurant) and institutional arrangements corresponding to larger institutions (sponsorship, donor program, temporary exhibitions), which makes it plausible that it reflects the size of an organization.
+
 The second dimension seems to measure the extent of artistic support, education and research.
+
 Figure \ref{fig:p_pca_scores} shows positioning of the museums on both dimensions.
+
 Table \ref{tbl:t_reg_coxph_dimred} shows models with one or both of these components included:
+
 Both components are highly significantly associated with closing, improve model performance and change a number of main results, such as the coefficient of the death of the founder (significant when the first component is addded) and the main effect of local population (insignificant when the first component is addded), as well as the covid pandemic effect (significant in all model with principal components).
@@
 While it is plausible that larger organizations face a lower closing risk, I ultimately consider the coefficients are too large to be plausibly reflect primary an influence of institutional characteristics.
+
 While some size effect may exist, I consider it more plausible that this is indicator much more strongly reflects whether a museum is open or closed in the first place (as data collection was much more difficult for closed museums, the  measurement error is systematically related with the outcome variable), and therefore do not include it in the main regression model to avoid a circular rationale.
@@
 Table \ref{tbl:t_drop1} shows model fit improvement by adding each variable to the model with the other main variables but without the variable in question.
+
 For the most part, variables that are significant in the main model (self-identification and the main effects and interaction of population and private museums in the local environment) significantly improve the model when added.
+
 The one variable deviating from this pattern is the dummy variable for the years of the Great Recession, which despite an insignificant model coefficient significantly improves model fit; however model improvement is relatively small compared to the other variables.

### 2024-10-08 texts/paper_closing.tex
new title, abstract, word cutting, subheadings

@@
-% Created 2024-10-07 ma 14:02
+% Created 2024-10-08 di 10:05
 % Intended LaTeX compiler: pdflatex
@@
 
-\section*{Stayin' Alive: The unexpected longevity of founder-centered private art museums}
+\section*{The show must go on: Can private art museums survive?}
 
+\subsection*{Abstract}
+
+Hundreds of art collectors have decided to open their private art museums in the last decades.
+As their numbers have grown, so have questions whether this new organizational form can endure in the long term.
+Using a newly constructed database of 503 museums and 68 closures (6096 museum years), I use Cox Proportional Hazard models to investigate which factors increase the chance of private museum closure.
+While most research has been skeptical of the long-term prospects, in particular as reliance on an individual founder has been seen as a risk factor, no significant association is found between the museum's likelihood to close and the death of the founder or their loss of status.
+Instead, a museum's survival chances are found to depend primarily on its name (reflecting lack of recognition, or their founders' temporarily bounded plans) and location (reflecting complex competitive dynamics).
 \subsection*{Introduction}
@@
 The central role of the founder delimits a private museum from other organizational forms such as public museums supported by local or state governments, corporate museums run by companies or other non-profit museums operated by associations or foundations with more dispersed ownership and control.\footnote{Which is not to say that for an institution to be considered a private museum, it has to be legal personal ownership of the founder.
-Instead, the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms; generally, this has to be assessed on a case-by-case basis.}
+Instead, the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms and has to be assessed on a case-by-case basis.}
+\subsubsection*{Financial conditions in the cultural sector}
 
@@
 \textcite{Adam_2021_rise} argues that "most of the cases of defunct private museums come back to the issue of cost" (p.79); a sentiment shared by \textcite{Walker_2019_collector} who notes that "private institutions struggle to contain escalating costs that are associated with running a museum" (p.234).
-In other studies, "insufficient funding, high maintenance costs and lack of strong government support" \parencite[p.7]{Zennaro_2017_shanghai}, a "shortage of fundings and interruptions in cash" \parencite[p.45]{Song_2008_private}, bankruptcies \parencite{Velthuis_Gera_2024_fragility,Liu_2019_identities,DeNigris_2018_museums}, costly legal battles \parencite{Velthuis_Gera_2024_fragility}, stock devaluations \parencite{Walker_2019_collector} or failing auction sales \parencite{Bechtler_Imhof_2018_future} have been found as central reasons that forced private museums to close.
+In other studies, "insufficient funding, high maintenance costs and lack of strong government support" \parencite[p.7]{Zennaro_2017_shanghai}, a "shortage of fundings and interruptions in cash" \parencite[p.45]{Song_2008_private}, bankruptcies \parencite{Velthuis_Gera_2024_fragility,DeNigris_2018_museums}, costly legal battles \parencite{Velthuis_Gera_2024_fragility}, stock devaluations \parencite{Walker_2019_collector} or failing auction sales \parencite{Bechtler_Imhof_2018_future} have been found as central reasons that forced private museums to close.
 In a systematic review of closing reasons given in newspapers, magazines, social media accounts and personal exchanges, \textcite{Velthuis_Gera_2024_fragility} find financial issues as the most commonly mentioned reasons for private museum closing.
-\subsubsection*{diversification}
+\subsubsection*{The risks of relying on single founders}
 
@@
 While limited research exists that investigates reputation effects for (art) museums, its effects have been investigated for non-profits more widely.
-Here reputation is often referred to as an organization's resource or asset \parencite{Kong_Farrell_2010_image,Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}. 
+Here reputation is often referred to as an organization's resource or asset \parencite{Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}. 
 Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survival \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}, with most studies finding support for a positive effect of reputation.
@@
 \textbf{Hypothesis 1b}: Private museums are more likely to close after a decline of their founder's status.
+\subsubsection*{Environmental risks}
 
@@
 
-\paragraph*{Founder death}
+\paragraph*{Founder Death}
 
 A measure of founder death is constructed as a time-varying covariate with values of 1 from the year of the founder's death onwards and 0 otherwise.
-\paragraph*{Founder reputaton}
+\paragraph*{Founder Reputation}
 
@@
  \hline
- Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
-  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
-  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
-  None &  64 & Other & The Bunker, The Broad \\ 
-  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
-  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
-  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
-  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
-  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
-  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
-  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
+ Museum & 190 & $Museum$ & Museum Kampa, Museum Barberini \\ 
+  Foundation & 104 & $Foundation$ & Marciano Art Foundation, Hill Art Foundation \\ 
+  Collection &  69 & $Collection$ & The Farjam Collection, Sammlung Boros \\ 
+  None &  64 & $Other$ & The Bunker, The Broad \\ 
+  Center &  17 & $Other$ & Dairy Art Centre, Art Center Nabi \\ 
+  Gallery &  14 & $Other$ & Saatchi Gallery, Galerie C15 \\ 
+  Art space &  13 & $Other$ & El Espacio 23, Qiao Space \\ 
+  House / villa &  11 & $Other$ & Villa La Fleur, Casa Daros Rio \\ 
+  Institute &  10 & $Other$ & Instituto Inhotim, Woods Art Institute \\ 
+  Kunsthalle &   8 & $Other$ & Kunsthalle Würth, G2 Kunsthalle \\ 
+  Park / garden &   3 & $Other$ & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
    \hline
@@
 To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55,000 museums, are analyzed.
-In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts, preliminary investigations of the database indicated that it has been updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of an institutions' recognition as a museum.}
+In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it is also possible to measure legitimacy via inclusion in the MOW database, as it represents recognition of the organization as a museum by experts, preliminary investigations indicated that the MOW database has been updated too sparsely in recent years for inclusion in it (or the lack therefore) to constitute an accurate measurement of an institutions' legitimacy.}
 At the same time, for an association between name and survival to be attributed to the name, the name and other organizational characteristics cannot be linked too closely.
@@
   \multicolumn{8}{l}{\textbf{Founder}} \\ 
- & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
-   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
-   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
-   & Founder died &  &  & 0.097 & 0.30 & 0 & 1 \\ 
+ & Gender - Male & $294$ & $0.584$ & $0.604$ & $0.49$ & $0$ & $1$ \\ 
+   & Gender - Female & $79$ & $0.157$ & $0.166$ & $0.37$ & $0$ & $1$ \\ 
+   & Gender - Couple & $130$ & $0.258$ & $0.231$ & $0.42$ & $0$ & $1$ \\ 
+   & Founder died & $NA$ & $NA$ & $0.097$ & $0.30$ & $0$ & $1$ \\ 
    \multicolumn{8}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
-   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
-   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
-   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
-   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
-   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
-   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
-   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
+ & Self-Identification - Museum & $190$ & $0.378$ & $0.408$ & $0.49$ & $0$ & $1$ \\ 
+   & Self-Identification - Foundation & $104$ & $0.207$ & $0.189$ & $0.39$ & $0$ & $1$ \\ 
+   & Self-Identification - Collection & $69$ & $0.137$ & $0.130$ & $0.34$ & $0$ & $1$ \\ 
+   & Self-Identification - Other & $140$ & $0.278$ & $0.274$ & $0.45$ & $0$ & $1$ \\ 
+   & Founder name in Museum name & $240$ & $0.477$ & $0.477$ & $0.50$ & $0$ & $1$ \\ 
+   & AN Ranking - Not Included & $NA$ & $NA$ & $0.802$ & $0.40$ & $0$ & $1$ \\ 
+   & AN Ranking - Included & $NA$ & $NA$ & $0.144$ & $0.35$ & $0$ & $1$ \\ 
+   & AN Ranking - Dropped & $NA$ & $NA$ & $0.053$ & $0.23$ & $0$ & $1$ \\ 
    \multicolumn{8}{l}{\textbf{Environment}} \\ 
- & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
-   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
-   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
-   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
-   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
-   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
-   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
-   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
-   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
-   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
-   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
+ & PM density (country) & $NA$ & $NA$ & $0.450$ & $1.26$ & $0.00077$ & $27.26$ \\ 
+   & Pop. (millions) within 10km & $NA$ & $NA$ & $1.337$ & $1.68$ & $0.000087$ & $10.81$ \\ 
+   & Nbr PM within 10km & $NA$ & $NA$ & $1.778$ & $3.14$ & $0$ & $16$ \\ 
+   & Great Recession (2008/09) & $NA$ & $NA$ & $0.076$ & $0.27$ & $0$ & $1$ \\ 
+   & Covid Pandemic (2020/21) & $NA$ & $NA$ & $0.145$ & $0.35$ & $0$ & $1$ \\ 
+   & Region - Africa & $8$ & $0.016$ & $0.012$ & $0.11$ & $0$ & $1$ \\ 
+   & Region - Asia & $142$ & $0.282$ & $0.292$ & $0.45$ & $0$ & $1$ \\ 
+   & Region - Europe & $248$ & $0.493$ & $0.497$ & $0.50$ & $0$ & $1$ \\ 
+   & Region - Latin America & $23$ & $0.046$ & $0.042$ & $0.20$ & $0$ & $1$ \\ 
+   & Region - North America & $72$ & $0.143$ & $0.138$ & $0.34$ & $0$ & $1$ \\ 
+   & Region - Oceania & $10$ & $0.020$ & $0.019$ & $0.13$ & $0$ & $1$ \\ 
    \hline
@@
 \item \textcite{Bowen_etal_1994_charitable} investigate the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
-\item \textcite{Gordon_etal_2013_insolvency} observe 35 closures based on 5,167 museum-years between 2000 and 2003 (p.368), resulting in an average annual closing rate of 0.68\% (p.377)\footnote{The difference to \cite{Bowen_etal_1994_charitable} is likely due to exclusion of organizations with revenues below 150,000 USD.}.
+\item \textcite{Gordon_etal_2013_insolvency} observe 35 closures based on 5,167 museum-years between 2000 and 2003 (p.368), resulting in an average annual closing rate of 0.68\% (p.377)\footnote{The difference to \textcite{Bowen_etal_1994_charitable} is likely due to exclusion of organizations with revenues below 150,000 USD.}.
 \item \textcite{Hager_2001_vulnerability} has conducted the only study specifically on art museums (NTEE code A51); he observes 42 closures over a period of four years (1994-1997) from a starting population of 448 (p.383), corresponding to an average yearly closing rate of 2.4\%, or around 1.9\% under the more realistic assumption of effectively using a five-year time period.
@@
 \centering
-\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
+\begin{tabular}{p{0mm}ll}
   \hline 
@@
   \multicolumn{3}{l}{\textbf{Founder}} \\ 
- & Gender - Female & -.04 \; (0.34) \\ 
-   & Gender - Couple & -.14 \; (0.32) \\ 
-   & Founder died & .28 \; (0.43) \\ 
+ & Gender - Female & $-.04 \; (0.34)$ \\ 
+   & Gender - Couple & $-.14 \; (0.32)$ \\ 
+   & Founder died & $.28 \; (0.43)$ \\ 
    \multicolumn{3}{l}{\textbf{Museum}} \\ 
- & Self-Identification - Foundation & .20 \; (0.41) \\ 
-   & Self-Identification - Collection & -.45 \; (0.54) \\ 
-   & Self-Identification - Other & 1.09 \; (0.30)^{***} \\ 
-   & AN Ranking - Included & .19 \; (0.34) \\ 
-   & AN Ranking - Dropped & .46 \; (0.50) \\ 
-   & Founder name in Museum name & .05 \; (0.28) \\ 
+ & Self-Identification - Foundation & $.20 \; (0.41)$ \\ 
+   & Self-Identification - Collection & $-.45 \; (0.54)$ \\ 
+   & Self-Identification - Other & $1.09 \; (0.30)^{***}$ \\ 
+   & AN Ranking - Included & $.19 \; (0.34)$ \\ 
+   & AN Ranking - Dropped & $.46 \; (0.50)$ \\ 
+   & Founder name in Museum name & $.05 \; (0.28)$ \\ 
    \multicolumn{3}{l}{\textbf{Environment}} \\ 
- & PM density (country) & .65 \; (0.34) \\ 
-   & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
-   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
-   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
-   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
-   & Great Recession (2008/09) & -1.59 \; (1.01) \\ 
-   & Covid Pandemic (2020/21) & .42 \; (0.29) \\ 
+ & PM density (country) & $.65 \; (0.34)$ \\ 
+   & PM density$^{2}$ (country) & $-.03 \; (0.02)$ \\ 
+   & Pop. (millions) within 10km & $.27 \; (0.09)^{**}$ \\ 
+   & Nbr PM within 10km & $.26 \; (0.08)^{***}$ \\ 
+   & Nbr PM (10km) * Pop (10km) & $-.09 \; (0.03)^{**}$ \\ 
+   & Great Recession (2008/09) & $-1.59 \; (1.01)$ \\ 
+   & Covid Pandemic (2020/21) & $.42 \; (0.29)$ \\ 
    \hline
- & Museums & 503 \\ 
-   & Museum-years & 6096 \\ 
-   & Closures & 68 \\ 
-   & log. Likelihood & -339.68 \\ 
-   & AIC & 711.35 \\ 
-   & BIC & 746.87 \\ 
+ & Museums & $503$ \\ 
+   & Museum-years & $6096$ \\ 
+   & Closures & $68$ \\ 
+   & log. Likelihood & $-339.68$ \\ 
+   & AIC & $711.35$ \\ 
+   & BIC & $746.87$ \\ 
    \hline 
@@
 \centering
-\includegraphics[width=18cm]{../figures/p_surv_death.pdf}
+\includegraphics[width=18cm]{../figures/p_surv_death.png}
 \caption{\label{fig:p_surv_death}Comparison of Survival Estimates by Founder Death (95\% CI)}
@@
 \centering
-\includegraphics[width=18cm]{../figures/p_condmef.pdf}
+\includegraphics[width=18cm]{../figures/p_condmef.png}
 \caption{\label{fig:p_condmef}Conditional effects of Regional PM Density and Population}
@@
 \centering
-\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
+\includegraphics[width=18cm]{../figures/p_pred_heatmap.png}
 \caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population (at available values)}
@@
 
-Similarly, characterizations of private museums as generally fragile \cite{Adam_2020_close,Bechtler_Imhof_2018_future} are not supported here either.
+Similarly, characterizations of private museums as generally fragile \parencite{Adam_2020_close,Bechtler_Imhof_2018_future} are not supported here either.
 While the descriptive comparison to other studies allows only preliminary conclusions, it still shows the importance of considering closings not in isolation, but in comparison to both non-closures and closures of comparable institutions.
@@
 The effort to compile such information on a global scale ranges from extremely challenging (harmonizing different reporting standards and language barriers) to outright impossible for institutions that do not even (have to) report public financial information.
-Similarly, other museum characteristics which were not considered here, such as museum size, facilities, as well as marketing and outreach activities, might be related to long-term survival prospects.\footnote{While the original data collection included the assessment of various museum characteristics, such as floor and collection size, facilities, and cooperations, it became clear during data analysis that the data collected was unsuitable to construct accurate indicators from these findings due to difficulty in assessing them in many cases.
-Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Wayback machine, less central pages (such as those with information about facilities and activities), were archived much less frequently, and sometimes inaccessible despite being archived due to changes in web technology (such as the retirement of Adobe flash).
+Similarly, other museum characteristics which were not considered here, such as museum size, facilities, as well as marketing and outreach activities, might be related to long-term survival prospects.\footnote{While the original data collection included the assessment of various museum characteristics, such as floor and collection size, facilities, and co-operations, it became clear during data analysis that the data collected was unsuitable for constructing accurate indicators due to the difficulty in assessing them in many cases.
+Especially for closed museums data collection proved difficult, as many websites had been shut down, and while often snapshots of the main website were available in the Wayback machine, less central pages (such as those with information about facilities and activities), were archived much less frequently, and sometimes inaccessible despite being archived due to changes in web technology (such as the retirement of Adobe flash).
 Analyses based on this data are reported in the supplementary materials.}

### 2024-10-09 texts/paper_closing.tex
minor rephrasing/rewriting

@@
-% Created 2024-10-08 di 10:05
+% Created 2024-10-08 di 12:23
 % Intended LaTeX compiler: pdflatex
@@
 
-While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than loaning or donating their collection or opening museums as a group.
-This phenomenon of private collectors taking the initiative in setting up a museum of their own has become increasingly widespread, with around 80\% of currently open private museums having opened since 2000 \parencite{Velthuis_etal_2023_boom}.
+While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{Higonnet_2003_sight,Duncan_1995_civilizing}, in recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than loaning or donating their collection or opening museums as a group.
+This phenomenon of private collectors taking the initiative of setting up a museum of their own has become increasingly widespread, with around 80\% of currently open private museums having opened since 2000 \parencite{Velthuis_etal_2023_boom}.
 To be considered as a private museum for this study, a collector needs to have amassed a substantial art collection, which he or she exhibits in a building in a way that is accessible to the public while receiving limited public and corporate funding.
@@
  & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
-\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\
+  \cmidrule(r){3-4}\cmidrule(r){5-8}
+  \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\
  \hline
@@
  & Gender - Couple                  & $130$ & $0.258$ & $0.231$ & $0.42$ & $0$        & $1$     \\ 
-   & Founder died & $NA$ & $NA$ & $0.097$ & $0.30$ & $0$ & $1$ \\ 
+ & Founder died                     &       &         & $0.097$ & $0.30$ & $0$        & $1$     \\ 
    \multicolumn{8}{l}{\textbf{Museum}}                                                          \\ 
@@
  & Founder name in Museum name      & $240$ & $0.477$ & $0.477$ & $0.50$ & $0$        & $1$     \\ 
-   & AN Ranking - Not Included & $NA$ & $NA$ & $0.802$ & $0.40$ & $0$ & $1$ \\ 
-   & AN Ranking - Included & $NA$ & $NA$ & $0.144$ & $0.35$ & $0$ & $1$ \\ 
-   & AN Ranking - Dropped & $NA$ & $NA$ & $0.053$ & $0.23$ & $0$ & $1$ \\ 
+ & AN Ranking - Not Included        &       &         & $0.802$ & $0.40$ & $0$        & $1$     \\ 
+ & AN Ranking - Included            &       &         & $0.144$ & $0.35$ & $0$        & $1$     \\ 
+ & AN Ranking - Dropped             &       &         & $0.053$ & $0.23$ & $0$        & $1$     \\ 
    \multicolumn{8}{l}{\textbf{Environment}}                                                     \\ 
- & PM density (country) & $NA$ & $NA$ & $0.450$ & $1.26$ & $0.00077$ & $27.26$ \\ 
-   & Pop. (millions) within 10km & $NA$ & $NA$ & $1.337$ & $1.68$ & $0.000087$ & $10.81$ \\ 
-   & Nbr PM within 10km & $NA$ & $NA$ & $1.778$ & $3.14$ & $0$ & $16$ \\ 
-   & Great Recession (2008/09) & $NA$ & $NA$ & $0.076$ & $0.27$ & $0$ & $1$ \\ 
-   & Covid Pandemic (2020/21) & $NA$ & $NA$ & $0.145$ & $0.35$ & $0$ & $1$ \\ 
+ & PM density (country)             &       &         & $0.450$ & $1.26$ & $0.00077$  & $27.26$ \\ 
+ & Pop. (millions) within 10km      &       &         & $1.337$ & $1.68$ & $0.000087$ & $10.81$ \\ 
+ & Nbr PM within 10km               &       &         & $1.778$ & $3.14$ & $0$        & $16$    \\ 
+ & Great Recession (2008/09)        &       &         & $0.076$ & $0.27$ & $0$        & $1$     \\ 
+ & Covid Pandemic (2020/21)         &       &         & $0.145$ & $0.35$ & $0$        & $1$     \\ 
  & Region - Africa                  & $8$   & $0.016$ & $0.012$ & $0.11$ & $0$        & $1$     \\ 
@@
 The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e.
-museums are not significantly more likely to close after their founder has died, which provides little support to H1a.\footnote{An alternative specification of founder death which partitions the time after the death into a short-term and long-term period is reported in the supplementary materials; this specification also provides little evidence for a significant effect of the death of the founder}
+museums are not significantly more likely to close after their founder has died, which provides little support to H1a.\footnote{An alternative specification of founder death which partitions the time after the death into a short-term and long-term period is reported in the supplementary materials; this specification also provides little evidence for a significant effect of the death of the founder.}
 While the point estimate is positive (0.280, corresponding to a 32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that even decade-long survival prospects do not differ substantially despite the cumulative character of risk (figure \ref{fig:p_surv_death}).

### 2024-10-16 scripts/closing_main.R
export data for OSF

@@ -440,6 +440,18 @@ gdtbl("t_reg_coxph")
 ## gd_reg_coxph(l_mdls$r_more, "r_more")
 
 
+## export data
+
+## yeet identifying data
+l_pmdbcols_idfng <- .c(name, insta_handle,  founder_name, lat, long, address_formatted, mission, website)
+
+dt_pmdb_xp <- dt_pmdb[, .SD, .SDcols = setdiff(names(dt_pmdb), l_pmdbcols_idfng)]
+dt_pmcpct
+dt_pmyear
+
+DIR_DATAXP <- "/home/johannes/Dropbox/phd/papers/closing/dataxp/"
+
+map(c("dt_pmdb_xp", "dt_pmcpct", "dt_pmyear"), ~fwrite(get(.x), sprintf("%s%s.csv", DIR_DATAXP, .x)))
 
 stop("everything is DONE")
 

### 2024-10-16 texts/sup_materials.tex
include founder death/museum name interaction in sup materials

--- 2024-09-30 texts/sup_materials.tex
@@
-% Created 2024-09-30 ma 14:08
+% Created 2024-10-16 wo 12:28
 % Intended LaTeX compiler: pdflatex
@@
 
+\subsection*{Alternative founder death specification}
+
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Fri Sep 27 17:51:20 2024
+\begin{table}[ht]
+\centering
+\begin{tabular}{rD{)}{)}{8)3}D{)}{)}{8)3}}
+  \hline 
+ \multicolumn{1}{l}{Recent death length} & \multicolumn{1}{l}{Recently dead} & \multicolumn{1}{l}{Long dead}\\ 
+ \hline
+   1 & .97 \; (1.02) & .19 \; (0.46) \\ 
+    2 & 1.37 \; (0.61)^{*} & -.16 \; (0.55) \\ 
+    3 & 1.06 \; (0.61) & -.09 \; (0.55) \\ 
+    4 & .83 \; (0.61) & -.02 \; (0.55) \\ 
+    5 & .62 \; (0.61) & .07 \; (0.55) \\ 
+    6 & .50 \; (0.61) & .13 \; (0.55) \\ 
+    7 & .87 \; (0.49) & -.51 \; (0.75) \\ 
+    8 & .80 \; (0.49) & -.45 \; (0.75) \\ 
+    9 & .91 \; (0.46)^{*} & -1.11 \; (1.03) \\ 
+   10 & .83 \; (0.46) & -1.03 \; (1.03) \\ 
+   11 & .78 \; (0.46) & -.98 \; (1.03) \\ 
+   12 & .71 \; (0.46) & -.90 \; (1.03) \\ 
+   \hline
+\end{tabular}
+\caption{Cox PH regression results with different death configurations} 
+\label{tbl:t_reg_coxph_deathcfg}
+\end{table}
+
+It is possible to construct an alternative measure of founder death by partitioning the time after the death in a short-term and long-term period; the short-term period might then capture the disruption by the founder, whereas the long-term period would only be reached by museums who have successfully acquired alternative funding models and are hence relatively viable.
+However, the choice of choosing a cut-off point between the short- and long-term periods is relatively arbitrary.
+
+Table \ref{tbl:t_reg_coxph_deathcfg} shows coefficients of both periods with different cut-off points.
+While the coefficient in the short-term period is consistently higher than both the overall death coefficient and the long-term period coefficients, so far the evidence is inconclusive as only few cases are statistically significant\footnote{P-values are also not adjusted for multiple tests}.
+Furthermore, such a shock passes quickly relative to the predicted median lifetime of museums of 52 years, thus "giving" the founder death little time to lead to many museum closures. 
+Considering the raw numbers underlying the death effect estimates illustrates the uncertainty involved in determining the effect of the death of the founder on closing: 
+While 47 private museums have seen the death of their founders, only 3 of these have closed in the following 5 years; given such low numbers it cannot be ruled out that the statistical significance in a few configurations of founder death time results from random fluctuations rather than an underlying pattern.
+\subsection*{Interaction of Founder name in Museum name and founder death}
+
+% latex table generated in R 4.3.3 by xtable 1.8-4 package
+% Mon Sep 30 14:43:50 2024
+\begin{table}[ht]
+\centering
+\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
+  \hline 
+ \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_founder\_name\_death\_int}\\ 
+ \hline
+  \multicolumn{4}{l}{\textbf{Founder}} \\ 
+ & Gender - Female & -.04 \; (0.34) & -.02 \; (0.34) \\ 
+   & Gender - Couple & -.14 \; (0.32) & -.12 \; (0.32) \\ 
+   & Founder died & .28 \; (0.43) & .73 \; (0.75) \\ 
+   \multicolumn{4}{l}{\textbf{Museum}} \\ 
+ & Self-Identification - Foundation & .20 \; (0.41) & .21 \; (0.41) \\ 
+   & Self-Identification - Collection & -.45 \; (0.54) & -.47 \; (0.54) \\ 
+   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.08 \; (0.30)^{***} \\ 
+   & AN Ranking - Included & .19 \; (0.34) & .19 \; (0.34) \\ 
+   & AN Ranking - Dropped & .46 \; (0.50) & .48 \; (0.50) \\ 
+   & Founder name in Museum name & .05 \; (0.28) & .09 \; (0.29) \\ 
+   & Founder name in Museumm name * Founder died &  & -.62 \; (0.90) \\ 
+   \multicolumn{4}{l}{\textbf{Environment}} \\ 
+ & PM density (country) & .65 \; (0.34) & .64 \; (0.34) \\ 
+   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) \\ 
+   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} \\ 
+   & Nbr PM within 10km & .26 \; (0.08)^{***} & .27 \; (0.08)^{***} \\ 
+   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} \\ 
+   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.59 \; (1.01) \\ 
+   & Covid Pandemic (2020/21) & .42 \; (0.29) & .41 \; (0.29) \\ 
+   \hline
+ & Museums & 503 & 503 \\ 
+   & Museum-years & 6096 & 6096 \\ 
+   & Closures & 68 & 68 \\ 
+   & log. Likelihood & -339.68 & -339.46 \\ 
+   & AIC & 711.35 & 712.92 \\ 
+   & BIC & 746.87 & 750.65 \\ 
+   \hline 
+ \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
+\end{tabular}
+\caption{Cox PH regression models with additional specifications} 
+\label{tbl:t_reg_coxph_addgns}
+\end{table}
+
+While private museums generally do not experience a significantly higher risk of closing after the death of their founders, such effect might be present for a subgroup.
+The most likely candidate for this would be Museums whose name include the name of the founder, as including the founder name in the museum might indicate disproportionate commitment by the founder (which would be absent after their death) as well as disincentivize third parties to contribute.
+To investigate this possibility, an interaction between Founder death and inclusion of Founder name in museum name is added, results are presented in table \ref{tbl:t_reg_coxph_addgns}.
+As both the main effects and the interaction are not significant, the effect of the founder's death on a musuem's closing risk does not significantly differ between museums which do include their founder's name in their name and those who do not.
 \subsection*{Alternative competition specifications}
@@
 For models with country-dummies, country-level private museum density variables are removed as the high collinearity led to unreasonably high country-dummy estimates.
-As many countries and some UN subregions have too few private museums for the model to converge correctly, the dataset is reduced to include only regions or countries with 10 or more private museums (in the case of country2, 15 private museums).
+As many countries and some UN subregions have too few private museums for the model to converge correctly, the dataset is reduced to include only regions or countries with 10 or more private museums.
 To identify whether any change in coefficients is due to addition of variables or exclusion of cases, a separate model with the same restricted sample but without region/country dummies is included.
@@
 Figure \ref{fig:p_vrblcvrg_ratio} shows the variable coverage by whether a museum is open or closed at the status of data collection (2020-2022).
-Not only is coverage on most variables far from complete, which would already make it difficult to construct indicators of them, but variable coverage is substantially worse for closed museums than for open museums, especially variables related to the collection, operation, relations to other actors and social media.
+Not only is coverage on most variables far from complete, which would already make it difficult to construct indicators of them, but variable coverage is substantially worse for closed museums than for open museums, especially for variables related to the collection, operation, relations to other actors and social media.
 In principle it is possible to treat absence of evidence as evidence of absence, and assume that not measuring the presence of e.g.

### 2024-10-16 texts/paper_closing.tex
add keywords, organizational contributions

@@
-% Created 2024-10-08 di 12:23
+% Created 2024-10-16 wo 10:48
 % Intended LaTeX compiler: pdflatex
@@
 Finally, private museums face higher closing risks under certain environmental conditions, such as high competition from other private museums and, unexpectedly, the presence of large audiences.
+
+Beyond private museums, this study highlights how organizational dissolution can be investigated via their key decision makers.
+While a rich literature on non-profit survival exists, it focuses primarily organization-level variables; and previous studies that have investigated the relation between closing and key personnel variables have been limited by small samples \parencite{Searing_2020_zombies}, ad-hoc data collection \parencite{Chambre_Fatt_2002_liability} or sampling on the dependent variable \parencite{HernandezOrtiz_2022_discontinuity,Hager_etal_1996_grave}.
+It furthermore advances the measurement of key constructs in organizational research, in particular legitimacy via naming conventions and competition via geospatial methods and datasets.
 \subsection*{Private museums definition and dependency relations}
@@
 But there are so many organizations applying for the same grants" (ibid.).
-Quantitative studies have identified a relation between competition and non-profit closing primarily via measuring competition over density \parencite{Park_Shon_Lu_2021_mortality,Haugh_etal_2021_nascent,Lu_Shon_Zhang_2019_dissolution}, with higher number of non-profits increasing the chance of non-profit dissolution.
+Quantitative studies have identified a relation between competition and non-profit closing primarily via measuring competition via density \parencite{Park_Shon_Lu_2021_mortality,Haugh_etal_2021_nascent,Lu_Shon_Zhang_2019_dissolution}, with higher number of non-profits increasing the chance of non-profit dissolution.
 Thus, a hypothesis regarding competition can be formulated as:
